### 2017-12-21 vaught_2017.tex
Add Figs,Bib/Latex

\documentclass[twocolumn]{aastex6}
\usepackage{natbib}
\bibliographystyle{aasjournal}
\usepackage{graphicx}
\usepackage{amsmath}

\begin{document}
\title{A VLT/FORS2 Narrowband Imaging Search for MgII Emission Around z$\sim$0.7 Galaxies }
\author{Ryan Rickards Vaught \altaffilmark{1}, Kate Rubin \altaffilmark{1}, Fabrizio Arrigoni Battaia \altaffilmark{2}, Xavier Prochaska, Joseph Hennawi}

\altaffiltext{1}{San Diego State University 5500 Campanile Dr, San Diego, CA 92182}
 \altaffiltext{2}{Max-Planck-Institut fur Astronomie, Konigstuhl 17, D- 69117 Heidelberg, Germany}

\begin{abstract}
Galactic-scale outflows are thought to be the primary mechanism in the removal of cool gas in star-forming galaxies. Presently, the mass and energy of these flows remain poorly constrained. One way to better constrain these parameters is to measure the spatial extent of the outflow; however, measuring the spatial extent of such outflows via spectral methods has been traditionally very difficult due to the faintness of emission lines tracing outflowing material. We present VLT/FORS2 narrowband imaging of 5 star forming galaxies at redshift z=0.67-0.69 in the GOODS-S field as part of an effort to spatially resolve large-scale outflows traced by MgII emission. Previous spectra of this sample have already revealed winds traced by MgII absorption. At our sample redshift, the MgII emission lines fall exactly within the FORS2 HeII+47 and HeII/3000+48 interference filters. The total integration time of 10 hrs obtained in each filter permits the analysis of the flow surface brightness and extent on scales over which MgII is typically detected in absorption ( i.e, projected distances > 100 kpc). Such measurements can provide stronger constraints on the mass and energy of feedback, helping to advance our understanding of the processes regulating galaxy evolution up to z=1. 
\end{abstract}

\maketitle

\section{Introduction}
Galactic scale outflows are considered to be the main driver of galaxy evolution, as they provide a means to transport cool gas away from star forming regions out to the intergalactic medium. In other words, this removal of cool gas carries away the necessary fuel that is required for stellar formation. Even though outflows play a critical role in the star formation rates and mass of a the host galaxy\citep{Werk_2014}, the physical production mechanism that powers these outflows remains uncertain. Despite the uncertainty, some possible mechanics have been proposed by theoretical studies that include thermal pressure from core collapse supernova, radiation pressure from starbursts and finally cosmic ray pressure\citep{Sugahara_2017,Larson_1974,Chevalier_1985,Springel_2003}. An accurate picture of what types of galaxies host outflows comes from numerous spectroscopic studies(authors), as outflows are detected by measuring the blueshift of absorption transitions with respect to the host galaxy systematic velocities. Spectroscopy of galaxies from small to large redshifts and over a wide range of star formation sequence have revealed outflows in galaxies which host a large concentrations of massive stars (e.g., \cite{Rubin_2014} Martin 2012).

One common practice in detecting the presence of gas in distant galaxies has been to spectroscopically probe galactic halos along background quasar sight lines and down-the-barrel observations. With temperatures of the cool halo gas component on the order of $10^4\ K$, the gas can be traced by the absorption of metals such \ion{Mg}{2}, Fe and others \citep{Bordoloi_2011, Bergeron_1986}.  Nonetheless, this method is weak in constraining the overall radial profile, extent and morphology of the outflow. It follows from these weak constraints that estimates of mass and energy loss are left uncertain by at least two order of magnitude \citep{Rubin_2011}.

In a study by \cite{Rubin_2010a} strong \ion{Mg}{2} emission with a P-Cygni line profile was observed in the GOODS-N galaxy TKRS 4389. A proposed production mechanism for the observed \ion{Mg}{2} emission is photon scattering.

\section{Observations and Data Reduction}
Our sample consists of 5 GOODS-S galaxies. These galaxies were selected from a Keck/LRIS survey of UV absorption lines in 100 objects having redshifts $0.3< z , 1.4$ and $B_{AB}< 23$ in fields with deep HST/ACS imaging \cite{Rubin_2014}. The full sample is fortuitously distributed on the sky such that it can be imaged in a single FORS2 pointing.

The data were taken in service-mode using the FORS2 instrument on the VLT 8.2m telescope Antu between October 2012 and February 2013. We used two narrowband filters, HeII+47 and HeII/3000+48, that have peak transmission at wavelengths that correspond to the MgII doublet lines at our sample redshift of $z\approx 0.7$, (see Table \ref{tab:filters}). The FORS2 has a pixel scale of $0.25''$ pixel$^{-1}$ and a field of view of $7'\times7'$. Summing the individual exposure times for each image results in a combined exposure time of $10.0$ hours each for the HeII+47 and HeII/3000+48 filters. We carried out our observations under photometric and thin cloud conditions (program ID: 090.A-0427A).

\begin{figure}[!h]
\centering
\includegraphics[scale=.55]{sample_v2.png}
\caption{HST/ACS imaging of the each galaxy in our sample. From Top Left to Right Bottom: J033230.03, J033230.64, J033225.26, J033231.36, J033230.57.}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[scale=.55]{avg_seeing_HEII.pdf}
\includegraphics[scale=.55]{avg_seeing_HEII3000.pdf}
\caption{ The seeing conditions were calculated by ESO and were provided in the header of each science image. \textbf{(Top)} Distribution of seeing for the HeII+47 images. The median seeing is $1.03''$ \textbf{(Bottom)} : Same for the HEII/3000+48 images. The median seeing is $1.08''$ }
\end{figure}

The data were reduced using custom routines written in \textbf{Python}. The images were first corrected by subtracting and removing the overscan region of the CCD. Then the images were bias-subtracted and flat-fielded using twilight flats. Each individual image was cleaned of cosmic rays and bad pixels by utilizing the L.A Cosmic algorithm. The astrometry solutions were calculated via Astrometry.net \citep{Lang} with a standard deviation in the galaxy coordinates of $\sigma \approx 0.10''$.

Before image stacking, we ran each frame through \textbf{SExtractor} \citep{Bertin} in order to create a Root-Mean-Square map of each science image. These frames, in addition to the science images, are stacked to create a co-added RMS image.

The final stacked images for each filter is obtained using \textbf{SWarp} \citep{Bertin}. Each individual frame is first sky-subtracted using a background mesh size of 256 pixels which is approximately $64''$. We chose the mesh size to be large enough such that the extended emission is not mistakenly subtracted \citep{Battaia_2015}. The frame, after background-subtraction, is resampled onto a common astrometric solution using a \textit{Lancosz3} interpolation kernel. The images are median-combined in order to increase the signal to noise of any MgII emission. \textbf{SWarp} is also configured to produce RMS weight map from our \textbf{SExtractor} weighted images.

Once image stacking was done, we were left with two images to perform photometry on. One image contains only continuum photons, while the other one contains continuum + MgII photons.  (see Figure \ref{fig:stacked_image}). One side effect from stacking is that the east and west borders of each image contain greater noise compared to the center of the image. This is due to the imperfect overlap of the 3 pointings used. However, the sample galaxies are sufficiently distant from these low S/N regions that their photometry is not affected. As a final step, both images are aligned in physical coordinates via the IRAF \textbf{Imalign} command \citep{Tody_1986}.

\begin{table}[h!]
\caption{VLT/FORS2 Observations: Filter and exposure properties of the VLT observations. The width of the transmission curves are calculated by convolving the transmission curve with the total wavelength range of the filter. These values differ slightly from those reported by the European Space Observatory. }
\begin{tabular}{llllll} \hline \hline 
Filter & $\lambda_{eff}$(\AA)\footnote{$\lambda_{eff}$ is the effective wavelength of the filter transmission curve.} & $\lambda_{width}$(\text{\AA})    & $N_{images}$   & $t_{tot}(s)$ & $S$\footnote{S is in units of ergs counts$^{-1}$ cm$^{-2}$ }\smallskip \\ 
& & & & & $\times10^{-17}$ \\ \hline 
HeII  & 4675.21 & 50.11 & 38  & 35,959 & 2.45 \\
HeII/3000 & 4722.46  & 44.82 & 38 &   36,937 & 2.40       \\ \hline
\end{tabular}
\label{tab:filters}
\end{table}

\begin{table*}[t]
\centering
\caption{Properties of 5 galaxies in our sample :  These properties were taken from \cite{Rubin_2014}. All galaxies are at roughly the same redshift. The star formation rates for the sample range from 3.8 to 40.5 solar mass per year. The EW are for the blended components of the MgII doublet and were calculated with Eq. \ref{eq:specEW} and the supplemental Keck/LRIS spectra}
\begin{tabular}{lllllll} \hline \hline
Object & R.A. & Dec  & $z$ & SFR($M_{\odot} yr^{-1}$) & $\log{M_{*}/M_{\odot}}$ & EW(\AA) \smallskip      \\ \hline 
J033225.26-      & 03:32:25.26 & -27:45:23.9 & 0.6660 & $9.1_{-3.7}^{+1.3}$& $9.86_{-0.04}^{+0.05}$ & $7.00\pm 0.51$\\ 
274524.0     & &  &  &         \\
J033231.36-      & 03:32:31.35 & -27:47:24.9 &   0.6669 & $10.5_{-1.6}^{+1.7}$ & $10.02_{-0.03}^{+0.03}$&$6.50 \pm 0.51$\\
274725.0      & &  &   &        \\
J033230.03-      & 03:32:30.03 & -27:43:47.2  &   0.6679 & $3.8_{-0}^{+0}$ & $10.98_{-0.0}^{+0.01}$ &$6.44 \pm 0.51$\\
274347.3      & &  &   &        \\
J033229.64-      & 03:32:29.64 & -27:42:42.5 & 0.6671 & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &$6.70 \pm 0.51$\\
274242.6     & &  &     &      \\
J033230.57-      & 03:32:30.56 & -27:45:18.2 &   0.6807  & $12.6_{-2.1}^{+1.7}$ & $10.48_{-0.07}^{+0.03}$ &$5.60 \pm 0.52$ \\
274518.2      & &  &  &         \\ \hline 
\end{tabular}

\label{tab:prop}
\end{table*}

\subsection{Supplemental Keck/LRIS spectra}
In addition to VLT imaging, we utilize galaxy spectra taken from the \cite{Rubin_2014} Keck I Low Resolution Imaging Spectrometer (LRIS) program. A $0.9''$ slit width was used for all slitmasks and the median FWHM resolution for the spectra is 274 km s$^{-1}$ at $\lambda$ rest $\approx$ 2800 \AA and 286 km s$^{-1}$  at $\lambda$ rest $\approx$ 2600 \AA, see Figure (\ref{fig:spec_images}).

\subsection{Absolute Flux Calibration}
We acquired observations of the standard star GD50 from archival ESO calibration imaging. From this standard we calculated the atmospheric extinction coefficients to be 0.181 magnitudes for the HeII/3000+48 filter and 0.190 magnitudes for the HeII+47 filter. Since we have imaging of the standard star GD50 in our two filters, and access to GD50's spectral energy distribution and each filters transmission curve through the ESO website, we are able to perform absolute flux calibration using the methods of Jacoby et al. (1990). We first convolve the spectral energy distribution of the standard star, $F(\lambda)$ in ergs sec$^{-1}$ \AA$^{-1}$ cm$^{-2}$, with that of the known transmission curve of the filter, $T_{i}(\lambda)$. This yeilds, $F_i$, the total observable flux in each bandpass filter $i$ with units of ergs sec$^{-1}$ cm$^{-2}$.
\begin{equation*}
F_{i}=\int F(\lambda)T_{i}(\lambda)d\lambda
\end{equation*}
It is not uncommon to assume that $F(\lambda)$ is constant over the small width of the filter. However, our filter transmission curves are sampled at $5$\ \AA\ intervals which is the same sampling as the spectral energy distribution of the standard star obtained from the ESO archives. Therefore we calculate the integral numerically.
The system sensitivity, including the defects of the telescope optics and detector response is then given by
\begin{equation*}
S_{i}=\dfrac{F_{i}}{C10^{k_{i}A}},
\end{equation*}\\
where $k_i$ is the extinction in magnitudes per airmass, A is the airmass for each individual exposure, C is the measured count rate of the standard star and $S$ is in units of ergs counts$^{-1}$ cm$^{-2}$. Before image co-addition, each science image is corrected for atmospheric extinction by multiplying each frame by $10^{k_{i}A}$. Next, the image is divided by the exposure time, effectively putting the image in units of counts per sec. After co-addition, the images are then multiplied by the appropriate sensitivity factor $S_{i}$. This puts the final images in the appropriate flux units ergs sec $^{-1}$ cm$^{-2}$.

\begin{figure*}[ht!]
\centering
\includegraphics[scale=.61]{HEII_final.png}
\includegraphics[scale=.61]{HEII3000_final.png}
\caption{Top: HeII+47 image after stacking. Bottom: HeII3000+48 image after stacking. }
\label{fig:stacked_image}
\end{figure*}
\section{Analysis}

\subsection{Spectral Correction}
With the supplementary spectra from \cite{Rubin_2014}, we can fit the continuum and determine the slope of each galaxy spectrum in order to determine if the spectral slope gives rise to differences in continuum flux between the two filters. We use the interactive fitting routine \textbf{lt\_continuumfit} from the linetools package (Prochaska et al. 2016)\footnote{https://github.com/linetools/linetools} to fit the continuum. By fitting the continuum we are masking the absorption features and making an effectively flat spectrum, which we use as a model. We find the total flux in each filter by convolving the fitted continuum with each filter's transmission curve. Next, we take the ratio of both integrated totals, as the ratio will indicate the scaling factor needed to correct either of the filters. Comparing these ratios between each galaxy, we find that each ratio is effectively the same, within 1/1000 percent, with a value of 1.118. This value is equal to the ratio between the FWHM of the transmission curves, allowing us to conclude that the slope of the spectrum of each galaxy does not affect the continuum values collected in either filter.

\subsection{Continuum Subtraction}
To properly continuum-subtract the image taken with the emission filter in excess of the continuum, we follow a prescription given by \cite{Battaia_2015}. 
We first determine the continuum flux density from the off-\ion{Mg}{2} filter,
\begin{equation}
f_{cont}=\frac{F_{cont}}{\Delta \lambda_{cont}},
\end{equation}\\
where $F_{cont}$ and $\Delta \lambda_{cont}$ are the observed flux per pixel of the continuum image per pixel and the transmission FWHM of the continuum filter, respectively. With $f_{cont}$ it is then possible to calculate the flux of any excess emission, $F_{line}$:
\begin{equation}
F_{line}=F_{MgII}-f_{cont} \Delta \lambda_{MgII}
\label{eq:subtraction}
\end{equation}
where $F_{MgII}$ and $\Delta \lambda_{MgII}$ are the observed flux per pixel in the \ion{Mg}{2} filter and the transmission FWHM of the \ion{Mg}{2} filter. The continuum subtracted images of each galaxy are shown in Fig. \ref{fig:stamp_images}.

\subsection{Surface Brightness Profiles and Limits}

In order to test for the presence of \ion{Mg}{2} emission, we perform aperture photometry on the continuum subtracted images using the python library Photutils. We choose apertures with thickness of 2 pixels or $0.50 ''$, such that, $r_{inner}=r_{outer}-2$ (in pixels). Each aperture is centered on the flux-weighted centroid of the galaxy. We also consider an aperture with an inner radius of 24 pixels ($6''$) and outer radius of 30 pixels ($7.5''$) in order to increase our sensitivity to extended emission. Dividing the summed flux in each aperture by the area in arcsecs we produced surface brightness (SB) profiles for each galaxy.

The error bars are determined from a weight image produced by \textbf{SWarp}. The weight image is converted to an RMS image by taking the square root of the inverse weight. We then place apertures that are identical to the apertures used to find the SB profiles for each galaxy. To calculate the variance inside each aperture, we sum the RMS pixel values in quadrature, then divide by the area of each aperture.

To calculate the $3\sigma$ SB detection limit in each filter, we first masked out all the sources, their associated extended halos, and edge noise in both the HE+47 and HE/3000+48 images. We then calculated the root-mean-square of the background in randomly placed apertures with radii that matched the aperture radii used to measure the SB of the galaxies. The RMS values were then converted into SB in 1 square arcsec apertures. These values are calculated to be $5.120\times10^{-18}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ and $4.154\times10^{-18} $ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ in the HeII/3000 and HeII filters, respectively. We repeated the above procedure to obtain SB limits for the set of continuum-subtracted images: we calculated the root-mean-square of the flux inside the largest aperture. We determined the 3$\sigma$ SB limits to be $2.09\times10^{-18}$ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ and $1.87\times10^{-18}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ for the HeII - HeII/3000 combination and the HeII/3000 - HeII combination.

\subsection{Equivalent Widths}
Here we derive an expression to calculate the equivalent width (EW) of any absorption or emission features observed in our narrow-band imaging. Start from the expression for EW used in the context of spectroscopy,
\begin{equation}
EW=\int (1-\frac{f_{line}}{f_{cont}})d\lambda
\label{eq:specEW}
\end{equation}
We begin by dividing Eq \ref{eq:subtraction} by the flux density of the continuum and the FWHM of the on-line filter,
\begin{equation}
\frac{F_{line}}{f_{cont}\Delta \lambda_{MgII}}=\frac{F_{MgII}}{f_{cont}\Delta \lambda_{MgII}}- 1
\end{equation}
Next, we rearrange the above expression such that we produce the argument of the integrand in Eq. \ref{eq:specEW} on the RHS,
\begin{equation}
-\frac{F_{line}}{f_{cont}\Delta \lambda_{MgII}}=1-\frac{f_{MgII}}{f_{cont}}.
\end{equation}
We then approximate the integration in Eq. \ref{eq:specEW} by multiplying the integrand above by the FWHM of the on-line filter $d\lambda=\Delta \lambda_{MgII},$
\begin{equation}
-\frac{F_{line}}{f_{cont}}=(1-\frac{f_{MgII}}{f_{cont}})\Delta \lambda_{MgII};
\end{equation}
such that
\begin{equation}
EW=-\frac{F_{line}}{f_{cont}}.
\end{equation}

Using the above equation along with the continuum and continuum subtracted images, we produce images of the of equivalent widths. The EW are displayed inside a 1$\sigma$ SB contour of Continuum flux. Outside this contour, the EW become large due to the lack of S/N on the continuum, see Figure \ref{fig:ew_images}.

\section{Results}
In this section we present the results from the continuum-subtraction of the off-line continuum filter to that of the on-line emission filter.

\subsection{Limits on the MgII emission}
The surface brightness profiles presented in Fig. \ref{fig:sb_profiles} do not exhibit any signs of extended MgII emission. Previous constraints on the brightness of any possible emission are given by  \citep{Rubin_2011}. In this work the authors studied emission in a starburst galaxy at $z=0.69$ with a star formation rate of 80 $M_{\odot} yr^{-1}$. In a two-dimensional Keck/LRIS spectrum of this galaxy, they measured fluxes of $4.04 \pm 0.4$ to $8.0\pm 0.4$ $10^{-18}$ergs sec $^{-1}$ cm$^{-2}$  above and below the continuum region of the 2D spectra at $\lambda 2796$. Converting the 3$\sigma$ detection limit of our continuum-subtracted MgII image into flux units, we report the MgII emission 3$\sigma$ limits as 5.37 $10^{-18}$ergs sec $^{-1}$ cm$^{-2}$. Comparing our SB limit to previously reported values, it should be possible to detect the emission of this galaxy.

\subsection{MgII absorption in the line-profile}
Although we do not measure any extended MgII emission, we do observe a decrement of flux in the galaxy continua measured in the MgII filter in 3 galaxies out of the 5 galaxy sample. In the following section we discuss the absorption in each of these three galaxies, as well as our null detections.

We first discuss the case of a null detection of MgII absorption. The galaxy J033230.57 at a redshift of $z=0.6807$ is the most redshifted galaxy of the sample. This galaxy shows no significant flux decrement in the MgII filter. Examining Figure \ref{fig:case_images}, we can see that there should not be any absorption measured in J033230.57, as the absorption profile in the spectrum appears both in the HeII and HeII/3000 filter. This is a good test of our flux calibration, as it appears that there are no hints of systematic false absorption signatures.

We have a second case in which we detect quite strong absorption. The galaxy J033230.64 exhibits a maximum flux decrement of roughly $4\times10^{-18}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^{-1}$ due to \ion{Mg}{2} absorption. The absorption is exhibited predominantly within the $1\sigma$ SB outline of the continuum. The mean value of the EW in all the pixels within the $1\sigma$ SB outline of this galaxy is $7.88 \pm 0.403$ \AA, which is relatively close to the EW calculated from the spectra, $6.70 \pm 0.51$\ \AA. We expect that the small difference is due to the collecting area of the different methods. We calculate the EW inside a $1\sigma$ region around the core of the galaxy, whereas the spectrim is obtained in a $0.9''$ slit width. In addition, further inspecting of the distribution of the EW over the pixels, there appear to be two outlier values of $EW\approx 20$\ \AA that are influencing the mean value.

The next galaxy that shows an decrement of flux from MgII absorption is J033231.36. The MgII absorption spills outside the $1\sigma$ continuum flux contour, however a significant amount lies within our $1\sigma$ significant detection. The mean value of the EW of this galaxy is $6.91 \pm 0.560$ \AA, and is in good agreement with the EW calculated from the Keck/LRIS spectra, $6.50 \pm 0.51$ \AA. Again, inspection of the distribution of the EW over the pixels, reveal a possible outlier of an $EW\approx 20$\ \AA.

\begin{figure*}
\centering
\gridline{\fig{J033225_26.pdf}{0.5\textwidth}{(J033225.26)}
          \fig{J033230_03.pdf}{0.5\textwidth}{(J033230.03)}}
\gridline{\fig{J033230_64.pdf}{0.5\textwidth}{(J033230.64)}
          \fig{J033231_36.pdf}{0.5\textwidth}{(J033231.36)}}
\caption{Surface brightness profiles for galaxies that exhibit flux decrements from MgII absorption. Photometry was performed with circular apertures with increasing inner and outer radii. The error bars are determined from a SWarp RMS map .}
\label{fig:sb_profiles}
\end{figure*}

\begin{figure*}[!htb]
\centering
\includegraphics[scale=0.7]{stamps.pdf}
\caption{ $10'' \times 10''$ images stamps. Bottom: Continuum flux in ergs/s/cm$^2$/arcsec. Top: Continuum subtracted MgII flux, absorption can be seen in 3 of 5 galaxies. Each stamp is scaled with symmetric limits around 0.}
\label{fig:stamp_images}
\end{figure*}

\begin{figure*}[!htb]
\centering
\includegraphics[scale=0.58]{filt_57_spectra.pdf}
\includegraphics[scale=0.58]{filt_64_spectra.pdf}
\includegraphics[scale=0.58]{filt_03_spectra.pdf}
\includegraphics[scale=0.58]{filt_26_spectra.pdf}
\includegraphics[scale=0.58]{filt_36_spectra.pdf}
\caption{KECK/LRIS spectra plotted with the transmission curves of the filters HeII+47 and HeII/3000+48. The MgII doublet falls fortuitously the central wavelength of the HEII+47 filter. }
\label{fig:spec_images}
\end{figure*}

\begin{figure*}[ht!]
\centering
\includegraphics[scale=.58]{J03EW.pdf}
\includegraphics[scale=.58]{J64EW.pdf}
\includegraphics[scale=.58]{J26EW.pdf}
\includegraphics[scale=.58]{J57EW.pdf}
\includegraphics[scale=.58]{J36EW.pdf}
\caption{ Plots of the distribution of equivalent widths inside a $1\sigma$ continuum flux outline. }
\label{fig:ew_images}
\end{figure*}

\section{Analysis}
\section{Conclusion}
We presented the results of a narrowband imaging search for MgII emission in a sample of GOODS-S galaxies at a redshift of $z \approx 0.70$. Although we were unable to detect any measurable amount of MgII emission, We were able to detect a non-trivial amount of MgII absorption in 3 of our 5 galaxy sample. Our images, which are effective in creating absorption maps, were used to calculate the EW of absorption inside a $1\sigma$ continuum contour. 
\bibliography{references2017}

\end{document}

### 2017-12-26 Manuscript/vaught_2017.tex
Reorganized Files

--- 2017-12-21 vaught_2017.tex
@@
 Galactic-scale outflows are thought to be the primary mechanism in the removal of cool gas in star-forming galaxies. 
+%
 Presently, the mass and energy of these flows remain poorly constrained.
+%
 One way to better constrain these parameters is to measure the spatial extent of the outflow; however, measuring the spatial extent of such outflows via spectral methods has been traditionally very difficult due to the faintness of emission lines tracing outflowing material.
+%
 We present VLT/FORS2 narrowband imaging of 5 star forming galaxies at redshift z=0.67-0.69 in the GOODS-S field as part of an effort to spatially resolve large-scale outflows traced by MgII emission. 
+%
 Previous spectra of this sample have already revealed winds traced by MgII absorption. 
+%
 At our sample redshift, the MgII emission lines fall exactly within the FORS2 HeII+47 and HeII/3000+48 interference filters.
+%
 The total integration time of 10 hrs obtained in each filter permits the analysis of the flow surface brightness and extent on scales over which MgII is typically detected in absorption ( i.e, projected distances > 100 kpc).
+%
 Such measurements can provide stronger constraints on the mass and energy of feedback, helping to advance our understanding of the processes regulating galaxy evolution up to z=1. 
@@
 Galactic scale outflows are considered to be the main driver of galaxy evolution, as they provide a means to transport cool gas away from star forming regions out to the intergalactic medium. 
+%
+%
 In other words, this removal of cool gas carries away the necessary fuel that is required for stellar formation. 
+%
+%
 Even though outflows play a critical role in the star formation rates and mass of a the host galaxy\citep{Werk_2014}, the physical production mechanism that powers these outflows remains uncertain.
+%
+%
 Despite the uncertainty, some possible mechanics have been proposed by theoretical studies that include thermal pressure from core collapse supernova, radiation pressure from starbursts and finally cosmic ray pressure\citep{Sugahara_2017,Larson_1974,Chevalier_1985,Springel_2003}.
+%
+%
 An accurate picture of what types of galaxies host outflows comes from numerous spectroscopic studies(authors), as outflows are detected by measuring the blueshift of absorption transitions with respect to the host galaxy systematic velocities.
+%
+%
 Spectroscopy of galaxies from small to large redshifts and over a wide range of star formation sequence have revealed outflows in galaxies which host a large concentrations of massive stars (e.g., \cite{Rubin_2014} Martin 2012).
-
+%
+% New Paragraph
 One common practice in detecting the presence of gas in distant galaxies has been to spectroscopically probe galactic halos along background quasar sight lines and down-the-barrel observations.
+%
 With temperatures of the cool halo gas component on the order of $10^4\ K$, the gas can be traced by the absorption of metals such \ion{Mg}{2}, Fe and others \citep{Bordoloi_2011, Bergeron_1986}. 
+%
 Nonetheless, this method is weak in constraining the overall radial profile, extent and morphology of the outflow. 
+%
 It follows from these weak constraints that estimates of mass and energy loss are left uncertain by at least two order of magnitude \citep{Rubin_2011}.
@@
 These galaxies were selected from a Keck/LRIS survey of UV absorption lines in 100 objects having redshifts $0.3< z , 1.4$ and $B_{AB}< 23$ in fields with deep HST/ACS imaging \cite{Rubin_2014}.
+%
 The full sample is fortuitously distributed on the sky such that it can be imaged in a single FORS2 pointing.
-
+% New Paragraph
 The data were taken in service-mode using the FORS2 instrument on the VLT 8.2m telescope Antu between October 2012 and February 2013. 
+%
 We used two narrowband filters, HeII+47 and HeII/3000+48, that have peak transmission at wavelengths that correspond to the MgII doublet lines at our sample redshift of $z\approx 0.7$, (see Table \ref{tab:filters}).
+%
 The FORS2 has a pixel scale of $0.25''$ pixel$^{-1}$ and a field of view of $7'\times7'$.
+%
 Summing the individual exposure times for each image results in a combined exposure time of $10.0$ hours each for the HeII+47 and HeII/3000+48 filters.
+%
 We carried out our observations under photometric and thin cloud conditions (program ID: 090.A-0427A).
@@
 \centering
-\includegraphics[scale=.55]{sample_v2.png}
+\includegraphics[scale=.55]{/Users/ryan/Desktop/papers/rrvaught_2018/Figures/sample_v2.png}
 \caption{HST/ACS imaging of the each galaxy in our sample. From Top Left to Right Bottom: J033230.03, J033230.64, J033225.26, J033231.36, J033230.57.}
@@
 \centering
-\includegraphics[scale=.55]{avg_seeing_HEII.pdf}
-\includegraphics[scale=.55]{avg_seeing_HEII3000.pdf}
+\includegraphics[scale=.55]{/Users/ryan/Desktop/papers/rrvaught_2018/Figures/avg_seeing_HEII.pdf}
+\includegraphics[scale=.55]{/Users/ryan/Desktop/papers/rrvaught_2018/Figures/avg_seeing_HEII3000.pdf}
 \caption{ The seeing conditions were calculated by ESO and were provided in the header of each science image.
@@
 The data were reduced using custom routines written in \textbf{Python}. 
+%%
 The images were first corrected by subtracting and removing the overscan region of the CCD. 
+%%
 Then the images were bias-subtracted and flat-fielded using twilight flats. 
+%%
 Each individual image was cleaned of cosmic rays and bad pixels by utilizing the L.A Cosmic algorithm.
+%%
  The astrometry solutions were calculated via Astrometry.net \citep{Lang} with a standard deviation in the galaxy coordinates of $\sigma \approx 0.10''$. 
-
+%%
 Before image stacking, we ran each frame through \textbf{SExtractor} \citep{Bertin} in order to create a Root-Mean-Square map of each science image.
+%%
  These frames, in addition to the science images, are stacked to create a co-added RMS image.
-
+%% New Paragraph
 The final stacked images for each filter is obtained using \textbf{SWarp} \citep{Bertin}.
+%%
 Each individual frame is first sky-subtracted using a background mesh size of 256 pixels which is approximately $64''$. 
+%%
 We chose the mesh size to be large enough such that the extended emission is not mistakenly subtracted \citep{Battaia_2015}. 
+%%
 The frame, after background-subtraction, is resampled onto a common astrometric solution using a \textit{Lancosz3} interpolation kernel. 
-The images are median-combined in order to increase the signal to noise of any MgII emission.
-\textbf{SWarp} is also configured to produce RMS weight map from our \textbf{SExtractor} weighted images.
+%%
+The images are median-combined in order to increase the signal to noise of any MgII emission. \textbf{SWarp} is also configured to produce RMS weight map from our \textbf{SExtractor} weighted images.
 
@@
 \centering
-\includegraphics[scale=.61]{HEII_final.png}
-\includegraphics[scale=.61]{HEII3000_final.png}
+\includegraphics[scale=.61]{/Users/ryan/Desktop/papers/rrvaught_2018/Figures/HEII_final.png}
+\includegraphics[scale=.61]{/Users/ryan/Desktop/papers/rrvaught_2018/Figures/HEII3000_final.png}
 \caption{Top: HeII+47 image after stacking. Bottom: HeII3000+48 image after stacking. }
@@
 \centering
-\gridline{\fig{J033225_26.pdf}{0.5\textwidth}{(J033225.26)}
-          \fig{J033230_03.pdf}{0.5\textwidth}{(J033230.03)}}
-\gridline{\fig{J033230_64.pdf}{0.5\textwidth}{(J033230.64)}
-          \fig{J033231_36.pdf}{0.5\textwidth}{(J033231.36)}}
+\gridline{\fig{/Users/ryan/Desktop/papers/rrvaught_2018/Figures/J033225_26.pdf}{0.5\textwidth}{(J033225.26)}
+          \fig{/Users/ryan/Desktop/papers/rrvaught_2018/Figures/J033230_03.pdf}{0.5\textwidth}{(J033230.03)}}
+\gridline{\fig{/Users/ryan/Desktop/papers/rrvaught_2018/Figures/J033230_64.pdf}{0.5\textwidth}{(J033230.64)}
+          \fig{/Users/ryan/Desktop/papers/rrvaught_2018/Figures/J033231_36.pdf}{0.5\textwidth}{(J033231.36)}}
 \caption{Surface brightness profiles for galaxies that exhibit flux decrements from MgII absorption.
@@
 \centering
-\includegraphics[scale=0.7]{stamps.pdf}
+\includegraphics[scale=0.7]{/Users/ryan/Desktop/papers/rrvaught_2018/Figures/stamps.pdf}
 \caption{ $10'' \times 10''$ images stamps.
@@
 \centering
-\includegraphics[scale=0.58]{filt_57_spectra.pdf}
-\includegraphics[scale=0.58]{filt_64_spectra.pdf}
-\includegraphics[scale=0.58]{filt_03_spectra.pdf}
-\includegraphics[scale=0.58]{filt_26_spectra.pdf}
-\includegraphics[scale=0.58]{filt_36_spectra.pdf}
+\includegraphics[scale=0.58]{/Users/ryan/Desktop/papers/rrvaught_2018/Figures/filt_57_spectra.pdf}
+\includegraphics[scale=0.58]{/Users/ryan/Desktop/papers/rrvaught_2018/Figures/filt_64_spectra.pdf}
+\includegraphics[scale=0.58]{/Users/ryan/Desktop/papers/rrvaught_2018/Figures/filt_03_spectra.pdf}
+\includegraphics[scale=0.58]{/Users/ryan/Desktop/papers/rrvaught_2018/Figures/filt_26_spectra.pdf}
+\includegraphics[scale=0.58]{/Users/ryan/Desktop/papers/rrvaught_2018/Figures/filt_36_spectra.pdf}
 \caption{KECK/LRIS spectra plotted with the transmission curves of the filters HeII+47 and HeII/3000+48. The MgII doublet falls fortuitously the central wavelength of the HEII+47 filter. }
@@
 \centering
-\includegraphics[scale=.58]{J03EW.pdf}
-\includegraphics[scale=.58]{J64EW.pdf}
-\includegraphics[scale=.58]{J26EW.pdf}
-\includegraphics[scale=.58]{J57EW.pdf}
-\includegraphics[scale=.58]{J36EW.pdf}
+\includegraphics[scale=.58]{/Users/ryan/Desktop/papers/rrvaught_2018/Figures/J03EW.pdf}
+\includegraphics[scale=.58]{/Users/ryan/Desktop/papers/rrvaught_2018/Figures/J64EW.pdf}
+\includegraphics[scale=.58]{/Users/ryan/Desktop/papers/rrvaught_2018/Figures/J26EW.pdf}
+\includegraphics[scale=.58]{/Users/ryan/Desktop/papers/rrvaught_2018/Figures/J57EW.pdf}
+\includegraphics[scale=.58]{/Users/ryan/Desktop/papers/rrvaught_2018/Figures/J36EW.pdf}
 \caption{ Plots of the distribution of equivalent widths inside a $1\sigma$ continuum flux outline. }

### 2018-01-03 Manuscript/vaught_2017.tex
update tex file

--- 2017-12-21 vaught_2017.tex
@@
 \begin{document}
-\title{A VLT/FORS2 Narrowband Imaging Search for MgII Emission Around z$\sim$0.7 Galaxies }
-\author{Ryan Rickards Vaught \altaffilmark{1}, Kate Rubin \altaffilmark{1}, Fabrizio Arrigoni Battaia \altaffilmark{2}, Xavier Prochaska, Joseph Hennawi}
+\title{A VLT/FORS2 Narrowband Imaging Search for \ion{Mg}{2} Emission Around $\lowercase{z}\sim0.7$ Galaxies }
+\author{Ryan Rickards Vaught \altaffilmark{1}, Kate H. R. Rubin \altaffilmark{1}, Fabrizio Arrigoni Battaia \altaffilmark{2},  Joseph Hennawi, J. Xavier Prochaska}
 
@@
 Galactic-scale outflows are thought to be the primary mechanism in the removal of cool gas in star-forming galaxies. 
+%
 Presently, the mass and energy of these flows remain poorly constrained.
+%
 One way to better constrain these parameters is to measure the spatial extent of the outflow; however, measuring the spatial extent of such outflows via spectral methods has been traditionally very difficult due to the faintness of emission lines tracing outflowing material.
-We present VLT/FORS2 narrowband imaging of 5 star forming galaxies at redshift z=0.67-0.69 in the GOODS-S field as part of an effort to spatially resolve large-scale outflows traced by MgII emission.
-Previous spectra of this sample have already revealed winds traced by MgII absorption.
-At our sample redshift, the MgII emission lines fall exactly within the FORS2 HeII+47 and HeII/3000+48 interference filters.
-The total integration time of 10 hrs obtained in each filter permits the analysis of the flow surface brightness and extent on scales over which MgII is typically detected in absorption ( i.e, projected distances > 100 kpc).
-Such measurements can provide stronger constraints on the mass and energy of feedback, helping to advance our understanding of the processes regulating galaxy evolution up to z=1.
+%
+We present VLT/FORS2 narrowband imaging of 5 star forming galaxies at redshift $z=0.67-0.69$ in the GOODS-S field as part of an effort to spatially resolve large-scale outflows traced by \ion{Mg}{2} emission.
+%
+Previous spectra of this sample have already revealed winds traced by \ion{Mg}{2} absorption. 
+%
+At our sample redshift, the \ion{Mg}{2} emission lines fall exactly within the FORS2 HeII+47 and HeII/3000+48 interference filters.
+%
+The total integration time of 10 hrs obtained in each filter permits the analysis of the flow surface brightness and extent on scales over which \ion{Mg}{2} is typically detected in absorption (i.e., projected distances $> 100$ kpc).
+%
+Such measurements can provide stronger constraints on the mass and energy of feedback, helping to advance our understanding of the processes regulating galaxy evolution up to $z=1$. 
 \end{abstract}
@@
 \section{Introduction}
-Galactic scale outflows are considered to be the main driver of galaxy evolution, as they provide a means to transport cool gas away from star forming regions out to the intergalactic medium.
+Galactic scale outflows are considered to be a main driver of galaxy evolution, as they provide a means to transport cool gas away from star forming regions out to the intergalactic medium. 
+%
+%
 In other words, this removal of cool gas carries away the necessary fuel that is required for stellar formation. 
-Even though outflows play a critical role in the star formation rates and mass of a the host galaxy\citep{Werk_2014}, the physical production mechanism that powers these outflows remains uncertain.
-Despite the uncertainty, some possible mechanics have been proposed by theoretical studies that include thermal pressure from core collapse supernova, radiation pressure from starbursts and finally cosmic ray pressure\citep{Sugahara_2017,Larson_1974,Chevalier_1985,Springel_2003}.
+%
+%
+Even though outflows play a critical role in the star formation rates and mass of the host galaxy \citep{Werk_2014}, the physical production mechanism that powers these outflows remains uncertain.
+%
+%
+Despite the uncertainty, some possible mechanics have been proposed by theoretical studies that include thermal pressure from core collapse supernova, radiation pressure from starbursts and finally cosmic ray pressure \citep{Sugahara_2017,Larson_1974,Chevalier_1985,Springel_2003}.
+%
+%
 An accurate picture of what types of galaxies host outflows comes from numerous spectroscopic studies(authors), as outflows are detected by measuring the blueshift of absorption transitions with respect to the host galaxy systematic velocities.
-Spectroscopy of galaxies from small to large redshifts and over a wide range of star formation sequence have revealed outflows in galaxies which host a large concentrations of massive stars (e.g., \cite{Rubin_2014} Martin 2012).
+%
+%
+Spectroscopy of galaxies from low to high redshifts and over a wide range of star formation rates have revealed outflows in galaxies which host large concentrations of massive stars (e.g., \cite{Rubin_2014} Martin 2012).
+%
 
+% New Paragraph
 One common practice in detecting the presence of gas in distant galaxies has been to spectroscopically probe galactic halos along background quasar sight lines and down-the-barrel observations.
+%
 With temperatures of the cool halo gas component on the order of $10^4\ K$, the gas can be traced by the absorption of metals such \ion{Mg}{2}, Fe and others \citep{Bordoloi_2011, Bergeron_1986}. 
+%
 Nonetheless, this method is weak in constraining the overall radial profile, extent and morphology of the outflow. 
-It follows from these weak constraints that estimates of mass and energy loss are left uncertain by at least two order of magnitude \citep{Rubin_2011}.
+%
+It follows from these weak constraints that estimates of mass and energy loss are left uncertain by at least two order of magnitude \citep{Rubin_2014}.
 
-In a study by \cite{Rubin_2010a} strong \ion{Mg}{2} emission with a P-Cygni line profile was observed in the GOODS-N galaxy TKRS 4389.
+%%%% KHRR
+\begin{itemize}
+\item One novel way of developing these constraints is to trace the extent of winds in emission
+
+\item This has been done in the optical (in H$\alpha$, [\ion{O}{3}]) for nearby starbursts -- these transitions trace a warm, shock-heated phase
+
+\item In a study by \cite{Rubin_2011} strong \ion{Mg}{2} emission with a P-Cygni line profile was observed in the GOODS-N galaxy TKRS 4389.
 A proposed production mechanism for the observed \ion{Mg}{2} emission is photon scattering.
 
+\item This latter mechanism makes it possible to study winds in emission beyond the local universe
+
+\item Summary of experiment: in this paper, we present the first narrowband imaging of \ion{Mg}{2} line emission in a sample of five distant ($z\sim0.7$) star-forming galaxies.
+State the measurement we're making (SB limit, 2D absorption morphology).
+
+\item Roadmap of paper sections for the reader.
+
+\end{itemize}
+%%%% end KHRR
+
 \section{Observations and Data Reduction}
-Our sample consists of 5 GOODS-S galaxies.
-These galaxies were selected from a Keck/LRIS survey of UV absorption lines in 100 objects having redshifts $0.3< z , 1.4$ and $B_{AB}< 23$ in fields with deep HST/ACS imaging \cite{Rubin_2014}.
-The full sample is fortuitously distributed on the sky such that it can be imaged in a single FORS2 pointing.
 
+%%%% KHRR
+\subsection{Sample Selection}
+
+Our target galaxies were selected from a Keck/LRIS survey of UV absorption lines in $\approx 100$ objects having redshifts $0.3< z < 1.4$ and $B_{AB}< 23$ in fields with deep \emph{HST}/ACS imaging \citep{Rubin_2014}.
+In particular, this parent survey targeted galaxies in a total of nine Keck/LRIS pointings located in both of the GOODS fields \citep{Giavalisco2004} and the AEGIS survey field (the Extended Groth Strip; \cite{Davis2007}).
+In inspecting the redshift distribution of this sample,
+
+Figure~\ref{fig.hstims}
+%%%%
+
+%
+The  sample is fortuitously distributed on the sky such that it can be imaged in a single FORS2 pointing.
+
+\subsection{VLT/FORS2 Observations}
+% New Paragraph
 The data were taken in service-mode using the FORS2 instrument on the VLT 8.2m telescope Antu between October 2012 and February 2013. 
-We used two narrowband filters, HeII+47 and HeII/3000+48, that have peak transmission at wavelengths that correspond to the MgII doublet lines at our sample redshift of $z\approx 0.7$, (see Table \ref{tab:filters}).
+%
+We used two narrowband filters, HeII+47 and HeII/3000+48, that have peak transmission at wavelengths that correspond to the \ion{Mg}{2} doublet lines at our sample redshift of $z\approx 0.7$ (see Table \ref{tab:filters}).
+%
 The FORS2 has a pixel scale of $0.25''$ pixel$^{-1}$ and a field of view of $7'\times7'$.
+%
 Summing the individual exposure times for each image results in a combined exposure time of $10.0$ hours each for the HeII+47 and HeII/3000+48 filters.
+%
 We carried out our observations under photometric and thin cloud conditions (program ID: 090.A-0427A).
 
-\begin{figure}[!h]
+\begin{figure*}[!ht]
 \centering
-\includegraphics[scale=.55]{sample_v2.png}
-\caption{HST/ACS imaging of the each galaxy in our sample. From Top Left to Right Bottom: J033230.03, J033230.64, J033225.26, J033231.36, J033230.57.}
-\end{figure}
+\includegraphics[scale=.75,trim=50 100 100 350,clip=]{../Figures/fors2_color_imstamps.pdf}
+\caption{Color imaging of our sample galaxies in the \emph{HST}/ACS F435W, F606W, and F775W filters obtained as part of the GOODS survey \citep{Giavalisco2004}.
+%From Top Left to Right Bottom: J033230.03, J033230.64, J033225.26, J033231.36, J033230.57.
+Each image is $5\arcsec\times5\arcsec$.
+%%% Reminder to KHRR: made with ~/Research/MgII/paper_mgii/Paper2/Analysis/figpro/vaught2017_make_justcolorims.pro
+\label{fig.hstims}}
+\end{figure*}
 
@@
 \centering
-\includegraphics[scale=.55]{avg_seeing_HEII.pdf}
-\includegraphics[scale=.55]{avg_seeing_HEII3000.pdf}
-\caption{ The seeing conditions were calculated by ESO and were provided in the header of each science image.
-\textbf{(Top)} Distribution of seeing for the HeII+47 images.
-The median seeing is $1.03''$ \textbf{(Bottom)} : Same for the HEII/3000+48 images.
-The median seeing is $1.08''$ }
+\includegraphics[scale=.55]{../Figures/avg_seeing_HEII.pdf}
+\includegraphics[scale=.55]{../Figures/avg_seeing_HEII3000.pdf}
+\caption{  Distribution of seeing conditions for individual exposures comprising our dataset.
+\textbf{Top}: for the HeII+47 images. The median seeing is $1.03\arcsec$ 
+\textbf{Bottom}: Same for the HEII/3000+48 images. The median seeing is $1.08\arcsec$. 
+The seeing conditions were calculated by ESO and were provided in the header of each science image.}
 \end{figure}
@@
 The data were reduced using custom routines written in \textbf{Python}. 
+%%
 The images were first corrected by subtracting and removing the overscan region of the CCD. 
+%%
 Then the images were bias-subtracted and flat-fielded using twilight flats. 
+%%
 Each individual image was cleaned of cosmic rays and bad pixels by utilizing the L.A Cosmic algorithm.
+%%
  The astrometry solutions were calculated via Astrometry.net \citep{Lang} with a standard deviation in the galaxy coordinates of $\sigma \approx 0.10''$. 
-
+%%
 Before image stacking, we ran each frame through \textbf{SExtractor} \citep{Bertin} in order to create a Root-Mean-Square map of each science image.
+%%
  These frames, in addition to the science images, are stacked to create a co-added RMS image.
-
+%% New Paragraph
 The final stacked images for each filter is obtained using \textbf{SWarp} \citep{Bertin}.
+%%
 Each individual frame is first sky-subtracted using a background mesh size of 256 pixels which is approximately $64''$. 
+%%
 We chose the mesh size to be large enough such that the extended emission is not mistakenly subtracted \citep{Battaia_2015}. 
+%%
 The frame, after background-subtraction, is resampled onto a common astrometric solution using a \textit{Lancosz3} interpolation kernel. 
-The images are median-combined in order to increase the signal to noise of any MgII emission.
+%%
+The images are median-combined in order to increase the signal to noise of any \ion{Mg}{2} emission.
 \textbf{SWarp} is also configured to produce RMS weight map from our \textbf{SExtractor} weighted images.
@@
 Once image stacking was done, we were left with two images to perform photometry on.
-One image contains only continuum photons, while the other one contains continuum + MgII photons.
+One image contains only continuum photons, while the other one contains continuum + \ion{Mg}{2} photons.
 (see Figure \ref{fig:stacked_image}).
@@
 The star formation rates for the sample range from 3.8 to 40.5 solar mass per year.
-The EW are for the blended components of the MgII doublet and were calculated with Eq.
+The EW are for the blended components of the \ion{Mg}{2} doublet and were calculated with Eq.
 \ref{eq:specEW} and the supplemental Keck/LRIS spectra}
@@
 \centering
-\includegraphics[scale=.61]{HEII_final.png}
-\includegraphics[scale=.61]{HEII3000_final.png}
+\includegraphics[scale=.61]{../Figures/HEII_final.png}
+\includegraphics[scale=.61]{../Figures/HEII3000_final.png}
 \caption{Top: HeII+47 image after stacking. Bottom: HeII3000+48 image after stacking. }
@@
 
-\subsection{Limits on the MgII emission}
+\subsection{Limits on the \ion{Mg}{2} emission}
 The surface brightness profiles presented in Fig.
-\ref{fig:sb_profiles} do not exhibit any signs of extended MgII emission.
+\ref{fig:sb_profiles} do not exhibit any signs of extended \ion{Mg}{2} emission.
 Previous constraints on the brightness of any possible emission are given by  \citep{Rubin_2011}.
@@
 In a two-dimensional Keck/LRIS spectrum of this galaxy, they measured fluxes of $4.04 \pm 0.4$ to $8.0\pm 0.4$ $10^{-18}$ergs sec $^{-1}$ cm$^{-2}$  above and below the continuum region of the 2D spectra at $\lambda 2796$.
-Converting the 3$\sigma$ detection limit of our continuum-subtracted MgII image into flux units, we report the MgII emission 3$\sigma$ limits as 5.37 $10^{-18}$ergs sec $^{-1}$ cm$^{-2}$.
+Converting the 3$\sigma$ detection limit of our continuum-subtracted \ion{Mg}{2} image into flux units, we report the \ion{Mg}{2} emission 3$\sigma$ limits as 5.37 $10^{-18}$ergs sec $^{-1}$ cm$^{-2}$.
 Comparing our SB limit to previously reported values, it should be possible to detect the emission of this galaxy.
 
-\subsection{MgII absorption in the line-profile}
-Although we do not measure any extended MgII emission, we do observe a decrement of flux in the galaxy continua measured in the MgII filter in 3 galaxies out of the 5 galaxy sample.
+\subsection{\ion{Mg}{2} absorption in the line-profile}
+Although we do not measure any extended \ion{Mg}{2} emission, we do observe a decrement of flux in the galaxy continua measured in the \ion{Mg}{2} filter in 3 galaxies out of the 5 galaxy sample.
 In the following section we discuss the absorption in each of these three galaxies, as well as our null detections.
 
-We first discuss the case of a null detection of MgII absorption.
+We first discuss the case of a null detection of \ion{Mg}{2} absorption.
 The galaxy J033230.57 at a redshift of $z=0.6807$ is the most redshifted galaxy of the sample.
-This galaxy shows no significant flux decrement in the MgII filter.
+This galaxy shows no significant flux decrement in the \ion{Mg}{2} filter.
 Examining Figure \ref{fig:case_images}, we can see that there should not be any absorption measured in J033230.57, as the absorption profile in the spectrum appears both in the HeII and HeII/3000 filter.
@@
 
-The next galaxy that shows an decrement of flux from MgII absorption is J033231.36.
-The MgII absorption spills outside the $1\sigma$ continuum flux contour, however a significant amount lies within our $1\sigma$ significant detection.
+The next galaxy that shows an decrement of flux from \ion{Mg}{2} absorption is J033231.36.
+The \ion{Mg}{2} absorption spills outside the $1\sigma$ continuum flux contour, however a significant amount lies within our $1\sigma$ significant detection.
 The mean value of the EW of this galaxy is $6.91 \pm 0.560$ \AA, and is in good agreement with the EW calculated from the Keck/LRIS spectra, $6.50 \pm 0.51$ \AA.
@@
 \centering
-\gridline{\fig{J033225_26.pdf}{0.5\textwidth}{(J033225.26)}
-          \fig{J033230_03.pdf}{0.5\textwidth}{(J033230.03)}}
-\gridline{\fig{J033230_64.pdf}{0.5\textwidth}{(J033230.64)}
-          \fig{J033231_36.pdf}{0.5\textwidth}{(J033231.36)}}
-\caption{Surface brightness profiles for galaxies that exhibit flux decrements from MgII absorption.
+\gridline{\fig{../Figures/J033225_26.pdf}{0.5\textwidth}{(J033225.26)}
+          \fig{../Figures/J033230_03.pdf}{0.5\textwidth}{(J033230.03)}}
+\gridline{\fig{../Figures/J033230_64.pdf}{0.5\textwidth}{(J033230.64)}
+          \fig{../Figures/J033231_36.pdf}{0.5\textwidth}{(J033231.36)}}
+\caption{Surface brightness profiles for galaxies that exhibit flux decrements from \ion{Mg}{2} absorption.
 Photometry was performed with circular apertures with increasing inner and outer radii.
@@
 \centering
-\includegraphics[scale=0.7]{stamps.pdf}
+\includegraphics[scale=0.7]{../Figures/stamps.pdf}
 \caption{ $10'' \times 10''$ images stamps.
 Bottom: Continuum flux in ergs/s/cm$^2$/arcsec.
-Top: Continuum subtracted MgII flux, absorption can be seen in 3 of 5 galaxies.
+Top: Continuum subtracted \ion{Mg}{2} flux, absorption can be seen in 3 of 5 galaxies.
 Each stamp is scaled with symmetric limits around 0.}
@@
 \centering
-\includegraphics[scale=0.58]{filt_57_spectra.pdf}
-\includegraphics[scale=0.58]{filt_64_spectra.pdf}
-\includegraphics[scale=0.58]{filt_03_spectra.pdf}
-\includegraphics[scale=0.58]{filt_26_spectra.pdf}
-\includegraphics[scale=0.58]{filt_36_spectra.pdf}
-\caption{KECK/LRIS spectra plotted with the transmission curves of the filters HeII+47 and HeII/3000+48. The MgII doublet falls fortuitously the central wavelength of the HEII+47 filter. }
+\includegraphics[scale=0.58]{../Figures/filt_57_spectra.pdf}
+\includegraphics[scale=0.58]{../Figures/filt_64_spectra.pdf}
+\includegraphics[scale=0.58]{../Figures/filt_03_spectra.pdf}
+\includegraphics[scale=0.58]{../Figures/filt_26_spectra.pdf}
+\includegraphics[scale=0.58]{../Figures/filt_36_spectra.pdf}
+\caption{KECK/LRIS spectra plotted with the transmission curves of the filters HeII+47 and HeII/3000+48. The \ion{Mg}{2} doublet falls fortuitously the central wavelength of the HEII+47 filter. }
 \label{fig:spec_images}
@@
 \centering
-\includegraphics[scale=.58]{J03EW.pdf}
-\includegraphics[scale=.58]{J64EW.pdf}
-\includegraphics[scale=.58]{J26EW.pdf}
-\includegraphics[scale=.58]{J57EW.pdf}
-\includegraphics[scale=.58]{J36EW.pdf}
+\includegraphics[scale=.58]{../Figures/J03EW.pdf}
+\includegraphics[scale=.58]{../Figures/J64EW.pdf}
+\includegraphics[scale=.58]{../Figures/J26EW.pdf}
+\includegraphics[scale=.58]{../Figures/J57EW.pdf}
+\includegraphics[scale=.58]{../Figures/J36EW.pdf}
 \caption{ Plots of the distribution of equivalent widths inside a $1\sigma$ continuum flux outline. }
@@
 \section{Conclusion}
-We presented the results of a narrowband imaging search for MgII emission in a sample of GOODS-S galaxies at a redshift of $z \approx 0.70$.
-Although we were unable to detect any measurable amount of MgII emission, We were able to detect a non-trivial amount of MgII absorption in 3 of our 5 galaxy sample.
+We presented the results of a narrowband imaging search for \ion{Mg}{2} emission in a sample of GOODS-S galaxies at a redshift of $z \approx 0.70$.
+Although we were unable to detect any measurable amount of \ion{Mg}{2} emission, We were able to detect a non-trivial amount of \ion{Mg}{2} absorption in 3 of our 5 galaxy sample.
 Our images, which are effective in creating absorption maps, were used to calculate the EW of absorption inside a $1\sigma$ continuum contour.

### 2018-01-04 Manuscript/vaught_2017.tex
More edits to manuscript

@@
 \usepackage{amsmath}
+
+\def \lya {Ly$\alpha$ }
+\def \mkms {{\rm \; km\;s^{-1}}}
+\def \msunperyr {{\; M_{\odot}\rm \;yr^{-1}}}
 
@@
 In particular, this parent survey targeted galaxies in a total of nine Keck/LRIS pointings located in both of the GOODS fields \citep{Giavalisco2004} and the AEGIS survey field (the Extended Groth Strip; \cite{Davis2007}).
-In inspecting the redshift distribution of this sample,
+In inspecting the redshift distribution of the portion of this sample observable from the Southern Hemisphere, we uncovered a narrow peak of nine galaxies in the interval $0.66 < z < 0.68$.
+This peak is in fact the global maximum of the distribution, as all other bins of width $\Delta z = 0.02$ have at most four galaxies.
+Moreover, there are two narrow interference filters available on VLT/FORS2 centered at $\lambda \sim 468.4$ and 472.6 nm which cover the \ion{Mg}{2} $\lambda \lambda 2796, 2803$ transition in precisely this redshift interval.
+We selected our final sample of five of these galaxies at $0.66 < z < 0.68$ to be close on the sky such that they could be imaged in a single $7\arcmin \times 7\arcmin$ FORS2 pointing.
 
-Figure~\ref{fig.hstims}
+The absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2}  with velocities $\sim150-420\mkms$ and equivalent widths $\sim 2-3$ \AA.
+Modeling of the galaxy broad-band spectral energy distributions obtained from multiwavelength ancillary imaging data yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$.
+These properties, as well as precise target coordinates, are listed in Table~\ref{tab:prop}.
+\emph{HST}/ACS images of the galaxy sample are shown in
+Figure~\ref{fig.hstims}.  The Keck/LRIS spectroscopy of this sample published in \cite{Rubin_2014} is shown in Figure~\ref{fig:spec_images}.
+
 %%%%
@@
 %
-The  sample is fortuitously distributed on the sky such that it can be imaged in a single FORS2 pointing.
+%The  sample is fortuitously distributed on the sky such that it can be imaged in a single FORS2 pointing.
 
@@
 We used two narrowband filters, HeII+47 and HeII/3000+48, that have peak transmission at wavelengths that correspond to the \ion{Mg}{2} doublet lines at our sample redshift of $z\approx 0.7$ (see Table \ref{tab:filters}).
+%%%% KHRR
+[{\bf This is demonstrated nicely in Figure~\ref{fig:spec_images}, so I think we should explain it fully and refer to it here.}]
+%%%%
+
 %
@@
 %
-We carried out our observations under photometric and thin cloud conditions (program ID: 090.A-0427A).
+Our observations were carried out under photometric and thin cloud conditions (program ID: 090.A-0427A).
+%%%% KHRR
+[{\bf Explain seeing conditions here and refer to Figure~\ref{fig.seeing}.  You should also explain that the data were taken with three pointings offset by XXX arcmin somewhere in this subsection.}]
+%%%%
 
@@
 
+\begin{figure*}[!htb]
+\centering
+\includegraphics[scale=0.58]{../Figures/filt_57_spectra.pdf}
+\includegraphics[scale=0.58]{../Figures/filt_64_spectra.pdf}
+\includegraphics[scale=0.58]{../Figures/filt_03_spectra.pdf}
+\includegraphics[scale=0.58]{../Figures/filt_26_spectra.pdf}
+\includegraphics[scale=0.58]{../Figures/filt_36_spectra.pdf}
+\caption{KECK/LRIS spectra plotted with the transmission curves of the filters HeII+47 and HeII/3000+48. 
+%%%% KHRR
+[{\bf Explain the two different y axes, add units to the left-hand y axis, explain what the vertical dashed lines mean.}]
+%%%%
+The \ion{Mg}{2} doublet falls fortuitously at the central wavelength of the HEII+47 filter. }
+\label{fig:spec_images}
+\end{figure*}
+
 \begin{figure}[h]
@@
 \caption{  Distribution of seeing conditions for individual exposures comprising our dataset.
-\textbf{Top}: for the HeII+47 images. The median seeing is $1.03\arcsec$ 
-\textbf{Bottom}: Same for the HEII/3000+48 images. The median seeing is $1.08\arcsec$. 
-The seeing conditions were calculated by ESO and were provided in the header of each science image.}
+%%%% KHRR
+\textbf{Top}: Seeing distribution for the XXX HeII+47 images. The median seeing in this filter is $1.03\arcsec$.
+\textbf{Bottom}: Same distribution for the XXX HEII/3000+48 images. The median seeing is $1.08\arcsec$. 
+%%%%
+The seeing conditions were calculated by ESO and were provided in the header of each science image.
+\label{fig.seeing}}
 \end{figure}
 
+\subsection{Supplemental Keck/LRIS spectra}
+In addition to VLT imaging, in the present analysis we utilize galaxy spectra taken from the \cite{Rubin_2014} Keck I Low Resolution Imaging Spectrometer (LRIS) program.
+A $0.9''$ slit width was used for all slitmasks and the median FWHM resolution for the spectra is 274 km s$^{-1}$ at $\lambda_{\rm rest} \approx$ 2800 \AA\ and $286\mkms$  at $\lambda_{\rm rest}\approx$ 2600 \AA\ (see Figure \ref{fig:spec_images}).
+
+\subsection{Image Reduction}
 The data were reduced using custom routines written in \textbf{Python}. 
@@
 %%
-Each individual image was cleaned of cosmic rays and bad pixels by utilizing the L.A Cosmic algorithm.
+Each individual image was cleaned of cosmic rays and bad pixels by utilizing the L.A. Cosmic algorithm.
 %%
  The astrometry solutions were calculated via Astrometry.net \citep{Lang} with a standard deviation in the galaxy coordinates of $\sigma \approx 0.10''$.
+
 %%
-Before image stacking, we ran each frame through \textbf{SExtractor} \citep{Bertin} in order to create a Root-Mean-Square map of each science image.
+Before image stacking, we ran each frame through \textbf{SExtractor} \citep{Bertin} in order to create a root mean square (RMS) map of each science image.
 %%
@@
 %%
-The images are median-combined in order to increase the signal to noise of any \ion{Mg}{2} emission.
-\textbf{SWarp} is also configured to produce RMS weight map from our \textbf{SExtractor} weighted images.
+The images are median-combined in order to increase the signal-to-noise of any \ion{Mg}{2} emission.
+\textbf{SWarp} is also configured to produce RMS weight maps from our \textbf{SExtractor} weighted images.
 
-Once image stacking was done, we were left with two images to perform photometry on.
+%%%% KHRR
+Our final stacked images in each filter are shown in Figure~\ref{fig:stacked_image} with the target galaxies indicated.  
+%Once image stacking was done, we were left with two images to perform photometry on.
 One image contains only continuum photons, while the other one contains continuum + \ion{Mg}{2} photons.
 (see Figure \ref{fig:stacked_image}).
+%%%%
 One side effect from stacking is that the east and west borders of each image contain greater noise compared to the center of the image.
@@
 The EW are for the blended components of the \ion{Mg}{2} doublet and were calculated with Eq.
-\ref{eq:specEW} and the supplemental Keck/LRIS spectra}
+\ref{eq:specEW} and the supplemental Keck/LRIS spectra.
+%%%% KHRR
+{\bf I think you have updates to these EWs and their errors, correct?}
+%%%%
+}
 \begin{tabular}{lllllll} \hline \hline
@@
 
-\subsection{Supplemental Keck/LRIS spectra}
-In addition to VLT imaging, we utilize galaxy spectra taken from the \cite{Rubin_2014} Keck I Low Resolution Imaging Spectrometer (LRIS) program.
-A $0.9''$ slit width was used for all slitmasks and the median FWHM resolution for the spectra is 274 km s$^{-1}$ at $\lambda$ rest $\approx$ 2800 \AA and 286 km s$^{-1}$  at $\lambda$ rest $\approx$ 2600 \AA, see Figure (\ref{fig:spec_images}).
-
 \subsection{Absolute Flux Calibration}
-We acquired observations of the standard star GD50 from archival ESO calibration imaging.
+We acquired observations of the standard star GD50 from archival ESO calibration imaging
+%%%% KHRR
+at XXX independent epochs.
+%%%% 
 From this standard we calculated the atmospheric extinction coefficients to be 0.181 magnitudes for the HeII/3000+48 filter and 0.190 magnitudes for the HeII+47 filter.
-Since we have imaging of the standard star GD50 in our two filters, and access to GD50's spectral energy distribution and each filters transmission curve through the ESO website, we are able to perform absolute flux calibration using the methods of Jacoby et al.
+Since we have imaging of the standard star GD50 in our two filters, and access to GD50's spectral energy distribution (cite!) and each filter's transmission curve through the ESO website, we are able to perform absolute flux calibration using the methods of Jacoby et al.
 (1990).
 We first convolve the spectral energy distribution of the standard star, $F(\lambda)$ in ergs sec$^{-1}$ \AA$^{-1}$ cm$^{-2}$, with that of the known transmission curve of the filter, $T_{i}(\lambda)$.
-This yeilds, $F_i$, the total observable flux in each bandpass filter $i$ with units of ergs sec$^{-1}$ cm$^{-2}$.
+This yields $F_i$, the total observable flux in each bandpass filter $i$ with units of ergs sec$^{-1}$ cm$^{-2}$:
 \begin{equation*}
-F_{i}=\int F(\lambda)T_{i}(\lambda)d\lambda
+F_{i}=\int F(\lambda)T_{i}(\lambda)d\lambda.
 \end{equation*}
@@
 \includegraphics[scale=.61]{../Figures/HEII3000_final.png}
-\caption{Top: HeII+47 image after stacking. Bottom: HeII3000+48 image after stacking. }
+\caption{Top: HeII+47 image after stacking. Bottom: HeII3000+48 image after stacking. 
+%%%% KHRR
+[{\bf Add total exposure time of each image, specify the total field of view, that east is up and north is to the right, and that the sample galaxies are indicated with blue symbols.
+Also, what is the grayscale here?
+Are these in counts/sec or in flux units?}]
+%%%%
+}
 \label{fig:stacked_image}
 \end{figure*}
+
 \section{Analysis}
+
+%%%% KHRR
+ We have two goals for our study: (1) assess the surface brightness of line emission in the \ion{Mg}{2} transition in and around each target galaxy; and (2) spatially resolve the morphology of the strong \ion{Mg}{2} absorption observed against the galaxy continua.
+To reach the both of these goals, we must perform accurate subtraction of the continuum flux of each object from the filter covering the targeted line emission.
+For four of the five objects in our sample, the HeII+47 image includes both line and continuum emission, and 
+the HeII3000+48 image provides a high S/N measurement of the continuum only $\approx30$ \AA\ redward of the line emission in the rest-frame.
+We detail our method of continuum subtraction using these data in Section~\ref{subsec.cont_sub} below, and follow with a presentation of the resulting surface brightness profiles (Section~\ref{subsec.sb}) and EW images (Section~\ref{subsec.ew}).
+%%%%
 
@@
 Comparing these ratios between each galaxy, we find that each ratio is effectively the same, within 1/1000 percent, with a value of 1.118.
+%%%% KHRR
+[{\bf 1/1000 percent would be 0.00001 -- which seems unrealistically small.}]
+%%%%
 This value is equal to the ratio between the FWHM of the transmission curves, allowing us to conclude that the slope of the spectrum of each galaxy does not affect the continuum values collected in either filter.
 
-\subsection{Continuum Subtraction}
+\subsection{Continuum Subtraction}\label{subsec.cont_sub}
 To properly continuum-subtract the image taken with the emission filter in excess of the continuum, we follow a prescription given by \cite{Battaia_2015}. 
@@
 
-\subsection{Surface Brightness Profiles and Limits}
+\begin{figure*}[!htb]
+\centering
+\includegraphics[scale=0.7]{../Figures/stamps.pdf}
+\caption{ $10'' \times 10''$ images stamps.
+Top row: Continuum flux in ergs/s/cm$^2$/arcsec.
+Bottom row: Continuum subtracted \ion{Mg}{2} flux.
+Absorption can be seen in 3 of 5 galaxies.
+Each stamp is scaled with symmetric limits around 0.
+%%%% KHRR
+[{\bf Explain what the red contours are, and add color bar if possible.
+Also, label axes with ``arcsec''.
+Would be nice to add labels indicating the IDs of each galaxy.
+Also, I expect Joe will ask for a $\chi^2$ version of these postage stamps, as in Fabrizio's Fig.
+10.}]
+%%%%
+}
+\label{fig:stamp_images}
+\end{figure*}
 
-In order to test for the presence of \ion{Mg}{2} emission, we perform aperture photometry on the continuum subtracted images using the python library Photutils.
-We choose apertures with thickness of 2 pixels or $0.50 ''$, such that, $r_{inner}=r_{outer}-2$ (in pixels).
+\subsection{Surface Brightness Profiles and Limits}\label{subsec.sb}
+
+In order to test for the presence of \ion{Mg}{2} emission, we perform aperture photometry on the continuum subtracted images using the python library Photutils. We choose apertures
+%%%% KHRR
+[{\bf I think we may want to replace the word ``apertures'' with ``annuli'' throughout this paragraph and the next -- do you agree?}]
+%%%%
+ with thickness of 2 pixels or $0.50 ''$, such that, $r_{inner}=r_{outer}-2$ (in pixels).
 Each aperture is centered on the flux-weighted centroid of the galaxy.
@@
 The RMS values were then converted into SB in 1 square arcsec apertures.
+%%%% KHRR
+[{\bf Up to here in this paragraph, it seems like the word ``apertures'' should stay -- but do you mean annuli below?
+That is, are you calculating a SB limit for a doughnut-shaped annulus?
+(And if not, doesn't the absorption screw with the measurement a bit?)}]
+%%%%
 These values are calculated to be $5.120\times10^{-18}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ and $4.154\times10^{-18} $ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ in the HeII/3000 and HeII filters, respectively.
@@
 
-\subsection{Equivalent Widths}
+\subsection{Equivalent Widths}\label{subsec.ew}
 Here we derive an expression to calculate the equivalent width (EW) of any absorption or emission features observed in our narrow-band imaging.
-Start from the expression for EW used in the context of spectroscopy,
+Starting from the expression for EW used in the context of spectroscopy,
 \begin{equation}
@@
 \end{equation}
-We begin by dividing Eq \ref{eq:subtraction} by the flux density of the continuum and the FWHM of the on-line filter,
+we begin by dividing Eq \ref{eq:subtraction} by the flux density of the continuum and the FWHM of the on-line filter,
 \begin{equation}
-\frac{F_{line}}{f_{cont}\Delta \lambda_{MgII}}=\frac{F_{MgII}}{f_{cont}\Delta \lambda_{MgII}}- 1
+\frac{F_{line}}{f_{cont}\Delta \lambda_{MgII}}=\frac{F_{MgII}}{f_{cont}\Delta \lambda_{MgII}}- 1.
 \end{equation}
@@
 
-Using the above equation along with the continuum and continuum subtracted images, we produce images of the of equivalent widths.
-The EW are displayed inside a 1$\sigma$ SB contour of Continuum flux.
-Outside this contour, the EW become large due to the lack of S/N on the continuum, see Figure \ref{fig:ew_images}.
+Using the above equation along with the continuum and continuum subtracted images, we produce images of the EW. 
+%%%% KHRR
+These images are displayed in Figure~\ref{fig:ew_images} within the 1$\sigma$ SB contours of the corresponding continuum images.
+%%%%
+%The EW are displayed inside a 1$\sigma$ SB contour of continuum flux.
+ Outside this contour, the EWs become poorly constrained due to the lack of S/N in the continuum.  %, see Figure \ref{fig:ew_images}.
 
@@
 \ref{fig:sb_profiles} do not exhibit any signs of extended \ion{Mg}{2} emission.
-Previous constraints on the brightness of any possible emission are given by  \citep{Rubin_2011}.
+Previous constraints on the brightness of any possible emission are given by  \cite{Rubin_2011}.
 In this work the authors studied emission in a starburst galaxy at $z=0.69$ with a star formation rate of 80 $M_{\odot} yr^{-1}$.
@@
 Converting the 3$\sigma$ detection limit of our continuum-subtracted \ion{Mg}{2} image into flux units, we report the \ion{Mg}{2} emission 3$\sigma$ limits as 5.37 $10^{-18}$ergs sec $^{-1}$ cm$^{-2}$.
-Comparing our SB limit to previously reported values, it should be possible to detect the emission of this galaxy.
+%%%% KHRR
+[{\bf How do you convert to flux units here?  What size are you assuming?}]
+%%%%
+Comparing our SB limit to previously reported values, it should be possible to detect the emission of this particular starburst galaxy in our FORS2 imaging.
 
@@
 This galaxy shows no significant flux decrement in the \ion{Mg}{2} filter.
-Examining Figure \ref{fig:case_images}, we can see that there should not be any absorption measured in J033230.57, as the absorption profile in the spectrum appears both in the HeII and HeII/3000 filter.
+Examining Figure \ref{fig:spec_images}, we can see that there should not be any absorption measured in J033230.57, as the absorption profile in the spectrum appears both in the HeII and HeII/3000 filter.
 This is a good test of our flux calibration, as it appears that there are no hints of systematic false absorption signatures.
@@
 We expect that the small difference is due to the collecting area of the different methods.
-We calculate the EW inside a $1\sigma$ region around the core of the galaxy, whereas the spectrim is obtained in a $0.9''$ slit width.
-In addition, further inspecting of the distribution of the EW over the pixels, there appear to be two outlier values of $EW\approx 20$\ \AA that are influencing the mean value.
+We calculate the EW inside a $1\sigma$ region around the core of the galaxy
+%%%% KHRR
+[{\bf which is approximately how big in arcsec?}]
+%%%%
+, whereas the spectrum is obtained using a $0.9''$ slit width.
+In addition, further inspecting the distribution of the EW over the pixels, there are two outlier values of EW$\approx 20$ \AA\ that are influencing the mean value.
 
-The next galaxy that shows an decrement of flux from \ion{Mg}{2} absorption is J033231.36.
+The next galaxy that shows a decrement of flux from \ion{Mg}{2} absorption is J033231.36.
 The \ion{Mg}{2} absorption spills outside the $1\sigma$ continuum flux contour, however a significant amount lies within our $1\sigma$ significant detection.
 The mean value of the EW of this galaxy is $6.91 \pm 0.560$ \AA, and is in good agreement with the EW calculated from the Keck/LRIS spectra, $6.50 \pm 0.51$ \AA.
-Again, inspection of the distribution of the EW over the pixels, reveal a possible outlier of an $EW\approx 20$\ \AA.
+Again, inspection of the distribution of the EW over the pixels reveals a possible outlier of an EW$\approx 20$\ \AA.
 
@@
 Photometry was performed with circular apertures with increasing inner and outer radii.
-The error bars are determined from a SWarp RMS map .}
+The error bars are determined from a SWarp RMS map.
+%%%% KHRR
+[{\bf Explain what each color means.
+And it would be great if you could add your measurement for the extra-thick annulus here -- perhaps with a different symbol.
+Actually...
+didn't you show me a newer version of these figures recently?}]
+%%%%
+}
 \label{fig:sb_profiles}
@@
 
-\begin{figure*}[!htb]
-\centering
-\includegraphics[scale=0.7]{../Figures/stamps.pdf}
-\caption{ $10'' \times 10''$ images stamps.
-Bottom: Continuum flux in ergs/s/cm$^2$/arcsec.
-Top: Continuum subtracted \ion{Mg}{2} flux, absorption can be seen in 3 of 5 galaxies.
-Each stamp is scaled with symmetric limits around 0.}
-\label{fig:stamp_images}
-\end{figure*}
-
-\begin{figure*}[!htb]
-\centering
-\includegraphics[scale=0.58]{../Figures/filt_57_spectra.pdf}
-\includegraphics[scale=0.58]{../Figures/filt_64_spectra.pdf}
-\includegraphics[scale=0.58]{../Figures/filt_03_spectra.pdf}
-\includegraphics[scale=0.58]{../Figures/filt_26_spectra.pdf}
-\includegraphics[scale=0.58]{../Figures/filt_36_spectra.pdf}
-\caption{KECK/LRIS spectra plotted with the transmission curves of the filters HeII+47 and HeII/3000+48. The \ion{Mg}{2} doublet falls fortuitously the central wavelength of the HEII+47 filter. }
-\label{fig:spec_images}
-\end{figure*}
-
-\begin{figure*}[ht!]
+\begin{figure*}[h!]
 \centering
@@
 \includegraphics[scale=.58]{../Figures/J36EW.pdf}
-\caption{ Plots of the distribution of equivalent widths inside a $1\sigma$ continuum flux outline. }
+\caption{ Plots of the distribution of equivalent widths inside a $1\sigma$ continuum flux outline. 
+%%%% KHRR
+[{\bf Are these white contours the same as the red contours in Fig. 5?  If so, you should state this.}]
+%%%%
+}
 \label{fig:ew_images}
@@
 
-\section{Analysis}
+\section{Discussion}
+
+%%%% KHRR
+\begin{itemize}
+
+\item Plot of SFR or $M_*$ vs.\ \ion{Mg}{2} SB for this sample, plus \cite{Rubin_2011} and \cite{Martin_2013} galaxies?  (Might be able to include an SB from \cite{Erb_2012} as well.)
+
+\item Construct simple model to investigate effects of seeing / absorption signal on our sensitivity to extended emission?
+
+\item Can we comment on wind morphology / isotropy?  How does absorption EW compare with emission EW implied by our SB limit?
+
+\end{itemize}
+%%%%
+
 \section{Conclusion}

### 2018-05-29 Manuscript/vaught_2017.tex
updated paper May29th

@@
-\documentclass[twocolumn]{aastex6}
+\documentclass[twocolumn]{aastex61}
 \usepackage{natbib}
-\bibliographystyle{aasjournal}
+\bibliographystyle{apj}
 \usepackage{graphicx}
 \usepackage{amsmath}
+
+\newcommand{\citeth}[1]{(\citeauthor{#1}\ \citeyear{#1})}
+\newcommand{\citethnop}[1]{\citeauthor{#1}\ \citeyear{#1}}
+\newcommand{\citethnopp}[1]{\citeauthor{#1}\ (\citeyear{#1})}
 
@@
 \title{A VLT/FORS2 Narrowband Imaging Search for \ion{Mg}{2} Emission Around $\lowercase{z}\sim0.7$ Galaxies }
-\author{Ryan Rickards Vaught \altaffilmark{1}, Kate H. R. Rubin \altaffilmark{1}, Fabrizio Arrigoni Battaia \altaffilmark{2},  Joseph Hennawi, J. Xavier Prochaska}
+\author{Ryan Rickards Vaught}
+\affiliation{San Diego State University 5500 Campanile Dr, San Diego, CA 92182}
+\affiliation{Department of Physics, University of California, San Diego, CA}
 
-\altaffiltext{1}{San Diego State University 5500 Campanile Dr, San Diego, CA 92182}
- \altaffiltext{2}{Max-Planck-Institut fur Astronomie, Konigstuhl 17, D- 69117 Heidelberg, Germany}
+ \author{Kate H. R. Rubin }
+ \affiliation{San Diego State University 5500 Campanile Dr, San Diego, CA 92182}
+
+ \author{Fabrizio Arrigoni Battaia }
+ \affiliation{Max-Planck-Institut fur Astronomie, Konigstuhl 17, D- 69117 Heidelberg, Germany}
+
+ \author{J. Xavier Prochaska}
+ \affiliation{Astronomy \& Astrophysics, UC Santa Cruz, 1156 High St., Santa Cruz, CA 95064 USA}
+
+\author{Joseph Hennawi,}
+\affiliation{Department of Physics, Broida Hall, University of California, Santa Barbara, CA 93106-9530}
+
+\correspondingauthor{Ryan Rickards Vaught}
+\email{rjvaught@gmail.com}
 
 \begin{abstract}
-Galactic-scale outflows are thought to be the primary mechanism in the removal of cool gas in star-forming galaxies. 
-%
+
+Galactic-scale outflows are thought to be the primary mechanism in the removal of cool gas from star-forming galaxies.
 Presently, the mass and energy of these flows remain poorly constrained.
-%
-One way to better constrain these parameters is to measure the spatial extent of the outflow; however, measuring the spatial extent of such outflows via spectral methods has been traditionally very difficult due to the faintness of emission lines tracing outflowing material.
-%
-We present VLT/FORS2 narrowband imaging of 5 star forming galaxies at redshift $z=0.67-0.69$ in the GOODS-S field as part of an effort to spatially resolve large-scale outflows traced by \ion{Mg}{2} emission.
-%
-Previous spectra of this sample have already revealed winds traced by \ion{Mg}{2} absorption. 
-%
-At our sample redshift, the \ion{Mg}{2} emission lines fall exactly within the FORS2 HeII+47 and HeII/3000+48 interference filters.
-%
-The total integration time of 10 hrs obtained in each filter permits the analysis of the flow surface brightness and extent on scales over which \ion{Mg}{2} is typically detected in absorption (i.e., projected distances $> 100$ kpc).
-%
-Such measurements can provide stronger constraints on the mass and energy of feedback, helping to advance our understanding of the processes regulating galaxy evolution up to $z=1$. 
+One way to better constrain these parameters is to measure the spatial extent of the outflow; however, measuring this quantity via spectral methods has been traditionally very difficult due to the faintness of emission lines tracing outflowing material.
+We perform a VLT/FORS2 narrowband imaging of 5 star-forming galaxies at redshift $z=0.67-0.69$ in the GOODS-S field as part of an effort to spatially resolve and constrain the radial extent of large-scale outflows traced by \ion{Mg}{2} emission.
+These observations probe \ion{Mg}{2} to unmatched surface brightness limits of 5.74 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ (5$\sigma$).
+We do not detect any extended \ion{Mg}{2} emission in any of our galaxies, suggesting that the wind material does not extend beyond the galaxies' stellar component.
+Our observations also allow us to create the first ever spatially-resolved map of  \ion{Mg}{2} absorption, revealing approximately constant absorption strengths across the galaxy disks.
+
 \end{abstract}
 
-\maketitle
+\keywords{Galaxy Evolution, Galactic Winds}
 
-\section{Introduction}
-Galactic scale outflows are considered to be a main driver of galaxy evolution, as they provide a means to transport cool gas away from star forming regions out to the intergalactic medium. 
-%
-%
-In other words, this removal of cool gas carries away the necessary fuel that is required for stellar formation. 
-%
-%
-Even though outflows play a critical role in the star formation rates and mass of the host galaxy \citep{Werk_2014}, the physical production mechanism that powers these outflows remains uncertain.
-%
-%
-Despite the uncertainty, some possible mechanics have been proposed by theoretical studies that include thermal pressure from core collapse supernova, radiation pressure from starbursts and finally cosmic ray pressure \citep{Sugahara_2017,Larson_1974,Chevalier_1985,Springel_2003}.
-%
-%
-An accurate picture of what types of galaxies host outflows comes from numerous spectroscopic studies(authors), as outflows are detected by measuring the blueshift of absorption transitions with respect to the host galaxy systematic velocities.
-%
-%
-Spectroscopy of galaxies from low to high redshifts and over a wide range of star formation rates have revealed outflows in galaxies which host large concentrations of massive stars (e.g., \cite{Rubin_2014} Martin 2012).
-%
+\section{Introduction}\label{sec:intro}
+Galactic winds play a critical role in regulating the star formation rates and stellar masses of galaxies \citeth{Werk_2014}; however, the physical mechanism that powers these galactic winds remains uncertain.
+Some possible mechanics have been proposed by theoretical studies that include thermal pressure from core collapse supernova, radiation pressure from starbursts and finally cosmic ray pressure (\citethnop{Larson_1974}; \citethnop{Chevalier_1985}; \citethnop{Springel_2003}; \citethnop{Sugahara_2017}).
+However it is very difficult to distinguish between these mechanisms with current observational techniques.
+Additionally, the impact galactic winds have on their host galaxies (i.e, their mass and energy content) has remained difficult to constrain with observations.
 
-% New Paragraph
-One common practice in detecting the presence of gas in distant galaxies has been to spectroscopically probe galactic halos along background quasar sight lines and down-the-barrel observations.
-%
-With temperatures of the cool halo gas component on the order of $10^4\ K$, the gas can be traced by the absorption of metals such \ion{Mg}{2}, Fe and others \citep{Bordoloi_2011, Bergeron_1986}. 
-%
-Nonetheless, this method is weak in constraining the overall radial profile, extent and morphology of the outflow. 
-%
-It follows from these weak constraints that estimates of mass and energy loss are left uncertain by at least two order of magnitude \citep{Rubin_2014}.
+An accurate picture of what types of galaxies host outflows comes from numerous absorption line studies of galaxies (\citethnop{Veilleux2005}; \citethnop{Weiner2009}; \citethnop{Martin2012}; \citethnop{Rubin_2014}).
+Outflows are detected by measuring the blueshift (outflow) or redshift (inflow) of absorption transitions with respect to the host galaxy systematic velocities.
+Spectroscopy of galaxies from low to high redshifts probing cold gas which absorbs in \ion{Na}{1} and cool gas in \ion{Mg}{2} has revealed outflows in most galaxies that host active star-formation (e.g.
+\citethnop{Martin2012}; \citethnop{Rubin_2014}).
+Even though these probes can ascertain: the radial velocity, column density and covering fraction of the flow, this method is weak in constraining the overall radial extent and provides no information on the morphology of the outflow.
 
-%%%% KHRR
-\begin{itemize}
-\item One novel way of developing these constraints is to trace the extent of winds in emission
+One novel way of developing these constraints is to trace the extent of winds in emission.
+This has been demonstrated in the optical using rest frame near infrared transitions (i.e H$\alpha$ and \ion{O}{3} etc) as tracers for nearby starbursts (\citethnop{Matsubayashi2009}; \citethnop{Veilleux2009}; \citethnop{Tripp2011}) because these transitions can trace the warm shock heated phase of the gas.
+However, it is difficult to use these rest frame near infrared transitions to probe winds at higher redshift because the faint emission can be redshifted into the infrared where the sky background is bright.
+At higher redshifts, it is advantageous to trace winds in the optical with the rest frame ultraviolet ion, \ion{Mg}{2} (Weiner et al.
+2009; Kornei et al.
+2013)\nocite{Weiner2009, Kornei2013}
 
-\item This has been done in the optical (in H$\alpha$, [\ion{O}{3}]) for nearby starbursts -- these transitions trace a warm, shock-heated phase
+Typically, studies of winds using \ion{Mg}{2} have focused on its absorption kinematics.
+However, recently in a study by \cite{Rubin_2011}, strong \ion{Mg}{2} emission with a P-Cygni line profile was observed in the 2D spectrum of a strongly star-forming galaxy at redshift $z = 0.694$.
+This emission was the first detection of an outflow beyond the spatial extent of the galaxy continuum in the distant universe, with a minimum spatial extent  $>$ 7 kpc.
+One proposed production mechanism for the galaxy's observed \ion{Mg}{2} line profile is photon scattering.
 
-\item In a study by \cite{Rubin_2011} strong \ion{Mg}{2} emission with a P-Cygni line profile was observed in the GOODS-N galaxy TKRS 4389.
-A proposed production mechanism for the observed \ion{Mg}{2} emission is photon scattering.
+In this mechanism, \ion{Mg}{2} ions in the region of the wind closest to the observer will absorb continuum photons in the resonant transitions, $\lambda_{2796}$ and $\lambda_{2803}$.
+Once these transitions are excited, they may only decay back to the ground state and if the optical depth of the gas is high, then the gas will resonantly trap the absorbed photons.
+Because the photons are absorbed in the rest frame of the gas, the absorption will be blueshifted relative to the galaxy's systematic velocity.
+The \ion{Mg}{2} ions in the section of the wind farthest from the observer will absorb and scatter photons that are redshifted relative to the front portion of the wind.
+Because the photons are redshifted, the photons will be able to travel freely towards the observer through the wind to produce emission at and redward of the systematic velocity of the galaxy \citeth{Rubin_2011}.
+The photon scattering model, as explained, is described for the geometry of an isotropic wind \citeth{Prochaska_2011}.
+For anisotropic bi-conical winds, the emission induced from photon scattering will be highly suppressed.
+Since the first detection of \ion{Mg}{2} emission by \citeth{Rubin_2011}, further detections of extended \ion{Mg}{2} emission are by \cite{Erb2012} and \cite{Martin2013} have shown that emission is stronger for higher mass galaxies and that outflows can extend out to at least 18 kpc.
 
-\item This latter mechanism makes it possible to study winds in emission beyond the local universe
-
-\item Summary of experiment: in this paper, we present the first narrowband imaging of \ion{Mg}{2} line emission in a sample of five distant ($z\sim0.7$) star-forming galaxies.
-State the measurement we're making (SB limit, 2D absorption morphology).
-
-\item Roadmap of paper sections for the reader.
-
-\end{itemize}
-%%%% end KHRR
+We aim to take advantage of this photon scattering as we present the first narrowband imaging of \ion{Mg}{2} line emission of 5 star-forming ($z \sim 0.7$) galaxies located in the deep Great Observatories Origins Deep Survey south (GOODS-S) field.
+The value in using narrowband imaging is the ability to spatially resolve any absoroption and emission from a galaxy.
+We use two filters: a line filter and a continuum filter.
+The line filter covers the \ion{Mg}{2} doublet, while the continuum filter is off-set from line filter.
+The continuum filter will allow us to observe the continuum level of the galaxy near the \ion{Mg}{2} doublet.
+With the resulting images taken using the two filters, we can subtract the continuum image from the \ion{Mg}{2} image, effectively creating an image that contains only photons from \ion{Mg}{2}.
+Contrary to 1D spectra, the narrowband imaging has the ability to measure the surface brightness, optical depth and radial extent of a wind.
+This narrowband imaging will allow us to create the first ever spatially resolved map of \ion{Mg}{2} emission.
 
@@
 
-%%%% KHRR
 \subsection{Sample Selection}
-
-Our target galaxies were selected from a Keck/LRIS survey of UV absorption lines in $\approx 100$ objects having redshifts $0.3< z < 1.4$ and $B_{AB}< 23$ in fields with deep \emph{HST}/ACS imaging \citep{Rubin_2014}.
-In particular, this parent survey targeted galaxies in a total of nine Keck/LRIS pointings located in both of the GOODS fields \citep{Giavalisco2004} and the AEGIS survey field (the Extended Groth Strip; \cite{Davis2007}).
+Our target galaxies were selected from a Keck/LRIS survey of UV absorption lines in $\approx 100$ objects having redshifts $0.3< z < 1.4$ and $B_{AB}< 23$ in fields with deep \emph{HST}/ACS imaging (Rubin et al.
+2014)\nocite{Rubin_2014}.
+In particular, this parent survey targeted galaxies in a total of nine Keck/LRIS pointings located in both of the GOODS fields (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004})and the AEGIS survey field (the Extended Groth Strip; Davis et al.
+2007)\nocite{Davis2007}.
 In inspecting the redshift distribution of the portion of this sample observable from the Southern Hemisphere, we uncovered a narrow peak of nine galaxies in the interval $0.66 < z < 0.68$.
@@
 Moreover, there are two narrow interference filters available on VLT/FORS2 centered at $\lambda \sim 468.4$ and 472.6 nm which cover the \ion{Mg}{2} $\lambda \lambda 2796, 2803$ transition in precisely this redshift interval.
-We selected our final sample of five of these galaxies at $0.66 < z < 0.68$ to be close on the sky such that they could be imaged in a single $7\arcmin \times 7\arcmin$ FORS2 pointing.
+We selected our final sample of five of these galaxies at $0.66 < z < 0.68$ to be close on the sky such that they could be imaged in a single $7' \times 7' $ FORS2 pointing.
 
-The absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2}  with velocities $\sim150-420\mkms$ and equivalent widths $\sim 2-3$ \AA.
-Modeling of the galaxy broad-band spectral energy distributions obtained from multiwavelength ancillary imaging data yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$.
-These properties, as well as precise target coordinates, are listed in Table~\ref{tab:prop}.
-\emph{HST}/ACS images of the galaxy sample are shown in
-Figure~\ref{fig.hstims}.  The Keck/LRIS spectroscopy of this sample published in \cite{Rubin_2014} is shown in Figure~\ref{fig:spec_images}.
-
-%%%%
-
-%
-%The  sample is fortuitously distributed on the sky such that it can be imaged in a single FORS2 pointing.
+The absorption line modeling presented in (Rubin et al.
+2014)\nocite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2}  with velocities $\sim150-420\mkms$ and equivalent widths (EW) $\sim 2-3$ \AA.
+Modeling of the galaxy broad-band spectral energy distributions obtained from multi-wavelength ancillary imaging data yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$.
+The properties of the sample, as well as precise target coordinates, taken from \cite{Rubin_2014} are listed in Table \ref{tab:prop}.
 
 \subsection{VLT/FORS2 Observations}
-% New Paragraph
 The data were taken in service-mode using the FORS2 instrument on the VLT 8.2m telescope Antu between October 2012 and February 2013. 
-%
 We used two narrowband filters, HeII+47 and HeII/3000+48, that have peak transmission at wavelengths that correspond to the \ion{Mg}{2} doublet lines at our sample redshift of $z\approx 0.7$ (see Table \ref{tab:filters}).
-%%%% KHRR
-[{\bf This is demonstrated nicely in Figure~\ref{fig:spec_images}, so I think we should explain it fully and refer to it here.}]
-%%%%
+The transmission curves are plotted along with each galaxy's spectrum in Figure~\ref{fig:spec_images}.
 
-%
-The FORS2 has a pixel scale of $0.25''$ pixel$^{-1}$ and a field of view of $7'\times7'$.
-%
+FORS2 has a pixel scale of $0.25''$ pixel$^{-1}$ and a field of view of $7'\times7'$.
 Summing the individual exposure times for each image results in a combined exposure time of $10.0$ hours each for the HeII+47 and HeII/3000+48 filters.
-%
 Our observations were carried out under photometric and thin cloud conditions (program ID: 090.A-0427A).
-%%%% KHRR
-[{\bf Explain seeing conditions here and refer to Figure~\ref{fig.seeing}.  You should also explain that the data were taken with three pointings offset by XXX arcmin somewhere in this subsection.}]
-%%%%
+The seeing (see Figure \ref{fig.seeing}) ranged from 0.5 arcsec to 2.5 arcsec.
+The data were taken with three pointings offset by 0.25'.
 
@@
 \centering
-\includegraphics[scale=.75,trim=50 100 100 350,clip=]{../Figures/fors2_color_imstamps.pdf}
-\caption{Color imaging of our sample galaxies in the \emph{HST}/ACS F435W, F606W, and F775W filters obtained as part of the GOODS survey \citep{Giavalisco2004}.
-%From Top Left to Right Bottom: J033230.03, J033230.64, J033225.26, J033231.36, J033230.57.
-Each image is $5\arcsec\times5\arcsec$.
-%%% Reminder to KHRR: made with ~/Research/MgII/paper_mgii/Paper2/Analysis/figpro/vaught2017_make_justcolorims.pro
-\label{fig.hstims}}
+\includegraphics[scale=.73]{../Figures/fors2_color_imstamps.pdf}
+\caption{Color imaging of our sample galaxies in the \emph{HST}/ACS F435W, F606W, and F775W filters obtained as part of the GOODS survey (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004}).
+Each image is 5'' $\times$ 5''.\label{fig:hstims}}
 \end{figure*}
@@
 \includegraphics[scale=0.58]{../Figures/filt_36_spectra.pdf}
-\caption{KECK/LRIS spectra plotted with the transmission curves of the filters HeII+47 and HeII/3000+48. 
-%%%% KHRR
-[{\bf Explain the two different y axes, add units to the left-hand y axis, explain what the vertical dashed lines mean.}]
-%%%%
-The \ion{Mg}{2} doublet falls fortuitously at the central wavelength of the HEII+47 filter. }
+\caption{KECK/LRIS spectrum of the sample galaxies and the transmission curves of the filters HeII+47 and HeII/3000+48.
+The left-hand axis is in units of flux density and the right-hand axis is the percentage of light transmitted the filter at each wavelength.
+Vertical dotted lines indicate the wavelength of the redshifted \ion{Mg}{2}\ doublet.
+The \ion{Mg}{2}\ doublet falls fortuitously at the central wavelength of the HEII+47 filter.}
 \label{fig:spec_images}
@@
 \caption{  Distribution of seeing conditions for individual exposures comprising our dataset.
-%%%% KHRR
-\textbf{Top}: Seeing distribution for the XXX HeII+47 images. The median seeing in this filter is $1.03\arcsec$.
-\textbf{Bottom}: Same distribution for the XXX HEII/3000+48 images. The median seeing is $1.08\arcsec$. 
-%%%%
+\textbf{Top}: Seeing distribution for the 38 HeII+47 images. The median seeing in this filter is $1.03\arcsec$.
+\textbf{Bottom}: Same distribution for the 38 HEII/3000+48 images. The median seeing is $1.08\arcsec$. 
 The seeing conditions were calculated by ESO and were provided in the header of each science image.
@@
 The data were reduced using custom routines written in \textbf{Python}. 
-%%
 The images were first corrected by subtracting and removing the overscan region of the CCD. 
-%%
 Then the images were bias-subtracted and flat-fielded using twilight flats.
-%%
-Each individual image was cleaned of cosmic rays and bad pixels by utilizing the L.A. Cosmic algorithm.
-%%
- The astrometry solutions were calculated via Astrometry.net \citep{Lang} with a standard deviation in the galaxy coordinates of $\sigma \approx 0.10''$.
+To improve the flat-fielding essential for detecting faint extended emission across the fields,we further correct for the illumination patterns using night-sky flats.
+The night-sky flats were produced by combining the unregistered science frames with an average sigma-clipping algorithm after masking out all the objects, and any bad pixels.
+Each individual image was cleaned of cosmic rays and bad pixels by utilizing the L.A.
+Cosmic algorithm.
+The astrometry solutions were calculated via Astrometry.net (Lang et al.
+2010)\nocite{Lang} with a standard deviation in the galaxy coordinates of $\sigma \approx 0.10''$.
+Before image stacking, we ran each frame through \textbf{SExtractor} \citeth{Bertin} in order to create a root mean square (RMS) map of each science image.
+These frames, in addition to the science images, are stacked to create a co-added RMS image.
 
-%%
-Before image stacking, we ran each frame through \textbf{SExtractor} \citep{Bertin} in order to create a root mean square (RMS) map of each science image.
-%%
- These frames, in addition to the science images, are stacked to create a co-added RMS image.
-%% New Paragraph
-The final stacked images for each filter is obtained using \textbf{SWarp} \citep{Bertin}.
-%%
+The final stacked images for each filter is obtained using \textbf{SWarp} \citeth{Bertin}.
 Each individual frame is first sky-subtracted using a background mesh size of 256 pixels which is approximately $64''$. 
-%%
-We chose the mesh size to be large enough such that the extended emission is not mistakenly subtracted \citep{Battaia_2015}. 
-%%
+We chose the mesh size to be large enough such that the extended emission is not mistakenly subtracted (Arrigoni Battaia et al. 2015) \nocite{Battaia_2015}. 
 The frame, after background-subtraction, is resampled onto a common astrometric solution using a \textit{Lancosz3} interpolation kernel. 
-%%
-The images are median-combined in order to increase the signal-to-noise of any \ion{Mg}{2} emission.
+The images are average-combined and weighted by the night-flat image in order to increase the signal-to-noise of any \ion{Mg}{2} emission.
 \textbf{SWarp} is also configured to produce RMS weight maps from our \textbf{SExtractor} weighted images.
+Our final stacked images in each filter are shown in Figure~\ref{fig:stacked_image} with the target galaxies indicated.
 
-%%%% KHRR
-Our final stacked images in each filter are shown in Figure~\ref{fig:stacked_image} with the target galaxies indicated.  
-%Once image stacking was done, we were left with two images to perform photometry on.
-One image contains only continuum photons, while the other one contains continuum + \ion{Mg}{2} photons.
-(see Figure \ref{fig:stacked_image}).
-%%%%
 One side effect from stacking is that the east and west borders of each image contain greater noise compared to the center of the image.
@@
 However, the sample galaxies are sufficiently distant from these low S/N regions that their photometry is not affected.
-As a final step, both images are aligned in physical coordinates via the IRAF \textbf{Imalign} command \citep{Tody_1986}.
 
@@
 \begin{tabular}{llllll} \hline \hline 
-Filter & $\lambda_{eff}$(\AA)\footnote{$\lambda_{eff}$ is the effective wavelength of the filter transmission curve.} & $\lambda_{width}$(\text{\AA})    & $N_{images}$   & $t_{tot}(s)$ & $S$\footnote{S is in units of ergs counts$^{-1}$ cm$^{-2}$ }\smallskip \\
-& & & & & $\times10^{-17}$ \\ \hline 
+Filter & $\lambda_{eff}$(\AA)\footnote{$\lambda_{eff}$ is the effective wavelength of the filter transmission curve.} & $\lambda_{width}$(\text{\AA})    & $N_{\text{img}}$   & $t_{tot}(s)$ & $S$\footnote{S is in units of $10^{-17}$ ergs counts$^{-1}$ cm$^{-2}$ }\smallskip  \\ \hline
 HeII  & 4675.21 & 50.11 & 38  & 35,959 & 2.45 \\
@@
 \centering
-\caption{Properties of 5 galaxies in our sample :  These properties were taken from \cite{Rubin_2014}.
-All galaxies are at roughly the same redshift.
+\caption{Properties of 5 galaxies in our sample :  All galaxies are at roughly the same redshift.
 The star formation rates for the sample range from 3.8 to 40.5 solar mass per year.
-The EW are for the blended components of the \ion{Mg}{2} doublet and were calculated with Eq.
+The EW include both components of the \ion{Mg}{2} doublet and were calculated with Eq.
 \ref{eq:specEW} and the supplemental Keck/LRIS spectra.
-%%%% KHRR
-{\bf I think you have updates to these EWs and their errors, correct?}
-%%%%
-}
+\emph{HST}/ACS images of the galaxy sample are shown in Figure~\ref{fig:hstims}.
+The Keck/LRIS spectroscopy of this sample published in \cite{Rubin_2014} is shown in Figure~\ref{fig:spec_images}}
 \begin{tabular}{lllllll} \hline \hline
-Object & R.A. & Dec  & $z$ & SFR($M_{\odot} yr^{-1}$) & $\log{M_{*}/M_{\odot}}$ & EW(\AA) \smallskip      \\ \hline 
-J033225.26-      & 03:32:25.26 & -27:45:23.9 & 0.6660 & $9.1_{-3.7}^{+1.3}$& $9.86_{-0.04}^{+0.05}$ & $7.00\pm 0.51$\\ 
+Object & R.A. & Dec  & $z$ & SFR($M_{\odot}$ yr$^{-1}$) & $\log{M_{*}/M_{\odot}}$ & EW(\AA) \smallskip      \\ \hline 
+J033225.26-      & 03:32:25.26 & -27:45:23.9 & 0.6660 & $9.1_{-3.7}^{+1.3}$& $9.86_{-0.04}^{+0.05}$ & $7.539\pm 0.354$\\ 
 274524.0     & &  &  &         \\
-J033231.36-      & 03:32:31.35 & -27:47:24.9 &   0.6669 & $10.5_{-1.6}^{+1.7}$ & $10.02_{-0.03}^{+0.03}$&$6.50 \pm 0.51$\\
+J033231.36-      & 03:32:31.35 & -27:47:24.9 &   0.6669 & $10.5_{-1.6}^{+1.7}$ & $10.02_{-0.03}^{+0.03}$&$5.835 \pm 0.493$\\
 274725.0      & &  &   &        \\
-J033230.03-      & 03:32:30.03 & -27:43:47.2  &   0.6679 & $3.8_{-0}^{+0}$ & $10.98_{-0.0}^{+0.01}$ &$6.44 \pm 0.51$\\
+J033230.03-      & 03:32:30.03 & -27:43:47.2  &   0.6679 & $3.8_{-0}^{+0}$ & $10.98_{-0.0}^{+0.01}$ &$12.794 \pm 1.710$\\
 274347.3      & &  &   &        \\
-J033229.64-      & 03:32:29.64 & -27:42:42.5 & 0.6671 & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &$6.70 \pm 0.51$\\
+J033229.64-      & 03:32:29.64 & -27:42:42.5 & 0.6671 & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &$13.239 \pm 0.263$\\
 274242.6     & &  &     &      \\
-J033230.57-      & 03:32:30.56 & -27:45:18.2 &   0.6807  & $12.6_{-2.1}^{+1.7}$ & $10.48_{-0.07}^{+0.03}$ &$5.60 \pm 0.52$ \\
+J033230.57-      & 03:32:30.56 & -27:45:18.2 &   0.6807  & $12.6_{-2.1}^{+1.7}$ & $10.48_{-0.07}^{+0.03}$ &$6.106 \pm 0.370$ \\
 274518.2      & &  &  &         \\ \hline 
 \end{tabular}
-
 \label{tab:prop}
@@
 \subsection{Absolute Flux Calibration}
-We acquired observations of the standard star GD50 from archival ESO calibration imaging
-%%%% KHRR
-at XXX independent epochs.
-%%%% 
-From this standard we calculated the atmospheric extinction coefficients to be 0.181 magnitudes for the HeII/3000+48 filter and 0.190 magnitudes for the HeII+47 filter.
+We acquired observations of the standard star GD50 from archival ESO calibration imaging at 4 independent epochs.From this standard we calculated the atmospheric extinction coefficients to be 0.181 magnitudes for the HeII/3000+48 filter and 0.190 magnitudes for the HeII+47 filter.
 Since we have imaging of the standard star GD50 in our two filters, and access to GD50's spectral energy distribution (cite!) and each filter's transmission curve through the ESO website, we are able to perform absolute flux calibration using the methods of Jacoby et al.
@@
 \includegraphics[scale=.61]{../Figures/HEII3000_final.png}
-\caption{Top: HeII+47 image after stacking. Bottom: HeII3000+48 image after stacking. 
-%%%% KHRR
-[{\bf Add total exposure time of each image, specify the total field of view, that east is up and north is to the right, and that the sample galaxies are indicated with blue symbols.
-Also, what is the grayscale here?
-Are these in counts/sec or in flux units?}]
-%%%%
-}
-\label{fig:stacked_image}
+\caption{Top: HeII+47 image after stacking.
+Bottom: HeII3000+48 image after stacking.
+The exposure time of each image is $\approx 10$ hours.
+Each image has a FOV of $7' \times 7'$ which fortuitously contains the full sample of galaxies (indicated by the blue circles) in a single pointing.
+East is up and North is right.
+\label{fig:stacked_image}}
 \end{figure*}
@@
 \section{Analysis}
-
-%%%% KHRR
 We have two goals for our study: (1) assess the surface brightness of line emission in the \ion{Mg}{2} transition in and around each target galaxy; and (2) spatially resolve the morphology of the strong \ion{Mg}{2} absorption observed against the galaxy continua.
 To reach the both of these goals, we must perform accurate subtraction of the continuum flux of each object from the filter covering the targeted line emission.
-For four of the five objects in our sample, the HeII+47 image includes both line and continuum emission, and 
-the HeII3000+48 image provides a high S/N measurement of the continuum only $\approx30$ \AA\ redward of the line emission in the rest-frame.
-We detail our method of continuum subtraction using these data in Section~\ref{subsec.cont_sub} below, and follow with a presentation of the resulting surface brightness profiles (Section~\ref{subsec.sb}) and EW images (Section~\ref{subsec.ew}).
-%%%%
+For four of the five objects in our sample, the HeII+47 image includes both line and continuum emission, and the HeII3000+48 image provides a high S/N measurement of the continuum only $\approx30$ \AA\ redward of the line emission in the rest-frame.
+We detail our method of continuum subtraction using these data in Section~\ref{sec.cont_sub} below, and follow with a presentation of the resulting surface brightness profiles (Section~\ref{sec.sb}) and EW images (Section~\ref{subsec.ew}).
 
 \subsection{Spectral Correction}
-With the supplementary spectra from \cite{Rubin_2014}, we can fit the continuum and determine the slope of each galaxy spectrum in order to determine if the spectral slope gives rise to differences in continuum flux between the two filters.
+With the supplementary spectra from \citeth{Rubin_2014}, we can fit the continuum and determine the slope of each galaxy spectrum in order to test whether the spectral slope gives rise to differences in continuum flux between the two filters.
 We use the interactive fitting routine \textbf{lt\_continuumfit} from the linetools package (Prochaska et al.
-2016)\footnote{https://github.com/linetools/linetools} to fit the continuum.
+2016)\footnote{https://github.com/linetools/linetools}\nocite{Prochaska2016} to fit the continuum.
 By fitting the continuum we are masking the absorption features and making an effectively flat spectrum, which we use as a model.
 We find the total flux in each filter by convolving the fitted continuum with each filter's transmission curve.
-Next, we take the ratio of both integrated totals, as the ratio will indicate the scaling factor needed to correct either of the filters.
-Comparing these ratios between each galaxy, we find that each ratio is effectively the same, within 1/1000 percent, with a value of 1.118.
-%%%% KHRR
-[{\bf 1/1000 percent would be 0.00001 -- which seems unrealistically small.}]
-%%%%
-This value is equal to the ratio between the FWHM of the transmission curves, allowing us to conclude that the slope of the spectrum of each galaxy does not affect the continuum values collected in either filter.
+Next, we take the ratio of both integrated totals, as the ratio will indicate the scaling factor needed to correct our flux measurements prior to continuum subtraction.
+Comparing these ratios between each galaxy, we find that each ratio is effectively the same, within 3 decimal places, with a value of 1.118.
+This value is equal to the ratio between the FWHM of the transmission curves, allowing us to conclude that the slope of the spectrum of each galaxy is flat, and hence that the continuum level measured in the off-line filter provides an accurate measure of the continuum contribution to the on-line filter flux.
 
-\subsection{Continuum Subtraction}\label{subsec.cont_sub}
+\subsection{Continuum Subtraction}\label{sec.cont_sub}
 To properly continuum-subtract the image taken with the emission filter in excess of the continuum, we follow a prescription given by \cite{Battaia_2015}. 
@@
 \includegraphics[scale=0.7]{../Figures/stamps.pdf}
-\caption{ $10'' \times 10''$ images stamps.
-Top row: Continuum flux in ergs/s/cm$^2$/arcsec.
+\caption{ $10'' \times 10''$ images of each galaxy in our sample.
+Top row: Continuum flux in ergs/s/cm$^2$/sq.arcsec.
 Bottom row: Continuum subtracted \ion{Mg}{2} flux.
-Absorption can be seen in 3 of 5 galaxies.
-Each stamp is scaled with symmetric limits around 0.
-%%%% KHRR
-[{\bf Explain what the red contours are, and add color bar if possible.
-Also, label axes with ``arcsec''.
-Would be nice to add labels indicating the IDs of each galaxy.
-Also, I expect Joe will ask for a $\chi^2$ version of these postage stamps, as in Fabrizio's Fig.
-10.}]
-%%%%
-}
+Absorption can be seen in 4 of 5 galaxies.
+The red contours represent the outline of the 1$\sigma$ surface brightness limit of continuum flux in the HeII/3000+38 image, defined in Sec.
+\ref{sec.sb}.
+The colorbar shows the scaling used for the line emission images.}
 \label{fig:stamp_images}
@@
 
-\subsection{Surface Brightness Profiles and Limits}\label{subsec.sb}
+\subsection{Surface Brightness Profiles and Limits}\label{sec.sb}
 
-In order to test for the presence of \ion{Mg}{2} emission, we perform aperture photometry on the continuum subtracted images using the python library Photutils. We choose apertures
-%%%% KHRR
-[{\bf I think we may want to replace the word ``apertures'' with ``annuli'' throughout this paragraph and the next -- do you agree?}]
-%%%%
- with thickness of 2 pixels or $0.50 ''$, such that, $r_{inner}=r_{outer}-2$ (in pixels).
-Each aperture is centered on the flux-weighted centroid of the galaxy.
-We also consider an aperture with an inner radius of 24 pixels ($6''$) and outer radius of 30 pixels ($7.5''$) in order to increase our sensitivity to extended emission.
-Dividing the summed flux in each aperture by the area in arcsecs we produced surface brightness (SB) profiles for each galaxy.
+In order to test for the presence of \ion{Mg}{2} emission, we perform aperture photometry on the continuum subtracted images using the python library Photutils.
+We choose annuli with a radial thickness of 1 pixel or $0.25 ''$, such that, $r_{inner}=r_{outer}-1$ (in pixels).
+Each annulus is centered on the flux-weighted centroid of the galaxy.
+By dividing the summed flux in each annulus by the area in arcseconds we produced surface brightness (SB) profiles for each galaxy which are shown in Figure \ref{fig:sb_profiles}.
 
-The error bars are determined from a weight image produced by \textbf{SWarp}.
-The weight image is converted to an RMS image by taking the square root of the inverse weight.
-We then place apertures that are identical to the apertures used to find the SB profiles for each galaxy.
-To calculate the variance inside each aperture, we sum the RMS pixel values in quadrature, then divide by the area of each aperture.
+The error in this quantity is determined from an RMS image produced by \textbf{SWarp}.
+We place annuli that are identical to the annuli used to find the SB profiles for each galaxy.
+To calculate the variance inside each annulus, we sum the RMS pixel values in quadrature, then divide by the area of each annulus.
 
-To calculate the $3\sigma$ SB detection limit in each filter, we first masked out all the sources, their associated extended halos, and edge noise in both the HE+47 and HE/3000+48 images.
-We then calculated the root-mean-square of the background in randomly placed apertures with radii that matched the aperture radii used to measure the SB of the galaxies.
-The RMS values were then converted into SB in 1 square arcsec apertures.
-%%%% KHRR
-[{\bf Up to here in this paragraph, it seems like the word ``apertures'' should stay -- but do you mean annuli below?
-That is, are you calculating a SB limit for a doughnut-shaped annulus?
-(And if not, doesn't the absorption screw with the measurement a bit?)}]
-%%%%
-These values are calculated to be $5.120\times10^{-18}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ and $4.154\times10^{-18} $ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ in the HeII/3000 and HeII filters, respectively.
-We repeated the above procedure to obtain SB limits for the set of continuum-subtracted images: we calculated the root-mean-square of the flux inside the largest aperture.
-We determined the 3$\sigma$ SB limits to be $2.09\times10^{-18}$ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ and $1.87\times10^{-18}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ for the HeII - HeII/3000 combination and the HeII/3000 - HeII combination.
+To calculate the $1\sigma$ SB limit we follow the recipe found in \cite{Battaia_2015}.
+We first masked out all the sources, their associated extended halos, and edge noise in both the HEII+47 and HEII/3000+48 images.
+We then calculate the root-mean-square (rms) of the background in randomly placed 1" apertures.
+We convert these rms values to SB limits $per$ 1 sq.arcsec aperture.
+We find that the 1$\sigma$ detection limits per 1 arcsec$^2$ aperture (SB$_1$) are $6.332\times10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ and $5.808\times10^{-19} $ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ in the HeII/3000 and HeII filters, respectively.
+With the 1$\sigma$ detection limit, SB$_1$, determined for the continuum+\ion{Mg}{2} (HeII) image, we define an extended annulus to be used to detect any extended \ion{Mg}{2} emission.
+This extended annulus has an inner radius approximately the size of a unique SB$_1$ isophotal contour for each galaxy.
+The outer radius will be the inner radius extended by an arbitrary choice of 5 pixels.
+
+The sensitivity required to detect an extended source depends on its size because one can reach lower SB levels by spatially averaging over large apertures.
+In the ideal case of perfect sky subtraction and continuum subtraction, the 1$\sigma$ SB limit for an extended source is $SB_{1}/\sqrt{A_\text{src}}$, where $A_\text{src}$ is the area in arcsec$^2$ and $SB_{1}$ is the surface brightness limit per 1 arcsec$^2$ aperture.
+In practice, the actual detection limits are limited by systematics from imperfect subtraction.
+Therefore, we empirically determine the limits as follows.
+We mask all the artifacts and sources in the continuum-subtracted images.
+Next generate randomly sized annuli, place them at random and extract the fluxes, $F_{\text{src}}$, within these annuli.
+In the ideal case that the sky and continuum are perfectly subtracted, the fluxes, $F_{\text{src}}$, from many random annuli should follow a Gaussian distribution with a width of $\sigma_{\text{src}} \equiv SB_{1}\sqrt{A_\text{src}}$.
+We find that the actual Gaussian width, $\sigma'_{\text{src}}$ of the distribution is broader than $\sigma_{\text{src}}$.
+We adopt $F_{\text{limit}} \equiv \sigma'_{\text{src}}$  as the $1 \sigma$ upper limit on the total line flux of extended \ion{Mg}{2} emission.
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[scale=0.6]{../Figures/hist_sblim.pdf}
+\caption{Normalized distribution of $F_{\text{src}}/\sigma_{\text{src}}$ values, for random circular annuli.
+$F_{\text{src}}$ is the total flux within the largest annulus and $\sigma_{\text{src}}$ is the expected $1\sigma$ flux limit in the ideal case of perfect sky and continuum subtraction, i.e $SB_{1}\sqrt{A_\text{src}}$.}
+\label{fig:limits}
+\end{figure}
+
+\begin{table}[h]
+\centering
+%\begin{minipage}{4in}
+\caption{Significance of Extracted Flux \label{tab:sb_lims}}  
+\begin{tabular}{llll} \hline \hline
+Object & F(\ion{Mg}{2})\footnote{\ion{Mg}{2} flux is in $10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$.
+The value in the parenthesis is the statistical significance with respect to $\sigma_{\text{src}}$ } & Area\footnote{Area of the extended annulus in sq.arcsec} \\  \hline
+J033225.26-274524.0 &  2.44(0.92)	& 21 \\
+J033232.36-274725.0 &  -1.40(-0.53) & 21 \\
+J033230.03-274347.3 &  -5.23(-1.75) & 27 \\
+J033229.64-274242.5 &  1.23 (0.44) & 26 \\
+J033230.57-274518.2 &  -2.53 (-1.00) & 18 \\ \hline
+\end{tabular}
+%\end{minipage}
+\end{table}
+
+In order to show that our detection limits are reasonable, we create simulated emission with varying intensities to see if we can visually detect any \ion{Mg}{2} emission.
+The results of this exercise are shown in Figure \ref{fig:sigmas} For each galaxy, we assume a constant surface brightness corresponding to an excess of surface brightness 0, 1, 3, 5, 10 and 20 times the $1\sigma$ SB$_{\text{limit}}$ inside the largest annulus used.
+Additionally, we assume gaussian noise with a variance equal to 1SB$_{\text{limit}}$.
+After placing the simulated emission around the galaxy, we subtract the continuum in the same manner as explained in Section \ref{sec.cont_sub}.
+To test the detectability of measuring extended emission we construct a smoothed $\chi$ image following the technique in \cite{Hennawi2013} and \cite{Battaia_2015}.
+First, we smooth the continuum-subtracted image:
+
+\begin{equation}
+I_{\text{smth}}= \text{CONVOLVE[NB-CONTINUUM]},
+\end{equation}
+where the CONVOLVE operation indicates convolution of the images with a Gaussian kernel with FWHM=1.5 pixels.
+Next, we computed the sigma image ($\sigma_{\text{smth}}$) for the smoothed image ($I_{\text{smth}}$) by propagating the noise image of the unsmoothed data:
+\begin{equation}
+\sigma_{\text{smth}}=\sqrt{\text{CONVOLVE}^2[\sigma^2_{\text{unsmth}}]},
+\end{equation}
+where the CONVOLVE$^2$ operation indicates the convolution of the noise image with the square of the Gaussian kernel. The smoothed $\chi$ image is defined by
+\begin{equation}
+\chi_{\text{smth}}=\frac{I_{\text{smth}}}{\sigma_{\text{smth}}}.
+\end{equation}
+This $\chi_{\text{smth}}$ image aids in recognizing the presence of extended \ion{Mg}{2} emission.
+
+Figure \ref{fig:sigmas} shows the $\chi_{\text{smth}}$ image for the synthetic \ion{Mg}{2} emission.
+Galaxies are outlined by a black isophotal contour corresponding to 1SB$_1$ and the simulated emission is contained inside an annulus surrounding the contours.
+The  $\chi_{\text{smth}}$  images confirm that we should be able to detect extended \ion{Mg}{2} emission down to a conservative level of 5SB$_{\text{limit}}$.
+Note again that the SB$_{\text{limit}}$ does indeed take into account the systematics from imperfect continuum subtraction.
+
+\begin{table}[]
+\centering
+%\begin{minipage}{4.5in}
+\caption{Empirically Determined Detection Limits \label{tab:det_lims}}  
+\begin{tabular}{llll} \hline \hline
+Object & 5SB$_{\text{limit}}$\footnote{Limits are in $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$} &Area\footnote{Area of the extended annulus in sq.arcsec} \\  \hline
+J033225.26-274524.0 &  6.51 & 21 \\
+J033232.36-274725.0 & 6.51 & 21 \\
+J033230.03-274347.3 & 5.74 & 27 \\
+J033229.64-274242.5 & 6.22  & 26 \\
+J033230.57-274518.2 & 6.81 & 18 \\ \hline
+\end{tabular}
+%\end{minipage}
+\end{table}
+
+\begin{figure*}[p]
+\centering
+\includegraphics[scale=1.2]{../Figures/sigmas.pdf}
+\caption{Postage stamp $\chi_{\text{smth}}$ images of the 5 galaxies in our sample.
+Every galaxy is placed in the same row in each column.
+The columns show simulated emission, with levels of 0, 1, 3, 5, 10, and 20 times SB$_{lim}$.
+Each postage stamp has a size of $5'' \times 5''$ (corresponding to $35$ kpc $\times$ $35$ kpc at $z\sim 0.70$).
+Each stamp shows the galaxy along with the same isophotal contour used in previous figures.
+Comparing the $0$SB$_{\text{limit}}$ column with the continuum-subtracted images in Figure \ref{fig:stamp_images} suggests that we did not detect any \ion{Mg}{2}\ emission.}
+\label{fig:sigmas}
+\end{figure*}
 
@@
 
-Using the above equation along with the continuum and continuum subtracted images, we produce images of the EW. 
-%%%% KHRR
-These images are displayed in Figure~\ref{fig:ew_images} within the 1$\sigma$ SB contours of the corresponding continuum images.
-%%%%
-%The EW are displayed inside a 1$\sigma$ SB contour of continuum flux.
- Outside this contour, the EWs become poorly constrained due to the lack of S/N in the continuum.  %, see Figure \ref{fig:ew_images}.
+Using the above equation along with the continuum and continuum-subtracted images, we produce images of the EWs.
+The EW images are displayed in Figures \ref{fig:ew11}, \ref{fig:ew22}, \ref{fig:ew33}, \ref{fig:ew44}, \ref{fig:ew55}, and show only the EWs within the 1$\sigma$ SB$_1$ contours of the corresponding \ion{Mg}{2} images (prior to continuum subtraction).
 
-\section{Results}
-In this section we present the results from the continuum-subtraction of the off-line continuum filter to that of the on-line emission filter.
+To compare our map of EWs to the values measured from the Keck/LRIS spectra, we place 0.9 arcsec wide apertures on top of each galaxy.
+The width and angle of the apertures replicate the orientation of the slits used to obtain the spectra.
+Next, we determine which pixels lie outside the 1$\sigma$ SB$_1$ contours and set those to zero.
+Outside this contour, the EWs become poorly constrained due to the lack of S/N in the continuum.
+We then apply a S/N $= 1.5$ cut to the continuum image and create a histogram to show the distribution of EWs as shown in Figures \ref{fig:ew1} through \ref{fig:ew5}.
+Having removed EWs with low-S/N continuum values from our images, we compute the mean equivalent width inside the Keck/LRIS apertures.
+These values are summarized in Table \ref{tab:abs_props}.
 
-\subsection{Limits on the \ion{Mg}{2} emission}
-The surface brightness profiles presented in Fig.
-\ref{fig:sb_profiles} do not exhibit any signs of extended \ion{Mg}{2} emission.
-Previous constraints on the brightness of any possible emission are given by  \cite{Rubin_2011}.
-In this work the authors studied emission in a starburst galaxy at $z=0.69$ with a star formation rate of 80 $M_{\odot} yr^{-1}$.
-In a two-dimensional Keck/LRIS spectrum of this galaxy, they measured fluxes of $4.04 \pm 0.4$ to $8.0\pm 0.4$ $10^{-18}$ergs sec $^{-1}$ cm$^{-2}$  above and below the continuum region of the 2D spectra at $\lambda 2796$.
-Converting the 3$\sigma$ detection limit of our continuum-subtracted \ion{Mg}{2} image into flux units, we report the \ion{Mg}{2} emission 3$\sigma$ limits as 5.37 $10^{-18}$ergs sec $^{-1}$ cm$^{-2}$.
-%%%% KHRR
-[{\bf How do you convert to flux units here?  What size are you assuming?}]
-%%%%
-Comparing our SB limit to previously reported values, it should be possible to detect the emission of this particular starburst galaxy in our FORS2 imaging.
+In order to get information on the morphology of the \ion{Mg}{2}, we determine the distance of each pixel from the center of each galaxy in kiloparsecs.
+We plot the EWs over this projected distance for each galaxy in Figures \ref{fig:ew1} through \ref{fig:ew55}.
+Although some of the plots suggest a slight upward trend in the values of the EW at increasingly large radii, we cannot be confident in this trend because of large scatter.
+To better visualize the data and test the significance of the trend, we bin the data radially.
+For example, in Figure \ref{fig:ew44}, the EW from absorption extends out to $\sim$ 25 kpc.
+The EWs are binned in 5 kpc increments.
+We calculate the mean and scatter of the EWs in each bin and show these values in Figure \ref{fig:ew_comb}.
 
-\subsection{\ion{Mg}{2} absorption in the line-profile}
-Although we do not measure any extended \ion{Mg}{2} emission, we do observe a decrement of flux in the galaxy continua measured in the \ion{Mg}{2} filter in 3 galaxies out of the 5 galaxy sample.
-In the following section we discuss the absorption in each of these three galaxies, as well as our null detections.
+\section{Discussion}\label{sec.results}
+In this chapter we present the results from the continuum-subtraction of the off-line continuum filter to that of the on-line emission filter.
 
-We first discuss the case of a null detection of \ion{Mg}{2} absorption.
-The galaxy J033230.57 at a redshift of $z=0.6807$ is the most redshifted galaxy of the sample.
-This galaxy shows no significant flux decrement in the \ion{Mg}{2} filter.
-Examining Figure \ref{fig:spec_images}, we can see that there should not be any absorption measured in J033230.57, as the absorption profile in the spectrum appears both in the HeII and HeII/3000 filter.
-This is a good test of our flux calibration, as it appears that there are no hints of systematic false absorption signatures.
+\subsection{Limits on MgII emission}
 
-We have a second case in which we detect quite strong absorption.
-The galaxy J033230.64 exhibits a maximum flux decrement of roughly $4\times10^{-18}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^{-1}$ due to \ion{Mg}{2} absorption.
-The absorption is exhibited predominantly within the $1\sigma$ SB outline of the continuum.
-The mean value of the EW in all the pixels within the $1\sigma$ SB outline of this galaxy is $7.88 \pm 0.403$ \AA, which is relatively close to the EW calculated from the spectra, $6.70 \pm 0.51$\ \AA.
-We expect that the small difference is due to the collecting area of the different methods.
-We calculate the EW inside a $1\sigma$ region around the core of the galaxy
-%%%% KHRR
-[{\bf which is approximately how big in arcsec?}]
-%%%%
-, whereas the spectrum is obtained using a $0.9''$ slit width.
-In addition, further inspecting the distribution of the EW over the pixels, there are two outlier values of EW$\approx 20$ \AA\ that are influencing the mean value.
+We do not detect any significant amount of \ion{Mg}{2} emission in any of our sampled galaxies.
+The $\chi_{\text{smth}}$ images shown in Figure \ref{fig:sigmas} confirm this.
+A comparison of the simulated emission with the $\chi_{\text{smth}}$ image of the original stamps, shown in the first column, similarly suggests that we do not detect any extended \ion{Mg}{2} emission.
+We thus place conservative $5\sigma$ upper limits on \ion{Mg}{2} emission for each galaxy in the sample, summarized in Table \ref{tab:det_lims}.
+The most sensitive detection limit using the largest area is SB(\ion{Mg}{2}) = 5.74 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$, computed for the galaxy J033230.03.
+Our least sensitive detection limit is SB(\ion{Mg}{2}) = 6.81 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$, computed for the galaxy J033230.57.
 
-The next galaxy that shows a decrement of flux from \ion{Mg}{2} absorption is J033231.36.
-The \ion{Mg}{2} absorption spills outside the $1\sigma$ continuum flux contour, however a significant amount lies within our $1\sigma$ significant detection.
-The mean value of the EW of this galaxy is $6.91 \pm 0.560$ \AA, and is in good agreement with the EW calculated from the Keck/LRIS spectra, $6.50 \pm 0.51$ \AA.
-Again, inspection of the distribution of the EW over the pixels reveals a possible outlier of an EW$\approx 20$\ \AA.
+\subsection{Previous Detections of extended \ion{Mg}{2} emission}
+Previous constraints on the brightness of scattered \ion{Mg}{2} emission were reported by \cite{Rubin_2011}.
+In this work the authors studied emission from the starburst galaxy TKRS 4389 at $z = 0.69$ with a star formation rate of $49.8\msunperyr$.
+This emission was detected in a 2-dimensional KECK/LRIS spectrum, with flux from the emission reaching $8.0 \pm 0.4$ and $4.4 \pm 0.4$ $\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at  $\lambda _{2796}$ and $4.0 \pm 0.3$ and $2.5 \pm 0.4$ $\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at $\lambda_{2803}$ in two independent locations spatially offset from the galaxy continuum.
+The flux from the emission can be converted into two surface brightness values by taking the average of the flux measured at each location and each transition, and dividing by a 1 sq.arcsec aperture.
+
+Figure \ref{fig:detection_lim} shows a plot of the 5$\sigma$ detection limits determined for each galaxy in our sample as well as the SB calculated for the galaxy TKRS 4389.
+The figure suggests that we should be able to detect scattered \ion{Mg}{2} emission with strengths similar to that detected in TKRS 4389.
+Given if  additional detections of extended \ion{Mg}{2} emission are made, it could be possible that there exists the possibility of a relationship between SB and star-formation rate, as the study by \cite{Erb2012} discuss that emission strength is stronger in high mass galaxies.
+This could be one explanation as to why we did not detect any extended \ion{Mg}{2} emission Further studies need to be pursued to add additional points to Figure \ref{fig:detection_lim}.
+
+\subsection{Geometry of re-emitted photons}
+In idealized wind models of cool gas outflows, discussed in \cite{Prochaska_2011}, strong \ion{Mg}{2} emission is predicted to be generated along with ubiquitous blueshifted absorption of \ion{Mg}{2}.
+For isotropic and dust-free scenarios, this absorption and emission is simply produced by the conservation of photons, as any absorbed continuum photon is eventually re-emitted in emission.
+Because of this photon exchange the total equivalent width of both the absorption and emission features is equal to zero.
+Assuming that our galaxies host an isotropic and dust-free wind, we wish to determine how much emission is predicted to be missing from our imaging, and how the SB of this missing emission compares to our detection limits, for different distributions of emission.
+
+To find the amount of missing emission, we first need to calculate how much continuum has been absorbed by \ion{Mg}{2}.
+Using our Keck/LRIS spectra, we find the average value of the continuum near the \ion{Mg}{2} doublet and multiply this value by the EW of the doublet.
+Although we know how much emission is missing, we do not know how this emission is distributed outside the galaxy.
+As a conservative estimate of the SB, we distribute the missing emission uniformly inside multiple and increasingly sized annuli.
+These annuli are fixed to have an inner radius equal to the galaxy's isophotal radius and an increasing outer radius.
+Additionally, since our SB limits are dependent on the size of the aperture used, we calculate the SB limits inside each of the aforementioned annuli.
+Figure \ref{fig.emission} shows how the SB of emission varies with the spatial extent of the annulus, as well as how the SB compares with our detection limits..
+
+Excluding the galaxy J033230.03, the SB of this missing emission lie above our detection limits. This result shows that these galaxies do not host an isotropic dust-free wind.
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[scale=0.6]{../Figures/limits.pdf}
+\caption{Comparison of our detection limits to the measured extended emission of TKRS 4389.
+Our imaging is sufficiently sensitive to detect extended emission at similar strengths to the extended emission measured for TKRS 4389.}
+\label{fig:detection_lim}
+\end{figure}
+
+\subsection{Spatially Resolved Maps of \ion{Mg}{2} Absorption}
+In this section we discuss the details of the absorption detected in our images and compare our measurements to those obtained in the Keck/LRIS spectra of each galaxy..
+
+\subsubsection{\ion{Mg}{2}\ absorption in surface brightness profiles}
+Although we do not detect any extended \ion{Mg}{2} emission, we do observe a decrement of flux in the SB profiles of 4 out of 5 galaxies in our sample.
+
+\subsubsection{J033225.26} 
+Figure \ref{fig:sb_profiles} shows the SB profile for J033225.26.
+We report that the maximum decrement in the SB profile due to absorption is strongest at the center of the galaxy.
+The SB measured in the center aperture is -5.39 $\pm$ 0.128 $\times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
+The absorption in the profile decreases radially outward and is detected out to the largest distance sampled, $\sim 18$ kpc, away from the center of the galaxy.
+
+\subsubsection{J033231.36} 
+Figure \ref{fig:sb_profiles} shows the SB profile for J033231.36.
+We report that the maximum decrement in the SB profile due to absorption is strongest at the center of the galaxy.
+The SB measured in the center aperture is -5.64 $\pm$ 0.121 $\times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
+The absorption in the profile decreases radially outward and is detected out to the largest distance sampled, $\sim 18$ kpc, away from the center of the galaxy.
+
+\subsubsection{J033230.03} 
+Figure \ref{fig:sb_profiles} shows the SB profile for J033230.03.
+We report that the maximum decrement in the SB profile due to absorption is strongest at the center of the galaxy.
+The SB measured in the center aperture is -4.41 $\pm$ 0.622 $10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
+The absorption in the profile decreases radially outward and out to the largest distance sampled, $\sim 25$ kpc, away from the center of the galaxy.
+
+\subsubsection{J033229.64} 
+Figure \ref{fig:sb_profiles} shows the SB profile for J033229.64.
+We report that the maximum decrement in the SB profile due to absorption is strongest at the center of the galaxy.
+The SB measured in the center aperture is -18.2 $\pm$ 0.127 $\times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
+The absorption in the profile decreases radially outward and is detected out to the largest distance sampled, $\sim 14$ kpc, away from the center of the galaxy.
+
+\subsubsection{J033230.57} 
+Figure \ref{fig:sb_profiles} shows the SB profile for J033230.57.
+The absorption decrement is strongest at the center of the galaxy with a SB value of -1.25 $\pm$ 1.15 $10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
+However, the measured SB of this decrement including error is consistent with measuring zero absorption.
+The measurement of zero absorption for J033230.57 was expected.
+Figure \ref{fig:spec_images} shows the KECK/LRIS spectrum of J033230.57 and the transmission curves of the filters HeII+47 and HeII/3000+48.
+The \ion{Mg}{2} transitions of the galaxy are equally sampled by both of our filters.
+Simply put, each image of J033230.57 contains equal amounts of continuum and \ion{Mg}{2}.
+When we subtract the continuum image from the \ion{Mg}{2} image we are effectively canceling out the \ion{Mg}{2} absorption as well.
+This measurement can stand as a test of the quality of our continuum subtraction.
+\\
+
+The surface brightness profiles presented in Figures \ref{fig:sb_profiles} do not exhibit any signs of extended \ion{Mg}{2} emission. \\
+
+\subsection{Morphology of MgII Absorption}
+
+Figures \ref{fig:ew1} through \ref{fig:ew5} show the EW images, distributions and radial projections of \ion{Mg}{2} EWs.
+We have zeroed out any EWs that lie outside the SB$_1$ contours for each galaxy.
+We imposed a signal-to-noise cut, only including EWs where the continuum flux S/N greater than $|1.5|$.
+The mean EW is computed for all pixels inside each Keck/LRIS aperture, defined in Sec.
+\ref{subsec.ew}, and are summarized in Table \ref{tab:abs_props}.
+Comparing our measured EWs with those measured from the spectra, we find good agreement to within 1$\sigma$ or 2$\sigma$ for most of the galaxies except and J033230.57.
+
+In the case of J033230.57 we can easily understand why the EW measured is not in agreement with the spectra EW.
+Figure \ref{fig:sb_profiles}  shows the SB profile coverage of J033230.57, in this galaxy's profile we do not detect any significant decrements due to absorption.
+This is due to the fact that our two filters cover the \ion{Mg}{2} doublet equally, see Figure  \ref{fig:spec_images}.
+Any signal of absorption in the EW images arise from noise.
+Figure \ref{fig:ew5} shows the radial projection of the EWs measure for this galaxy which are centered around zero.
+
+To get a better sense of how the EW of \ion{Mg}{2} absorption changes with radius as well as account for any effects due to seeing, $\sim 7 kpc$, we bin the EWs in radial bins with 5, 4 or 3 kpc widths as shown in Figures \label{fig:ew1} through \label{fig:ew5}.
+A majority of the galaxies appear to show large scatter in the EWs out to larger radii.
+To better understand the significance of these trends, we construct a plot that compiles the mean EWs for all the galaxies, shown in Figure \ref{fig:ew_comb}.
+To take into account the varying size of the galaxies, we normalize the distances by the approximate radius of the SB$_1$ contour for each galaxy.
+
+Upon inspection of Figure \ref{fig:ew_comb}, we see that all the galaxies exhibit a constant mean EW inside our 1SB$_1$ isophotal radius.
+
+\section{CONCLUSION AND FUTURE WORK}
+We presented the results from a narrowband imaging search for \ion{Mg}{2} emission in a sample of star-forming galaxies at a redshift of $z \sim 0.70$.
+Although we were unable to detect any measurable amount of \ion{Mg}{2} emission, we are able to report a conservative $5\sigma$ detection limit of  SB(\ion{Mg}{2}) = 5.74 $\times 10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$.
+We detected a significant amount of \ion{Mg}{2} absorption in a total of 4 galaxies out of our 5 galaxy sample.
+Furthermore, our imaging allows us to generate spatially-resolved maps of \ion{Mg}{2} absorption in a distant galaxy sample for the first time.
+This absorption covered the center of the galaxies out to the SB$_1$ continuum + \ion{Mg}{2} isophotal radius, at approximately $\sim 22$ kpc, suggesting that the absorbing gas fully covers the stellar disks out to this distance.
+The measured EWs measured in these maps are in broad agreement with measured EWs using Keck/LRIS integrated slit spectroscopy.
+Additionally, our radial projections of the mean EW for our sample galaxies suggest that the EWs due to \ion{Mg}{2} are approximately constant out towards the edges of the galaxies.
+Finally, we compared our detection limits with estimated SB \ion{Mg}{2} emission, based on the radiative transfer models of \cite{Prochaska_2011}.
+For an isotropic dust-free wind, \ion{Mg}{2} is predicted to be generate alongside ubiquitous \ion{Mg}{2} absorption.
+Our detection limits are suitable to detect the estimated SB \ion{Mg}{2} emission and since we do not detect the excess emission, the  isotropic morphology of a wind is ruled out in our galaxy sample.
+
+In the future, we hope to observe these galaxies using an Integral Field spectrograph (IFU).
+IFUs take the signal from an individual pixel and feeds it into a spectrograph.
+The spectrograph then generates a spectrum for that pixel, allowing us to view the flux at specific transitions.
+IFUs cover large 2D fields of view, contrary to single point 1D spectroscopy or the slice of 2D longslit spectroscopy, makes them exceptionally useful in resolving the spectrum of a target for multiple sightlines.
+Thus, IFUs are useful in detecting the gas of extended objects, such as galaxies.
+Because IFUs would allow us to observe the spectrum of a galaxy's extended region, we will be able to compare our EW maps, as well as EW radial projections, with higher resolution observations.
+
+Based on the radial extent and strength of our measured \ion{Mg}{2} absorption, the \ion{Mg}{2} is optically thick.
+However, we need to compare our measured absorption strength and radial extent with radiative transfer models.
+In the radiative transfer models of \cite{Prochaska_2011}, scattered emission is predicted for an isotropic, optically thick,and dust free wind with density that decreases as an inverse square law, however galaxies are not spherically symmetric and sources driving the wind may not be distributed spherically.
+Allowing for a bi-conical anisotropic wind, \cite{Prochaska_2011} state that the scattered \ion{Mg}{2} emission will become suppressed compared to the strengths an isotropic wind.
+Future observations of our galaxies in IFUs could perhaps shed light on this alternate scenario.
 
@@
 \gridline{\fig{../Figures/J033225_26.pdf}{0.5\textwidth}{(J033225.26)}
-          \fig{../Figures/J033230_03.pdf}{0.5\textwidth}{(J033230.03)}}
-\gridline{\fig{../Figures/J033230_64.pdf}{0.5\textwidth}{(J033230.64)}
           \fig{../Figures/J033231_36.pdf}{0.5\textwidth}{(J033231.36)}}
-\caption{Surface brightness profiles for galaxies that exhibit flux decrements from \ion{Mg}{2} absorption.
-Photometry was performed with circular apertures with increasing inner and outer radii.
-The error bars are determined from a SWarp RMS map.
-%%%% KHRR
-[{\bf Explain what each color means.
-And it would be great if you could add your measurement for the extra-thick annulus here -- perhaps with a different symbol.
-Actually...
-didn't you show me a newer version of these figures recently?}]
-%%%%
-}
+\gridline{\fig{../Figures/J033230_03.pdf}{0.5\textwidth}{(J033230.03)}
+          \fig{../Figures/J033230_64.pdf}{0.5\textwidth}{(J033230.64)}}
+           \fig{../Figures/J033230_57.pdf}{0.5\textwidth}{(J033230.57)}
+\caption{SB profile for our sample galaxies.
+(Top) Continuum SB (black) measured for the galaxy in the continuum image.
+Mg II + continuum SB (green) measured for the galaxy in the pre-continuum subtracted image.
+Mg II line SB (blue) measured for the galaxy in the continuum subtracted line emission image.The profile exhibits SB decrements from \ion{Mg}{2} absorption.
+Photometry was performed in circular annuli.
+(Bottom) The vertical hashes in the bottom show the inner and outer radius of each annulus in kpc.
+Distance from the center of the galaxy (x-axis) is computed using the average value of each annulus inner and outer radii of each annuli.}
 \label{fig:sb_profiles}
@@
 
-\begin{figure*}[h!]
+ \begin{figure*}[]
 \centering
-\includegraphics[scale=.58]{../Figures/J03EW.pdf}
-\includegraphics[scale=.58]{../Figures/J64EW.pdf}
-\includegraphics[scale=.58]{../Figures/J26EW.pdf}
-\includegraphics[scale=.58]{../Figures/J57EW.pdf}
-\includegraphics[scale=.58]{../Figures/J36EW.pdf}
-\caption{ Plots of the distribution of equivalent widths inside a $1\sigma$ continuum flux outline. 
-%%%% KHRR
-[{\bf Are these white contours the same as the red contours in Fig. 5?  If so, you should state this.}]
-%%%%
-}
-\label{fig:ew_images}
+\includegraphics[scale=0.9]{../Figures/J26EW.pdf}
+\includegraphics[scale=0.9]{../Figures/J26EW_2.pdf}
+\caption{Equivalent width images, distribution and radial projection for J033225.26.
+(Top Left) image of the \ion{Mg}{2} equivalent widths inside the red 1SB$_1$ contour.
+The white contour represents the $0.9''$ wide  slit used to measure the equivalent width of absorption in the Keck/LRIS spectra.
+(Top Right) Distribution of absorption pixels with continuum flux S/N greater than 1.5 inside the slit aperture.
+(Bottom Left) The EWs of absorption vs projected distance from center.
+(Bottom Right) Binned EW measurements.
+Each point represents the mean EW measured in 3 kpc wide bins.}
+\label{fig:ew11}
 \end{figure*}
 
-\section{Discussion}
+\begin{figure*}[]
+\centering
+\includegraphics[scale=0.9]{../Figures/J36EW.pdf}
+\includegraphics[scale=0.9]{../Figures/J36EW_2.pdf}
+\caption{Equivalent width images, distribution and radial projection for J033231.36.
+(Top Left) image of the \ion{Mg}{2} equivalent widths inside the red 1SB$_1$ contour.
+The white contour represents the $0.9''$ wide  slit used to measure the equivalent width of absorption in the Keck/LRIS spectra.
+(Top Right) Distribution of absorption pixels with continuum flux S/N greater than 1.5 inside the slit aperture.
+(Bottom Left) The EWs of absorption vs projected distance from center.
+(Bottom Right) Binned EW measurements.
+Each point represents the mean EW measured in 4 kpc wide bins.}
+\label{fig:ew22}
+\end{figure*}
 
-%%%% KHRR
-\begin{itemize}
+\begin{figure*}[]
+\centering
+\includegraphics[scale=0.9]{../Figures/J03EW.pdf}
+\includegraphics[scale=0.9]{../Figures/J03EW_2.pdf}
+\caption{Equivalent width images, distribution and radial projection for J033230.03.
+(Top Left) Stamp of the equivalent widths (EWs) inside the red 1SB$_1$ contour.
+The white contour represents the $0.9''$ aperture slit used to measure the equivalent width of absorption in the Keck/LRIS spectra.
+(Top Right) Distribution of absorption pixels with continuum flux S/N greater than 1.5 inside the slit aperture.
+(Bottom Left) The EWs of absorption projected in distance from center.
+(Bottom Right) Binned EW measurements.
+Each point represents the mean EW measured in 5 kpc increment bins.
+}
+\label{fig:ew33}
+\end{figure*}
 
-\item Plot of SFR or $M_*$ vs.\ \ion{Mg}{2} SB for this sample, plus \cite{Rubin_2011} and \cite{Martin_2013} galaxies?  (Might be able to include an SB from \cite{Erb_2012} as well.)
+\begin{figure*}[]
+\centering
+\includegraphics[scale=0.9]{../Figures/J64EW.pdf}
+\includegraphics[scale=0.9]{../Figures/J64EW_2.pdf}
+\caption{ Equivalent width images, distribution and radial projection for J033229.64.
+(Top Left) Stamp of the equivalent widths (EWs) inside the red 1SB$_1$ contour.
+The white contour represents the $0.9''$ aperture slit used to measure the equivalent width of absorption in the Keck/LRIS spectra.
+(Top Right) Distribution of absorption pixels with continuum flux S/N greater than 1.5 inside the slit aperture.
+(Bottom Left) The EWs of absorption projected in distance from center.
+(Bottom Right) Binned EW measurements.
+Each point represents the mean EW measured in 4 kpc wide bins.}
+\label{fig:ew44}
+\end{figure*}
 
-\item Construct simple model to investigate effects of seeing / absorption signal on our sensitivity to extended emission?
+\begin{figure*}[]
+\centering
+\includegraphics[scale=0.9]{../Figures/J57EW.pdf}
+\includegraphics[scale=0.9]{../Figures/J57EW_2.pdf}
+\caption{Equivalent width images, distribution and radial projection for J033230.57.
+(Top Left) Stamp of the equivalent widths (EWs) inside the red 1SB$_1$ contour.
+The white contour represents the $0.9''$ aperture slit used to measure the equivalent width of absorption in the Keck/LRIS spectra.
+(Top Right) Distribution of absorption pixels with continuum flux S/N greater than 1.5 inside the slit aperture.
+(Bottom Left) The EWs of absorption projected in distance from center.
+(Bottom Right) Binned EW measurements.
+Each point represents the mean EW measured in 4 kpc wide bins.}
+\label{fig:ew55}
+\end{figure*}
 
-\item Can we comment on wind morphology / isotropy?  How does absorption EW compare with emission EW implied by our SB limit?
+\begin{figure*}[!htb]
+\centering
+\includegraphics[scale=0.9]{../Figures/ew_comb.pdf}
+\caption{Normalized radial profile of the mean EW of \ion{Mg}{2} absorption for all galaxies.
+Measurements for the mean EW binned in radial increments compiled to test the significance of any trends found in the individual galaxy profiles.
+There is significant scatter relative to the error bars at extended distances.}
+\label{fig:ew_comb}
+\end{figure*}
 
-\end{itemize}
-%%%%
+\begin{table*}[]
+\centering
+\caption{Properties of \ion{Mg}{2}\ Absorption\label{tab:abs_props}}  
+\begin{tabular}{llllll} \hline \hline
+Object & Max(SB$_{abs}$)\footnote{SB Values are in units of $10^{-18}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$} & $R_{\text{SB}_1}(kpc)$ &\ \ \ EW($\AA$)\footnote{ Measured from EW images} & EW($\AA$)\footnote{Measured from Keck/LRIS spectra}  \\  \hline
+J033225.26-274524.0 &  $-5.39 \pm 1.28 $ & 8 &     $\ \ \ 3.511 \pm 0.795$ & $7.539 \pm 0.354 $\\
+J033232.36-274725.0 &  $-5.64 \pm 0.121 $ & 15 & $\ \ \ 7.694 \pm 1.016$ & $5.835 \pm 0.493$\\
+J033230.03-274347.3 &  $-4.41 \pm 0.622 $ & 21 & $\ \ \ 5.388 \pm 0.712$ & $12.79 \pm 1.710$\\
+J033229.64-274242.5 &  $-18.2 \pm 0.127 $ & 10 & $\ \ \ 7.546 \pm 0.660$ & $13.24 \pm 0.263$\\
+J033230.57-274518.2 &  $-1.25 \pm 1.15   $ & 11& -$0.6532 \pm 0.589$ & $6.106 \pm 0.370$\\ \hline
+\end{tabular}
+\end{table*}
 
-\section{Conclusion}
-We presented the results of a narrowband imaging search for \ion{Mg}{2} emission in a sample of GOODS-S galaxies at a redshift of $z \approx 0.70$.
-Although we were unable to detect any measurable amount of \ion{Mg}{2} emission, We were able to detect a non-trivial amount of \ion{Mg}{2} absorption in 3 of our 5 galaxy sample.
-Our images, which are effective in creating absorption maps, were used to calculate the EW of absorption inside a $1\sigma$ continuum contour.
+\begin{figure*}
+\centering
+\gridline{\fig{../Figures/geo_J26.pdf}{0.5\textwidth}{(J033225.26)}
+          \fig{../Figures/geo_J36.pdf}{0.5\textwidth}{(J033231.36)}}
+\gridline{\fig{../Figures/geo_J03.pdf}{0.5\textwidth}{(J033230.03)}
+          \fig{../Figures/geo_J64.pdf}{0.5\textwidth}{(J033230.64)}}
+\caption{ Estimated SB profile of \ion{Mg}{2} emission.
+The square points are SB of missing \ion{Mg}{2} emission uniformly distributed inside an annulus.
+The solid line shows the value of the SB detection limits.
+The dashed vertical and horizontal lines represent outer radius of }
+\label{fig.emission}
+\end{figure*}
+
+\newpage
 \bibliography{references2017}

### 2018-06-06 Manuscript/vaught_2017.tex
updated paper May29th
updated June6th

@@
 \author{Ryan Rickards Vaught}
-\affiliation{San Diego State University 5500 Campanile Dr, San Diego, CA 92182}
-\affiliation{Department of Physics, University of California, San Diego, CA}
+\affiliation{Department of Astronomy, San Diego State University, San Diego, CA 92182}
+\affiliation{Center for Astrophysics and Space Sciences, Department of Physics, University of California, San Diego, CA}
 
  \author{Kate H. R. Rubin }
- \affiliation{San Diego State University 5500 Campanile Dr, San Diego, CA 92182}
+ \affiliation{Department of Astronomy, San Diego State University, San Diego, CA 92182}
 
@@
 
-\author{Joseph Hennawi,}
+\author{Joseph Hennawi}
 \affiliation{Department of Physics, Broida Hall, University of California, Santa Barbara, CA 93106-9530}
@@
 \correspondingauthor{Ryan Rickards Vaught}
-\email{rjvaught@gmail.com}
+\email{rjrickar@ucsd.edu}
 
@@
 
-Galactic-scale outflows are thought to be the primary mechanism in the removal of cool gas from star-forming galaxies.
-Presently, the mass and energy of these flows remain poorly constrained.
-One way to better constrain these parameters is to measure the spatial extent of the outflow; however, measuring this quantity via spectral methods has been traditionally very difficult due to the faintness of emission lines tracing outflowing material.
+The mass and energy of galactic winds remain poorly constrained via traditional absorption line studies.
+One way to better constrain these parameters is to measure the spatial extent of the outflow in emission.
 We perform a VLT/FORS2 narrowband imaging of 5 star-forming galaxies at redshift $z=0.67-0.69$ in the GOODS-S field as part of an effort to spatially resolve and constrain the radial extent of large-scale outflows traced by \ion{Mg}{2} emission.
-These observations probe \ion{Mg}{2} to unmatched surface brightness limits of 5.74 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ (5$\sigma$).
-We do not detect any extended \ion{Mg}{2} emission in any of our galaxies, suggesting that the wind material does not extend beyond the galaxies' stellar component.
-Our observations also allow us to create the first ever spatially-resolved map of  \ion{Mg}{2} absorption, revealing approximately constant absorption strengths across the galaxy disks.
+These observations probe extended \ion{Mg}{2} emission down to unmatched surface brightness limits of 5.74 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ (5$\sigma$).
+We do not detect any extended \ion{Mg}{2} emission in any of our galaxies, thus placing strong upper limits on the strength of \ion{Mg}{2} emission in the sample galaxies.
+Our observations allow us to create the first ever spatially-resolved map of \ion{Mg}{2} absorption, revealing approximately constant absorption strengths across the galaxy disks.
+Our detection limits in concert with a previous studies Keck/LRIS spectra allow us to model \ion{Mg}{2} emission for isotropic and anisotropic dust-free winds.
+We find that anisotropic winds reduce the strength of estimated missing \ion{Mg}{2} emission below our 5$\sigma$ limit.
 
@@
 
-\keywords{Galaxy Evolution, Galactic Winds}
+\keywords{galaxies: evolution, Galactic Winds}
 
@@
 
-\subsection{Geometry of re-emitted photons}
-In idealized wind models of cool gas outflows, discussed in \cite{Prochaska_2011}, strong \ion{Mg}{2} emission is predicted to be generated along with ubiquitous blueshifted absorption of \ion{Mg}{2}.
-For isotropic and dust-free scenarios, this absorption and emission is simply produced by the conservation of photons, as any absorbed continuum photon is eventually re-emitted in emission.
-Because of this photon exchange the total equivalent width of both the absorption and emission features is equal to zero.
-Assuming that our galaxies host an isotropic and dust-free wind, we wish to determine how much emission is predicted to be missing from our imaging, and how the SB of this missing emission compares to our detection limits, for different distributions of emission.
-
-To find the amount of missing emission, we first need to calculate how much continuum has been absorbed by \ion{Mg}{2}.
-Using our Keck/LRIS spectra, we find the average value of the continuum near the \ion{Mg}{2} doublet and multiply this value by the EW of the doublet.
-Although we know how much emission is missing, we do not know how this emission is distributed outside the galaxy.
-As a conservative estimate of the SB, we distribute the missing emission uniformly inside multiple and increasingly sized annuli.
-These annuli are fixed to have an inner radius equal to the galaxy's isophotal radius and an increasing outer radius.
-Additionally, since our SB limits are dependent on the size of the aperture used, we calculate the SB limits inside each of the aforementioned annuli.
-Figure \ref{fig.emission} shows how the SB of emission varies with the spatial extent of the annulus, as well as how the SB compares with our detection limits..
-
-Excluding the galaxy J033230.03, the SB of this missing emission lie above our detection limits. This result shows that these galaxies do not host an isotropic dust-free wind.
-
 \begin{figure}[!htb]
@@
 \end{figure}
+
+\subsection{Geometry of re-emitted photons}
+In idealized wind models of cool gas outflows, discussed in \cite{Prochaska_2011}, strong \ion{Mg}{2} emission is predicted to be generated along with ubiquitous blueshifted absorption of \ion{Mg}{2}.
+For isotropic and dust-free scenarios, this absorption and emission is simply produced by the conservation of photons, as any absorbed continuum photon is eventually re-emitted in emission.
+Because of this photon exchange the total equivalent width of both the absorption and emission features is equal to zero.
+Assuming that our galaxies host an isotropic and dust-free wind, we wish to determine how much emission is predicted to be missing from our imaging, and how the SB of this missing emission compares to our detection limits, for different distributions of emission.
+
+To find the amount of missing emission, we first calculate how much continuum has been absorbed by \ion{Mg}{2}.
+Using our Keck/LRIS spectra, we find the average value of the continuum near the \ion{Mg}{2} doublet and multiply this value by the EW of the doublet.
+Although we know how much emission is missing, we do not know how this emission is distributed outside the galaxy.
+As a conservative estimate of the SB, we distribute the missing emission uniformly inside multiple and increasingly sized annuli.
+These annuli are fixed to have an inner radius equal to the galaxy's isophotal radius and an increasing outer radius.
+Additionally, since our SB limits are dependent on the size of the aperture used, we calculate the SB detection limits of our images inside each of the aforementioned annuli.
+Figure \ref{fig.emission} shows how the SB of emission varies with the spatial extent of the annulus, as well as how the SB compares with our detection limits.
+Excluding the galaxy J033230.03, the SB of this missing emission lie above our detection limits.
+This result shows that these galaxies do not host an isotropic dust-free wind.
+
+There are many phenomena that we can employ to reduce the SB of the missing \ion{Mg}{2} emission to better match our observations.
+Introducing dust into the wind can reduce the observed emission as it can change the observed line profile in a critical way as re-emitted photons have to travel farther distances to escape the wind and therefore the profile will suffer greater extinction.
+Another factor that can reduce the amount of emission is anisotropy of the wind.
+Isotropic winds are idealized, but galaxies are not spherically symmetric and the shape of the galaxies interstellar medium may preferentially suppress outflows at varying strengths for different galactic longitudes.
+We now assume that the emission in our galaxies is reduced by purely by the effects anisotropy, as the constraints on dust attenuation or unknown.
+For the anisotropic winds modeled in \cite{Prochaska_2011}, the factor that the emission is reduced is given by the scaling $\Omega/4\pi$, where $\Omega$ is the angular extent of the wind which is constrained to point towards the observer $\Omega > 2\pi$.
+We show the anisotropic wind SB profiles in Figure  \ref{fig.emission}.
+
+After reducing the SB of the missing \ion{Mg}{2} emission by the minimum opening angle $\Omega=2\pi$, we are able to profiles that fall below our SB detection limits for galaxy's J033225.26 and J033231.36.
+However, the SB profile of J033229.64 remains above our SB detection limits, suggesting additional phenomena are needed to reduce the strength of missing emission.
 
@@
 
+\begin{table*}[]
+\centering
+\caption{Properties of \ion{Mg}{2}\ Absorption\label{tab:abs_props}}  
+\begin{tabular}{llllll} \hline \hline
+Object & Max(SB$_{abs}$)\footnote{SB Values are in units of $10^{-18}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$} & $R_{\text{SB}_1}(kpc)$ &\ \ \ EW($\AA$)\footnote{ Measured from EW images} & EW($\AA$)\footnote{Measured from Keck/LRIS spectra}  \\  \hline
+J033225.26-274524.0 &  $-5.39 \pm 1.28 $ & 8 &     $\ \ \ 3.511 \pm 0.795$ & $7.539 \pm 0.354 $\\
+J033232.36-274725.0 &  $-5.64 \pm 0.121 $ & 15 & $\ \ \ 7.694 \pm 1.016$ & $5.835 \pm 0.493$\\
+J033230.03-274347.3 &  $-4.41 \pm 0.622 $ & 21 & $\ \ \ 5.388 \pm 0.712$ & $12.79 \pm 1.710$\\
+J033229.64-274242.5 &  $-18.2 \pm 0.127 $ & 10 & $\ \ \ 7.546 \pm 0.660$ & $13.24 \pm 0.263$\\
+J033230.57-274518.2 &  $-1.25 \pm 1.15   $ & 11& -$0.6532 \pm 0.589$ & $6.106 \pm 0.370$\\ \hline
+\end{tabular}
+\end{table*}
 \subsection{Morphology of MgII Absorption}
@@
 
-\section{CONCLUSION AND FUTURE WORK}
+\section{CONCLUSION}
 We presented the results from a narrowband imaging search for \ion{Mg}{2} emission in a sample of star-forming galaxies at a redshift of $z \sim 0.70$.
@@
 Additionally, our radial projections of the mean EW for our sample galaxies suggest that the EWs due to \ion{Mg}{2} are approximately constant out towards the edges of the galaxies.
+
 Finally, we compared our detection limits with estimated SB \ion{Mg}{2} emission, based on the radiative transfer models of \cite{Prochaska_2011}.
-For an isotropic dust-free wind, \ion{Mg}{2} is predicted to be generate alongside ubiquitous \ion{Mg}{2} absorption.
-Our detection limits are suitable to detect the estimated SB \ion{Mg}{2} emission and since we do not detect the excess emission, the  isotropic morphology of a wind is ruled out in our galaxy sample.
+We are able to rule out that the winds in our sample are isotropic, as our detection limits are suitable to detect the predicted emission.
+By assuming anisotropic winds, we were able to reduce the strength of the predicted emission to lie below our detection limit, albeit one galaxy that needs additional phenomena like dust to achieve non-detectability in our images.
 
-In the future, we hope to observe these galaxies using an Integral Field spectrograph (IFU).
+Based on the radial extent and strength of our measured \ion{Mg}{2} absorption, the \ion{Mg}{2} is optically thick.
+Deeper images in \ion{Mg}{2} are required to observe any extended emission beyond the depth of our images.
+Although we are able to rule out that the winds in our sample are isotropic and dust-free, questions linger on weather the wind is anisotropic as well as dust-free.
+A new generation of instruments such as the Keck Cosmic Web Imager (KCWI) or the Multi Unit Spectroscopic Explorer (MUSE) should be used to answer the prevailing questions
+
+%In the future, we hope to observe these galaxies using an Integral Field spectrograph (IFU).
 IFUs take the signal from an individual pixel and feeds it into a spectrograph.
@@
 
-Based on the radial extent and strength of our measured \ion{Mg}{2} absorption, the \ion{Mg}{2} is optically thick.
+%Based on the radial extent and strength of our measured \ion{Mg}{2} absorption, the \ion{Mg}{2} is optically thick.
 However, we need to compare our measured absorption strength and radial extent with radiative transfer models.
@@
 
-\begin{table*}[]
-\centering
-\caption{Properties of \ion{Mg}{2}\ Absorption\label{tab:abs_props}}  
-\begin{tabular}{llllll} \hline \hline
-Object & Max(SB$_{abs}$)\footnote{SB Values are in units of $10^{-18}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$} & $R_{\text{SB}_1}(kpc)$ &\ \ \ EW($\AA$)\footnote{ Measured from EW images} & EW($\AA$)\footnote{Measured from Keck/LRIS spectra}  \\  \hline
-J033225.26-274524.0 &  $-5.39 \pm 1.28 $ & 8 &     $\ \ \ 3.511 \pm 0.795$ & $7.539 \pm 0.354 $\\
-J033232.36-274725.0 &  $-5.64 \pm 0.121 $ & 15 & $\ \ \ 7.694 \pm 1.016$ & $5.835 \pm 0.493$\\
-J033230.03-274347.3 &  $-4.41 \pm 0.622 $ & 21 & $\ \ \ 5.388 \pm 0.712$ & $12.79 \pm 1.710$\\
-J033229.64-274242.5 &  $-18.2 \pm 0.127 $ & 10 & $\ \ \ 7.546 \pm 0.660$ & $13.24 \pm 0.263$\\
-J033230.57-274518.2 &  $-1.25 \pm 1.15   $ & 11& -$0.6532 \pm 0.589$ & $6.106 \pm 0.370$\\ \hline
-\end{tabular}
-\end{table*}
-
-\begin{figure*}
+\begin{figure*}[h]
 \centering
@@
           \fig{../Figures/geo_J64.pdf}{0.5\textwidth}{(J033230.64)}}
-\caption{ Estimated SB profile of \ion{Mg}{2} emission.
-The square points are SB of missing \ion{Mg}{2} emission uniformly distributed inside an annulus.
+\caption{Estimated SB profile of \ion{Mg}{2} emission for Isotropic and Anisotropic dust-free winds.
+The black square points are SB of missing \ion{Mg}{2} emission uniformly distributed inside an annulus for an angle $\Omega=4\pi$, or an isotropic wind.
+The blue diamond points are SB of missing \ion{Mg}{2} emission uniformly distributed inside an annulus for an angle $\Omega=2\pi$, or an anisotropic wind.
 The solid line shows the value of the SB detection limits.
-The dashed vertical and horizontal lines represent outer radius of }
+The dashed vertical and horizontal lines represent outer radius of the extended annulus use to measure the initial detection limits and the value of SB detection limit in that annulus.}
 \label{fig.emission}

### 2018-06-15 Manuscript/vaught_2017.tex
updated June15th

@@
 Some possible mechanics have been proposed by theoretical studies that include thermal pressure from core collapse supernova, radiation pressure from starbursts and finally cosmic ray pressure (\citethnop{Larson_1974}; \citethnop{Chevalier_1985}; \citethnop{Springel_2003}; \citethnop{Sugahara_2017}).
-However it is very difficult to distinguish between these mechanisms with current observational techniques.
 Additionally, the impact galactic winds have on their host galaxies (i.e, their mass and energy content) has remained difficult to constrain with observations.
@@
 An accurate picture of what types of galaxies host outflows comes from numerous absorption line studies of galaxies (\citethnop{Veilleux2005}; \citethnop{Weiner2009}; \citethnop{Martin2012}; \citethnop{Rubin_2014}).
-Outflows are detected by measuring the blueshift (outflow) or redshift (inflow) of absorption transitions with respect to the host galaxy systematic velocities.
-Spectroscopy of galaxies from low to high redshifts probing cold gas which absorbs in \ion{Na}{1} and cool gas in \ion{Mg}{2} has revealed outflows in most galaxies that host active star-formation (e.g.
-\citethnop{Martin2012}; \citethnop{Rubin_2014}).
-Even though these probes can ascertain: the radial velocity, column density and covering fraction of the flow, this method is weak in constraining the overall radial extent and provides no information on the morphology of the outflow.
+Outflows are detected by measuring the blueshift (outflow) or redshift (inflow) of absorption transitions with respect to the host galaxy systematic velocity.
+Spectroscopy of galaxies from low to high redshifts probing cold gas ($T \lesssim 10^4$ K) which absorbs in \ion{Na}{1} and cool gas ($T \sim 10^4$ K) in \ion{Mg}{2} has revealed outflows in most galaxies that host active star-formation (e.g.
+\citethnop{chen2010}; \citethnop{Martin2012}; \citethnop{Rubin_2014}).
+Even though these probes can constrain: the radial velocity, column density and covering fraction of the flow, this method is weak in constraining the overall radial extent and provides no information on the morphology of the outflow.
 
-One novel way of developing these constraints is to trace the extent of winds in emission.
-This has been demonstrated in the optical using rest frame near infrared transitions (i.e H$\alpha$ and \ion{O}{3} etc) as tracers for nearby starbursts (\citethnop{Matsubayashi2009}; \citethnop{Veilleux2009}; \citethnop{Tripp2011}) because these transitions can trace the warm shock heated phase of the gas.
-However, it is difficult to use these rest frame near infrared transitions to probe winds at higher redshift because the faint emission can be redshifted into the infrared where the sky background is bright.
-At higher redshifts, it is advantageous to trace winds in the optical with the rest frame ultraviolet ion, \ion{Mg}{2} (Weiner et al.
+One way of developing these constraints is to trace the extent of winds in emission.
+This has been demonstrated using rest-frame optical transitions (i.e H$\alpha$, [\ion{O}{3}], etc) as tracers for winds around nearby starbursts (\citethnop{Matsubayashi2009}; \citethnop{Veilleux2009}; \citethnop{Tripp2011}) as these transitions can trace the warm shock heated phase of the gas.
+A novel, alternative transition potentially useful for tracing winds in emission is the \ion{Mg}{2} $\lambda\lambda 2976,2803$ doublet in the rest-frame ultraviolet (UV)
+(Weiner et al.
 2009; Kornei et al.
-2013)\nocite{Weiner2009, Kornei2013}
+2013)\nocite{Weiner2009, Kornei2013}.
+While most studies of winds using \ion{Mg}{2} have focused on its absorption kinematics, \cite{Rubin_2011}  recently observed  strong \ion{Mg}{2} emission with a P-Cygni line profile in the spectrum of a strongly star-forming galaxy at redshift $z = 0.694$.
+This emission was the first detection of an outflow beyond the spatial extent of the galaxy continuum in the distant universe, with a minimum spatial extent  $>$ 7 kpc.
 
-Typically, studies of winds using \ion{Mg}{2} have focused on its absorption kinematics.
-However, recently in a study by \cite{Rubin_2011}, strong \ion{Mg}{2} emission with a P-Cygni line profile was observed in the 2D spectrum of a strongly star-forming galaxy at redshift $z = 0.694$.
-This emission was the first detection of an outflow beyond the spatial extent of the galaxy continuum in the distant universe, with a minimum spatial extent  $>$ 7 kpc.
 One proposed production mechanism for the galaxy's observed \ion{Mg}{2} line profile is photon scattering.
-
 In this mechanism, \ion{Mg}{2} ions in the region of the wind closest to the observer will absorb continuum photons in the resonant transitions, $\lambda_{2796}$ and $\lambda_{2803}$.
@@
 The \ion{Mg}{2} ions in the section of the wind farthest from the observer will absorb and scatter photons that are redshifted relative to the front portion of the wind.
-Because the photons are redshifted, the photons will be able to travel freely towards the observer through the wind to produce emission at and redward of the systematic velocity of the galaxy \citeth{Rubin_2011}.
-The photon scattering model, as explained, is described for the geometry of an isotropic wind \citeth{Prochaska_2011}.
-For anisotropic bi-conical winds, the emission induced from photon scattering will be highly suppressed.
-Since the first detection of \ion{Mg}{2} emission by \citeth{Rubin_2011}, further detections of extended \ion{Mg}{2} emission are by \cite{Erb2012} and \cite{Martin2013} have shown that emission is stronger for higher mass galaxies and that outflows can extend out to at least 18 kpc.
+Because the photons are redshifted, the photons will be able to travel freely towards the observer through the wind to produce emission at and redward of the systematic velocity of the galaxy (\citethnop{Rubin_2011}, \citethnop{Prochaska_2011}).
+Since the first detection of \ion{Mg}{2} emission by \citeth{Rubin_2011}, a further detection of extended \ion{Mg}{2} emission is found in \cite{Martin2013}, where they observe \ion{Mg}{2} emission that extends $12-18$ kpc for the galaxy 32016857 at $z=0.9392$.
+Additionally, \ion{Mg}{2} is found in 1D and IFU spectra (\citethnop{Erb2012} and Feltre et.
+al (2018)).
+In these surveys of galaxies between with redshift $ 0.70 < z < 2.30$, \ion{Mg}{2} is detected in pure emission, pure absorption and with P-Cygni profiles.
+Detections of \ion{Mg}{2} in emission was found to be associated with galaxies of lower stellar mass and bluer spectral slopes.
 
-We aim to take advantage of this photon scattering as we present the first narrowband imaging of \ion{Mg}{2} line emission of 5 star-forming ($z \sim 0.7$) galaxies located in the deep Great Observatories Origins Deep Survey south (GOODS-S) field.
-The value in using narrowband imaging is the ability to spatially resolve any absoroption and emission from a galaxy.
+Various models of galactic winds are explored in \citethnop{Prochaska_2011}.
+This analysis involved generating spectra for the  \ion{Mg}{2} and  \ion{Fe}{2}$^*$ transitions, using a set of radiative transfer algorithms, for an isotropic and anisotropic set of dust and dust-free winds.
+The authors demonstrated that isotropic dust-free winds will conserve photon flux, thus predicting that blueshifted absorption lines should be accompanied by emission profiles of winds with similar equivalent widths (EW).
+Anisotropic winds however were demonstrated to significantly weaken emission at strengths proportional to the angular extent of the wind.
+The scattered emission was additionally weakened by the inclusion of dust and the affect of a strong interstellar medium (ISM).
+
+In this paper, we present the first narrowband imaging of \ion{Mg}{2} line emission around 5 star-forming  galaxies located in the deep Great Observatories Origins Deep Survey south (GOODS-S) field at redshift $z \sim 0.7$.
+The value in using narrowband imaging is the ability to spatially resolve any absorption and emission from a galaxy.
 We use two filters: a line filter and a continuum filter.
@@
 
-\section{Observations and Data Reduction}
+In Section \ref{sec:obs_red} we describe our sample of GOOD-S galaxies, Keck/LRIS spectra as well as our VLT/FORS2 observations, imaging, and absolute flux calibration.
+We go into detail in our method of image subtraction in Section \ref{sec.cont_sub}.
+The analysis of these data are included in Section \ref{sec:analysis}, in detail we discuss the production surface bright profiles and limits for each galaxy, as well as the production of narrowband measured equivalent widths.
+Section \ref{sec:results} contains the results from our narrowband imaging analysis.
+We compare our SB detections limits to previous detections of extended \ion{Mg}{2} emission, additionally we compare our observations to predictions made by radiative transfer models in Section \ref{sec:discussion}.
+We conclude this paper in Section \ref{sec:conclusion}.
+We adopt a $\Lambda$CDM cosmology with $h_{70} = H_0/(70\ \rm{ km}\ \rm{ s}^{-1}\ \rm{ Mpc}^{-1})$, $\Omega_{\rm{M}}= 0.3$, and $\Omega_{\Lambda} = 0.7$.
 
+\section{Observations and Data Reduction}\label{sec:obs_red}
 \subsection{Sample Selection}
@@
 2014)\nocite{Rubin_2014}.
-In particular, this parent survey targeted galaxies in a total of nine Keck/LRIS pointings located in both of the GOODS fields (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004})and the AEGIS survey field (the Extended Groth Strip; Davis et al.
+In particular, this parent survey targeted galaxies in a total of nine Keck/LRIS pointings located in both of the GOODS fields (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004}) and the AEGIS survey field (the Extended Groth Strip; Davis et al.
 2007)\nocite{Davis2007}.
@@
 Modeling of the galaxy broad-band spectral energy distributions obtained from multi-wavelength ancillary imaging data yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$.
-The properties of the sample, as well as precise target coordinates, taken from \cite{Rubin_2014} are listed in Table \ref{tab:prop}.
+The properties of the sample, as well as precise target coordinates taken from \cite{Rubin_2014}, are listed in Table \ref{tab:prop}.
 
 \subsection{VLT/FORS2 Observations}
-The data were taken in service-mode using the FORS2 instrument on the VLT 8.2m telescope Antu between October 2012 and February 2013. 
-We used two narrowband filters, HeII+47 and HeII/3000+48, that have peak transmission at wavelengths that correspond to the \ion{Mg}{2} doublet lines at our sample redshift of $z\approx 0.7$ (see Table \ref{tab:filters}).
-The transmission curves are plotted along with each galaxy's spectrum in Figure~\ref{fig:spec_images}.
+Our barrow-band imaging data were taken in service-mode using the FORS2 instrument on the VLT 8.2m telescope Antu between October 2012 and February 2013. 
+We used two narrowband filters, HeII+47 and HeII/3000+48, that have peak transmission at wavelengths that correspond to the \ion{Mg}{2} doublet lines at our sample redshift of $z\sim0.7$ (see Table \ref{tab:filters}).
+The filter transmission curves are plotted along with each galaxy's spectrum in Figure~\ref{fig:spec_images}.
 
-FORS2 has a pixel scale of $0.25''$ pixel$^{-1}$ and a field of view of $7'\times7'$.
-Summing the individual exposure times for each image results in a combined exposure time of $10.0$ hours each for the HeII+47 and HeII/3000+48 filters.
+FORS2 has a pixel scale of $0.25''$ pixel$^{-1}$ and a field of view of $7'\times7'$ with $2 \times 2$ binning.
 Our observations were carried out under photometric and thin cloud conditions (program ID: 090.A-0427A).
 The seeing (see Figure \ref{fig.seeing}) ranged from 0.5 arcsec to 2.5 arcsec.
-The data were taken with three pointings offset by 0.25'.
+The data were taken with three pointings offset by 0.25' East/West with exposure times of $\approx$ 1000 s.
+A total of 38  exposures were taken in each filter.
+Summing the individual exposure times for each filter results in a combined exposure time of $10.0$ hours each for the HeII+47 and HeII/3000+48 filters.
 
@@
 
-\begin{figure*}[!htb]
+\begin{figure*}[!h]
 \centering
-\includegraphics[scale=0.58]{../Figures/filt_57_spectra.pdf}
-\includegraphics[scale=0.58]{../Figures/filt_64_spectra.pdf}
-\includegraphics[scale=0.58]{../Figures/filt_03_spectra.pdf}
-\includegraphics[scale=0.58]{../Figures/filt_26_spectra.pdf}
-\includegraphics[scale=0.58]{../Figures/filt_36_spectra.pdf}
-\caption{KECK/LRIS spectrum of the sample galaxies and the transmission curves of the filters HeII+47 and HeII/3000+48.
+\gridline{\fig{../Figures/filt_26_spectra.pdf}{0.5\textwidth}{(a)}
+          \fig{../Figures/filt_36_spectra.pdf}{0.5\textwidth}{(b)}}
+\gridline{\fig{../Figures/filt_03_spectra.pdf}{0.5\textwidth}{(c)}
+          \fig{../Figures/filt_64_spectra.pdf}{0.5\textwidth}{(d)}}
+           \fig{../Figures/filt_57_spectra.pdf}{0.5\textwidth}{(e)}
+\caption{Keck/LRIS spectra of the sample galaxies and the transmission curves of the filters HeII+47 (blue dashed line) and HeII/3000+48 (red dashed line) .
 The left-hand axis is in units of flux density and the right-hand axis is the percentage of light transmitted the filter at each wavelength.
-Vertical dotted lines indicate the wavelength of the redshifted \ion{Mg}{2}\ doublet.
+Vertical dashed lines indicate the wavelength of the redshifted \ion{Mg}{2}\ doublet.
 The \ion{Mg}{2}\ doublet falls fortuitously at the central wavelength of the HEII+47 filter.}
@@
 \textbf{Top}: Seeing distribution for the 38 HeII+47 images. The median seeing in this filter is $1.03\arcsec$.
-\textbf{Bottom}: Same distribution for the 38 HEII/3000+48 images. The median seeing is $1.08\arcsec$. 
+\textbf{Bottom}: Same distribution for the 38 HeII/3000+48 images. The median seeing is $1.08\arcsec$. 
 The seeing conditions were calculated by ESO and were provided in the header of each science image.
@@
 The night-sky flats were produced by combining the unregistered science frames with an average sigma-clipping algorithm after masking out all the objects, and any bad pixels.
-Each individual image was cleaned of cosmic rays and bad pixels by utilizing the L.A.
-Cosmic algorithm.
+Each individual image was cleaned of cosmic rays and bad pixels by utilizing the \emph{L.A.
+Cosmic} algorithm \citep{Dokkum2001}.
 The astrometry solutions were calculated via Astrometry.net (Lang et al.
-2010)\nocite{Lang} with a standard deviation in the galaxy coordinates of $\sigma \approx 0.10''$.
-Before image stacking, we ran each frame through \textbf{SExtractor} \citeth{Bertin} in order to create a root mean square (RMS) map of each science image.
-These frames, in addition to the science images, are stacked to create a co-added RMS image.
+2010)\nocite{Lang}, yield a standard deviation in the galaxy coordinates of $\sigma \approx 0.10''$.
+Before image stacking, we ran each frame through \emph{SExtractor} \citeth{Bertin} in order to create a root mean square (RMS) map of each science image.
 
-The final stacked images for each filter is obtained using \textbf{SWarp} \citeth{Bertin}.
+The final stacked image for each filter is obtained using \emph{SWarp} \citeth{Bertin}.
 Each individual frame is first sky-subtracted using a background mesh size of 256 pixels which is approximately $64''$. 
 We chose the mesh size to be large enough such that the extended emission is not mistakenly subtracted (Arrigoni Battaia et al. 2015) \nocite{Battaia_2015}. 
-The frame, after background-subtraction, is resampled onto a common astrometric solution using a \textit{Lancosz3} interpolation kernel. 
+The frames, after background-subtraction, are resampled onto a common astrometric solution using a \textit{Lancosz3} interpolation kernel. 
 The images are average-combined and weighted by the night-flat image in order to increase the signal-to-noise of any \ion{Mg}{2} emission.
-\textbf{SWarp} is also configured to produce RMS weight maps from our \textbf{SExtractor} weighted images.
+Additionally, \emph{SWarp} generates a final set of RMS image from the night flats and the combination of RMS images for individual science frames.
 Our final stacked images in each filter are shown in Figure~\ref{fig:stacked_image} with the target galaxies indicated.
 
-One side effect from stacking is that the east and west borders of each image contain greater noise compared to the center of the image.
-This is due to the imperfect overlap of the 3 pointings used.
-However, the sample galaxies are sufficiently distant from these low S/N regions that their photometry is not affected.
-
 \begin{table}[h!]
-\caption{VLT/FORS2 Observations: Filter and exposure properties of the VLT observations.
-The width of the transmission curves are calculated by convolving the transmission curve with the total wavelength range of the filter.
+\caption{Filter properties  and exposure times of the VLT/FORS2 observations.
+The width of the transmission curves ($\Delta\lambda$) are calculated by convolving the transmission curve with the total wavelength range of the filter.
 These values differ slightly from those reported by the European Space Observatory.
@@
 \begin{tabular}{llllll} \hline \hline 
-Filter & $\lambda_{eff}$(\AA)\footnote{$\lambda_{eff}$ is the effective wavelength of the filter transmission curve.} & $\lambda_{width}$(\text{\AA})    & $N_{\text{img}}$   & $t_{tot}(s)$ & $S$\footnote{S is in units of $10^{-17}$ ergs counts$^{-1}$ cm$^{-2}$ }\smallskip  \\ \hline
-HeII  & 4675.21 & 50.11 & 38  & 35,959 & 2.45 \\
-HeII/3000 & 4722.46  & 44.82 & 38 &   36,937 & 2.40       \\ \hline
+Filter & $\lambda_{\rm{eff}}$(\AA)\footnote{$\lambda_{\rm{eff}}$ is the effective wavelength of the filter transmission curve.} & $\Delta\lambda$(\text{\AA})    & $N$\footnote{Total number of images}   & $T(s)$\footnote{Total exposure time} & $S$\footnote{S, the sensitivity of the filter, is in units of $10^{-17}$ ergs counts$^{-1}$ cm$^{-2}$ }\smallskip  \\ \hline
+HeII+47  & 4675.21 & 50.11 & 38  & 35,959 & 2.45 \\
+HeII/3000+48 & 4722.46  & 44.82 & 38 &   36,937 & 2.40  \\ \hline
 \end{tabular}
@@
 \centering
-\caption{Properties of 5 galaxies in our sample :  All galaxies are at roughly the same redshift.
-The star formation rates for the sample range from 3.8 to 40.5 solar mass per year.
-The EW include both components of the \ion{Mg}{2} doublet and were calculated with Eq.
-\ref{eq:specEW} and the supplemental Keck/LRIS spectra.
-\emph{HST}/ACS images of the galaxy sample are shown in Figure~\ref{fig:hstims}.
-The Keck/LRIS spectroscopy of this sample published in \cite{Rubin_2014} is shown in Figure~\ref{fig:spec_images}}
+\caption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}.
+The EW ( in the observed frame) include both components of the \ion{Mg}{2} doublet and were calculated with Eq.
+\ref{eq:specEW} and the supplemental Keck/LRIS spectra.}
 \begin{tabular}{lllllll} \hline \hline
-Object & R.A. & Dec  & $z$ & SFR($M_{\odot}$ yr$^{-1}$) & $\log{M_{*}/M_{\odot}}$ & EW(\AA) \smallskip      \\ \hline 
+Object & R.A. & Dec  & $z$ & SFR($M_{\odot}$ yr$^{-1}$) & $\log{M_{*}/M_{\odot}}$ & EW$_{\rm{obs}}$(\AA) \smallskip      \\ \hline 
 J033225.26-      & 03:32:25.26 & -27:45:23.9 & 0.6660 & $9.1_{-3.7}^{+1.3}$& $9.86_{-0.04}^{+0.05}$ & $7.539\pm 0.354$\\ 
@@
 \subsection{Absolute Flux Calibration}
-We acquired observations of the standard star GD50 from archival ESO calibration imaging at 4 independent epochs.From this standard we calculated the atmospheric extinction coefficients to be 0.181 magnitudes for the HeII/3000+48 filter and 0.190 magnitudes for the HeII+47 filter.
-Since we have imaging of the standard star GD50 in our two filters, and access to GD50's spectral energy distribution (cite!) and each filter's transmission curve through the ESO website, we are able to perform absolute flux calibration using the methods of Jacoby et al.
+We acquired observations of the standard star GD50 from archival ESO calibration imaging at 4 independent epochs.
+Performing aperture photometry at each epoch and airmass, we calculated the atmospheric extinction coefficients ($k$) to be 0.181 magnitudes for the HeII/3000+48 filter and 0.190 magnitudes for the HeII+47 filter.
+We perform absolute flux calibration using the methods of Jacoby et al.
 (1990).
@@
 It is not uncommon to assume that $F(\lambda)$ is constant over the small width of the filter.
-However, our filter transmission curves are sampled at $5$\ \AA\ intervals which is the same sampling as the spectral energy distribution of the standard star obtained from the ESO archives.
+However, our filter transmission curves are sampled at $5$\ \AA\ intervals which is the same sampling as the spectral energy distribution of the standard star obtained from the ESO archives (WILL CHECK CALSPEC).
 Therefore we calculate the integral numerically.
@@
 \end{equation*}\\
-where $k_i$ is the extinction in magnitudes per airmass, A is the airmass for each individual exposure, C is the measured count rate of the standard star and $S$ is in units of ergs counts$^{-1}$ cm$^{-2}$.
+where $k_i$ is the extinction in magnitudes per airmass, A is the airmass for each individual exposure, C is the measured count rate of the standard star and $S_i$ is in units of ergs counts$^{-1}$ cm$^{-2}$.
 Before image co-addition, each science image is corrected for atmospheric extinction by multiplying each frame by $10^{k_{i}A}$.
@@
 After co-addition, the images are then multiplied by the appropriate sensitivity factor $S_{i}$.
-This puts the final images in the appropriate flux units ergs sec $^{-1}$ cm$^{-2}$.
+This puts the final images in the appropriate flux units, ergs sec $^{-1}$ cm$^{-2}$.
 
@@
 \includegraphics[scale=.61]{../Figures/HEII3000_final.png}
-\caption{Top: HeII+47 image after stacking.
-Bottom: HeII3000+48 image after stacking.
+\caption{Top: Stacked HeII+47 image of the galaxy sample.
+Bottom: Stacked HeII3000+48 image of the same pointing.
 The exposure time of each image is $\approx 10$ hours.
-Each image has a FOV of $7' \times 7'$ which fortuitously contains the full sample of galaxies (indicated by the blue circles) in a single pointing.
+Each image has a FOV of $7' \times 7'$ which fortuitously contains the full sample of galaxies (indicated by the blue circles).
 East is up and North is right.
@@
 
-\section{Analysis}
-We have two goals for our study: (1) assess the surface brightness of line emission in the \ion{Mg}{2} transition in and around each target galaxy; and (2) spatially resolve the morphology of the strong \ion{Mg}{2} absorption observed against the galaxy continua.
-To reach the both of these goals, we must perform accurate subtraction of the continuum flux of each object from the filter covering the targeted line emission.
-For four of the five objects in our sample, the HeII+47 image includes both line and continuum emission, and the HeII3000+48 image provides a high S/N measurement of the continuum only $\approx30$ \AA\ redward of the line emission in the rest-frame.
-We detail our method of continuum subtraction using these data in Section~\ref{sec.cont_sub} below, and follow with a presentation of the resulting surface brightness profiles (Section~\ref{sec.sb}) and EW images (Section~\ref{subsec.ew}).
+\section{Image Subtraction}\label{sec.cont_sub}
 
 \subsection{Spectral Correction}
-With the supplementary spectra from \citeth{Rubin_2014}, we can fit the continuum and determine the slope of each galaxy spectrum in order to test whether the spectral slope gives rise to differences in continuum flux between the two filters.
-We use the interactive fitting routine \textbf{lt\_continuumfit} from the linetools package (Prochaska et al.
+In preparation for continuum subtraction, we first consider whether the continuum level of each galaxy spectrum changes significantly over the passbands of our two filters.
+We use the supplementary spectra from \citeth{Rubin_2014}, to fit the continuum and determine the spectral slope of each galaxy.
+We use the interactive fitting routine \emph{lt\_continuumfit} from the \emph{linetools} package (Prochaska et al.
 2016)\footnote{https://github.com/linetools/linetools}\nocite{Prochaska2016} to fit the continuum.
-By fitting the continuum we are masking the absorption features and making an effectively flat spectrum, which we use as a model.
-We find the total flux in each filter by convolving the fitted continuum with each filter's transmission curve.
+We then find the total continnum flux in each filter by convolving the fitted continuum with each filter's transmission curve.
 Next, we take the ratio of both integrated totals, as the ratio will indicate the scaling factor needed to correct our flux measurements prior to continuum subtraction.
-Comparing these ratios between each galaxy, we find that each ratio is effectively the same, within 3 decimal places, with a value of 1.118.
-This value is equal to the ratio between the FWHM of the transmission curves, allowing us to conclude that the slope of the spectrum of each galaxy is flat, and hence that the continuum level measured in the off-line filter provides an accurate measure of the continuum contribution to the on-line filter flux.
+Comparing these ratios between each galaxy, we find that they are effectively the same, within 0.1\%, with a value of 1.118.
+This value is equal to the ratio between the FWHM of the filter transmission curves, allowing us to conclude that the slope of the spectrum of each galaxy is flat, and hence that the continuum level measured in the off-line filter provides an accurate measure of the continuum contribution to the on-line filter flux.
 
-\subsection{Continuum Subtraction}\label{sec.cont_sub}
-To properly continuum-subtract the image taken with the emission filter in excess of the continuum, we follow a prescription given by \cite{Battaia_2015}. 
+\subsection{Continuum Subtraction}
+To properly continuum-subtract the image taken with the on-line filter in excess of the continuum, we follow a prescription given by \cite{Battaia_2015}. 
 We first determine the continuum flux density from the off-\ion{Mg}{2} filter,
 \begin{equation}
-f_{cont}=\frac{F_{cont}}{\Delta \lambda_{cont}},
+f_{\rm{cont}}=\frac{F_{\rm{cont}}}{\Delta \lambda_{\rm{cont}}},
 \end{equation}\\
-where $F_{cont}$ and $\Delta \lambda_{cont}$ are the observed flux per pixel of the continuum image per pixel and the transmission FWHM of the continuum filter, respectively.
-With $f_{cont}$ it is then possible to calculate the flux of any excess emission, $F_{line}$:
+where $F_{\rm{cont}}$ and $\Delta \lambda_{\rm{cont}}$ are the observed flux per pixel of the continuum image and the transmission FWHM of the continuum filter, respectively.
+With $f_{cont}$ it is then possible to calculate the flux of any excess emission, $F_{\rm{line}}$:
 \begin{equation}
-F_{line}=F_{MgII}-f_{cont} \Delta \lambda_{MgII}
+F_{\rm{line}}=F_{\rm{MgII}}-f_{\rm{cont}} \Delta \lambda_{\rm{MgII}}
 \label{eq:subtraction}
 \end{equation}
-where $F_{MgII}$ and $\Delta \lambda_{MgII}$ are the observed flux per pixel in the \ion{Mg}{2} filter and the transmission FWHM of the \ion{Mg}{2} filter.
+where $F_{\rm{MgII}}$ and $\Delta \lambda_{MgII}$ are the observed flux per pixel in the \ion{Mg}{2} filter and the transmission FWHM of the \ion{Mg}{2} filter.
 The continuum subtracted images of each galaxy are shown in Fig.
 \ref{fig:stamp_images}.
+The continuum subtracted image has uniform background and no obvious signatures of emission.
 
@@
 \caption{ $10'' \times 10''$ images of each galaxy in our sample.
-Top row: Continuum flux in ergs/s/cm$^2$/sq.arcsec.
-Bottom row: Continuum subtracted \ion{Mg}{2} flux.
+Top row: Continuum surface brightness in ergs/s/cm$^2$/sq.arcsec.
+Bottom row: Continuum subtracted \ion{Mg}{2} surface brightness.
 Absorption can be seen in 4 of 5 galaxies.
-The red contours represent the outline of the 1$\sigma$ surface brightness limit of continuum flux in the HeII/3000+38 image, defined in Sec.
+The red contours represent the outline of the 1$\sigma$ surface brightness limit in the HeII/3000+38 image, defined in Sec.
 \ref{sec.sb}.
-The colorbar shows the scaling used for the line emission images.}
+The colorbar shows the scaling used for the \ion{Mg}{2} images.}
 \label{fig:stamp_images}
@@
 
+\section{Analysis} \label{sec:analysis}
+We have two goals for our study: (1) assess the surface brightness of line emission in the \ion{Mg}{2} transition in and around each target galaxy; and (2) spatially resolve the morphology of the strong \ion{Mg}{2} absorption observed against the galaxy continua.
+To reach the both of these goals, we must perform accurate subtraction of the continuum flux of each object from the filter covering the targeted line emission.
+For four of the five objects in our sample, the HeII+47 image includes both line and continuum emission, and the HeII3000+48 image provides a high S/N measurement of the continuum only $\approx30$ \AA\ redward of the line emission in the rest-frame.
+We detail below the resulting surface brightness profiles (Section~\ref{sec.sb}) and detection limits (Section \ref{subsec:test}) as well at the EW$_{\rm{MgII}}$ generated from these data (Section~\ref{subsec.ew}).
+
 \subsection{Surface Brightness Profiles and Limits}\label{sec.sb}
 
-In order to test for the presence of \ion{Mg}{2} emission, we perform aperture photometry on the continuum subtracted images using the python library Photutils.
+In order to test for the presence of \ion{Mg}{2} emission, we perform aperture photometry on the continuum subtracted images using the python library \emph{Photutils}.
 We choose annuli with a radial thickness of 1 pixel or $0.25 ''$, such that, $r_{inner}=r_{outer}-1$ (in pixels).
 Each annulus is centered on the flux-weighted centroid of the galaxy.
-By dividing the summed flux in each annulus by the area in arcseconds we produced surface brightness (SB) profiles for each galaxy which are shown in Figure \ref{fig:sb_profiles}.
+By dividing the summed flux in each annulus by the area in arcseconds we produce surface brightness (SB) profiles for each galaxy.
+These profiles are shown in Figure \ref{fig:sb_profiles}.
 
-The error in this quantity is determined from an RMS image produced by \textbf{SWarp}.
+\begin{figure*}
+\centering
+\gridline{\fig{../Figures/J033225_26.pdf}{0.5\textwidth}{(a)}
+          \fig{../Figures/J033231_36.pdf}{0.5\textwidth}{(b)}}
+\gridline{\fig{../Figures/J033230_03.pdf}{0.5\textwidth}{(c)}
+          \fig{../Figures/J033230_64.pdf}{0.5\textwidth}{(d)}}
+           \fig{../Figures/J033230_57.pdf}{0.5\textwidth}{(e)}
+\caption{SB profiles for our sample galaxies.
+(Top panel) Continuum SB (black) measured for each galaxy.
+The green points show the Mg II + continuum SB measured for the galaxy in the pre-continuum subtracted image.
+The blue points show the Mg II line SB measured for the galaxy in the continuum subtracted line emission image.The profile exhibits SB decrements from \ion{Mg}{2} absorption.
+Photometry was performed in circular annuli.
+(Bottom panel) The vertical hashes in the bottom show the inner and outer radius of each annulus in kpc.
+Distance from the center of the galaxy (x-axis) is computed using the average value of the inner and outer radii of each annulus.}
+\label{fig:sb_profiles}
+\end{figure*}
+
+The error in the SB is determined from the stacked RMS images of each object \textbf{SWarp}.
 We place annuli that are identical to the annuli used to find the SB profiles for each galaxy.
@@
 
-To calculate the $1\sigma$ SB limit we follow the recipe found in \cite{Battaia_2015}.
-We first masked out all the sources, their associated extended halos, and edge noise in both the HEII+47 and HEII/3000+48 images.
-We then calculate the root-mean-square (rms) of the background in randomly placed 1" apertures.
-We convert these rms values to SB limits $per$ 1 sq.arcsec aperture.
-We find that the 1$\sigma$ detection limits per 1 arcsec$^2$ aperture (SB$_1$) are $6.332\times10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ and $5.808\times10^{-19} $ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ in the HeII/3000 and HeII filters, respectively.
-With the 1$\sigma$ detection limit, SB$_1$, determined for the continuum+\ion{Mg}{2} (HeII) image, we define an extended annulus to be used to detect any extended \ion{Mg}{2} emission.
-This extended annulus has an inner radius approximately the size of a unique SB$_1$ isophotal contour for each galaxy.
-The outer radius will be the inner radius extended by an arbitrary choice of 5 pixels.
+To calculate the $1\sigma$ SB limit we follow the procedure of \cite{Battaia_2015}.
+We first mask out all the sources, their associated extended halos, and edge noise in both the HeII+47 and HeII/3000+48 images.
+We then calculate the RMS of the background in randomly-placed 1" apertures.
+We convert these RMS values to SB limits $per$ 1 sq.arcsec aperture.
+We find that the 1$\sigma$ detection limits per 1 arcsec$^2$ aperture (SB$_1$) are $6.332\times10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ and $5.808\times10^{-19} $ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ in the HeII/3000+48 and HeII+47 filters, respectively.
+With the 1$\sigma$ detection limit, SB$_1$, determined for the continuum+\ion{Mg}{2} (HeII) image, we define a thicker (or "extended") annulus to be used to search for any extended \ion{Mg}{2} emission.
+This extended annulus has an inner radius approximately the size of the SB$_1$ isophotal contour for each galaxy.
+The outer radius is chosen to be the inner radius plus 5 pixels.
 
-The sensitivity required to detect an extended source depends on its size because one can reach lower SB levels by spatially averaging over large apertures.
+The sensitivity required to detect an extended source depends on its size, as one can reach lower SB levels by spatially averaging over large apertures.
 In the ideal case of perfect sky subtraction and continuum subtraction, the 1$\sigma$ SB limit for an extended source is $SB_{1}/\sqrt{A_\text{src}}$, where $A_\text{src}$ is the area in arcsec$^2$ and $SB_{1}$ is the surface brightness limit per 1 arcsec$^2$ aperture.
-In practice, the actual detection limits are limited by systematics from imperfect subtraction.
+In practice, the actual detection limits are affected by systematics from imperfect subtraction.
 Therefore, we empirically determine the limits as follows.
 We mask all the artifacts and sources in the continuum-subtracted images.
-Next generate randomly sized annuli, place them at random and extract the fluxes, $F_{\text{src}}$, within these annuli.
-In the ideal case that the sky and continuum are perfectly subtracted, the fluxes, $F_{\text{src}}$, from many random annuli should follow a Gaussian distribution with a width of $\sigma_{\text{src}} \equiv SB_{1}\sqrt{A_\text{src}}$.
-We find that the actual Gaussian width, $\sigma'_{\text{src}}$ of the distribution is broader than $\sigma_{\text{src}}$.
+Next, we generate randomly sized apertures, place them at random, and extract the fluxes, $F_{\text{src}}$, within these apertures.
+In the ideal case that the sky and continuum are perfectly subtracted, the fluxes, $F_{\text{src}}$, from many random apertures should follow a Gaussian distribution with a width of $\sigma_{\text{src}} \equiv SB_{1}\sqrt{A_\text{src}}$.
+The distribution of $F_{\text{src}}$ for these apertures are shown in Figure \ref{fig:limits}.
+We calculate the variance and mean of the distribution and find that Gaussian width, $\sigma'_{\text{src}}=1.1$, of the distribution is broader than $\sigma_{\text{src}}$.
 We adopt $F_{\text{limit}} \equiv \sigma'_{\text{src}}$  as the $1 \sigma$ upper limit on the total line flux of extended \ion{Mg}{2} emission.
+The SB$_{\text{limit}}$ is just $F_{\text{limit}}/A_{\rm{src}}$.
+The values of $F_{\text{src}}$ and the 5SB$_{\text{limit}}$ for each galaxy are listed in Table \ref{tab:det_lims}.
 
@@
 \includegraphics[scale=0.6]{../Figures/hist_sblim.pdf}
-\caption{Normalized distribution of $F_{\text{src}}/\sigma_{\text{src}}$ values, for random circular annuli.
-$F_{\text{src}}$ is the total flux within the largest annulus and $\sigma_{\text{src}}$ is the expected $1\sigma$ flux limit in the ideal case of perfect sky and continuum subtraction, i.e $SB_{1}\sqrt{A_\text{src}}$.}
+\caption{Normalized distribution of $F_{\text{src}}/\sigma_{\text{src}}$ values for random circular annuli placed on the continuum-subtracted line image.
+$F_{\text{src}}$ is the total flux within an aperture and $\sigma_{\text{src}}$ is the expected $1\sigma$ flux limit in the ideal case of perfect sky and continuum subtraction, i.e $SB_{1}\sqrt{A_\text{src}}$.
+The black arrows point to the statistical significance of the flux inside the "extended annulus" of each galaxy.}
 \label{fig:limits}
@@
 %\begin{minipage}{4in}
-\caption{Significance of Extracted Flux \label{tab:sb_lims}}  
-\begin{tabular}{llll} \hline \hline
-Object & F(\ion{Mg}{2})\footnote{\ion{Mg}{2} flux is in $10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$.
-The value in the parenthesis is the statistical significance with respect to $\sigma_{\text{src}}$ } & Area\footnote{Area of the extended annulus in sq.arcsec} \\  \hline
-J033225.26-274524.0 &  2.44(0.92)	& 21 \\
-J033232.36-274725.0 &  -1.40(-0.53) & 21 \\
-J033230.03-274347.3 &  -5.23(-1.75) & 27 \\
-J033229.64-274242.5 &  1.23 (0.44) & 26 \\
-J033230.57-274518.2 &  -2.53 (-1.00) & 18 \\ \hline
+\caption{Significance of extracted flux and detection limits\label{tab:det_lims}}  
+\begin{tabular}{lllll} \hline \hline
+Object & F$_{\rm{src}}$(\ion{Mg}{2})\footnote{\ion{Mg}{2} flux is in $10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$.
+The value in the parenthesis is the statistical significance with respect to $\sigma_{\text{src}}$ } & 5SB$_{\text{limit}}$\footnote{Limits are in $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$} & Area\footnote{Area of the extended annulus in sq.arcsec} \\  \hline
+J033225.26-274524.0 &  2.44(0.92)& 6.51	& 21 \\
+J033232.36-274725.0 &  -1.40(-0.53)& 6.51 & 21 \\
+J033230.03-274347.3 &  -5.23(-1.75)& 5.74 & 27 \\
+J033229.64-274242.5 &  1.23 (0.44) & 6.22  &26 \\
+J033230.57-274518.2 &  -2.53 (-1.00) & 6.81 &18 \\ \hline
 \end{tabular}
@@
 
-In order to show that our detection limits are reasonable, we create simulated emission with varying intensities to see if we can visually detect any \ion{Mg}{2} emission.
-The results of this exercise are shown in Figure \ref{fig:sigmas} For each galaxy, we assume a constant surface brightness corresponding to an excess of surface brightness 0, 1, 3, 5, 10 and 20 times the $1\sigma$ SB$_{\text{limit}}$ inside the largest annulus used.
-Additionally, we assume gaussian noise with a variance equal to 1SB$_{\text{limit}}$.
+\subsection{Test of Surface Brightness Limits}\label{subsec:test}
+In order to show that our detection limits are reasonable, we simulate emission with varying intensities.
+The results of this exercise are shown in Figure \ref{fig:sigmas}.
+For each galaxy, we assign our simulated emission a constant surface brightness corresponding to 0, 1, 3, 5, 10 and 20 times the $1\sigma$ SB$_{\text{limit}}$ inside the largest annulus used (i.e., the extended annulus).
+Additionally, we assume Gaussian noise with 1$\sigma$ equal to 1SB$_{\text{limit}}$.
 After placing the simulated emission around the galaxy, we subtract the continuum in the same manner as explained in Section \ref{sec.cont_sub}.
-To test the detectability of measuring extended emission we construct a smoothed $\chi$ image following the technique in \cite{Hennawi2013} and \cite{Battaia_2015}.
-First, we smooth the continuum-subtracted image:
+
+We then construct a smoothed $\chi$ image following the techniques in \cite{Hennawi2013} and \cite{Battaia_2015}. First, we smooth the continuum-subtracted image:
 
@@
 
-Figure \ref{fig:sigmas} shows the $\chi_{\text{smth}}$ image for the synthetic \ion{Mg}{2} emission.
-Galaxies are outlined by a black isophotal contour corresponding to 1SB$_1$ and the simulated emission is contained inside an annulus surrounding the contours.
+Figure \ref{fig:sigmas} shows the $\chi_{\text{smth}}$ images for the 5 levels of simulated \ion{Mg}{2} emission.
+We also include the $\chi_{\text{smth}}$ image of each galaxy without any simulated emission (in the left most column).
+Galaxies are outlined by a black isophotal contour corresponding to 1SB$_1$ and the simulated emission is contained inside an annulus surrounding each contour.
 The  $\chi_{\text{smth}}$ images confirm that we should be able to detect extended \ion{Mg}{2} emission down to a conservative level of 5SB$_{\text{limit}}$.
@@
 
-\begin{table}[]
-\centering
-%\begin{minipage}{4.5in}
-\caption{Empirically Determined Detection Limits \label{tab:det_lims}}  
-\begin{tabular}{llll} \hline \hline
-Object & 5SB$_{\text{limit}}$\footnote{Limits are in $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$} &Area\footnote{Area of the extended annulus in sq.arcsec} \\  \hline
-J033225.26-274524.0 &  6.51 & 21 \\
-J033232.36-274725.0 & 6.51 & 21 \\
-J033230.03-274347.3 & 5.74 & 27 \\
-J033229.64-274242.5 & 6.22  & 26 \\
-J033230.57-274518.2 & 6.81 & 18 \\ \hline
-\end{tabular}
+%\begin{table}[]
+%\centering
+%%\begin{minipage}{4.5in}
+%\caption{Empirically Determined Detection Limits \label{tab:det_lims}}  
+%\begin{tabular}{llll} \hline \hline
+%Object & 5SB$_{\text{limit}}$\footnote{Limits are in $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$} &Area\footnote{Area of the extended annulus in sq.arcsec} \\  \hline
+%J033225.26-274524.0 &  6.51 & 21 \\
+%J033232.36-274725.0 & 6.51 & 21 \\
+%J033230.03-274347.3 & 5.74 & 27 \\
+%J033229.64-274242.5 & 6.22  & 26 \\
+%J033230.57-274518.2 & 6.81 & 18 \\ \hline
+%\end{tabular}
 %\end{minipage}
-\end{table}
+%\end{table}
 
@@
 Each postage stamp has a size of $5'' \times 5''$ (corresponding to $35$ kpc $\times$ $35$ kpc at $z\sim 0.70$).
-Each stamp shows the galaxy along with the same isophotal contour used in previous figures.
-Comparing the $0$SB$_{\text{limit}}$ column with the continuum-subtracted images in Figure \ref{fig:stamp_images} suggests that we did not detect any \ion{Mg}{2}\ emission.}
+Each stamp shows the galaxy along with the same isophotal contour used in previous figures.}
 \label{fig:sigmas}
@@
 \subsection{Equivalent Widths}\label{subsec.ew}
-Here we derive an expression to calculate the equivalent width (EW) of any absorption or emission features observed in our narrow-band imaging.
+Here we derive an expression to calculate the equivalent width (EW$_{\rm{MgII}}$) of any absorption or emission features observed in our narrow-band imaging.
 Starting from the expression for EW used in the context of spectroscopy,
 \begin{equation}
-EW=\int (1-\frac{f_{line}}{f_{cont}})d\lambda
+EW_{\lambda}=\int (1-\frac{f_{\lambda}}{f_{\rm{cont}}})d\lambda
 \label{eq:specEW}
@@
 \begin{equation}
-\frac{F_{line}}{f_{cont}\Delta \lambda_{MgII}}=\frac{F_{MgII}}{f_{cont}\Delta \lambda_{MgII}}- 1.
+\frac{F_{\lambda}}{f_{\rm{cont}}\Delta \lambda_{\rm{MgII}}}=\frac{F_{\rm{MgII}}}{f_{\rm{cont}}\Delta \lambda_{\rm{MgII}}}- 1.
 \end{equation}
-Next, we rearrange the above expression such that we produce the argument of the integrand in Eq. \ref{eq:specEW} on the RHS,
+Next, we rearrange the above expression such that we produce the argument of the integrand in Eq. \ref{eq:specEW} on the right hand side,
 \begin{equation}
--\frac{F_{line}}{f_{cont}\Delta \lambda_{MgII}}=1-\frac{f_{MgII}}{f_{cont}}.
+-\frac{F_{\lambda}}{f_{\rm{cont}}\Delta \lambda_{\rm{MgII}}}=1-\frac{f_{\rm{MgII}}}{f_{\rm{cont}}}.
 \end{equation}
-We then approximate the integration in Eq. \ref{eq:specEW} by multiplying the integrand above by the FWHM of the on-line filter $d\lambda=\Delta \lambda_{MgII},$
+We then approximate the integration in Eq. \ref{eq:specEW} by multiplying the integrand above by the FWHM of the on-line filter $d\lambda=\Delta \lambda_{\rm{MgII}},$
 \begin{equation}
--\frac{F_{line}}{f_{cont}}=(1-\frac{f_{MgII}}{f_{cont}})\Delta \lambda_{MgII};
+-\frac{F_{\lambda}}{f_{\rm{cont}}}=(1-\frac{f_{\rm{MgII}}}{f_{\rm{cont}}})\Delta \lambda_{\rm{MgII}};
 \end{equation}
@@
 \begin{equation}
-EW=-\frac{F_{line}}{f_{cont}}.
+EW_{\rm{MgII}}=-\frac{F_{\rm{MgII}}}{f_{\rm{cont}}}.
 \end{equation}
 
-Using the above equation along with the continuum and continuum-subtracted images, we produce images of the EWs.
-The EW images are displayed in Figures \ref{fig:ew11}, \ref{fig:ew22}, \ref{fig:ew33}, \ref{fig:ew44}, \ref{fig:ew55}, and show only the EWs within the 1$\sigma$ SB$_1$ contours of the corresponding \ion{Mg}{2} images (prior to continuum subtraction).
+Using the above equation along with the continuum and continuum-subtracted images, we produce images of the observed-frame EW$_{\rm{MgII}}$'s.
+The observed-frame  EW$_{\rm{MgII}}$images are displayed in Figures \ref{fig:ew11}, \ref{fig:ew22}, \ref{fig:ew33}, \ref{fig:ew44}, \ref{fig:ew55},[\textbf{WILL CONSOLIDATE THESE FIGURES}] and show only the EWs within the 1$\sigma$ SB$_1$ contours of the corresponding \ion{Mg}{2} images (prior to continuum subtraction).
 
-To compare our map of EWs to the values measured from the Keck/LRIS spectra, we place 0.9 arcsec wide apertures on top of each galaxy.
+To compare our map of EW$_{\rm{MgII}}$'s to the values measured from the Keck/LRIS spectra, we place 0.9 arcsec wide apertures on top of each galaxy.
 The width and angle of the apertures replicate the orientation of the slits used to obtain the spectra.
-Next, we determine which pixels lie outside the 1$\sigma$ SB$_1$ contours and set those to zero.
-Outside this contour, the EWs become poorly constrained due to the lack of S/N in the continuum.
-We then apply a S/N $= 1.5$ cut to the continuum image and create a histogram to show the distribution of EWs as shown in Figures \ref{fig:ew1} through \ref{fig:ew5}.
-Having removed EWs with low-S/N continuum values from our images, we compute the mean equivalent width inside the Keck/LRIS apertures.
+Next, we determine which pixels lie outside the 1$\sigma$ SB$_1$ contours and set their values to zero.
+Outside this contour, the EW$_{\rm{MgII}}$'s become poorly constrained due to the lack of S/N in the continuum.
+We then apply a S/N $= 1.5$ cut to the continuum image and create a histogram to show the distribution of EW$_{\rm{MgII}}$'s inside the contour.
+The histograms are shown in Figures \ref{fig:ew11} through \ref{fig:ew55}.
+Having removed EW$_{\rm{MgII}}$'s with low-S/N continuum values from our images, we compute the mean equivalent width inside the Keck/LRIS apertures.
 These values are summarized in Table \ref{tab:abs_props}.
 
-In order to get information on the morphology of the \ion{Mg}{2}, we determine the distance of each pixel from the center of each galaxy in kiloparsecs.
-We plot the EWs over this projected distance for each galaxy in Figures \ref{fig:ew1} through \ref{fig:ew55}.
-Although some of the plots suggest a slight upward trend in the values of the EW at increasingly large radii, we cannot be confident in this trend because of large scatter.
-To better visualize the data and test the significance of the trend, we bin the data radially.
-For example, in Figure \ref{fig:ew44}, the EW from absorption extends out to $\sim$ 25 kpc.
-The EWs are binned in 5 kpc increments.
-We calculate the mean and scatter of the EWs in each bin and show these values in Figure \ref{fig:ew_comb}.
+To assess the morphology of the \ion{Mg}{2} absorption, we determine the distance of each pixel from the center of each galaxy in kiloparsecs.
+We plot the EW$_{\rm{MgII}}$'s over this projected distance for each galaxy in Figures \ref{fig:ew11} through \ref{fig:ew55}.
+Although some of the plots suggest a slight upward trend in the values of the EW$_{\rm{MgII}}$ with increasing radii, we cannot be confident in this trend because of the large scatter.
+To better visualize the data and test the significance of the trend, we bin the data radially in 3-5 kpc bins.
+For example, in Figure \ref{fig:ew44}, the EW$_{\rm{MgII}}$ from absorption of J033230.03 extends out to $\sim$ 25 kpc.
+The EW$_{\rm{MgII}}$'s are binned in 5 kpc increments.
+We calculate the mean and scatter of the EW$_{\rm{MgII}}$'s in each bin and show these values in Figure \ref{fig:ew_comb}.
 
-\section{Discussion}\label{sec.results}
-In this chapter we present the results from the continuum-subtraction of the off-line continuum filter to that of the on-line emission filter.
+\section{Results}\label{sec:results}
 
-\subsection{Limits on MgII emission}
+\subsection{Spatially Resolved Maps of \ion{Mg}{2} Absorption}
+In this section we discuss the details of the absorption detected in our SB profiles as well as compare our EW$_{\rm{MgII}}$ measurements to those measured in the supplemental Keck/LRIS spectra.
 
-We do not detect any significant amount of \ion{Mg}{2} emission in any of our sampled galaxies.
+\subsubsection{\ion{Mg}{2}\ absorption in surface brightness profiles}
+Although we do not detect any extended \ion{Mg}{2} emission, we do observe a decrement of flux in the SB profiles of 4 out of 5 galaxies in our sample.
+Figure \ref{fig:sb_profiles} shows the SB profiles for the 5 galaxies in our sample.
+Absorption from \ion{Mg}{2} ions is prevalent in the profiles between 10 - 25 kpc, decreasing radially outward from the maximum absorption at the center of the galaxies.
+In Table \ref{tab:abs_props} we report for the galaxies: J033225.26, J033231.36 and J033230.03 a maximum decrement in the SB profile due to absorption $\sim$ -5.00$\times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
+Additionally, we report for galaxy J033229.64 a decrement one order of magnitude greater then the previous galaxies with a value of -18.2 $\pm$ 0.127 $\times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
+Finally, for galaxy J033230.57 the absorption decrement is strongest at the center of the galaxy with a SB value of -1.25 $\pm$ 1.15 $10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
+However, the measured SB of this decrement including error is consistent with measuring zero absorption.
+The measurement of zero absorption for J033230.57 was expected.
+Figure \ref{fig:spec_images} shows the KECK/LRIS spectrum of J033230.57 and the transmission curves of the filters HeII+47 and HeII/3000+48.
+The \ion{Mg}{2} transitions of the galaxy are equally sampled by both of our filters.
+When we subtract the continuum image from the \ion{Mg}{2} image we are effectively subtracting the \ion{Mg}{2} as well.
+This measurement suggests that the quality of our subtraction is satisfactory.
+Because of the lack of absorption we exclude this galaxy from our discussion.
+
+The surface brightness profiles presented in Figures \ref{fig:sb_profiles} do not exhibit any signs of extended \ion{Mg}{2} emission.
+
+\subsubsection{Morphology of MgII Absorption}
+Figures \ref{fig:ew11} through \ref{fig:ew55} show the images, distributions and radial projections of \ion{Mg}{2} EWs.
+We have zeroed out any values that lie outside the SB$_1$ contours for each galaxy.
+We also impose a signal-to-noise cut, only including EWs where the continuum S/N is greater than $1.5$.
+The mean EW is computed for all pixels inside each Keck/LRIS aperture, defined in Sec.
+\ref{subsec.ew}, and the resulting values are summarized in Table \ref{tab:abs_props}.
+Comparing our narrowband EWs with those measured from the spectra, we find good agreement to within a few $\sigma$ for galaxies J033225.26 and J033232.36, and statistically significant differences for galaxies J033230.03, J033229.64 and J033230.57.
+We discuss possible causes for these differences below.
+
+Figure \ref{fig:spec_images}(c) shows the Keck/LRIS spectrum of galaxy J033230.03.
+The continuum observed near the \ion{Mg}{2} transition is noisy, compared to the spectra of the rest of the sample.
+Since the value of the EW is dependent on the level of the continuum present near the \ion{Mg}{2} transition, it may well be that our choice of continuum level in calculting the EW from the spectrum might be over-estimating the EW of the doublet.
+
+Figure \ref{fig:spec_images}(d) shows the Keck/LRIS spectrum of galaxy J033229.64.
+This galaxy is the brightest galaxy in the sample, suggestive of a bright ISM, which causes the redder transition to almost leak out of the HeII+47 transmission curve.
+This suggests that it our \ion{Mg}{2} images are not measuring the most redward absorption feature, thus underestimating the value of the EW.
+
+In the case of J033230.57 we can easily understand why the EW measured is not in agreement with the spectral EW.
+Figure \ref{fig:sb_profiles}  shows the SB profile coverage of J033230.57.
+In this galaxy's profile we do not detect any significant SB decrements, due to absorption, as the two filters cover the \ion{Mg}{2} as discussed above.
+Any signal of absorption in the EW images arises from noise.
+Figure \ref{fig:ew5} shows that the radial projection of the EWs measured for this galaxy that are centered around zero.
+
+To get a better sense of how the EW of \ion{Mg}{2} absorption changes with radius as well as account for the effects of seeing, $FWHM \sim 7 kpc$, we bin the EWs in radial bins with 5, 4 or 3 kpc widths as shown in Figures \label{fig:ew1} through \label{fig:ew5}.
+A majority of the galaxies exhibit large scatter in the binned EWs out to larger radii.
+To better understand the significance of these trends, we construct a plot that compiles the mean EWs for all the galaxies, shown in Figure \ref{fig:ew_comb}.
+To take into account the varying size of the galaxies, we normalize the distances by the approximate radius of the SB$_1$ contour for each galaxy.
+
+Upon inspection of Figure \ref{fig:ew_comb}, we see that all the galaxies exhibit a constant mean EW inside our 1SB$_1$ isophotal radius, and suggestive that the covering fraction is also constant across the surface.
+
+\subsection{Limits on MgII Emission}
+We do not detect any significant amount of \ion{Mg}{2} emission in any of our target galaxies.
 The $\chi_{\text{smth}}$ images shown in Figure \ref{fig:sigmas} confirm this.
-A comparison of the simulated emission with the $\chi_{\text{smth}}$ image of the original stamps, shown in the first column, similarly suggests that we do not detect any extended \ion{Mg}{2} emission.
-We thus place conservative $5\sigma$ upper limits on \ion{Mg}{2} emission for each galaxy in the sample, summarized in Table \ref{tab:det_lims}.
+A comparison of the simulated emission with the $\chi_{\text{smth}}$ image of the original continuum-subtracted image, shown in the first column, similarly suggests that we do not detect any extended \ion{Mg}{2} emission.
+We thus place $5\sigma$ upper limits on \ion{Mg}{2} emission for each galaxy in the sample, summarized in Table \ref{tab:det_lims}.
 The most sensitive detection limit using the largest area is SB(\ion{Mg}{2}) = 5.74 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$, computed for the galaxy J033230.03.
@@
 
-\subsection{Previous Detections of extended \ion{Mg}{2} emission}
+\section{Discussion}\label{sec:discussion}
+
+\subsection{Previous Detections of Extended \ion{Mg}{2} Emission}
 Previous constraints on the brightness of scattered \ion{Mg}{2} emission were reported by \cite{Rubin_2011}.
 In this work the authors studied emission from the starburst galaxy TKRS 4389 at $z = 0.69$ with a star formation rate of $49.8\msunperyr$.
-This emission was detected in a 2-dimensional KECK/LRIS spectrum, with flux from the emission reaching $8.0 \pm 0.4$ and $4.4 \pm 0.4$ $\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at  $\lambda _{2796}$ and $4.0 \pm 0.3$ and $2.5 \pm 0.4$ $\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at $\lambda_{2803}$ in two independent locations spatially offset from the galaxy continuum.
+This emission was detected in a 2-dimensional Keck/LRIS spectrum, with flux from the emission reaching $(8.0 \pm 0.4)$ and $(4.4 \pm 0.4)$ $\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at  $\lambda _{2796}$ and $(4.0 \pm 0.3)$ and $(2.5 \pm 0.4)$ $\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at $\lambda_{2803}$ in two independent locations spatially offset from the galaxy continuum.
 The flux from the emission can be converted into two surface brightness values by taking the average of the flux measured at each location and each transition, and dividing by a 1 sq.arcsec aperture.
 
-Figure \ref{fig:detection_lim} shows a plot of the 5$\sigma$ detection limits determined for each galaxy in our sample as well as the SB calculated for the galaxy TKRS 4389.
+Figure \ref{fig:detection_lim} shows a plot of the 5$\sigma$ detection limits determined for each galaxy in our sample as well as the SB calculated for the galaxy TKRS 4389 vs SFR.
 The figure suggests that we should be able to detect scattered \ion{Mg}{2} emission with strengths similar to that detected in TKRS 4389.
-Given if  additional detections of extended \ion{Mg}{2} emission are made, it could be possible that there exists the possibility of a relationship between SB and star-formation rate, as the study by \cite{Erb2012} discuss that emission strength is stronger in high mass galaxies.
+Taken at face value the figure is consistent with a positive correlation between \ion{Mg}{2} SB and SFR.
+
+%The study by \cite{Erb2012} discuss that emission strength is stronger in low mass galaxies.
 This could be one explanation as to why we did not detect any extended \ion{Mg}{2} emission Further studies need to be pursued to add additional points to Figure \ref{fig:detection_lim}.
@@
 
-\subsection{Geometry of re-emitted photons}
-In idealized wind models of cool gas outflows, discussed in \cite{Prochaska_2011}, strong \ion{Mg}{2} emission is predicted to be generated along with ubiquitous blueshifted absorption of \ion{Mg}{2}.
-For isotropic and dust-free scenarios, this absorption and emission is simply produced by the conservation of photons, as any absorbed continuum photon is eventually re-emitted in emission.
-Because of this photon exchange the total equivalent width of both the absorption and emission features is equal to zero.
-Assuming that our galaxies host an isotropic and dust-free wind, we wish to determine how much emission is predicted to be missing from our imaging, and how the SB of this missing emission compares to our detection limits, for different distributions of emission.
+\subsection{Geometry of Scattering Materials}
+In idealized wind models of cool gas outflows, discussed in \cite{Prochaska_2011}, radiative transfer calculations suggest that strong \ion{Mg}{2} emission is predicted to be generated along with ubiquitous blueshifted absorption of \ion{Mg}{2}.
+For isotropic and dust-free scenarios, photons are conserved, as any absorbed continuum photon is eventually re-emitted, most likely at a different rest wavelength, therefore the total equivalent width of both the absorption and emission feature is equal to zero in such modes.
+Assuming that our galaxies host an isotropic and dust-free wind, we wish to determine how much emission is predicted to be generated by this wind, and how the SB of this emission compares to our detection limits.
 
-To find the amount of missing emission, we first calculate how much continuum has been absorbed by \ion{Mg}{2}.
-Using our Keck/LRIS spectra, we find the average value of the continuum near the \ion{Mg}{2} doublet and multiply this value by the EW of the doublet.
-Although we know how much emission is missing, we do not know how this emission is distributed outside the galaxy.
-As a conservative estimate of the SB, we distribute the missing emission uniformly inside multiple and increasingly sized annuli.
-These annuli are fixed to have an inner radius equal to the galaxy's isophotal radius and an increasing outer radius.
+To calculate the predicted emission flux we first determine the flux absorbed by \ion{Mg}{2} ions.
+Using our Keck/LRIS spectra, we find the average value of the continuum near the \ion{Mg}{2} doublet and multiply this value by the observed EW of the doublet.
+Then to estimate the SB, we distribute this flux uniformly inside multiple annuli of varying sizes.
+These annuli all have an inner radius equal to the galaxy's isophotal radius and successively larger outer radii.
 Additionally, since our SB limits are dependent on the size of the aperture used, we calculate the SB detection limits of our images inside each of the aforementioned annuli.
-Figure \ref{fig.emission} shows how the SB of emission varies with the spatial extent of the annulus, as well as how the SB compares with our detection limits.
-Excluding the galaxy J033230.03, the SB of this missing emission lie above our detection limits.
-This result shows that these galaxies do not host an isotropic dust-free wind.
+Figure \ref{fig.emission} shows how the SB of emission varies with the spatial extent of the annulus (black squares), as well as how the SB compares with our detection limits (thin black curve).
+Excepting the galaxy J033230.03, the SB of this missing emission lie above our detection limits.
+Without taking into account that the emission may not exceed to a radial extent outside the galaxy disk, this result suggests that these galaxies do not host an isotropic dust-free wind.
 
-There are many phenomena that we can employ to reduce the SB of the missing \ion{Mg}{2} emission to better match our observations.
-Introducing dust into the wind can reduce the observed emission as it can change the observed line profile in a critical way as re-emitted photons have to travel farther distances to escape the wind and therefore the profile will suffer greater extinction.
+There are many phenomena that may reduce the SB of the scattered \ion{Mg}{2} emission so that it is consistent with our observations.
+Introducing dust into the wind can reduce the observed emission strength, and shape in the line profile.
+In the absense of dust, the back scattered \ion{Mg}{2} photon can escape the galaxy free of collisions.
+With dust, the photons are susceptible to a number of collisions, with a greater possibility of being absorbed by dust.
+In the \cite{Prochaska_2011} radiative models with increasing dust, the dominant effect that dust has on the \ion{Mg}{2} transitions is that the dust suppresses the most redshifted emission.
+The strength of the flux is reduced by a factor of $(1+\tau_{\rm{dust}})^{-1}$, where $\tau_{\rm{dust}}$ is the integrated opacity of dust.
+
 Another factor that can reduce the amount of emission is anisotropy of the wind.
@@
 However, the SB profile of J033229.64 remains above our SB detection limits, suggesting additional phenomena are needed to reduce the strength of missing emission.
-
-\subsection{Spatially Resolved Maps of \ion{Mg}{2} Absorption}
-In this section we discuss the details of the absorption detected in our images and compare our measurements to those obtained in the Keck/LRIS spectra of each galaxy..
-
-\subsubsection{\ion{Mg}{2}\ absorption in surface brightness profiles}
-Although we do not detect any extended \ion{Mg}{2} emission, we do observe a decrement of flux in the SB profiles of 4 out of 5 galaxies in our sample.
-
-\subsubsection{J033225.26} 
-Figure \ref{fig:sb_profiles} shows the SB profile for J033225.26.
-We report that the maximum decrement in the SB profile due to absorption is strongest at the center of the galaxy.
-The SB measured in the center aperture is -5.39 $\pm$ 0.128 $\times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
-The absorption in the profile decreases radially outward and is detected out to the largest distance sampled, $\sim 18$ kpc, away from the center of the galaxy.
-
-\subsubsection{J033231.36} 
-Figure \ref{fig:sb_profiles} shows the SB profile for J033231.36.
-We report that the maximum decrement in the SB profile due to absorption is strongest at the center of the galaxy.
-The SB measured in the center aperture is -5.64 $\pm$ 0.121 $\times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
-The absorption in the profile decreases radially outward and is detected out to the largest distance sampled, $\sim 18$ kpc, away from the center of the galaxy.
-
-\subsubsection{J033230.03} 
-Figure \ref{fig:sb_profiles} shows the SB profile for J033230.03.
-We report that the maximum decrement in the SB profile due to absorption is strongest at the center of the galaxy.
-The SB measured in the center aperture is -4.41 $\pm$ 0.622 $10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
-The absorption in the profile decreases radially outward and out to the largest distance sampled, $\sim 25$ kpc, away from the center of the galaxy.
-
-\subsubsection{J033229.64} 
-Figure \ref{fig:sb_profiles} shows the SB profile for J033229.64.
-We report that the maximum decrement in the SB profile due to absorption is strongest at the center of the galaxy.
-The SB measured in the center aperture is -18.2 $\pm$ 0.127 $\times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
-The absorption in the profile decreases radially outward and is detected out to the largest distance sampled, $\sim 14$ kpc, away from the center of the galaxy.
-
-\subsubsection{J033230.57} 
-Figure \ref{fig:sb_profiles} shows the SB profile for J033230.57.
-The absorption decrement is strongest at the center of the galaxy with a SB value of -1.25 $\pm$ 1.15 $10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
-However, the measured SB of this decrement including error is consistent with measuring zero absorption.
-The measurement of zero absorption for J033230.57 was expected.
-Figure \ref{fig:spec_images} shows the KECK/LRIS spectrum of J033230.57 and the transmission curves of the filters HeII+47 and HeII/3000+48.
-The \ion{Mg}{2} transitions of the galaxy are equally sampled by both of our filters.
-Simply put, each image of J033230.57 contains equal amounts of continuum and \ion{Mg}{2}.
-When we subtract the continuum image from the \ion{Mg}{2} image we are effectively canceling out the \ion{Mg}{2} absorption as well.
-This measurement can stand as a test of the quality of our continuum subtraction.
-\\
-
-The surface brightness profiles presented in Figures \ref{fig:sb_profiles} do not exhibit any signs of extended \ion{Mg}{2} emission. \\
+Previously discussed in Section \ref{sec:results}, this galaxy is the intrinsically brightest galaxy of our sample, which suggests a strong ISM component.
+\ion{Mg}{2} photons can be more effectively trapped with the combination of  \cite{Prochaska_2011}.
 
@@
 \begin{tabular}{llllll} \hline \hline
-Object & Max(SB$_{abs}$)\footnote{SB Values are in units of $10^{-18}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$} & $R_{\text{SB}_1}(kpc)$ &\ \ \ EW($\AA$)\footnote{ Measured from EW images} & EW($\AA$)\footnote{Measured from Keck/LRIS spectra}  \\  \hline
+Object & Max(SB$_{abs}$)\footnote{SB Values are in units of $10^{-18}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$} & $R_{\text{SB}_1}(kpc)$ &\ \ \ EW$_{\rm{obs}}$($\AA$)\footnote{ Measured from EW images} & EW$_{\rm{obs}}$($\AA$)\footnote{Measured from Keck/LRIS spectra}  \\  \hline
 J033225.26-274524.0 &  $-5.39 \pm 1.28 $ & 8 &     $\ \ \ 3.511 \pm 0.795$ & $7.539 \pm 0.354 $\\
@@
 \end{table*}
-\subsection{Morphology of MgII Absorption}
 
-Figures \ref{fig:ew1} through \ref{fig:ew5} show the EW images, distributions and radial projections of \ion{Mg}{2} EWs.
-We have zeroed out any EWs that lie outside the SB$_1$ contours for each galaxy.
-We imposed a signal-to-noise cut, only including EWs where the continuum flux S/N greater than $|1.5|$.
-The mean EW is computed for all pixels inside each Keck/LRIS aperture, defined in Sec.
-\ref{subsec.ew}, and are summarized in Table \ref{tab:abs_props}.
-Comparing our measured EWs with those measured from the spectra, we find good agreement to within 1$\sigma$ or 2$\sigma$ for most of the galaxies except and J033230.57.
-
-In the case of J033230.57 we can easily understand why the EW measured is not in agreement with the spectra EW.
-Figure \ref{fig:sb_profiles}  shows the SB profile coverage of J033230.57, in this galaxy's profile we do not detect any significant decrements due to absorption.
-This is due to the fact that our two filters cover the \ion{Mg}{2} doublet equally, see Figure  \ref{fig:spec_images}.
-Any signal of absorption in the EW images arise from noise.
-Figure \ref{fig:ew5} shows the radial projection of the EWs measure for this galaxy which are centered around zero.
-
-To get a better sense of how the EW of \ion{Mg}{2} absorption changes with radius as well as account for any effects due to seeing, $\sim 7 kpc$, we bin the EWs in radial bins with 5, 4 or 3 kpc widths as shown in Figures \label{fig:ew1} through \label{fig:ew5}.
-A majority of the galaxies appear to show large scatter in the EWs out to larger radii.
-To better understand the significance of these trends, we construct a plot that compiles the mean EWs for all the galaxies, shown in Figure \ref{fig:ew_comb}.
-To take into account the varying size of the galaxies, we normalize the distances by the approximate radius of the SB$_1$ contour for each galaxy.
-
-Upon inspection of Figure \ref{fig:ew_comb}, we see that all the galaxies exhibit a constant mean EW inside our 1SB$_1$ isophotal radius.
-
-\section{CONCLUSION}
-We presented the results from a narrowband imaging search for \ion{Mg}{2} emission in a sample of star-forming galaxies at a redshift of $z \sim 0.70$.
-Although we were unable to detect any measurable amount of \ion{Mg}{2} emission, we are able to report a conservative $5\sigma$ detection limit of  SB(\ion{Mg}{2}) = 5.74 $\times 10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$.
+\section{CONCLUSION}\label{sec:conclusion}
+We presented the results from a narrowband imaging search for \ion{Mg}{2} emission in a sample of star-forming galaxies at a redshift of $z \sim 0.70$ which are known to drive outflows in  \ion{Mg}{2}.
+We did not detect any \ion{Mg}{2} emission in this sample, and place a $5\sigma$ detection upper limit of SB(\ion{Mg}{2}) $\approx$ 5.74 $\times 10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$, measured in an extended annulus outside the largest galaxy.
 We detected a significant amount of \ion{Mg}{2} absorption in a total of 4 galaxies out of our 5 galaxy sample.
 Furthermore, our imaging allows us to generate spatially-resolved maps of \ion{Mg}{2} absorption in a distant galaxy sample for the first time.
-This absorption covered the center of the galaxies out to the SB$_1$ continuum + \ion{Mg}{2} isophotal radius, at approximately $\sim 22$ kpc, suggesting that the absorbing gas fully covers the stellar disks out to this distance.
+This absorption covered the center of the galaxies out to an isophotal radius defined by the SB$_1$ (1$\sigma$) depth of a continuum + \ion{Mg}{2} image, at approximately $\sim 22$ kpc, suggesting that the absorbing gas fully covers the stellar disks out to this distance.
 The measured EWs measured in these maps are in broad agreement with measured EWs using Keck/LRIS integrated slit spectroscopy.
-Additionally, our radial projections of the mean EW for our sample galaxies suggest that the EWs due to \ion{Mg}{2} are approximately constant out towards the edges of the galaxies.
+Additionally, our radial projections of the mean EW for our sample galaxies suggest that the EWs due to \ion{Mg}{2} are approximately constant across the galaxies surfaces.
 
-Finally, we compared our detection limits with estimated SB \ion{Mg}{2} emission, based on the radiative transfer models of \cite{Prochaska_2011}.
-We are able to rule out that the winds in our sample are isotropic, as our detection limits are suitable to detect the predicted emission.
-By assuming anisotropic winds, we were able to reduce the strength of the predicted emission to lie below our detection limit, albeit one galaxy that needs additional phenomena like dust to achieve non-detectability in our images.
+We compared our detection limits with the prediction of the radiative transfer models of \cite{Prochaska_2011}.
+We are able to rule out that the winds in our sample are isotropic and dust free, as our images are sufficiently sensitive to detect the predicted emission from such models.
+By assuming anisotropic winds, we were able to reduce the strength of the predicted emission to lie below our detection limit for 3 of our sample galaxies.
+Albeit one galaxy that needs additional phenomena like dust to reduce the SB of emission and be consistent with our observations.
 
@@
 Future observations of our galaxies in IFUs could perhaps shed light on this alternate scenario.
-
-\begin{figure*}
-\centering
-\gridline{\fig{../Figures/J033225_26.pdf}{0.5\textwidth}{(J033225.26)}
-          \fig{../Figures/J033231_36.pdf}{0.5\textwidth}{(J033231.36)}}
-\gridline{\fig{../Figures/J033230_03.pdf}{0.5\textwidth}{(J033230.03)}
-          \fig{../Figures/J033230_64.pdf}{0.5\textwidth}{(J033230.64)}}
-           \fig{../Figures/J033230_57.pdf}{0.5\textwidth}{(J033230.57)}
-\caption{SB profile for our sample galaxies.
-(Top) Continuum SB (black) measured for the galaxy in the continuum image.
-Mg II + continuum SB (green) measured for the galaxy in the pre-continuum subtracted image.
-Mg II line SB (blue) measured for the galaxy in the continuum subtracted line emission image.The profile exhibits SB decrements from \ion{Mg}{2} absorption.
-Photometry was performed in circular annuli.
-(Bottom) The vertical hashes in the bottom show the inner and outer radius of each annulus in kpc.
-Distance from the center of the galaxy (x-axis) is computed using the average value of each annulus inner and outer radii of each annuli.}
-\label{fig:sb_profiles}
-\end{figure*}
 
@@
 \centering
-\includegraphics[scale=0.9]{../Figures/J57EW.pdf}
-\includegraphics[scale=0.9]{../Figures/J57EW_2.pdf}
-\caption{Equivalent width images, distribution and radial projection for J033230.57.
-(Top Left) Stamp of the equivalent widths (EWs) inside the red 1SB$_1$ contour.
-The white contour represents the $0.9''$ aperture slit used to measure the equivalent width of absorption in the Keck/LRIS spectra.
-(Top Right) Distribution of absorption pixels with continuum flux S/N greater than 1.5 inside the slit aperture.
-(Bottom Left) The EWs of absorption projected in distance from center.
-(Bottom Right) Binned EW measurements.
-Each point represents the mean EW measured in 4 kpc wide bins.}
+\includegraphics[scale=1.1]{../Figures/J57EW.pdf}
+\includegraphics[scale=1.1]{../Figures/J57EW.pdf}
+\caption{\textbf{Example of new figure style, Need to create for remaining galaxies}}
 \label{fig:ew55}

### 2018-06-16 Manuscript/vaught_2017.tex

@@
 
-\author{Joseph Hennawi}
+\author{Joseph F. Hennawi}
 \affiliation{Department of Physics, Broida Hall, University of California, Santa Barbara, CA 93106-9530}
@@
 These observations probe extended \ion{Mg}{2} emission down to unmatched surface brightness limits of 5.74 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ (5$\sigma$).
-We do not detect any extended \ion{Mg}{2} emission in any of our galaxies, thus placing strong upper limits on the strength of \ion{Mg}{2} emission in the sample galaxies.
+We do not detect any extended \ion{Mg}{2} emission in any of our galaxies, thus placing strong upper limits on the strength of \ion{Mg}{2} emission at projected distances $R_{\perp} = 8-21$ kpc from the sample galaxies.
 Our observations allow us to create the first ever spatially-resolved map of \ion{Mg}{2} absorption, revealing approximately constant absorption strengths across the galaxy disks.
@@
 
-\keywords{galaxies: evolution, Galactic Winds}
+\keywords{galaxies: evolution, galaxies: absorption lines}
 
@@
 Outflows are detected by measuring the blueshift (outflow) or redshift (inflow) of absorption transitions with respect to the host galaxy systematic velocity.
-Spectroscopy of galaxies from low to high redshifts probing cold gas ($T \lesssim 10^4$ K) which absorbs in \ion{Na}{1} and cool gas ($T \sim 10^4$ K) in \ion{Mg}{2} has revealed outflows in most galaxies that host active star-formation (e.g.
+Spectroscopy of galaxies from low to high redshifts probing cold gas ($T \lesssim 10^2$ K) which absorbs in \ion{Na}{1} and cool gas ($T \sim 10^4$ K) in \ion{Mg}{2} has revealed outflows in most galaxies that host active star-formation (e.g.
 \citethnop{chen2010}; \citethnop{Martin2012}; \citethnop{Rubin_2014}).
@@
 Because the photons are redshifted, the photons will be able to travel freely towards the observer through the wind to produce emission at and redward of the systematic velocity of the galaxy (\citethnop{Rubin_2011}, \citethnop{Prochaska_2011}).
-Since the first detection of \ion{Mg}{2} emission by \citeth{Rubin_2011}, a further detection of extended \ion{Mg}{2} emission is found in \cite{Martin2013}, where they observe \ion{Mg}{2} emission that extends $12-18$ kpc for the galaxy 32016857 at $z=0.9392$.
-Additionally, \ion{Mg}{2} is found in 1D and IFU spectra (\citethnop{Erb2012} and Feltre et.
+Since the first detection of \ion{Mg}{2} emission by \citet{Rubin_2011}, another detection was reported by \cite{Martin2013}, who observed \ion{Mg}{2} emission that extends $12-18$ kpc from a strongly star-forming galaxy
+at $z=0.9392$.
+\ion{Mg}{2} has also been studied in wide-field galaxy surveys conducted with Keck/DEIMOS and VLT/MUSE  (\citethnop{Erb2012} and Feltre et.
 al (2018)).
-In these surveys of galaxies between with redshift $ 0.70 < z < 2.30$, \ion{Mg}{2} is detected in pure emission, pure absorption and with P-Cygni profiles.
-Detections of \ion{Mg}{2} in emission was found to be associated with galaxies of lower stellar mass and bluer spectral slopes.
+These surveys, which include galaxies with redshifts $ 0.70 < z < 2.30$, find that \ion{Mg}{2} may be detected in pure emission, pure absorption or with P-Cygni profiles.
+Detections of \ion{Mg}{2} in emission were found to be associated with galaxies of lower stellar mass and bluer spectral slopes.
 
-Various models of galactic winds are explored in \citethnop{Prochaska_2011}.
-This analysis involved generating spectra for the  \ion{Mg}{2} and  \ion{Fe}{2}$^*$ transitions, using a set of radiative transfer algorithms, for an isotropic and anisotropic set of dust and dust-free winds.
+The diversity of these spectral profiles may be understood using radiative transfer modeling of galactic winds.
+%Various models of galactic winds are explored in 
+\citet{Prochaska_2011} have used this technique to predict 
+%This analysis involved generating 
+spectra for the  \ion{Mg}{2} and  \ion{Fe}{2}$^*$ transitions for a variety of wind morphologies.
+%, using a set of radiative transfer algorithms, for an isotropic and anisotropic set of dust and dust-free winds. 
 The authors demonstrated that isotropic dust-free winds will conserve photon flux, thus predicting that blueshifted absorption lines should be accompanied by emission profiles of winds with similar equivalent widths (EW).
-Anisotropic winds however were demonstrated to significantly weaken emission at strengths proportional to the angular extent of the wind.
-The scattered emission was additionally weakened by the inclusion of dust and the affect of a strong interstellar medium (ISM).
+Anisotropic winds, however, were demonstrated to exhibit significantly weaker emission at strengths proportional to the angular extent (i.e., solid angle) of the wind.
+The scattered emission was additionally weakened by the inclusion of dust and the presence of a strongly-absorbing interstellar medium (ISM).
+Thus, spatially-resolved measurement of the surface brightness of this emission constrains not only the radial extent of the emitting material, but also its morphology and dust content.
 
-In this paper, we present the first narrowband imaging of \ion{Mg}{2} line emission around 5 star-forming  galaxies located in the deep Great Observatories Origins Deep Survey south (GOODS-S) field at redshift $z \sim 0.7$.
-The value in using narrowband imaging is the ability to spatially resolve any absorption and emission from a galaxy.
-We use two filters: a line filter and a continuum filter.
-The line filter covers the \ion{Mg}{2} doublet, while the continuum filter is off-set from line filter.
-The continuum filter will allow us to observe the continuum level of the galaxy near the \ion{Mg}{2} doublet.
+In this paper, we present the first narrowband imaging of the \ion{Mg}{2} transition around 5 star-forming  galaxies located in the Great Observatories Origins Deep Survey south (GOODS-S) field at redshift $z \sim 0.7$.
+%The value in using narrowband imaging is the ability to spatially resolve any absorption and emission from a galaxy. 
+We use two filters: a line filter and a continuum filter. The line filter covers the \ion{Mg}{2} doublet, while the continuum filter is offset from the line filter by ${\sim}47$ \AA.    
+The resulting imaging in each filter has a total integration time of 10 hrs.
+%The continuum filter allows us to observe the continuum level of the galaxy near the \ion{Mg}{2} doublet.
 With the resulting images taken using the two filters, we can subtract the continuum image from the \ion{Mg}{2} image, effectively creating an image that contains only photons from \ion{Mg}{2}.
-Contrary to 1D spectra, the narrowband imaging has the ability to measure the surface brightness, optical depth and radial extent of a wind.
-This narrowband imaging will allow us to create the first ever spatially resolved map of \ion{Mg}{2} emission.
+As opposed to 1D spectra, the narrowband imaging constrains the surface brightness, optical depth and radial extent of the wind.
+This narrowband imaging allows us to create the first ever high-S/N spatially resolved map of \ion{Mg}{2} emission and absorption.
 
-In Section \ref{sec:obs_red} we describe our sample of GOOD-S galaxies, Keck/LRIS spectra as well as our VLT/FORS2 observations, imaging, and absolute flux calibration.
-We go into detail in our method of image subtraction in Section \ref{sec.cont_sub}.
-The analysis of these data are included in Section \ref{sec:analysis}, in detail we discuss the production surface bright profiles and limits for each galaxy, as well as the production of narrowband measured equivalent widths.
-Section \ref{sec:results} contains the results from our narrowband imaging analysis.
-We compare our SB detections limits to previous detections of extended \ion{Mg}{2} emission, additionally we compare our observations to predictions made by radiative transfer models in Section \ref{sec:discussion}.
+In Section \ref{sec:obs_red} we describe our sample of GOOD-S galaxies, supplemental Keck/LRIS spectra, as well as our VLT/FORS2 observations, image reduction, and absolute flux calibration.
+We go into detail in our method of continuum subtraction in Section \ref{sec.cont_sub}.
+The analysis of these data is presented in Section \ref{sec:analysis},
+including our methods for calculating surface brightness profiles and detection limits for each galaxy, as well as maps of \ion{Mg}{2} equivalent widths.
+%in detail we discuss the production surface bright profiles and limits for each galaxy, as well as the production of narrowband %measured equivalent widths. 
+Section \ref{sec:results} presents results from our narrowband imaging analysis.
+We compare our SB detection limits to previous detections of extended \ion{Mg}{2} emission,  and compare our observations to predictions made by radiative transfer models in Section \ref{sec:discussion}.
 We conclude this paper in Section \ref{sec:conclusion}.
@@
 This peak is in fact the global maximum of the distribution, as all other bins of width $\Delta z = 0.02$ have at most four galaxies.
-Moreover, there are two narrow interference filters available on VLT/FORS2 centered at $\lambda \sim 468.4$ and 472.6 nm which cover the \ion{Mg}{2} $\lambda \lambda 2796, 2803$ transition in precisely this redshift interval.
+Moreover, there are two narrow interference filters available on VLT/FORS2 centered at $\lambda \sim 4675$ and 4722 \AA\ which cover the \ion{Mg}{2} $\lambda \lambda 2796, 2803$ transition in precisely this redshift interval.
 We selected our final sample of five of these galaxies at $0.66 < z < 0.68$ to be close on the sky such that they could be imaged in a single $7' \times 7' $ FORS2 pointing.
+We show color {\it HST}/ACS images of these objects in Figure~\ref{fig:hstims}.
 
@@
 \subsection{VLT/FORS2 Observations}
-Our barrow-band imaging data were taken in service-mode using the FORS2 instrument on the VLT 8.2m telescope Antu between October 2012 and February 2013. 
+Our narrow-band imaging data were taken in service-mode using the FORS2 instrument on the VLT 8.2m telescope Antu between October 2012 and February 2013. 
 We used two narrowband filters, HeII+47 and HeII/3000+48, that have peak transmission at wavelengths that correspond to the \ion{Mg}{2} doublet lines at our sample redshift of $z\sim0.7$ (see Table \ref{tab:filters}).
 The filter transmission curves are plotted along with each galaxy's spectrum in Figure~\ref{fig:spec_images}.
+In the following, we will often refer to the HeII+47 filter as the ``line'' or \ion{Mg}{2} filter and the HeII/3000+48 filter as the ``continuum'' filter.
 
-FORS2 has a pixel scale of $0.25''$ pixel$^{-1}$ and a field of view of $7'\times7'$ with $2 \times 2$ binning.
+FORS2 has a native pixel scale of $0.125''$ pixel$^{-1}$ and a field of view of $7'\times7'$.  The data were taken with 
+the CCD binned $2\times2$, yielding a pixel scale of $0.25''$ pixel$^{-1}$.
+Images of three pointings offset by $0.25\arcmin$ East/West were obtained, with individual exposure times of $\approx$ 1000 sec.  A total of 38  exposures were taken in each filter. 
 Our observations were carried out under photometric and thin cloud conditions (program ID: 090.A-0427A).
-The seeing (see Figure \ref{fig.seeing}) ranged from 0.5 arcsec to 2.5 arcsec.
-The data were taken with three pointings offset by 0.25' East/West with exposure times of $\approx$ 1000 s.
-A total of 38  exposures were taken in each filter.
+The seeing (see Figure \ref{fig.seeing}) ranged from $0.5\arcsec$ to $2.5\arcsec$.
 Summing the individual exposure times for each filter results in a combined exposure time of $10.0$ hours each for the HeII+47 and HeII/3000+48 filters.
@@
 \caption{Keck/LRIS spectra of the sample galaxies and the transmission curves of the filters HeII+47 (blue dashed line) and HeII/3000+48 (red dashed line) .
-The left-hand axis is in units of flux density and the right-hand axis is the percentage of light transmitted the filter at each wavelength.
-Vertical dashed lines indicate the wavelength of the redshifted \ion{Mg}{2}\ doublet.
-The \ion{Mg}{2}\ doublet falls fortuitously at the central wavelength of the HEII+47 filter.}
+The left-hand axis is in units of flux density and the right-hand axis is the percentage of light transmitted by the filter at each wavelength.
+Vertical dashed lines indicate the wavelengths of the redshifted \ion{Mg}{2}\ doublet.
+The \ion{Mg}{2}\ doublet falls fortuitously at the central wavelength of the HeII+47 filter for the galaxies shown in panels (a) through (d).}
 \label{fig:spec_images}
@@
 A $0.9''$ slit width was used for all slitmasks and the median FWHM resolution for the spectra is 274 km s$^{-1}$ at $\lambda_{\rm rest} \approx$ 2800 \AA\ and $286\mkms$  at $\lambda_{\rm rest}\approx$ 2600 \AA\ (see Figure \ref{fig:spec_images}).
+The spectral coverage of these data extends from ${\sim}3200$ to 8000 \AA.
 
@@
 The astrometry solutions were calculated via Astrometry.net (Lang et al.
-2010)\nocite{Lang}, yield a standard deviation in the galaxy coordinates of $\sigma \approx 0.10''$.
+2010)\nocite{Lang}, and yield a standard deviation in the galaxy coordinates of $\sigma \approx 0.10''$.
 Before image stacking, we ran each frame through \emph{SExtractor} \citeth{Bertin} in order to create a root mean square (RMS) map of each science image.
@@
 Each individual frame is first sky-subtracted using a background mesh size of 256 pixels which is approximately $64''$. 
-We chose the mesh size to be large enough such that the extended emission is not mistakenly subtracted (Arrigoni Battaia et al. 2015) \nocite{Battaia_2015}. 
+We chose the mesh size to be large enough such that the extended emission is not mistakenly subtracted (Arrigoni Battaia et al. 2015)\nocite{Battaia_2015}. 
 The frames, after background-subtraction, are resampled onto a common astrometric solution using a \textit{Lancosz3} interpolation kernel. 
-The images are average-combined and weighted by the night-flat image in order to increase the signal-to-noise of any \ion{Mg}{2} emission.
-Additionally, \emph{SWarp} generates a final set of RMS image from the night flats and the combination of RMS images for individual science frames.
+The images are weighted by the night-flat image and then  average-combined  in order to increase the signal-to-noise of any \ion{Mg}{2} emission.
+Additionally, \emph{SWarp} generates stacked RMS images by propagating the error images for each science frame.
+%weighting and average-combining the RMS images for individual science frames.
+ %from the night flats and the combination of RMS images for individual science frames. 
 Our final stacked images in each filter are shown in Figure~\ref{fig:stacked_image} with the target galaxies indicated.
@@
 \caption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}.
-The EW ( in the observed frame) include both components of the \ion{Mg}{2} doublet and were calculated with Eq.
-\ref{eq:specEW} and the supplemental Keck/LRIS spectra.}
+The EW (in the observed frame) include both components of the \ion{Mg}{2} doublet and were %calculated with Eq.
+\ref{eq:specEW} and
+determined from analysis of 
+the supplemental Keck/LRIS spectra.}
 \begin{tabular}{lllllll} \hline \hline
 Object & R.A. & Dec  & $z$ & SFR($M_{\odot}$ yr$^{-1}$) & $\log{M_{*}/M_{\odot}}$ & EW$_{\rm{obs}}$(\AA) \smallskip      \\ \hline 
-J033225.26-      & 03:32:25.26 & -27:45:23.9 & 0.6660 & $9.1_{-3.7}^{+1.3}$& $9.86_{-0.04}^{+0.05}$ & $7.539\pm 0.354$\\ 
-274524.0     & &  &  &         \\
-J033231.36-      & 03:32:31.35 & -27:47:24.9 &   0.6669 & $10.5_{-1.6}^{+1.7}$ & $10.02_{-0.03}^{+0.03}$&$5.835 \pm 0.493$\\
-274725.0      & &  &   &        \\
-J033230.03-      & 03:32:30.03 & -27:43:47.2  &   0.6679 & $3.8_{-0}^{+0}$ & $10.98_{-0.0}^{+0.01}$ &$12.794 \pm 1.710$\\
-274347.3      & &  &   &        \\
-J033229.64-      & 03:32:29.64 & -27:42:42.5 & 0.6671 & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &$13.239 \pm 0.263$\\
-274242.6     & &  &     &      \\
-J033230.57-      & 03:32:30.56 & -27:45:18.2 &   0.6807  & $12.6_{-2.1}^{+1.7}$ & $10.48_{-0.07}^{+0.03}$ &$6.106 \pm 0.370$ \\
-274518.2      & &  &  &         \\ \hline 
+J033225.26-274524.0      & 03:32:25.26 & -27:45:23.9 & 0.6660 & $9.1_{-3.7}^{+1.3}$& $9.86_{-0.04}^{+0.05}$ & $7.539\pm 0.354$\\ 
+%274524.0     & &  &  &         \\
+J033231.36-274725.0       & 03:32:31.35 & -27:47:24.9 &   0.6669 & $10.5_{-1.6}^{+1.7}$ & $10.02_{-0.03}^{+0.03}$&$5.835 \pm 0.493$\\
+%274725.0      & &  &   &        \\
+J033230.03-274347.3       & 03:32:30.03 & -27:43:47.2  &   0.6679 & $3.8_{-0}^{+0}$ & $10.98_{-0.0}^{+0.01}$ &$12.794 \pm 1.710$\\
+%274347.3      & &  &   &        \\
+J033229.64-274242.6      & 03:32:29.64 & -27:42:42.5 & 0.6671 & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &$13.239 \pm 0.263$\\
+%274242.6     & &  &     &      \\
+J033230.57-274518.2      & 03:32:30.56 & -27:45:18.2 &   0.6807  & $12.6_{-2.1}^{+1.7}$ & $10.48_{-0.07}^{+0.03}$ &$6.106 \pm 0.370$ \\
+%274518.2      & &  &  &         \\ 
+\hline 
 \end{tabular}
@@
 \section{Image Subtraction}\label{sec.cont_sub}
+We have two goals for our study: (1) assess the surface brightness of line emission in the \ion{Mg}{2} transition in and around each target galaxy; and (2) spatially resolve the morphology of the strong \ion{Mg}{2} absorption observed against the galaxy continua.
+To reach both of these goals, we must perform accurate subtraction of the continuum flux of each object from the filter covering the targeted line emission.
+For four of the five objects in our sample, the HeII+47 image includes both line and continuum emission, and the HeII3000+48 image provides a high S/N measurement of the continuum only $\approx30$ \AA\ redward of the line emission in the rest-frame.
 
@@
 In preparation for continuum subtraction, we first consider whether the continuum level of each galaxy spectrum changes significantly over the passbands of our two filters.
-We use the supplementary spectra from \citeth{Rubin_2014}, to fit the continuum and determine the spectral slope of each galaxy.
+We use the supplementary spectra from \citet{Rubin_2014} to fit the continuum and determine the spectral slope of each galaxy.
 We use the interactive fitting routine \emph{lt\_continuumfit} from the \emph{linetools} package (Prochaska et al.
 2016)\footnote{https://github.com/linetools/linetools}\nocite{Prochaska2016} to fit the continuum.
-We then find the total continnum flux in each filter by convolving the fitted continuum with each filter's transmission curve.
+We then find the total continuum flux in each filter by convolving the fitted continuum with each filter's transmission curve.
 Next, we take the ratio of both integrated totals, as the ratio will indicate the scaling factor needed to correct our flux measurements prior to continuum subtraction.
@@
 
-\subsection{Continuum Subtraction}
-To properly continuum-subtract the image taken with the on-line filter in excess of the continuum, we follow a prescription given by \cite{Battaia_2015}. 
-We first determine the continuum flux density from the off-\ion{Mg}{2} filter,
+\subsection{Continuum Subtraction}\label{subsec.cont_sub}
+
+To properly continuum-subtract the image taken with the \ion{Mg}{2} filter, we follow a prescription given by \cite{Battaia_2015}. 
+We first determine the continuum flux density from the continuum filter,
 \begin{equation}
@@
 where $F_{\rm{cont}}$ and $\Delta \lambda_{\rm{cont}}$ are the observed flux per pixel of the continuum image and the transmission FWHM of the continuum filter, respectively.
-With $f_{cont}$ it is then possible to calculate the flux of any excess emission, $F_{\rm{line}}$:
+With $f_{\rm cont}$ it is then possible to calculate the flux of any excess emission, $F_{\rm{line}}$:
 \begin{equation}
@@
 \end{equation}
-where $F_{\rm{MgII}}$ and $\Delta \lambda_{MgII}$ are the observed flux per pixel in the \ion{Mg}{2} filter and the transmission FWHM of the \ion{Mg}{2} filter.
-The continuum subtracted images of each galaxy are shown in Fig.
-\ref{fig:stamp_images}.
+where $F_{\rm{MgII}}$ and $\Delta \lambda_{\rm MgII}$ are the observed flux per pixel in the \ion{Mg}{2} filter and the transmission FWHM of the \ion{Mg}{2} filter.
+The continuum subtracted images of each galaxy are shown in Figure \ref{fig:stamp_images}.
 The continuum subtracted image has uniform background and no obvious signatures of emission.
@@
 \caption{ $10'' \times 10''$ images of each galaxy in our sample.
-Top row: Continuum surface brightness in ergs/s/cm$^2$/sq.arcsec.
-Bottom row: Continuum subtracted \ion{Mg}{2} surface brightness.
+Top row: Continuum surface brightness in ergs/s/cm$^2$/sq.arcsec measured in the HeII/3000+48 filter.
+Bottom row: Continuum-subtracted \ion{Mg}{2} surface brightness.
 Absorption can be seen in 4 of 5 galaxies.
-The red contours represent the outline of the 1$\sigma$ surface brightness limit in the HeII/3000+38 image, defined in Sec.
+The red contours represent the outline of the 1$\sigma$ surface brightness limit in the HeII/3000+48 image, defined in Sec.
 \ref{sec.sb}.
@@
 \section{Analysis} \label{sec:analysis}
-We have two goals for our study: (1) assess the surface brightness of line emission in the \ion{Mg}{2} transition in and around each target galaxy; and (2) spatially resolve the morphology of the strong \ion{Mg}{2} absorption observed against the galaxy continua.
-To reach the both of these goals, we must perform accurate subtraction of the continuum flux of each object from the filter covering the targeted line emission.
-For four of the five objects in our sample, the HeII+47 image includes both line and continuum emission, and the HeII3000+48 image provides a high S/N measurement of the continuum only $\approx30$ \AA\ redward of the line emission in the rest-frame.
-We detail below the resulting surface brightness profiles (Section~\ref{sec.sb}) and detection limits (Section \ref{subsec:test}) as well at the EW$_{\rm{MgII}}$ generated from these data (Section~\ref{subsec.ew}).
+%   We detail below the resulting surface brightness profiles (Section~\ref{sec.sb}) and detection limits (Section \ref{subsec:test}) as well at the EW$_{\rm{MgII}}$ generated from these data (Section~\ref{subsec.ew}).
 
@@
 \caption{SB profiles for our sample galaxies.
-(Top panel) Continuum SB (black) measured for each galaxy.
+(Top panel) Continuum SB profile (black) measured for each galaxy.
 The green points show the Mg II + continuum SB measured for the galaxy in the pre-continuum subtracted image.
-The blue points show the Mg II line SB measured for the galaxy in the continuum subtracted line emission image.The profile exhibits SB decrements from \ion{Mg}{2} absorption.
+The blue points show the Mg II line SB measured for the galaxy in the continuum subtracted line emission image.
+The profile exhibits SB decrements from \ion{Mg}{2} absorption.
 Photometry was performed in circular annuli.
@@
 
-The error in the SB is determined from the stacked RMS images of each object \textbf{SWarp}.
-We place annuli that are identical to the annuli used to find the SB profiles for each galaxy.
+The error in the SB is determined from the stacked RMS images of each object.
+We adopt annuli that are identical to the annuli used to find the SB profiles for each galaxy.
 To calculate the variance inside each annulus, we sum the RMS pixel values in quadrature, then divide by the area of each annulus.
@@
 We first mask out all the sources, their associated extended halos, and edge noise in both the HeII+47 and HeII/3000+48 images.
-We then calculate the RMS of the background in randomly-placed 1" apertures.
-We convert these RMS values to SB limits $per$ 1 sq.arcsec aperture.
-We find that the 1$\sigma$ detection limits per 1 arcsec$^2$ aperture (SB$_1$) are $6.332\times10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ and $5.808\times10^{-19} $ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ in the HeII/3000+48 and HeII+47 filters, respectively.
-With the 1$\sigma$ detection limit, SB$_1$, determined for the continuum+\ion{Mg}{2} (HeII) image, we define a thicker (or "extended") annulus to be used to search for any extended \ion{Mg}{2} emission.
+We then calculate the RMS of the background in randomly-placed $1\arcsec$ apertures.
+We convert these RMS values to SB limits per $1~\rm arcsec^2$  aperture.
+We find that the 1$\sigma$ detection limits %per 1 arcsec$^2$ aperture
+(SB$_1$) are $6.332\times10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ and $5.808\times10^{-19} $ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ in the HeII/3000+48 and HeII+47 filters, respectively.
+With the 1$\sigma$ detection limit, SB$_1$, determined for the continuum+\ion{Mg}{2} (HeII+47) image, we define a thicker (or ``extended") annulus to be used to search for any extended \ion{Mg}{2} emission.
 This extended annulus has an inner radius approximately the size of the SB$_1$ isophotal contour for each galaxy.
 The outer radius is chosen to be the inner radius plus 5 pixels.
+The sizes of these radii in kiloparsecs and the resulting SB measurements are also shown in Figure~\ref{fig:sb_profiles}.
 
@@
 In the ideal case that the sky and continuum are perfectly subtracted, the fluxes, $F_{\text{src}}$, from many random apertures should follow a Gaussian distribution with a width of $\sigma_{\text{src}} \equiv SB_{1}\sqrt{A_\text{src}}$.
-The distribution of $F_{\text{src}}$ for these apertures are shown in Figure \ref{fig:limits}.
-We calculate the variance and mean of the distribution and find that Gaussian width, $\sigma'_{\text{src}}=1.1$, of the distribution is broader than $\sigma_{\text{src}}$.
+The distribution of $F_{\text{src}}$ for these apertures is shown in Figure \ref{fig:limits}.
+We calculate the variance and mean of the distribution and find that the standard deviation, $\sigma'_{\text{src}}=1.1$, 
+implies that the SB detection limit for our continuum-subtracted image is broader than 
+ $\sigma_{\text{src}}$.
 We adopt $F_{\text{limit}} \equiv \sigma'_{\text{src}}$  as the $1 \sigma$ upper limit on the total line flux of extended \ion{Mg}{2} emission.
-The SB$_{\text{limit}}$ is just $F_{\text{limit}}/A_{\rm{src}}$.
+The SB$_{\text{limit}}$ is then $F_{\text{limit}}/A_{\rm{src}}$.
 The values of $F_{\text{src}}$ and the 5SB$_{\text{limit}}$ for each galaxy are listed in Table \ref{tab:det_lims}.
@@
 $F_{\text{src}}$ is the total flux within an aperture and $\sigma_{\text{src}}$ is the expected $1\sigma$ flux limit in the ideal case of perfect sky and continuum subtraction, i.e $SB_{1}\sqrt{A_\text{src}}$.
-The black arrows point to the statistical significance of the flux inside the "extended annulus" of each galaxy.}
+The black arrows point to the statistical significance of the flux inside the ``extended annulus'' of each galaxy.}
 \label{fig:limits}
@@
 The results of this exercise are shown in Figure \ref{fig:sigmas}.
-For each galaxy, we assign our simulated emission a constant surface brightness corresponding to 0, 1, 3, 5, 10 and 20 times the $1\sigma$ SB$_{\text{limit}}$ inside the largest annulus used (i.e., the extended annulus).
+For each galaxy, we assign our simulated emission a constant surface brightness corresponding to 1, 3, 5, 10 and 20 times the $1\sigma$ SB$_{\text{limit}}$ inside the largest annulus used (i.e., the extended annulus).
 Additionally, we assume Gaussian noise with 1$\sigma$ equal to 1SB$_{\text{limit}}$.
-After placing the simulated emission around the galaxy, we subtract the continuum in the same manner as explained in Section \ref{sec.cont_sub}.
+After placing the simulated emission around the galaxy, we subtract the continuum in the same manner as explained in Section \ref{subsec.cont_sub}.
 
@@
 \end{equation}
-where the CONVOLVE$^2$ operation indicates the convolution of the noise image with the square of the Gaussian kernel. The smoothed $\chi$ image is defined by
+where the CONVOLVE$^2$ operation indicates the convolution of the variance image with the square of the Gaussian kernel. The smoothed $\chi$ image is defined by
 \begin{equation}
@@
 We also include the $\chi_{\text{smth}}$ image of each galaxy without any simulated emission (in the left most column).
-Galaxies are outlined by a black isophotal contour corresponding to 1SB$_1$ and the simulated emission is contained inside an annulus surrounding each contour.
+The galaxies are outlined by a black isophotal contour corresponding to 1SB$_1$ and the simulated emission is contained inside the extended annulus surrounding each contour.
 The  $\chi_{\text{smth}}$ images confirm that we should be able to detect extended \ion{Mg}{2} emission down to a conservative level of 5SB$_{\text{limit}}$.
@@
 
-Using the above equation along with the continuum and continuum-subtracted images, we produce images of the observed-frame EW$_{\rm{MgII}}$'s.
-The observed-frame  EW$_{\rm{MgII}}$images are displayed in Figures \ref{fig:ew11}, \ref{fig:ew22}, \ref{fig:ew33}, \ref{fig:ew44}, \ref{fig:ew55},[\textbf{WILL CONSOLIDATE THESE FIGURES}] and show only the EWs within the 1$\sigma$ SB$_1$ contours of the corresponding \ion{Mg}{2} images (prior to continuum subtraction).
+Using the above equation along with the continuum and continuum-subtracted images, we produce images of the observed-frame EW$_{\rm{MgII}}$.
+The observed-frame  EW$_{\rm{MgII}}$ images are displayed in Figures \ref{fig:ew11}, \ref{fig:ew22}, \ref{fig:ew33}, \ref{fig:ew44}, \ref{fig:ew55},[\textbf{WILL CONSOLIDATE THESE FIGURES}] and show only the EWs within the 1$\sigma$ SB$_1$ contours of the corresponding \ion{Mg}{2} images (prior to continuum subtraction).
 
-To compare our map of EW$_{\rm{MgII}}$'s to the values measured from the Keck/LRIS spectra, we place 0.9 arcsec wide apertures on top of each galaxy.
+To compare our map of EW$_{\rm{MgII}}$ to the values measured from the Keck/LRIS spectra, we place 0.9 arcsec wide apertures on top of each galaxy.
 The width and angle of the apertures replicate the orientation of the slits used to obtain the spectra.
 Next, we determine which pixels lie outside the 1$\sigma$ SB$_1$ contours and set their values to zero.
-Outside this contour, the EW$_{\rm{MgII}}$'s become poorly constrained due to the lack of S/N in the continuum.
-We then apply a S/N $= 1.5$ cut to the continuum image and create a histogram to show the distribution of EW$_{\rm{MgII}}$'s inside the contour.
+Outside this contour, the EW$_{\rm{MgII}}$ values become poorly constrained due to the lack of S/N in the continuum.
+We then apply a S/N $= 1.5$ cut to the continuum image and create a histogram to show the distribution of EW$_{\rm{MgII}}$ inside the contour.
 The histograms are shown in Figures \ref{fig:ew11} through \ref{fig:ew55}.
-Having removed EW$_{\rm{MgII}}$'s with low-S/N continuum values from our images, we compute the mean equivalent width inside the Keck/LRIS apertures.
+Having removed pixels with low-S/N continuum values from our images, we compute the mean equivalent width inside the Keck/LRIS apertures.
 These values are summarized in Table \ref{tab:abs_props}.
@@
 To assess the morphology of the \ion{Mg}{2} absorption, we determine the distance of each pixel from the center of each galaxy in kiloparsecs.
-We plot the EW$_{\rm{MgII}}$'s over this projected distance for each galaxy in Figures \ref{fig:ew11} through \ref{fig:ew55}.
+We plot the EW$_{\rm{MgII}}$ over this projected distance for each galaxy in Figures \ref{fig:ew11} through \ref{fig:ew55}.
 Although some of the plots suggest a slight upward trend in the values of the EW$_{\rm{MgII}}$ with increasing radii, we cannot be confident in this trend because of the large scatter.
-To better visualize the data and test the significance of the trend, we bin the data radially in 3-5 kpc bins.
+To better visualize the data and test the significance of the trend, we bin the data radially in 3-5 kpc-wide bins.
 For example, in Figure \ref{fig:ew44}, the EW$_{\rm{MgII}}$ from absorption of J033230.03 extends out to $\sim$ 25 kpc.
-The EW$_{\rm{MgII}}$'s are binned in 5 kpc increments.
-We calculate the mean and scatter of the EW$_{\rm{MgII}}$'s in each bin and show these values in Figure \ref{fig:ew_comb}.
+The EW$_{\rm{MgII}}$ values are binned in 5 kpc increments.
+We calculate the mean and scatter of the EW$_{\rm{MgII}}$ in each bin and show these values in Figure \ref{fig:ew_comb}.
 
@@
 Absorption from \ion{Mg}{2} ions is prevalent in the profiles between 10 - 25 kpc, decreasing radially outward from the maximum absorption at the center of the galaxies.
-In Table \ref{tab:abs_props} we report for the galaxies: J033225.26, J033231.36 and J033230.03 a maximum decrement in the SB profile due to absorption $\sim$ -5.00$\times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
-Additionally, we report for galaxy J033229.64 a decrement one order of magnitude greater then the previous galaxies with a value of -18.2 $\pm$ 0.127 $\times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
+In Table \ref{tab:abs_props} we report for the galaxies J033225.26, J033231.36 and J033230.03 a maximum decrement in the SB profile due to absorption $\sim$ -5.00$\times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
+Additionally, we report for galaxy J033229.64 a decrement one order of magnitude greater than the previous galaxies with a value of -18.2 $\pm$ 0.127 $\times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
 Finally, for galaxy J033230.57 the absorption decrement is strongest at the center of the galaxy with a SB value of -1.25 $\pm$ 1.15 $10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
@@
 The measurement of zero absorption for J033230.57 was expected.
-Figure \ref{fig:spec_images} shows the KECK/LRIS spectrum of J033230.57 and the transmission curves of the filters HeII+47 and HeII/3000+48.
+Figure \ref{fig:spec_images} shows the Keck/LRIS spectrum of J033230.57 and the transmission curves of the filters HeII+47 and HeII/3000+48.
 The \ion{Mg}{2} transitions of the galaxy are equally sampled by both of our filters.
@@
 This measurement suggests that the quality of our subtraction is satisfactory.
-Because of the lack of absorption we exclude this galaxy from our discussion.
+%Because of the lack of absorption we exclude this galaxy from our discussion.
 
@@
 \ref{subsec.ew}, and the resulting values are summarized in Table \ref{tab:abs_props}.
-Comparing our narrowband EWs with those measured from the spectra, we find good agreement to within a few $\sigma$ for galaxies J033225.26 and J033232.36, and statistically significant differences for galaxies J033230.03, J033229.64 and J033230.57.
+Comparing our narrowband EWs with those measured from the spectra, we find agreement to within a 1.6-4.6$\sigma$ for galaxies J033225.26 and J033232.36, and more statistically significant differences for galaxies J033230.03, J033229.64 and J033230.57.
 We discuss possible causes for these differences below.
@@
 The continuum observed near the \ion{Mg}{2} transition is noisy, compared to the spectra of the rest of the sample.
-Since the value of the EW is dependent on the level of the continuum present near the \ion{Mg}{2} transition, it may well be that our choice of continuum level in calculting the EW from the spectrum might be over-estimating the EW of the doublet.
+Since the value of the EW is dependent on the level of the continuum present near the \ion{Mg}{2} transition, it may well be that our choice of continuum level in calculating the EW from the spectrum might be higher relative to the continuum level implied by our narrow-band image.
+%might be over-estimating the EW of the doublet.
 
 Figure \ref{fig:spec_images}(d) shows the Keck/LRIS spectrum of galaxy J033229.64.
-This galaxy is the brightest galaxy in the sample, suggestive of a bright ISM, which causes the redder transition to almost leak out of the HeII+47 transmission curve.
-This suggests that it our \ion{Mg}{2} images are not measuring the most redward absorption feature, thus underestimating the value of the EW.
+This galaxy is the brightest galaxy in the sample, and also exhibits the highest-velocity wind.
+This shifts the \ion{Mg}{2} absorption profile toward the blue end of the
+HeII+47 transmission curve, which could cause the flux in this filter to be weighted toward the continuum level and the absorption signal to be underestimated.
+
+%suggestive of a bright ISM, which causes the redder transition to almost leak out of the HeII+47 transmission curve.
+This suggests %that it our \ion{Mg}{2} images are not measuring the most redward absorption feature, thus underestimating the value of the EW.
 
@@
 Any signal of absorption in the EW images arises from noise.
-Figure \ref{fig:ew5} shows that the radial projection of the EWs measured for this galaxy that are centered around zero.
+Figure \ref{fig:ew55} shows that the radial projection of the EWs measured for this galaxy that are centered around zero.
 
-To get a better sense of how the EW of \ion{Mg}{2} absorption changes with radius as well as account for the effects of seeing, $FWHM \sim 7 kpc$, we bin the EWs in radial bins with 5, 4 or 3 kpc widths as shown in Figures \label{fig:ew1} through \label{fig:ew5}.
-A majority of the galaxies exhibit large scatter in the binned EWs out to larger radii.
+%To get a better sense of how the EW of \ion{Mg}{2} absorption changes with radius as well as account for the effects of seeing, %$FWHM \sim 7 kpc$, we bin the EWs in radial bins with 5, 4 or 3 kpc widths as shown in Figures \label{fig:ew1} through %\label{fig:ew5}.
+As demonstrated in our radially-binned EW profiles,
+a majority of the galaxies exhibit large scatter in the binned EWs out to larger radii.
 To better understand the significance of these trends, we construct a plot that compiles the mean EWs for all the galaxies, shown in Figure \ref{fig:ew_comb}.
@@
 
-Upon inspection of Figure \ref{fig:ew_comb}, we see that all the galaxies exhibit a constant mean EW inside our 1SB$_1$ isophotal radius, and suggestive that the covering fraction is also constant across the surface.
+Upon inspection of Figure \ref{fig:ew_comb}, we see that the galaxies exhibit no statistically significant trend in the mean absorption EW as a function of radius inside our 1SB$_1$ isophotal contour, which suggests that the covering fraction is approximately constant across the surface.
 
-\subsection{Limits on MgII Emission}
-We do not detect any significant amount of \ion{Mg}{2} emission in any of our target galaxies.
+\subsection{Limits on \ion{Mg}{2} Emission}
+For our sample of galaxies, we are sensitive to extended emission at minimum projected distances of 
+8, 10, 15, and 21 kpc, respectively, from the centers of each target.
+%outside the center of the galxies at distances 8-21 kpc fr
+We do not detect any significant \ion{Mg}{2} emission at these distances around any of our target galaxies.
 The $\chi_{\text{smth}}$ images shown in Figure \ref{fig:sigmas} confirm this.
@@
 Taken at face value the figure is consistent with a positive correlation between \ion{Mg}{2} SB and SFR.
+[Planning to add more discussion of possible relationship between SB and stellar mass.]
 
@@
 
-\subsection{Geometry of Scattering Materials}
+\subsection{Geometry of Scattering Material}
 In idealized wind models of cool gas outflows, discussed in \cite{Prochaska_2011}, radiative transfer calculations suggest that strong \ion{Mg}{2} emission is predicted to be generated along with ubiquitous blueshifted absorption of \ion{Mg}{2}.
-For isotropic and dust-free scenarios, photons are conserved, as any absorbed continuum photon is eventually re-emitted, most likely at a different rest wavelength, therefore the total equivalent width of both the absorption and emission feature is equal to zero in such modes.
+For isotropic and dust-free scenarios, photons are conserved, as any absorbed continuum photon is eventually re-emitted, most likely at a different rest wavelength.
+Therefore, the total equivalent width of both the absorption and emission features is equal to zero in such models.
 Assuming that our galaxies host an isotropic and dust-free wind, we wish to determine how much emission is predicted to be generated by this wind, and how the SB of this emission compares to our detection limits.
@@
 Figure \ref{fig.emission} shows how the SB of emission varies with the spatial extent of the annulus (black squares), as well as how the SB compares with our detection limits (thin black curve).
-Excepting the galaxy J033230.03, the SB of this missing emission lie above our detection limits.
-Without taking into account that the emission may not exceed to a radial extent outside the galaxy disk, this result suggests that these galaxies do not host an isotropic dust-free wind.
+Excepting the galaxy J033230.03, the SB of this ``missing'' emission lies above our detection limits.
+%Without taking into account that the emission may not exceed to a radial extent outside the galaxy disk,
+Under the assumption that the wind in these galaxies does in fact extend beyond the $\rm SB_1$ isophotal contour (at $R_{\perp} = 8-21$ kpc), this result suggests that these galaxies do not host  isotropic, dust-free winds.
 
 There are many phenomena that may reduce the SB of the scattered \ion{Mg}{2} emission so that it is consistent with our observations.
-Introducing dust into the wind can reduce the observed emission strength, and shape in the line profile.
-In the absense of dust, the back scattered \ion{Mg}{2} photon can escape the galaxy free of collisions.
-With dust, the photons are susceptible to a number of collisions, with a greater possibility of being absorbed by dust.
-In the \cite{Prochaska_2011} radiative models with increasing dust, the dominant effect that dust has on the \ion{Mg}{2} transitions is that the dust suppresses the most redshifted emission.
+Introducing dust into the wind can reduce the observed emission strength, and affect the shape of the line profile.
+%In the absense of dust, the back scattered \ion{Mg}{2} photon can escape the galaxy free of collisions.
+With dust, the photons are %susceptible to a number of collisions, with a greater possibility of being absorbed by dust.
+In the \cite{Prochaska_2011} radiative models that include dust in the wind material, the dominant effect %that dust has on the
+ is that  the most redshifted emission is suppressed.
 The strength of the flux is reduced by a factor of $(1+\tau_{\rm{dust}})^{-1}$, where $\tau_{\rm{dust}}$ is the integrated opacity of dust.
+[Check on dust content implied by SED modeling from Rubin+14.]
 
 Another factor that can reduce the amount of emission is anisotropy of the wind. 
-Isotropic winds are idealized, but galaxies are not spherically symmetric and the shape of the galaxies interstellar medium may preferentially suppress outflows at varying strengths for different galactic longitudes.
-We now assume that the emission in our galaxies is reduced by purely by the effects anisotropy, as the constraints on dust attenuation or unknown.
-For the anisotropic winds modeled in \cite{Prochaska_2011}, the factor that the emission is reduced is given by the scaling $\Omega/4\pi$, where $\Omega$ is the angular extent of the wind which is constrained to point towards the observer $\Omega > 2\pi$.
-We show the anisotropic wind SB profiles in Figure  \ref{fig.emission}.
+[Planning to add discussion of evidence for bipolar wind morphology.]
+%Isotropic winds are idealized, but galaxies are not spherically symmetric and the shape of the galaxies interstellar medium may preferentially suppress outflows at varying strengths for different galactic longitudes.
+We now assume that the emission in our galaxies is reduced by the effect of anisotropy.  %, as the constraints on dust attenuation or %unknown. 
+For the anisotropic winds modeled in \cite{Prochaska_2011}, the emission is reduced by the factor $\Omega/4\pi$, where $\Omega$ is the angular extent of the wind. 
+As \citet{Prochaska_2011} points out, given that the outflow must cover most of the continuum in order to be detected, the value of $\Omega$ has an approximate lower limit of $\Omega > 2\pi$.
+%which is constrained to point towards the observer $\Omega > 2\pi$. 
+We show the predicted SB profiles for wind emission from our galaxies assuming  $\Omega = 2\pi$ with blue diamonds in Figure  \ref{fig.emission}.
 
-After reducing the SB of the missing \ion{Mg}{2} emission by the minimum opening angle $\Omega=2\pi$, we are able to profiles that fall below our SB detection limits for galaxy's J033225.26 and J033231.36.
-However, the SB profile of J033229.64 remains above our SB detection limits, suggesting additional phenomena are needed to reduce the strength of missing emission.
-Previously discussed in Section \ref{sec:results}, this galaxy is the intrinsically brightest galaxy of our sample, which suggests a strong ISM component.
-\ion{Mg}{2} photons can be more effectively trapped with the combination of  \cite{Prochaska_2011}.
+After reducing the SB of the expected \ion{Mg}{2} emission by the corresponding factor of 2, we predict profiles that fall below our SB detection limits for galaxies J033225.26 and J033231.36.
+However, the SB profile of J033229.64 remains above our SB detection limits, suggesting additional phenomena are needed to reduce the strength of scattered emission.
+Previously discussed in Section \ref{sec:results}, this object is the intrinsically brightest galaxy of our sample and exhibits the strong \ion{Mg}{2} absorption, which suggests a strong ISM component.
+\cite{Prochaska_2011} note that \ion{Mg}{2} photons can be more effectively trapped in objects with a large amount of dusty interstellar material.
 
@@
 Furthermore, our imaging allows us to generate spatially-resolved maps of \ion{Mg}{2} absorption in a distant galaxy sample for the first time.
-This absorption covered the center of the galaxies out to an isophotal radius defined by the SB$_1$ (1$\sigma$) depth of a continuum + \ion{Mg}{2} image, at approximately $\sim 22$ kpc, suggesting that the absorbing gas fully covers the stellar disks out to this distance.
-The measured EWs measured in these maps are in broad agreement with measured EWs using Keck/LRIS integrated slit spectroscopy.
+This absorption covers the center of the galaxies out to an isophotal radius defined by the SB$_1$ (1$\sigma$) depth of a continuum + \ion{Mg}{2} image, at approximately $\sim 22$ kpc, suggesting that the absorbing gas fully covers the stellar disks out to this distance.
+The EWs measured in these maps are in broad agreement with measured EWs using Keck/LRIS integrated slit spectroscopy.
 Additionally, our radial projections of the mean EW for our sample galaxies suggest that the EWs due to \ion{Mg}{2} are approximately constant across the galaxies surfaces.
@@
 By assuming anisotropic winds, we were able to reduce the strength of the predicted emission to lie below our detection limit for 3 of our sample galaxies.
-Albeit one galaxy that needs additional phenomena like dust to reduce the SB of emission and be consistent with our observations.
+We must invoke additional phenomena like dusty ISM material
+to reconcile the predicted SB of emission and our detection limits in the fourth sample galaxy.
+
+%A fourth galaxy that needs additional phenomena like dust to reduce the SB of emission and be consistent with our observations.
 
@@
 Deeper images in \ion{Mg}{2} are required to observe any extended emission beyond the depth of our images.
-Although we are able to rule out that the winds in our sample are isotropic and dust-free, questions linger on weather the wind is anisotropic as well as dust-free.
-A new generation of instruments such as the Keck Cosmic Web Imager (KCWI) or the Multi Unit Spectroscopic Explorer (MUSE) should be used to answer the prevailing questions
+Although our detection limits suggest that the winds in our sample are not isotropic and dust-free, questions linger regarding the relative roles wind anisotropy, dust content, and extent play in reducing scattered emission.
+%on whether the wind is anisotropic as well as dust-free. 
+A new generation of instruments such as the Keck Cosmic Web Imager (KCWI) or the Multi Unit Spectroscopic Explorer (MUSE) should be used to disentangle these issues.
 

### 2018-07-19 Manuscript/vaught_2017.tex
07/19/18

@@
  \author{Fabrizio Arrigoni Battaia }
- \affiliation{Max-Planck-Institut fur Astronomie, Konigstuhl 17, D- 69117 Heidelberg, Germany}
+ \affiliation{European Southern Observatory, Karl-Schwarzschild-Str. 2, D-85748 Garching bei M\"unchen, Germany}
 
@@
 These observations probe extended \ion{Mg}{2} emission down to unmatched surface brightness limits of 5.74 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ (5$\sigma$).
-We do not detect any extended \ion{Mg}{2} emission in any of our galaxies, thus placing strong upper limits on the strength of \ion{Mg}{2} emission at projected distances $R_{\perp} = 8-21$ kpc from the sample galaxies.
+We do not detect any extended \ion{Mg}{2} emission in any of our galaxies, thus placing strong upper limits on the strength of \ion{Mg}{2} emission at projected distances $R_{\perp} = 13-24$ kpc from the sample galaxies.
 Our observations allow us to create the first ever spatially-resolved map of \ion{Mg}{2} absorption, revealing approximately constant absorption strengths across the galaxy disks.
@@
 Outflows are detected by measuring the blueshift (outflow) or redshift (inflow) of absorption transitions with respect to the host galaxy systematic velocity.
-Spectroscopy of galaxies from low to high redshifts probing cold gas ($T \lesssim 10^2$ K) which absorbs in \ion{Na}{1} and cool gas ($T \sim 10^4$ K) in \ion{Mg}{2} has revealed outflows in most galaxies that host active star-formation (e.g.
+ %Spectroscopy of galaxies from low to high redshifts probing cold gas ($T \lesssim 10^2$ K) which absorbs in \ion{Na}{1} and cool gas ($T \sim 10^4$ K) in \ion{Mg}{2} has revealed outflows in most galaxies that host active star-formation (e.g.
 \citethnop{chen2010}; \citethnop{Martin2012}; \citethnop{Rubin_2014}).
-Even though these probes can constrain: the radial velocity, column density and covering fraction of the flow, this method is weak in constraining the overall radial extent and provides no information on the morphology of the outflow.
+Even though these probes can constrain: the radial velocity, column density and covering fraction of the flow, 
+this method is weak in constraining the overall radial extent and provides no information on the morphology of the outflow.
 
-One way of developing these constraints is to trace the extent of winds in emission.
+One way of constraining the radial extent and morphology of the outflow is to trace winds in emission.
 This has been demonstrated using rest-frame optical transitions (i.e H$\alpha$, [\ion{O}{3}], etc) as tracers for winds around nearby starbursts (\citethnop{Matsubayashi2009}; \citethnop{Veilleux2009}; \citethnop{Tripp2011}) as these transitions can trace the warm shock heated phase of the gas.
@@
 2013)\nocite{Weiner2009, Kornei2013}.
-While most studies of winds using \ion{Mg}{2} have focused on its absorption kinematics, \cite{Rubin_2011}  recently observed  strong \ion{Mg}{2} emission with a P-Cygni line profile in the spectrum of a strongly star-forming galaxy at redshift $z = 0.694$.
+While most studies of winds using \ion{Mg}{2} have focused on its absorption kinematics, \cite{Rubin_2011} observed  strong \ion{Mg}{2} emission with a P-Cygni line profile in the spectrum of a strongly star-forming galaxy at redshift $z = 0.694$.
 This emission was the first detection of an outflow beyond the spatial extent of the galaxy continuum in the distant universe, with a minimum spatial extent  $>$ 7 kpc.
@@
 at $z=0.9392$.
-\ion{Mg}{2} has also been studied in wide-field galaxy surveys conducted with Keck/DEIMOS and VLT/MUSE  (\citethnop{Erb2012} and Feltre et.
-al (2018)).
+\ion{Mg}{2} has also been studied in wide-field galaxy surveys conducted with Keck/DEIMOS and VLT/MUSE  (\citethnop{Erb2012}, \citethnop{Feltre2018}).
 These surveys, which include galaxies with redshifts $ 0.70 < z < 2.30$, find that \ion{Mg}{2} may be detected in pure emission, pure absorption or with P-Cygni profiles.
@@
 We adopt a $\Lambda$CDM cosmology with $h_{70} = H_0/(70\ \rm{ km}\ \rm{ s}^{-1}\ \rm{ Mpc}^{-1})$, $\Omega_{\rm{M}}= 0.3$, and $\Omega_{\Lambda} = 0.7$.
+In this cosmology, 1\arcsec is $\approx 7\ \rm kpc$ at $z \sim 0.7$.
 
@@
 \subsection{Sample Selection}
-Our target galaxies were selected from a Keck/LRIS survey of UV absorption lines in $\approx 100$ objects having redshifts $0.3< z < 1.4$ and $B_{AB}< 23$ in fields with deep \emph{HST}/ACS imaging (Rubin et al.
-2014)\nocite{Rubin_2014}.
+Our target galaxies were selected from a Keck/LRIS survey of UV absorption lines in $\approx 100$ objects having redshifts $0.3< z < 1.4$ and $B_{AB}< 23$ in fields with deep \emph{HST}/ACS imaging \citep{Rubin_2014}.
 In particular, this parent survey targeted galaxies in a total of nine Keck/LRIS pointings located in both of the GOODS fields (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004}) and the AEGIS survey field (the Extended Groth Strip; Davis et al.
@@
 
-The absorption line modeling presented in (Rubin et al.
-2014)\nocite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2}  with velocities $\sim150-420\mkms$ and equivalent widths (EW) $\sim 2-3$ \AA.
+The absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2}  with velocities $\sim150-420\mkms$ and equivalent widths (EW) $\sim 2-3$ \AA.
 Modeling of the galaxy broad-band spectral energy distributions obtained from multi-wavelength ancillary imaging data yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$.
-The properties of the sample, as well as precise target coordinates taken from \cite{Rubin_2014}, are listed in Table \ref{tab:prop}.
+The properties and nomenclature of the sample, as well as precise target coordinates taken from \cite{Rubin_2014} ) are listed in Table \ref{tab:prop}.
 
@@
 Our observations were carried out under photometric and thin cloud conditions (program ID: 090.A-0427A).
-The seeing (see Figure \ref{fig.seeing}) ranged from $0.5\arcsec$ to $2.5\arcsec$.
-Summing the individual exposure times for each filter results in a combined exposure time of $10.0$ hours each for the HeII+47 and HeII/3000+48 filters.
+The seeing, which ranged from $0.5\arcsec$ to $2.5\arcsec$, are given in the image header and are derived from DIMM seeing measurements.
+These DIMM values are calculated from zenith observations of bright stars at 0.5 microns, which are then reduced to the zenith angles and wavelengths of the science observation.
+Additionally, a first order correction is then applied for appropriate for a 8m telescope is applied (see Figure \ref{fig.seeing})  Summing the individual exposure times for each filter results in a combined exposure time of $10.0$ hours each for the HeII+47 and HeII/3000+48 filters.
 
@@
 \caption{Color imaging of our sample galaxies in the \emph{HST}/ACS F435W, F606W, and F775W filters obtained as part of the GOODS survey (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004}).
-Each image is 5'' $\times$ 5''.\label{fig:hstims}}
+Each image is 5'' $\times$ 5'' ( or about $ 40 \rm \ kpc \times 40 \rm \ kpc $) .\label{fig:hstims}}
 \end{figure*}
@@
 \includegraphics[scale=.55]{../Figures/avg_seeing_HEII3000.pdf}
-\caption{  Distribution of seeing conditions for individual exposures comprising our dataset.
-\textbf{Top}: Seeing distribution for the 38 HeII+47 images. The median seeing in this filter is $1.03\arcsec$.
-\textbf{Bottom}: Same distribution for the 38 HeII/3000+48 images. The median seeing is $1.08\arcsec$. 
-The seeing conditions were calculated by ESO and were provided in the header of each science image.
+\caption{\textbf{Top}: Distribution of seeings for the 38 HeII+47 images.
+\textbf{Bottom}: Same HeII/3000+48 images. The median seeing conditions for the images in both filters is $\sim 0.8\arcsec$. 
+The seeing conditions were calculated from DIMM measurements which are provided by ESO in the header of each science image.
 \label{fig.seeing}}
@@
 
+\begin{table*}[t]
+\centering
+\caption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) include both components of the \ion{Mg}{2} doublet and were 
+determined from analysis of the supplemental Keck/LRIS spectra.}
+\begin{tabular}{llllllll} \hline \hline
+Object\footnote{ Name in parenthesis to be used as shorthand for the objects throughout the remainder of the paper } & R.A.
+& Dec  & $z$ & SFR($M_{\odot}$ yr$^{-1}$) & $\log{M_{*}/M_{\odot}}$ & EW$_{\rm{obs}}$(\AA) & $\tau_V$\footnote{ 97.5th percentile of the $\tau_V$ distribution}\smallskip      \\ \hline
+J033225.26-274524.0 (J.26)      & 03:32:25.26 & -27:45:23.9 & 0.6660 & $9.1_{-3.7}^{+1.3}$& $9.86_{-0.04}^{+0.05}$ & $7.539\pm 0.354$ & 4.812\\
+
+J033231.36-274725.0 (J.36)      & 03:32:31.35 & -27:47:24.9 &   0.6669 & $10.5_{-1.6}^{+1.7}$ & $10.02_{-0.03}^{+0.03}$&$5.835 \pm 0.493$ & 3.427\\
+
+J033230.03-274347.3  (J.03)     & 03:32:30.03 & -27:43:47.2  &   0.6679 & $3.8_{-0}^{+0}$ & $10.98_{-0.0}^{+0.01}$ &$12.794 \pm 1.710$ & 2.867 \\
+
+J033229.64-274242.6  (J.64)    & 03:32:29.64 & -27:42:42.5 & 0.6671 & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &$13.239 \pm 0.263$ & 5.042\\
+
+J033230.57-274518.2  (J.57)    & 03:32:30.56 & -27:45:18.2 &   0.6807  & $12.6_{-2.1}^{+1.7}$ & $10.48_{-0.07}^{+0.03}$ &$6.106 \pm 0.370$ &4.022 \\
+
+\hline 
+\end{tabular}
+\label{tab:prop}
+\end{table*}
+
 \begin{table}[h!]
@@
 
-\begin{table*}[t]
-\centering
-\caption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}.
-The EW (in the observed frame) include both components of the \ion{Mg}{2} doublet and were %calculated with Eq.
-\ref{eq:specEW} and
-determined from analysis of 
-the supplemental Keck/LRIS spectra.}
-\begin{tabular}{lllllll} \hline \hline
-Object & R.A. & Dec  & $z$ & SFR($M_{\odot}$ yr$^{-1}$) & $\log{M_{*}/M_{\odot}}$ & EW$_{\rm{obs}}$(\AA) \smallskip      \\ \hline 
-J033225.26-274524.0      & 03:32:25.26 & -27:45:23.9 & 0.6660 & $9.1_{-3.7}^{+1.3}$& $9.86_{-0.04}^{+0.05}$ & $7.539\pm 0.354$\\ 
-%274524.0     & &  &  &         \\
-J033231.36-274725.0       & 03:32:31.35 & -27:47:24.9 &   0.6669 & $10.5_{-1.6}^{+1.7}$ & $10.02_{-0.03}^{+0.03}$&$5.835 \pm 0.493$\\
-%274725.0      & &  &   &        \\
-J033230.03-274347.3       & 03:32:30.03 & -27:43:47.2  &   0.6679 & $3.8_{-0}^{+0}$ & $10.98_{-0.0}^{+0.01}$ &$12.794 \pm 1.710$\\
-%274347.3      & &  &   &        \\
-J033229.64-274242.6      & 03:32:29.64 & -27:42:42.5 & 0.6671 & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &$13.239 \pm 0.263$\\
-%274242.6     & &  &     &      \\
-J033230.57-274518.2      & 03:32:30.56 & -27:45:18.2 &   0.6807  & $12.6_{-2.1}^{+1.7}$ & $10.48_{-0.07}^{+0.03}$ &$6.106 \pm 0.370$ \\
-%274518.2      & &  &  &         \\ 
-\hline 
-\end{tabular}
-\label{tab:prop}
-\end{table*}
-
 \subsection{Absolute Flux Calibration}
@@
 It is not uncommon to assume that $F(\lambda)$ is constant over the small width of the filter. 
-However, our filter transmission curves are sampled at $5$\ \AA\ intervals which is the same sampling as the spectral energy distribution of the standard star obtained from the ESO archives (WILL CHECK CALSPEC).
-Therefore we calculate the integral numerically.
+%However, our filter transmission curves are sampled at $5$\ \AA\ intervals which is the same sampling as the spectral energy distribution of the standard star obtained from the ESO archives (WILL CHECK CALSPEC).
+However, we calculate the integral numerically.
 The system sensitivity, including the defects of the telescope optics and detector response is then given by
@@
 The exposure time of each image is $\approx 10$ hours.
-Each image has a FOV of $7' \times 7'$ which fortuitously contains the full sample of galaxies (indicated by the blue circles).
+Each image shows half of the total FOV of $7' \times 7'$ which contains the full sample of galaxies (indicated by the white arrows).
 East is up and North is right.
@@
 To reach both of these goals, we must perform accurate subtraction of the continuum flux of each object from the filter covering the targeted line emission.
-For four of the five objects in our sample, the HeII+47 image includes both line and continuum emission, and the HeII3000+48 image provides a high S/N measurement of the continuum only $\approx30$ \AA\ redward of the line emission in the rest-frame.
+For four of the five galaxies in our sample, the HeII+47 image includes both line and continuum emission, and the HeII3000+48 image provides a high S/N measurement of the continuum only $\approx30$ \AA\ redward of the line emission in the rest-frame.
+The galaxy excluded from our analysis is instead used as a check on the quality of our continuum subtraction for reasons detailed in Section \ref{subsubsec:SBprofiles}.
 
@@
 \includegraphics[scale=0.7]{../Figures/stamps.pdf}
-\caption{ $10'' \times 10''$ images of each galaxy in our sample.
-Top row: Continuum surface brightness in ergs/s/cm$^2$/sq.arcsec measured in the HeII/3000+48 filter.
+\caption{ $10'' \times 10''$ (or about $70 \rm \ kpc \times 70 \rm \ kpc $) images of each galaxy in our sample.
+Top row: Continuum surface brightness in ergs s$^{-1}$ cm$^{-2}$ arcsec$^{-2}$ measured in the HeII/3000+48 filter.
 Bottom row: Continuum-subtracted \ion{Mg}{2} surface brightness.
 Absorption can be seen in 4 of 5 galaxies.
-The red contours represent the outline of the 1$\sigma$ surface brightness limit in the HeII/3000+48 image, defined in Sec.
+The red contours represent the outline of the 1$\sigma$ surface brightness limit in the HeII+47 image, defined in Sec.
 \ref{sec.sb}.
@@
 \centering
-\gridline{\fig{../Figures/J033225_26.pdf}{0.5\textwidth}{(a)}
-          \fig{../Figures/J033231_36.pdf}{0.5\textwidth}{(b)}}
-\gridline{\fig{../Figures/J033230_03.pdf}{0.5\textwidth}{(c)}
-          \fig{../Figures/J033230_64.pdf}{0.5\textwidth}{(d)}}
-           \fig{../Figures/J033230_57.pdf}{0.5\textwidth}{(e)}
+\gridline{\fig{../Figures/J_26.pdf}{0.5\textwidth}{(a)}
+          \fig{../Figures/J_36.pdf}{0.5\textwidth}{(b)}}
+\gridline{\fig{../Figures/J_03.pdf}{0.5\textwidth}{(c)}
+          \fig{../Figures/J_64.pdf}{0.5\textwidth}{(d)}}
+           \fig{../Figures/J_57.pdf}{0.5\textwidth}{(e)}
 \caption{SB profiles for our sample galaxies.
@@
 The outer radius is chosen to be the inner radius plus 5 pixels.
-The sizes of these radii in kiloparsecs and the resulting SB measurements are also shown in Figure~\ref{fig:sb_profiles}.
+Measurements of \ion{Mg}{2} SB will probe projected distances of 13, 18, 21 and 24 kpc from the centers of each target.
+The resulting SB measurements are shown in Figure~\ref{fig:sb_profiles}.
 
@@
 We mask all the artifacts and sources in the continuum-subtracted images.
-Next, we generate randomly sized apertures, place them at random, and extract the fluxes, $F_{\text{src}}$, within these apertures.
-In the ideal case that the sky and continuum are perfectly subtracted, the fluxes, $F_{\text{src}}$, from many random apertures should follow a Gaussian distribution with a width of $\sigma_{\text{src}} \equiv SB_{1}\sqrt{A_\text{src}}$.
-The distribution of $F_{\text{src}}$ for these apertures is shown in Figure \ref{fig:limits}.
-We calculate the variance and mean of the distribution and find that the standard deviation, $\sigma'_{\text{src}}=1.1$, 
-implies that the SB detection limit for our continuum-subtracted image is broader than 
- $\sigma_{\text{src}}$.
-We adopt $F_{\text{limit}} \equiv \sigma'_{\text{src}}$  as the $1 \sigma$ upper limit on the total line flux of extended \ion{Mg}{2} emission.
+Next, we generate apertures with sizes similar to our extended annulus $\sim 20 \rm\ sq.arcsec$, place them at random, and extract the fluxes, $F_{\text{src}}$, within these apertures.
+
+ In the ideal case that the sky and continuum are perfectly subtracted the value of $F_{\text{src}}/ \sigma_{\text{src}}$, where $\sigma_{\text{src}} \equiv SB_{1}\sqrt{A_\text{src}}$, from many random apertures should follow a Gaussian distribution with unit variance.
+The distribution of $F_{\text{src}}/\sigma_{\text{src}}$ for these apertures is shown in Figure \ref{fig:limits}.
+We calculate the variance and mean of the distribution and find that the variance of the distribution is $\sigma'_{\text{src}}=1.1$ and implies that the SB detection limit for our continuum-subtracted image is broader than $\sigma_{\text{src}}$ by 10\%.
+We thus adopt $F_{\text{limit}} \equiv \sigma'_{\text{src}}$  as the $1 \sigma$ upper limit on the total line flux of extended \ion{Mg}{2} emission.
 The SB$_{\text{limit}}$ is then $F_{\text{limit}}/A_{\rm{src}}$.
@@
 Object & F$_{\rm{src}}$(\ion{Mg}{2})\footnote{\ion{Mg}{2} flux is in $10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$.
-The value in the parenthesis is the statistical significance with respect to $\sigma_{\text{src}}$ } & 5SB$_{\text{limit}}$\footnote{Limits are in $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$} & Area\footnote{Area of the extended annulus in sq.arcsec} \\  \hline
+The value in the parenthesis is the statistical significance with respect to $\sigma_{\text{src}}$ } & 5SB$_{\text{limit}}$\footnote{Limits are in $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^{-2}$} & Area\footnote{Area of the extended annulus in sq.arcsec} \\  \hline
 J033225.26-274524.0 &  2.44(0.92)& 6.51	& 21 \\
@@
 \begin{equation}
-I_{\text{smth}}= \text{CONVOLVE[NB-CONTINUUM]},
+I_{\text{smooth}}= \text{CONVOLVE[NB-CONTINUUM]},
 \end{equation}
 where the CONVOLVE operation indicates convolution of the images with a Gaussian kernel with FWHM=1.5 pixels.
-Next, we computed the sigma image ($\sigma_{\text{smth}}$) for the smoothed image ($I_{\text{smth}}$) by propagating the noise image of the unsmoothed data:
+Next, we computed the sigma image ($\sigma_{\text{smooth}}$) for the smoothed image ($I_{\text{smooth}}$) by propagating the noise image of the unsmoothed data:
 \begin{equation}
-\sigma_{\text{smth}}=\sqrt{\text{CONVOLVE}^2[\sigma^2_{\text{unsmth}}]},
+\sigma_{\text{smooth}}=\sqrt{\text{CONVOLVE}^2[\sigma^2_{\text{unsmooth}}]},
 \end{equation}
@@
 \begin{equation}
-\chi_{\text{smth}}=\frac{I_{\text{smth}}}{\sigma_{\text{smth}}}.
+\chi_{\text{smooth}}=\frac{I_{\text{smooth}}}{\sigma_{\text{smooth}}}.
 \end{equation}
-This $\chi_{\text{smth}}$ image aids in recognizing the presence of extended \ion{Mg}{2} emission.
+This $\chi_{\text{smooth}}$ image aids in recognizing the presence of extended \ion{Mg}{2} emission.
 
-Figure \ref{fig:sigmas} shows the $\chi_{\text{smth}}$ images for the 5 levels of simulated \ion{Mg}{2} emission.
-We also include the $\chi_{\text{smth}}$ image of each galaxy without any simulated emission (in the left most column).
+Figure \ref{fig:sigmas} shows the $\chi_{\text{smooth}}$ images for the 5 levels of simulated \ion{Mg}{2} emission.
+We also include the $\chi_{\text{smooth}}$ image of each galaxy without any simulated emission (in the left most column).
 The galaxies are outlined by a black isophotal contour corresponding to 1SB$_1$ and the simulated emission is contained inside the extended annulus surrounding each contour.
-The  $\chi_{\text{smth}}$ images confirm that we should be able to detect extended \ion{Mg}{2} emission down to a conservative level of 5SB$_{\text{limit}}$.
+The  $\chi_{\text{smooth}}$ images confirm that we should be able to detect extended \ion{Mg}{2} emission down to a conservative level of 5SB$_{\text{limit}}$.
 Note again that the SB$_{\text{limit}}$ does indeed take into account the systematics from imperfect continuum subtraction.
-
-%\begin{table}[]
-%\centering
-%%\begin{minipage}{4.5in}
-%\caption{Empirically Determined Detection Limits \label{tab:det_lims}}  
-%\begin{tabular}{llll} \hline \hline
-%Object & 5SB$_{\text{limit}}$\footnote{Limits are in $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$} &Area\footnote{Area of the extended annulus in sq.arcsec} \\  \hline
-%J033225.26-274524.0 &  6.51 & 21 \\
-%J033232.36-274725.0 & 6.51 & 21 \\
-%J033230.03-274347.3 & 5.74 & 27 \\
-%J033229.64-274242.5 & 6.22  & 26 \\
-%J033230.57-274518.2 & 6.81 & 18 \\ \hline
-%\end{tabular}
-%\end{minipage}
-%\end{table}
 
@@
 \includegraphics[scale=1.2]{../Figures/sigmas.pdf}
-\caption{Postage stamp $\chi_{\text{smth}}$ images of the 5 galaxies in our sample.
+\caption{Postage stamp $\chi_{\text{smooth}}$ images for the Mg II emission of the 5 galaxies in our sample.
 Every galaxy is placed in the same row in each column.
@@
 Using the above equation along with the continuum and continuum-subtracted images, we produce images of the observed-frame EW$_{\rm{MgII}}$.
-The observed-frame  EW$_{\rm{MgII}}$ images are displayed in Figures \ref{fig:ew11}, \ref{fig:ew22}, \ref{fig:ew33}, \ref{fig:ew44}, \ref{fig:ew55},[\textbf{WILL CONSOLIDATE THESE FIGURES}] and show only the EWs within the 1$\sigma$ SB$_1$ contours of the corresponding \ion{Mg}{2} images (prior to continuum subtraction).
+The observed-frame EW$_{\rm{MgII}}$ images are displayed for each galaxy in Figure \ref{fig:ews} and show only the EWs within the 1$\sigma$ SB$_1$ contours of the corresponding \ion{Mg}{2} images (prior to continuum subtraction).
 
@@
 To better visualize the data and test the significance of the trend, we bin the data radially in 3-5 kpc-wide bins.
-For example, in Figure \ref{fig:ew44}, the EW$_{\rm{MgII}}$ from absorption of J033230.03 extends out to $\sim$ 25 kpc.
+For example, in Figure \ref{fig:ew44}, the EW$_{\rm{MgII}}$ from absorption of J.03 extends out to $\sim$ 25 kpc.
 The EW$_{\rm{MgII}}$ values are binned in 5 kpc increments.
@@
 
-\subsubsection{\ion{Mg}{2}\ absorption in surface brightness profiles}
+\subsubsection{\ion{Mg}{2}\ absorption in surface brightness profiles} \label{subsubsec:SBprofiles}
 Although we do not detect any extended \ion{Mg}{2} emission, we do observe a decrement of flux in the SB profiles of 4 out of 5 galaxies in our sample.
@@
 Absorption from \ion{Mg}{2} ions is prevalent in the profiles between 10 - 25 kpc, decreasing radially outward from the maximum absorption at the center of the galaxies.
-In Table \ref{tab:abs_props} we report for the galaxies J033225.26, J033231.36 and J033230.03 a maximum decrement in the SB profile due to absorption $\sim$ -5.00$\times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
-Additionally, we report for galaxy J033229.64 a decrement one order of magnitude greater than the previous galaxies with a value of -18.2 $\pm$ 0.127 $\times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
-Finally, for galaxy J033230.57 the absorption decrement is strongest at the center of the galaxy with a SB value of -1.25 $\pm$ 1.15 $10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
+In Table \ref{tab:abs_props} we report for the galaxies J.26, J.36 and J.03 a maximum decrement in the SB profile due to absorption $\sim$ -5.00$\times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
+Additionally, we report for galaxy J.64 a decrement one order of magnitude greater than the previous galaxies with a value of -18.2 $\pm$ 0.127 $\times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
+Finally, for galaxy J.57 the absorption decrement is strongest at the center of the galaxy with a SB value of -1.25 $\pm$ 1.15 $10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
 However, the measured SB of this decrement including error is consistent with measuring zero absorption.
-The measurement of zero absorption for J033230.57 was expected.
-Figure \ref{fig:spec_images} shows the Keck/LRIS spectrum of J033230.57 and the transmission curves of the filters HeII+47 and HeII/3000+48.
+The measurement of zero absorption for J.57 was expected.
+Figure \ref{fig:spec_images} shows the Keck/LRIS spectrum of J.57 and the transmission curves of the filters HeII+47 and HeII/3000+48.
 The \ion{Mg}{2} transitions of the galaxy are equally sampled by both of our filters.
@@
 This measurement suggests that the quality of our subtraction is satisfactory.
-%Because of the lack of absorption we exclude this galaxy from our discussion.
 
@@
 \subsubsection{Morphology of MgII Absorption}
-Figures \ref{fig:ew11} through \ref{fig:ew55} show the images, distributions and radial projections of \ion{Mg}{2} EWs.
+Figures \ref{fig:ews}  show the images, distributions and radial projections of \ion{Mg}{2} EWs.
 We have zeroed out any values that lie outside the SB$_1$ contours for each galaxy.
@@
 \ref{subsec.ew}, and the resulting values are summarized in Table \ref{tab:abs_props}.
-Comparing our narrowband EWs with those measured from the spectra, we find agreement to within a 1.6-4.6$\sigma$ for galaxies J033225.26 and J033232.36, and more statistically significant differences for galaxies J033230.03, J033229.64 and J033230.57.
-We discuss possible causes for these differences below.
+Comparing our narrowband EWs with those measured from the spectra, we find agreement to within a 1.6-4.6$\sigma$ for galaxies J.26 and J.36, and more statistically significant differences for galaxies J.03 and J.64 We discuss possible causes for these differences below.
 
-Figure \ref{fig:spec_images}(c) shows the Keck/LRIS spectrum of galaxy J033230.03.
+Figure \ref{fig:spec_images}(c) shows the Keck/LRIS spectrum of galaxy J.03.
 The continuum observed near the \ion{Mg}{2} transition is noisy, compared to the spectra of the rest of the sample.
@@
 
-Figure \ref{fig:spec_images}(d) shows the Keck/LRIS spectrum of galaxy J033229.64.
+Figure \ref{fig:spec_images}(d) shows the Keck/LRIS spectrum of galaxy J.64.
 This galaxy is the brightest galaxy in the sample, and also exhibits the highest-velocity wind.
@@
 
-In the case of J033230.57 we can easily understand why the EW measured is not in agreement with the spectral EW.
-Figure \ref{fig:sb_profiles}  shows the SB profile coverage of J033230.57.
+%In the case of J.57 we can easily understand why the EW measured is not in agreement with the spectral EW.
+Figure \ref{fig:sb_profiles}  shows the SB profile coverage of J.57.
 In this galaxy's profile we do not detect any significant SB decrements, due to absorption, as the two filters cover the \ion{Mg}{2} as discussed above.
@@
 %To get a better sense of how the EW of \ion{Mg}{2} absorption changes with radius as well as account for the effects of seeing, %$FWHM \sim 7 kpc$, we bin the EWs in radial bins with 5, 4 or 3 kpc widths as shown in Figures \label{fig:ew1} through %\label{fig:ew5}.
-As demonstrated in our radially-binned EW profiles,
-a majority of the galaxies exhibit large scatter in the binned EWs out to larger radii.
+As demonstrated in our radially-binned EW profiles, a majority of the galaxies exhibit large scatter in the binned EWs out to larger radii.
 To better understand the significance of these trends, we construct a plot that compiles the mean EWs for all the galaxies, shown in Figure \ref{fig:ew_comb}.
@@
 For our sample of galaxies, we are sensitive to extended emission at minimum projected distances of 
-8, 10, 15, and 21 kpc, respectively, from the centers of each target.
+13, 18, 21 and 24 kpc, respectively, from the centers of each target.
 %outside the center of the galxies at distances 8-21 kpc fr
 We do not detect any significant \ion{Mg}{2} emission at these distances around any of our target galaxies.
-The $\chi_{\text{smth}}$ images shown in Figure \ref{fig:sigmas} confirm this.
-A comparison of the simulated emission with the $\chi_{\text{smth}}$ image of the original continuum-subtracted image, shown in the first column, similarly suggests that we do not detect any extended \ion{Mg}{2} emission.
+The $\chi_{\text{smooth}}$ images shown in Figure \ref{fig:sigmas} confirm this.
+A comparison of the simulated emission with the $\chi_{\text{smooth}}$ image of the original continuum-subtracted image, shown in the first column, similarly suggests that we do not detect any extended \ion{Mg}{2} emission.
 We thus place $5\sigma$ upper limits on \ion{Mg}{2} emission for each galaxy in the sample, summarized in Table \ref{tab:det_lims}.
-The most sensitive detection limit using the largest area is SB(\ion{Mg}{2}) = 5.74 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$, computed for the galaxy J033230.03.
-Our least sensitive detection limit is SB(\ion{Mg}{2}) = 6.81 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$, computed for the galaxy J033230.57.
-
+The most sensitive detection limit using the largest area is SB(\ion{Mg}{2}) = 5.74 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$, computed for the galaxy J.03.
 \section{Discussion}\label{sec:discussion}
@@
 
-Figure \ref{fig:detection_lim} shows a plot of the 5$\sigma$ detection limits determined for each galaxy in our sample as well as the SB calculated for the galaxy TKRS 4389 vs SFR.
+Figure \ref{fig:SFR_lim} shows a plot of the 5$\sigma$ detection limits determined for each galaxy in our sample as well as the SB calculated for the galaxy TKRS 4389 vs SFR.
 The figure suggests that we should be able to detect scattered \ion{Mg}{2} emission with strengths similar to that detected in TKRS 4389.
-Taken at face value the figure is consistent with a positive correlation between \ion{Mg}{2} SB and SFR.
-[Planning to add more discussion of possible relationship between SB and stellar mass.]
-
-%The study by \cite{Erb2012} discuss that emission strength is stronger in low mass galaxies.
-This could be one explanation as to why we did not detect any extended \ion{Mg}{2} emission Further studies need to be pursued to add additional points to Figure \ref{fig:detection_lim}.
+Taken at face value the figure could be consistent with a positive correlation between \ion{Mg}{2} SB and SFR.
+Future observations are needed to verify this trend, and thus the possibility of detect \ion{Mg}{2} in emission for high SFR, $>\sim$50 $\msunperyr$.
+Figure \ref{fig:detection_lim} shows the same SB values as Figure \ref{fig:SFR_lim} vs $\log(M_*/M_{\odot})$.
+The figure is suggestive that \ion{Mg}{2} is stronger in emission in lower mass galaxies, and is consistent with the results in \cite{Erb2012} and \cite{Feltre2018}.
 
@@
 \includegraphics[scale=0.6]{../Figures/limits.pdf}
-\caption{Comparison of our detection limits to the measured extended emission of TKRS 4389.
-Our imaging is sufficiently sensitive to detect extended emission at similar strengths to the extended emission measured for TKRS 4389.}
+\caption{Comparison of our detection limits to the measured extended emission of TKRS 4389 vs SFR.
+The arrow color-galaxy scheme is: (Blue) J.26, (Green) J.36, (Red) J.03, (Cyan) J.64, (Magenta) J.57.
+Our imaging is sufficiently sensitive to detect extended emission at similar strengths to the extended emission measured for TKRS 4389 with SFR $\sim 50 \msunperyr$.}
+\label{fig:SFR_lim}
+\end{figure}
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[scale=0.6]{../Figures/mass_limits.pdf}
+\caption{Comparison of our detection limits to the measured extended emission of TKRS 4389 vs Mass.
+Our imaging is sufficiently sensitive to detect extended emission at similar strengths to the extended emission measured for TKRS 4389 with mass $\sim 10 \log(M_*/ M_{\odot})$.
+The color scheme is the same as Figure \ref{fig:SFR_lim}.}
 \label{fig:detection_lim}
@@
 Figure \ref{fig.emission} shows how the SB of emission varies with the spatial extent of the annulus (black squares), as well as how the SB compares with our detection limits (thin black curve).
-Excepting the galaxy J033230.03, the SB of this ``missing'' emission lies above our detection limits.
+Excepting the galaxy J.03, the SB of this ``missing'' emission lies above our detection limits.
 %Without taking into account that the emission may not exceed to a radial extent outside the galaxy disk,
@@
 Another factor that can reduce the amount of emission is anisotropy of the wind.
-[Planning to add discussion of evidence for bipolar wind morphology.]
-%Isotropic winds are idealized, but galaxies are not spherically symmetric and the shape of the galaxies interstellar medium may preferentially suppress outflows at varying strengths for different galactic longitudes.
-We now assume that the emission in our galaxies is reduced by the effect of anisotropy.  %, as the constraints on dust attenuation or %unknown. 
+Direct evidence of anisotropic winds, specifically bipolar morphology, has been observed in emission from cold and shock heated gas in local starburst galaxies \citep[e.g.][]{{Walter2002,Westmoquette2008M,Strickland2009}}.
+For distant galaxies, enhanced absorption \ion{Mg}{2} along a galaxy's minor axis (Bordoloi et al.
+2011; Bouche?
+et al.
+2012; Kacprzak et al.
+2012),  higher outflow velocities toward $z \sim 1$ galaxies having $i < 45 ^{\circ}$ are suggestive of bipolar outflows.
+Furthermore, \cite{Rubin_2014} analysis provide strong evidence for the ubiquity of bipolar outflows in distant galaxies.
+
+We now assume that the emission in our galaxies is reduced by the effect of anisotropy. 
 For the anisotropic winds modeled in \cite{Prochaska_2011}, the emission is reduced by the factor $\Omega/4\pi$, where $\Omega$ is the angular extent of the wind. 
 As \citet{Prochaska_2011} points out, given that the outflow must cover most of the continuum in order to be detected, the value of $\Omega$ has an approximate lower limit of $\Omega > 2\pi$. 
-%which is constrained to point towards the observer $\Omega > 2\pi$. 
 We show the predicted SB profiles for wind emission from our galaxies assuming  $\Omega = 2\pi$ with blue diamonds in Figure  \ref{fig.emission}.
 
-After reducing the SB of the expected \ion{Mg}{2} emission by the corresponding factor of 2, we predict profiles that fall below our SB detection limits for galaxies J033225.26 and J033231.36.
-However, the SB profile of J033229.64 remains above our SB detection limits, suggesting additional phenomena are needed to reduce the strength of scattered emission.
+After reducing the SB of the expected \ion{Mg}{2} emission by the corresponding factor of 2, we predict profiles that fall below our SB detection limits for galaxies J.26 and J.36.
+However, the SB profile of J.64 remains above our SB detection limits, suggesting additional phenomena are needed to reduce the strength of scattered emission.
 Previously discussed in Section \ref{sec:results}, this object is the intrinsically brightest galaxy of our sample and exhibits the strong \ion{Mg}{2} absorption, which suggests a strong ISM component.
@@
 We presented the results from a narrowband imaging search for \ion{Mg}{2} emission in a sample of star-forming galaxies at a redshift of $z \sim 0.70$ which are known to drive outflows in  \ion{Mg}{2}.
-We did not detect any \ion{Mg}{2} emission in this sample, and place a $5\sigma$ detection upper limit of SB(\ion{Mg}{2}) $\approx$ 5.74 $\times 10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$, measured in an extended annulus outside the largest galaxy.
+We did not detect any \ion{Mg}{2} emission in this sample, and place a $5\sigma$ detection upper limit of SB(\ion{Mg}{2}) $\approx$ 5.74 $\times 10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$, measured in an extended annulus outside the largest galaxy, at minimum projected distances of 13, 18, 21 and 24 kpc from the centers of each target.
 We detected a significant amount of \ion{Mg}{2} absorption in a total of 4 galaxies out of our 5 galaxy sample.
@@
 
-%A fourth galaxy that needs additional phenomena like dust to reduce the SB of emission and be consistent with our observations.
-
 Based on the radial extent and strength of our measured \ion{Mg}{2} absorption, the \ion{Mg}{2} is optically thick.
@@
 Although our detection limits suggest that the winds in our sample are not isotropic and dust-free, questions linger regarding the relative roles wind anisotropy, dust content, and extent play in reducing scattered emission.
-%on whether the wind is anisotropic as well as dust-free. 
+
 A new generation of instruments such as the Keck Cosmic Web Imager (KCWI) or the Multi Unit Spectroscopic Explorer (MUSE) should be used to disentangle these issues.
 
-%In the future, we hope to observe these galaxies using an Integral Field spectrograph (IFU).
-IFUs take the signal from an individual pixel and feeds it into a spectrograph.
-The spectrograph then generates a spectrum for that pixel, allowing us to view the flux at specific transitions.
-IFUs cover large 2D fields of view, contrary to single point 1D spectroscopy or the slice of 2D longslit spectroscopy, makes them exceptionally useful in resolving the spectrum of a target for multiple sightlines.
-Thus, IFUs are useful in detecting the gas of extended objects, such as galaxies.
-Because IFUs would allow us to observe the spectrum of a galaxy's extended region, we will be able to compare our EW maps, as well as EW radial projections, with higher resolution observations.
-
-%Based on the radial extent and strength of our measured \ion{Mg}{2} absorption, the \ion{Mg}{2} is optically thick.
-However, we need to compare our measured absorption strength and radial extent with radiative transfer models.
-In the radiative transfer models of \cite{Prochaska_2011}, scattered emission is predicted for an isotropic, optically thick,and dust free wind with density that decreases as an inverse square law, however galaxies are not spherically symmetric and sources driving the wind may not be distributed spherically.
-Allowing for a bi-conical anisotropic wind, \cite{Prochaska_2011} state that the scattered \ion{Mg}{2} emission will become suppressed compared to the strengths an isotropic wind.
-Future observations of our galaxies in IFUs could perhaps shed light on this alternate scenario.
-
- \begin{figure*}[]
+\begin{figure*}
 \centering
-\includegraphics[scale=0.9]{../Figures/J26EW.pdf}
-\includegraphics[scale=0.9]{../Figures/J26EW_2.pdf}
-\caption{Equivalent width images, distribution and radial projection for J033225.26.
-(Top Left) image of the \ion{Mg}{2} equivalent widths inside the red 1SB$_1$ contour.
-The white contour represents the $0.9''$ wide  slit used to measure the equivalent width of absorption in the Keck/LRIS spectra.
-(Top Right) Distribution of absorption pixels with continuum flux S/N greater than 1.5 inside the slit aperture.
-(Bottom Left) The EWs of absorption vs projected distance from center.
-(Bottom Right) Binned EW measurements.
-Each point represents the mean EW measured in 3 kpc wide bins.}
-\label{fig:ew11}
-\end{figure*}
-
-\begin{figure*}[]
-\centering
-\includegraphics[scale=0.9]{../Figures/J36EW.pdf}
-\includegraphics[scale=0.9]{../Figures/J36EW_2.pdf}
-\caption{Equivalent width images, distribution and radial projection for J033231.36.
-(Top Left) image of the \ion{Mg}{2} equivalent widths inside the red 1SB$_1$ contour.
-The white contour represents the $0.9''$ wide  slit used to measure the equivalent width of absorption in the Keck/LRIS spectra.
-(Top Right) Distribution of absorption pixels with continuum flux S/N greater than 1.5 inside the slit aperture.
-(Bottom Left) The EWs of absorption vs projected distance from center.
-(Bottom Right) Binned EW measurements.
-Each point represents the mean EW measured in 4 kpc wide bins.}
-\label{fig:ew22}
-\end{figure*}
-
-\begin{figure*}[]
-\centering
-\includegraphics[scale=0.9]{../Figures/J03EW.pdf}
-\includegraphics[scale=0.9]{../Figures/J03EW_2.pdf}
-\caption{Equivalent width images, distribution and radial projection for J033230.03.
-(Top Left) Stamp of the equivalent widths (EWs) inside the red 1SB$_1$ contour.
-The white contour represents the $0.9''$ aperture slit used to measure the equivalent width of absorption in the Keck/LRIS spectra.
-(Top Right) Distribution of absorption pixels with continuum flux S/N greater than 1.5 inside the slit aperture.
-(Bottom Left) The EWs of absorption projected in distance from center.
-(Bottom Right) Binned EW measurements.
-Each point represents the mean EW measured in 5 kpc increment bins.
-}
-\label{fig:ew33}
-\end{figure*}
-
-\begin{figure*}[]
-\centering
-\includegraphics[scale=0.9]{../Figures/J64EW.pdf}
-\includegraphics[scale=0.9]{../Figures/J64EW_2.pdf}
-\caption{ Equivalent width images, distribution and radial projection for J033229.64.
-(Top Left) Stamp of the equivalent widths (EWs) inside the red 1SB$_1$ contour.
-The white contour represents the $0.9''$ aperture slit used to measure the equivalent width of absorption in the Keck/LRIS spectra.
-(Top Right) Distribution of absorption pixels with continuum flux S/N greater than 1.5 inside the slit aperture.
-(Bottom Left) The EWs of absorption projected in distance from center.
-(Bottom Right) Binned EW measurements.
-Each point represents the mean EW measured in 4 kpc wide bins.}
-\label{fig:ew44}
-\end{figure*}
-
-\begin{figure*}[]
-\centering
-\includegraphics[scale=1.1]{../Figures/J57EW.pdf}
-\includegraphics[scale=1.1]{../Figures/J57EW.pdf}
-\caption{\textbf{Example of new figure style, Need to create for remaining galaxies}}
-\label{fig:ew55}
+\gridline{\fig{../Figures/J26EW.pdf}{0.8\textwidth}{(a: J.26)}}
+ \gridline{\fig{../Figures/J36EW.pdf}{0.8\textwidth}{(b: J.36)}}
+\gridline{\fig{../Figures/J03EW.pdf}{0.8\textwidth}{(c: J.03)}}
+ \gridline{\fig{../Figures/J64EW.pdf}{0.8\textwidth}{(d: J.64)}}
+\caption{(Left) Stamp of the equivalent widths (EWs) inside the red 1SB$_1$ contour.
+The white contour represents the 0.9\arcsec aperture slit used to measure the equivalent width of absorption in the Keck/LRIS spectra.
+(Middle) Distribution of absorption pixels with continuum flux S/N greater than 1.5 inside the slit aperture.
+(Right) The EWs of absorption projected in distance from center are in blue and binned EW measurements red.
+The error bars in the radial axis represent the width of the radial bin used.}
+\label{fig:ews}
 \end{figure*}
@@
           \fig{../Figures/geo_J64.pdf}{0.5\textwidth}{(J033230.64)}}
-\caption{Estimated SB profile of \ion{Mg}{2} emission for Isotropic and Anisotropic dust-free winds.
-The black square points are SB of missing \ion{Mg}{2} emission uniformly distributed inside an annulus for an angle $\Omega=4\pi$, or an isotropic wind.
+\caption{Estimated SB profile of \ion{Mg}{2} emission for isotropic and anisotropic dust-free winds.
+The black square points are SB of predicted \ion{Mg}{2} emission uniformly distributed inside an annulus for an angle $\Omega=4\pi$, or an isotropic wind.
 The blue diamond points are SB of missing \ion{Mg}{2} emission uniformly distributed inside an annulus for an angle $\Omega=2\pi$, or an anisotropic wind.
 The solid line shows the value of the SB detection limits.
-The dashed vertical and horizontal lines represent outer radius of the extended annulus use to measure the initial detection limits and the value of SB detection limit in that annulus.}
+The dashed vertical and horizontal lines represent outer radius of the extended annulus used to measure the initial detection limits and the value of the SB detection limit in that annulus.}
 \label{fig.emission}
@@
 
-\newpage
 \bibliography{references2017}

### 2018-07-19 Manuscript/vaught_2017.tex
7/19/18

@@
 Since the value of the EW is dependent on the level of the continuum present near the \ion{Mg}{2} transition, it may well be that our choice of continuum level in calculating the EW from the spectrum might be higher relative to the continuum level implied by our narrow-band image.
-%might be over-estimating the EW of the doublet.
 
@@
 
-%suggestive of a bright ISM, which causes the redder transition to almost leak out of the HeII+47 transmission curve.
-This suggests %that it our \ion{Mg}{2} images are not measuring the most redward absorption feature, thus underestimating the value of the EW.
-
-%In the case of J.57 we can easily understand why the EW measured is not in agreement with the spectral EW.
-Figure \ref{fig:sb_profiles}  shows the SB profile coverage of J.57.
-In this galaxy's profile we do not detect any significant SB decrements, due to absorption, as the two filters cover the \ion{Mg}{2} as discussed above.
-Any signal of absorption in the EW images arises from noise.
-Figure \ref{fig:ew55} shows that the radial projection of the EWs measured for this galaxy that are centered around zero.
-
-%To get a better sense of how the EW of \ion{Mg}{2} absorption changes with radius as well as account for the effects of seeing, %$FWHM \sim 7 kpc$, we bin the EWs in radial bins with 5, 4 or 3 kpc widths as shown in Figures \label{fig:ew1} through %\label{fig:ew5}.
 As demonstrated in our radially-binned EW profiles, a majority of the galaxies exhibit large scatter in the binned EWs out to larger radii.
@@
 13, 18, 21 and 24 kpc, respectively, from the centers of each target.
-%outside the center of the galxies at distances 8-21 kpc fr
+
 We do not detect any significant \ion{Mg}{2} emission at these distances around any of our target galaxies.
@@
 The most sensitive detection limit using the largest area is SB(\ion{Mg}{2}) = 5.74 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$, computed for the galaxy J.03.
+\begin{table}[]
+\centering
+\caption{Properties of \ion{Mg}{2}\ Absorption\label{tab:abs_props}}  
+\begin{tabular}{llllll} \hline \hline
+Object & SB$_{abs}$\footnote{Maximum SB decrement, values are in units of $10^{-18}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$} & $R$\footnote{Radius of SB$_1$ contour in kpc} &\ \ \ EW$_{\rm{obs}}$($\AA$)\footnote{ Measured from EW images} & EW$_{\rm{obs}}$($\AA$)\footnote{Measured from Keck/LRIS spectra}  \\  \hline
+J.26 &  $-5.39 \pm 1.28 $ & 8 &     $\ \ \ 3.51 \pm 0.80$ & $7.53 \pm 0.35 $\\
+J.36 &  $-5.64 \pm 0.121 $ & 15 & $\ \ \ 7.69 \pm 1.02$ & $5.83 \pm 0.49$\\
+J.03 &  $-4.41 \pm 0.622 $ & 21 & $\ \ \ 5.39 \pm 0.71$ & $12.7 \pm 1.71$\\
+J.64 &  $-18.2 \pm 0.127 $ & 10 & $\ \ \ 7.55 \pm 0.66$ & $13.2 \pm 0.26$\\
+J.57 &  $-1.25 \pm 1.15   $ & 11& -$0.653 \pm 0.58$ & $6.10 \pm 0.37$\\ \hline
+\end{tabular}
+\end{table}
+
 \section{Discussion}\label{sec:discussion}
-
 \subsection{Previous Detections of Extended \ion{Mg}{2} Emission}
@@
 
+\subsubsection{Anisotropic and Dust Free Winds}
+
 There are many phenomena that may reduce the SB of the scattered \ion{Mg}{2} emission so that it is consistent with our observations.
-Introducing dust into the wind can reduce the observed emission strength, and affect the shape of the line profile.
-%In the absense of dust, the back scattered \ion{Mg}{2} photon can escape the galaxy free of collisions.
-With dust, the photons are %susceptible to a number of collisions, with a greater possibility of being absorbed by dust.
-In the \cite{Prochaska_2011} radiative models that include dust in the wind material, the dominant effect %that dust has on the
- is that  the most redshifted emission is suppressed.
-The strength of the flux is reduced by a factor of $(1+\tau_{\rm{dust}})^{-1}$, where $\tau_{\rm{dust}}$ is the integrated opacity of dust.
-[Check on dust content implied by SED modeling from Rubin+14.]
-
-Another factor that can reduce the amount of emission is anisotropy of the wind.
+One factor that can affect the observed emission strength is morphology of the wind.
+Anisotropic winds were shown in \cite{Prochaska_2011} to exhibit reduced emission strength compared to an isotrpic wind.
 Direct evidence of anisotropic winds, specifically bipolar morphology, has been observed in emission from cold and shock heated gas in local starburst galaxies \citep[e.g.][]{{Walter2002,Westmoquette2008M,Strickland2009}}.
@@
 
-\begin{table*}[]
-\centering
-\caption{Properties of \ion{Mg}{2}\ Absorption\label{tab:abs_props}}  
-\begin{tabular}{llllll} \hline \hline
-Object & Max(SB$_{abs}$)\footnote{SB Values are in units of $10^{-18}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$} & $R_{\text{SB}_1}(kpc)$ &\ \ \ EW$_{\rm{obs}}$($\AA$)\footnote{ Measured from EW images} & EW$_{\rm{obs}}$($\AA$)\footnote{Measured from Keck/LRIS spectra}  \\  \hline
-J033225.26-274524.0 &  $-5.39 \pm 1.28 $ & 8 &     $\ \ \ 3.511 \pm 0.795$ & $7.539 \pm 0.354 $\\
-J033232.36-274725.0 &  $-5.64 \pm 0.121 $ & 15 & $\ \ \ 7.694 \pm 1.016$ & $5.835 \pm 0.493$\\
-J033230.03-274347.3 &  $-4.41 \pm 0.622 $ & 21 & $\ \ \ 5.388 \pm 0.712$ & $12.79 \pm 1.710$\\
-J033229.64-274242.5 &  $-18.2 \pm 0.127 $ & 10 & $\ \ \ 7.546 \pm 0.660$ & $13.24 \pm 0.263$\\
-J033230.57-274518.2 &  $-1.25 \pm 1.15   $ & 11& -$0.6532 \pm 0.589$ & $6.106 \pm 0.370$\\ \hline
-\end{tabular}
-\end{table*}
+\subsubsection{Anisotropic and Dusty Winds}
+
+Dust in the wind is another factor that can reduce the observed emission strength, and affect the shape of the line profile. 
+In the \cite{Prochaska_2011} radiative models that include dust in the wind material, the dominant effect is that the most redshifted emission is suppressed.
+The strength of the flux is reduced by a factor of $(1+\tau_{\rm{dust}})^{-1}$, where $\tau_{\rm{dust}}$ is the integrated opacity of dust.
+The green hexagons in Figure \ref{fig.emission} shows the predicted SB profile for an anisotropic wind with dust.
+As mentioned in the previous section, anisotropy alone does not reduce the predicted emission of J.64 below our detection limits.
+The profile in  Figure \ref{fig.emission} shows that combination of dust and anisotropy is sufficient in reducing the strength of the scattered emission below our detection limits.
+[ Unsure what to add next]
 
@@
 \centering
-\gridline{\fig{../Figures/geo_J26.pdf}{0.5\textwidth}{(J033225.26)}
-          \fig{../Figures/geo_J36.pdf}{0.5\textwidth}{(J033231.36)}}
-\gridline{\fig{../Figures/geo_J03.pdf}{0.5\textwidth}{(J033230.03)}
-          \fig{../Figures/geo_J64.pdf}{0.5\textwidth}{(J033230.64)}}
+\gridline{\fig{../Figures/geo_J26.pdf}{0.5\textwidth}{(J.26)}
+          \fig{../Figures/geo_J36.pdf}{0.5\textwidth}{(J.36)}}
+\gridline{\fig{../Figures/geo_J03.pdf}{0.5\textwidth}{(J.03)}
+          \fig{../Figures/geo_J64.pdf}{0.5\textwidth}{(J.64)}}
 \caption{Estimated SB profile of \ion{Mg}{2} emission for isotropic and anisotropic dust-free winds.
@@
 The blue diamond points are SB of missing \ion{Mg}{2} emission uniformly distributed inside an annulus for an angle $\Omega=2\pi$, or an anisotropic wind.
+The green hexagon points are SB of predicted emission for a wind that is isotropic and affected by dust.
 The solid line shows the value of the SB detection limits.

### 2018-07-25 Manuscript/vaught_2017.tex
7/25/18

@@
 
-The mass and energy of galactic winds remain poorly constrained via traditional absorption line studies.
+The mass and energy of galactic winds remain poorly constrained via QSO and ``down-the-barrel" absorption line studies.
 One way to better constrain these parameters is to measure the spatial extent of the outflow in emission.
@@
 We do not detect any extended \ion{Mg}{2} emission in any of our galaxies, thus placing strong upper limits on the strength of \ion{Mg}{2} emission at projected distances $R_{\perp} = 13-24$ kpc from the sample galaxies.
-Our observations allow us to create the first ever spatially-resolved map of \ion{Mg}{2} absorption, revealing approximately constant absorption strengths across the galaxy disks.
-Our detection limits in concert with a previous studies Keck/LRIS spectra allow us to model \ion{Mg}{2} emission for isotropic and anisotropic dust-free winds.
-We find that anisotropic winds reduce the strength of estimated missing \ion{Mg}{2} emission below our 5$\sigma$ limit.
+We do detect significant spatially-resolved \ion{Mg}{2} absorption, revealing approximately constant absorption strengths across the galaxy disks.
+Our detection limits in concert with a previous studies Keck/LRIS spectra allow us to compare our observations to previous radiative transfer models of \ion{Mg}{2} emission for isotropic and anisotropic dust/dust-free winds.
+Based on these comparisons, if our galaxies do host \ion{Mg}{2} emission, then the predicted \ion{Mg}{2} based on this modeling suggests that these winds are anisotropic and dusty for any scattered \ion{Mg}{2} emission to lie below our 5$\sigma$ detection limits.
 
@@
 One way of constraining the radial extent and morphology of the outflow is to trace winds in emission.
-This has been demonstrated using rest-frame optical transitions (i.e H$\alpha$, [\ion{O}{3}], etc) as tracers for winds around nearby starbursts (\citethnop{Matsubayashi2009}; \citethnop{Veilleux2009}; \citethnop{Tripp2011}) as these transitions can trace the warm shock heated phase of the gas.
-A novel, alternative transition potentially useful for tracing winds in emission is the \ion{Mg}{2} $\lambda\lambda 2976,2803$ doublet in the rest-frame ultraviolet (UV)
-(Weiner et al.
-2009; Kornei et al.
-2013)\nocite{Weiner2009, Kornei2013}.
+This has been demonstrated using rest-frame optical transitions (i.e H$\alpha$, [\ion{O}{3}], etc) as tracers for winds around nearby starbursts \citep[][]{{Matsubayashi2009,Veilleux2009,Tripp2011}} as these transitions can trace the warm shock heated phase of the gas.
+A novel, alternative transition potentially useful for tracing winds in emission is the \ion{Mg}{2} $\lambda\lambda 2976,2803$ doublet in the rest-frame ultraviolet
+\citep[UV,][]{{Weiner2009, Kornei2013}}.
 While most studies of winds using \ion{Mg}{2} have focused on its absorption kinematics, \cite{Rubin_2011} observed  strong \ion{Mg}{2} emission with a P-Cygni line profile in the spectrum of a strongly star-forming galaxy at redshift $z = 0.694$.
@@
 In this paper, we present the first narrowband imaging of the \ion{Mg}{2} transition around 5 star-forming  galaxies located in the Great Observatories Origins Deep Survey south (GOODS-S) field at redshift $z \sim 0.7$.
-%The value in using narrowband imaging is the ability to spatially resolve any absorption and emission from a galaxy. 
 We use two filters: a line filter and a continuum filter. The line filter covers the \ion{Mg}{2} doublet, while the continuum filter is offset from the line filter by ${\sim}47$ \AA.    
 The resulting imaging in each filter has a total integration time of 10 hrs.
-%The continuum filter allows us to observe the continuum level of the galaxy near the \ion{Mg}{2} doublet.
-With the resulting images taken using the two filters, we can subtract the continuum image from the \ion{Mg}{2} image, effectively creating an image that contains only photons from \ion{Mg}{2}.
+
 As opposed to 1D spectra, the narrowband imaging constrains the surface brightness, optical depth and radial extent of the wind.
@@
 We adopt a $\Lambda$CDM cosmology with $h_{70} = H_0/(70\ \rm{ km}\ \rm{ s}^{-1}\ \rm{ Mpc}^{-1})$, $\Omega_{\rm{M}}= 0.3$, and $\Omega_{\Lambda} = 0.7$.
-In this cosmology, 1\arcsec is $\approx 7\ \rm kpc$ at $z \sim 0.7$.
+In this cosmology, 1\arcsec\  is $\approx 7\ \rm kpc$ at $z \sim 0.7$.
 
@@
 Our target galaxies were selected from a Keck/LRIS survey of UV absorption lines in $\approx 100$ objects having redshifts $0.3< z < 1.4$ and $B_{AB}< 23$ in fields with deep \emph{HST}/ACS imaging \citep{Rubin_2014}.
-In particular, this parent survey targeted galaxies in a total of nine Keck/LRIS pointings located in both of the GOODS fields (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004}) and the AEGIS survey field (the Extended Groth Strip; Davis et al.
-2007)\nocite{Davis2007}.
+In particular, this parent survey targeted galaxies in a total of nine Keck/LRIS pointings located in both of the GOODS fields (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004}) and the AEGIS survey field \citep[the Extended Groth Strip;][]{Davis2007}.
 In inspecting the redshift distribution of the portion of this sample observable from the Southern Hemisphere, we uncovered a narrow peak of nine galaxies in the interval $0.66 < z < 0.68$.
@@
 Our observations were carried out under photometric and thin cloud conditions (program ID: 090.A-0427A). 
-The seeing, which ranged from $0.5\arcsec$ to $2.5\arcsec$, are given in the image header and are derived from DIMM seeing measurements.
-These DIMM values are calculated from zenith observations of bright stars at 0.5 microns, which are then reduced to the zenith angles and wavelengths of the science observation.
-Additionally, a first order correction is then applied for appropriate for a 8m telescope is applied (see Figure \ref{fig.seeing})  Summing the individual exposure times for each filter results in a combined exposure time of $10.0$ hours each for the HeII+47 and HeII/3000+48 filters.
+The seeing values, given in the header of each image, are derived from zenith observations at 0.5 microns with the Paranal differential image motion monitor \citep[DIMM,][]{Sarazin1990}.
+The initial DIMM values are then corrected to the airmass and wavelengths of the science observation.
+Finally, a first order correction is then applied for appropriate for a 8m telescope is applied (see Figure \ref{fig.seeing}).
+The median seeing for the images is $\sim 0.8\arcsec$
+
+Summing the individual exposure times for each filter results in a combined exposure time of $10.0$ hours each for the HeII+47 and HeII/3000+48 filters.
 
@@
 \subsection{Image Reduction}
-The data were reduced using custom routines written in \textbf{Python}. 
+The data were reduced using custom routines written in \emph{Python}. 
 The images were first corrected by subtracting and removing the overscan region of the CCD. 
@@
 Cosmic} algorithm \citep{Dokkum2001}.
-The astrometry solutions were calculated via Astrometry.net (Lang et al.
-2010)\nocite{Lang}, and yield a standard deviation in the galaxy coordinates of $\sigma \approx 0.10''$.
+The astrometry solutions were calculated via Astrometry.net \citep{Lang}, and yield a standard deviation in the galaxy coordinates of $\sigma \approx 0.10''$.
 Before image stacking, we ran each frame through \emph{SExtractor} \citeth{Bertin} in order to create a root mean square (RMS) map of each science image.
@@
 Each individual frame is first sky-subtracted using a background mesh size of 256 pixels which is approximately $64''$. 
-We chose the mesh size to be large enough such that the extended emission is not mistakenly subtracted (Arrigoni Battaia et al. 2015)\nocite{Battaia_2015}. 
+We chose the mesh size to be large enough such that the extended emission is not mistakenly subtracted \citep{Battaia_2015}. 
 The frames, after background-subtraction, are resampled onto a common astrometric solution using a \textit{Lancosz3} interpolation kernel. 
@@
 Additionally, \emph{SWarp} generates stacked RMS images by propagating the error images for each science frame.
-%weighting and average-combining the RMS images for individual science frames.
- %from the night flats and the combination of RMS images for individual science frames. 
  Our final stacked images in each filter are shown in Figure~\ref{fig:stacked_image} with the target galaxies indicated.
@@
 \begin{tabular}{llllllll} \hline \hline
-Object\footnote{ Name in parenthesis to be used as shorthand for the objects throughout the remainder of the paper } & R.A.
-& Dec  & $z$ & SFR($M_{\odot}$ yr$^{-1}$) & $\log{M_{*}/M_{\odot}}$ & EW$_{\rm{obs}}$(\AA) & $\tau_V$\footnote{ 97.5th percentile of the $\tau_V$ distribution}\smallskip      \\ \hline
-J033225.26-274524.0 (J.26)      & 03:32:25.26 & -27:45:23.9 & 0.6660 & $9.1_{-3.7}^{+1.3}$& $9.86_{-0.04}^{+0.05}$ & $7.539\pm 0.354$ & 4.812\\
+Object\footnote{ Name in parenthesis to be used as shorthand for the objects throughout the remainder of the paper.
+} & R.A.
+& Dec  & $z$ & SFR($M_{\odot}$ yr$^{-1}$) & $\log{M_{*}/M_{\odot}}$ & EW$_{\rm{obs}}$(\AA) & $\tau_V$\footnote{ Total V-band optical depth of dust.}\smallskip      \\ \hline
+J033225.26-274524.0 (J.26)      & 03:32:25.26 & -27:45:23.9 & 0.6660 & $9.1_{-3.7}^{+1.3}$& $9.86_{-0.04}^{+0.05}$ & $7.539\pm 0.354$ &  $1.227_{-0.20}^{+1.54}$\\
 
-J033231.36-274725.0 (J.36)      & 03:32:31.35 & -27:47:24.9 &   0.6669 & $10.5_{-1.6}^{+1.7}$ & $10.02_{-0.03}^{+0.03}$&$5.835 \pm 0.493$ & 3.427\\
+J033231.36-274725.0 (J.36)      & 03:32:31.35 & -27:47:24.9 &   0.6669 & $10.5_{-1.6}^{+1.7}$ & $10.02_{-0.03}^{+0.03}$&$5.835 \pm 0.493$ & $1.377_{-0.23}^{+0.60}$\\
 
-J033230.03-274347.3  (J.03)     & 03:32:30.03 & -27:43:47.2  &   0.6679 & $3.8_{-0}^{+0}$ & $10.98_{-0.0}^{+0.01}$ &$12.794 \pm 1.710$ & 2.867 \\
+J033230.03-274347.3  (J.03)     & 03:32:30.03 & -27:43:47.2  &   0.6679 & $3.8_{-0}^{+0}$ & $10.98_{-0.0}^{+0.01}$ &$12.794 \pm 1.710$ & $0.297_{-0.0}^{+0.0}$ \\
 
-J033229.64-274242.6  (J.64)    & 03:32:29.64 & -27:42:42.5 & 0.6671 & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &$13.239 \pm 0.263$ & 5.042\\
+J033229.64-274242.6  (J.64)    & 03:32:29.64 & -27:42:42.5 & 0.6671 & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &$13.239 \pm 0.263$ & $3.897_{-0.93}^{+1.15}$\\
 
-J033230.57-274518.2  (J.57)    & 03:32:30.56 & -27:45:18.2 &   0.6807  & $12.6_{-2.1}^{+1.7}$ & $10.48_{-0.07}^{+0.03}$ &$6.106 \pm 0.370$ &4.022 \\
+J033230.57-274518.2  (J.57)    & 03:32:30.56 & -27:45:18.2 &   0.6807  & $12.6_{-2.1}^{+1.7}$ & $10.48_{-0.07}^{+0.03}$ &$6.106 \pm 0.370$ & $1.262_{-0.40}^{+1.23}$ \\
 
@@
 \begin{tabular}{llllll} \hline \hline 
-Filter & $\lambda_{\rm{eff}}$(\AA)\footnote{$\lambda_{\rm{eff}}$ is the effective wavelength of the filter transmission curve.} & $\Delta\lambda$(\text{\AA})    & $N$\footnote{Total number of images}   & $T(s)$\footnote{Total exposure time} & $S$\footnote{S, the sensitivity of the filter, is in units of $10^{-17}$ ergs counts$^{-1}$ cm$^{-2}$ }\smallskip  \\ \hline
+Filter & $\lambda_{\rm{eff}}$(\AA)\footnote{$ \lambda_{\rm{eff}}$ is the effective wavelength of the filter transmission curve.} & $\Delta\lambda$(\text{\AA})    & $N$\footnote{ Total number of images.}   & $T(s)$\footnote{ Total exposure time.} & $S$\footnote{ S, the sensitivity of the filter, is in units of $10^{-17}$ ergs counts$^{-1}$ cm$^{-2}$ .}\smallskip  \\ \hline
 HeII+47  & 4675.21 & 50.11 & 38  & 35,959 & 2.45 \\
@@
 We acquired observations of the standard star GD50 from archival ESO calibration imaging at 4 independent epochs.
-Performing aperture photometry at each epoch and airmass, we calculated the atmospheric extinction coefficients ($k$) to be 0.181 magnitudes for the HeII/3000+48 filter and 0.190 magnitudes for the HeII+47 filter.
-We perform absolute flux calibration using the methods of Jacoby et al.
-(1990).
+Performing aperture photometry at each epoch and airmass, we calculated the atmospheric extinction coefficients, $k$, to be 0.181 magnitudes for the HeII/3000+48 filter and 0.190 magnitudes for the HeII+47 filter.
+We perform absolute flux calibration using the methods of \cite{Jacoby1987}.
 We first convolve the spectral energy distribution of the standard star, $F(\lambda)$ in ergs sec$^{-1}$ \AA$^{-1}$ cm$^{-2}$, with that of the known transmission curve of the filter, $T_{i}(\lambda)$.
@@
 We use the supplementary spectra from \citet{Rubin_2014} to fit the continuum and determine the spectral slope of each galaxy.
-We use the interactive fitting routine \emph{lt\_continuumfit} from the \emph{linetools} package (Prochaska et al.
-2016)\footnote{https://github.com/linetools/linetools}\nocite{Prochaska2016} to fit the continuum.
+We use the interactive fitting routine \emph{lt\_continuumfit} from the \emph{linetools} package \citep{Prochaska2016}\footnote{https://github.com/linetools/linetools} to fit the continuum.
 We then find the total continuum flux in each filter by convolving the fitted continuum with each filter's transmission curve.
@@
 \begin{tabular}{lllll} \hline \hline
-Object & F$_{\rm{src}}$(\ion{Mg}{2})\footnote{\ion{Mg}{2} flux is in $10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$.
-The value in the parenthesis is the statistical significance with respect to $\sigma_{\text{src}}$ } & 5SB$_{\text{limit}}$\footnote{Limits are in $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^{-2}$} & Area\footnote{Area of the extended annulus in sq.arcsec} \\  \hline
+Object & F$_{\rm{src}}$(\ion{Mg}{2})\footnote{ \ion{Mg}{2} flux is in $10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$.
+The value in the parenthesis is the statistical significance with respect to $\sigma_{\text{src}}$.
+} & 5SB$_{\text{limit}}$\footnote{ Limits are in $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^{-2}$.} & Area\footnote{ Area of the extended annulus in sq.arcsec.} \\  \hline
 J033225.26-274524.0 &  2.44(0.92)& 6.51	& 21 \\
@@
 Every galaxy is placed in the same row in each column.
-The columns show simulated emission, with levels of 0, 1, 3, 5, 10, and 20 times SB$_{lim}$.
+The columns show simulated emission, with levels of 0, 1, 3, 5, 10, and 20 times SB$_{\rm lim}$.
 Each postage stamp has a size of $5'' \times 5''$ (corresponding to $35$ kpc $\times$ $35$ kpc at $z\sim 0.70$).
@@
 We then apply a S/N $= 1.5$ cut to the continuum image and create a histogram to show the distribution of EW$_{\rm{MgII}}$ inside the contour.
-The histograms are shown in Figures \ref{fig:ew11} through \ref{fig:ew55}.
+The histograms are shown in Figure \ref{fig:ews}.
 Having removed pixels with low-S/N continuum values from our images, we compute the mean equivalent width inside the Keck/LRIS apertures.
@@
 To assess the morphology of the \ion{Mg}{2} absorption, we determine the distance of each pixel from the center of each galaxy in kiloparsecs.
-We plot the EW$_{\rm{MgII}}$ over this projected distance for each galaxy in Figures \ref{fig:ew11} through \ref{fig:ew55}.
+We plot the EW$_{\rm{MgII}}$ over this projected distance for each galaxy in Figure \ref{fig:ews}.
 Although some of the plots suggest a slight upward trend in the values of the EW$_{\rm{MgII}}$ with increasing radii, we cannot be confident in this trend because of the large scatter.
 To better visualize the data and test the significance of the trend, we bin the data radially in 3-5 kpc-wide bins.
-For example, in Figure \ref{fig:ew44}, the EW$_{\rm{MgII}}$ from absorption of J.03 extends out to $\sim$ 25 kpc.
+For example, in Figure \ref{fig:ews}(c), the EW$_{\rm{MgII}}$ from absorption of J.03 extends out to $\sim$ 25 kpc.
 The EW$_{\rm{MgII}}$ values are binned in 5 kpc increments.
@@
 \subsubsection{\ion{Mg}{2}\ absorption in surface brightness profiles} \label{subsubsec:SBprofiles}
-Although we do not detect any extended \ion{Mg}{2} emission, we do observe a decrement of flux in the SB profiles of 4 out of 5 galaxies in our sample.
+Although we do not detect any extended \ion{Mg}{2} emission, we do observe a decrement of flux, SB$_{\rm abs}$, in the SB profiles of 4 out of 5 galaxies in our sample.
 Figure \ref{fig:sb_profiles} shows the SB profiles for the 5 galaxies in our sample.
@@
 In Table \ref{tab:abs_props} we report for the galaxies J.26, J.36 and J.03 a maximum decrement in the SB profile due to absorption $\sim$ -5.00$\times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
-Additionally, we report for galaxy J.64 a decrement one order of magnitude greater than the previous galaxies with a value of -18.2 $\pm$ 0.127 $\times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
-Finally, for galaxy J.57 the absorption decrement is strongest at the center of the galaxy with a SB value of -1.25 $\pm$ 1.15 $10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
+Additionally, we report for galaxy J.64 a SB$_{\rm abs}$ one order of magnitude greater than the previous galaxies with a value of -18.2 $\pm$ 0.127 $\times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
+Finally, for galaxy J.57, SB$_{\rm abs}$ is strongest at the center of the galaxy with a SB value of -1.25 $\pm$ 1.15 $10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
 However, the measured SB of this decrement including error is consistent with measuring zero absorption.
@@
 \ref{subsec.ew}, and the resulting values are summarized in Table \ref{tab:abs_props}.
-Comparing our narrowband EWs with those measured from the spectra, we find agreement to within a 1.6-4.6$\sigma$ for galaxies J.26 and J.36, and more statistically significant differences for galaxies J.03 and J.64 We discuss possible causes for these differences below.
+Comparing our narrowband EWs with those measured from the spectra, we find agreement to within a 1.6-4.6$\sigma$ for galaxies J.26 and J.36, and more statistically significant differences for galaxies J.03 and J.64.
+We discuss possible causes for these differences below.
 
@@
 \begin{tabular}{llllll} \hline \hline
-Object & SB$_{abs}$\footnote{Maximum SB decrement, values are in units of $10^{-18}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$} & $R$\footnote{Radius of SB$_1$ contour in kpc} &\ \ \ EW$_{\rm{obs}}$($\AA$)\footnote{ Measured from EW images} & EW$_{\rm{obs}}$($\AA$)\footnote{Measured from Keck/LRIS spectra}  \\  \hline
+Object & SB$_{abs}$\footnote{ Maximum SB decrement, values are in units of $10^{-18}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$.} & $R$\footnote{ Radius of SB$_1$ contour in kpc.} &\ \ \ EW$_{\rm{obs}}$($\AA$)\footnote{ Measured from EW images.} & EW$_{\rm{obs}}$($\AA$)\footnote{ Measured from Keck/LRIS spectra.}  \\  \hline
 J.26 &  $-5.39 \pm 1.28 $ & 8 &     $\ \ \ 3.51 \pm 0.80$ & $7.53 \pm 0.35 $\\
@@
 Excepting the galaxy J.03, the SB of this ``missing'' emission lies above our detection limits.
-%Without taking into account that the emission may not exceed to a radial extent outside the galaxy disk,
 Under the assumption that the wind in these galaxies does in fact extend beyond the $\rm SB_1$ isophotal contour (at $R_{\perp} = 8-21$ kpc), this result suggests that these galaxies do not host isotropic, dust-free winds.
@@
 Direct evidence of anisotropic winds, specifically bipolar morphology, has been observed in emission from cold and shock heated gas in local starburst galaxies \citep[e.g.][]{{Walter2002,Westmoquette2008M,Strickland2009}}.
-For distant galaxies, enhanced absorption \ion{Mg}{2} along a galaxy's minor axis (Bordoloi et al.
-2011; Bouche?
-et al.
-2012; Kacprzak et al.
-2012),  higher outflow velocities toward $z \sim 1$ galaxies having $i < 45 ^{\circ}$ are suggestive of bipolar outflows.
+For distant galaxies, enhanced absorption \ion{Mg}{2} along a galaxy's minor axis \citep[][]{{Bordoloi2011,Kacprzak2012,Bouche2012}},  higher outflow velocities toward $z \sim 1$ galaxies having $i < 45 ^{\circ}$ are suggestive of bipolar outflows.
 Furthermore, \cite{Rubin_2014} analysis provide strong evidence for the ubiquity of bipolar outflows in distant galaxies.
@@
 The strength of the flux is reduced by a factor of $(1+\tau_{\rm{dust}})^{-1}$, where $\tau_{\rm{dust}}$ is the integrated opacity of dust.
+Estimates of the dust content of each galaxy come from SED modeling in \cite{Rubin_2014} and are shown in Table \ref{tab:prop}.
 The green hexagons in Figure \ref{fig.emission} shows the predicted SB profile for an anisotropic wind with dust.
-As mentioned in the previous section, anisotropy alone does not reduce the predicted emission of J.64 below our detection limits.
-The profile in  Figure \ref{fig.emission} shows that combination of dust and anisotropy is sufficient in reducing the strength of the scattered emission below our detection limits.
-[ Unsure what to add next]
+For the galaxies J.26, J.36 and J.03, the introduction of dust reduces the predicted emission further below our detection limits and profiles reduced by anisotropy only.
+For galaxy J.64, anisotropy alone does not reduce the predicted emission of J.64 below our detection limits.
+The profile in Figure \ref{fig.emission} shows that combination of dust and anisotropy is sufficient in reducing the strength of the scattered emission of J.64 below our detection limits.
 
@@
 We presented the results from a narrowband imaging search for \ion{Mg}{2} emission in a sample of star-forming galaxies at a redshift of $z \sim 0.70$ which are known to drive outflows in  \ion{Mg}{2}.
-We did not detect any \ion{Mg}{2} emission in this sample, and place a $5\sigma$ detection upper limit of SB(\ion{Mg}{2}) $\approx$ 5.74 $\times 10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$, measured in an extended annulus outside the largest galaxy, at minimum projected distances of 13, 18, 21 and 24 kpc from the centers of each target.
+We did not detect any \ion{Mg}{2} emission in this sample, and place a $5\sigma$ detection upper limit of SB(\ion{Mg}{2}) $\approx$ 5.74 $\times 10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$, measured in an extended annulus, $\sim 20$ sq.arcsec, at minimum projected distances of 13, 18, 21 and 24 kpc from the centers of each target.
 We detected a significant amount of \ion{Mg}{2} absorption in a total of 4 galaxies out of our 5 galaxy sample.
 Furthermore, our imaging allows us to generate spatially-resolved maps of \ion{Mg}{2} absorption in a distant galaxy sample for the first time.
-This absorption covers the center of the galaxies out to an isophotal radius defined by the SB$_1$ (1$\sigma$) depth of a continuum + \ion{Mg}{2} image, at approximately $\sim 22$ kpc, suggesting that the absorbing gas fully covers the stellar disks out to this distance.
+This absorption covers the center of the galaxies out to an isophotal radius defined by the SB$_1$ (1$\sigma$) depth of a continuum + \ion{Mg}{2} image, at approximately $\sim 22$ kpc, suggesting that the absorbing gas is optically thick and fully covers the stellar disks out to this distance.
 The EWs measured in these maps are in broad agreement with measured EWs using Keck/LRIS integrated slit spectroscopy.
@@
 We are able to rule out that the winds in our sample are isotropic and dust free, as our images are sufficiently sensitive to detect the predicted emission from such models.
-By assuming anisotropic winds, we were able to reduce the strength of the predicted emission to lie below our detection limit for 3 of our sample galaxies.
-We must invoke additional phenomena like dusty ISM material
-to reconcile the predicted SB of emission and our detection limits in the fourth sample galaxy.
+By assuming dust/dust-free anisotropic winds, we were able to reduce the strength of the predicted  \ion{Mg}{2} emission to lie below our detection limit for 4 of our sample galaxies.
+Although our detection limits suggest that the winds in our sample are not isotropic and dust-free, questions linger regarding the relative roles wind anisotropy, dust content, and extent play in reducing scattered emission.
+Thus, Deeper imaging in \ion{Mg}{2} are required to observe any extended emission beyond the depth of our images and up to our predicted SB profiles to characterize the morphology of these winds.
 
-Based on the radial extent and strength of our measured \ion{Mg}{2} absorption, the \ion{Mg}{2} is optically thick.
-Deeper images in \ion{Mg}{2} are required to observe any extended emission beyond the depth of our images.
-Although our detection limits suggest that the winds in our sample are not isotropic and dust-free, questions linger regarding the relative roles wind anisotropy, dust content, and extent play in reducing scattered emission.
-
-A new generation of instruments such as the Keck Cosmic Web Imager (KCWI) or the Multi Unit Spectroscopic Explorer (MUSE) should be used to disentangle these issues.
+%A new generation of instruments such as the Keck Cosmic Web Imager (KCWI) or the Multi Unit Spectroscopic Explorer (MUSE) should be used to disentangle these issues.
 
@@
 \centering
-\gridline{\fig{../Figures/geo_J26.pdf}{0.5\textwidth}{(J.26)}
-          \fig{../Figures/geo_J36.pdf}{0.5\textwidth}{(J.36)}}
-\gridline{\fig{../Figures/geo_J03.pdf}{0.5\textwidth}{(J.03)}
-          \fig{../Figures/geo_J64.pdf}{0.5\textwidth}{(J.64)}}
+\gridline{\fig{../Figures/geo_J26.pdf}{0.5\textwidth}{(a: J.26)}
+          \fig{../Figures/geo_J36.pdf}{0.5\textwidth}{(b: J.36)}}
+\gridline{\fig{../Figures/geo_J03.pdf}{0.5\textwidth}{(c: J.03)}
+          \fig{../Figures/geo_J64.pdf}{0.5\textwidth}{(d: J.64)}}
 \caption{Estimated SB profile of \ion{Mg}{2} emission for isotropic and anisotropic dust-free winds.
-The black square points are SB of predicted \ion{Mg}{2} emission uniformly distributed inside an annulus for an angle $\Omega=4\pi$, or an isotropic wind.
-The blue diamond points are SB of missing \ion{Mg}{2} emission uniformly distributed inside an annulus for an angle $\Omega=2\pi$, or an anisotropic wind.
-The green hexagon points are SB of predicted emission for a wind that is isotropic and affected by dust.
+The red hexagons points are SB of predicted \ion{Mg}{2} emission uniformly distributed inside an annulus for an angle $\Omega=4\pi$, or an isotropic wind.
+The black diamond points are SB of missing \ion{Mg}{2} emission uniformly distributed inside an annulus for an angle $\Omega=2\pi$, or an anisotropic wind.
+The blue triangle points are SB of predicted emission for a wind that is anisotropic and affected by dust.
 The solid line shows the value of the SB detection limits.
-The dashed vertical and horizontal lines represent outer radius of the extended annulus used to measure the initial detection limits and the value of the SB detection limit in that annulus.}
+The dashed vertical and horizontal lines represent outer radius of the extended annulus used to measure the initial detection limits and the value of the SB detection limit in that annulus.
+The legend in panel (a) holds for the remaining panels.}
 \label{fig.emission}

### 2018-07-27 Manuscript/vaught_2017.tex
7/25/18
7/27/18

@@
 \affiliation{Department of Astronomy, San Diego State University, San Diego, CA 92182}
-\affiliation{Center for Astrophysics and Space Sciences, Department of Physics, University of California, San Diego, CA}
+\affiliation{Department of Physics, University of California, San Diego, 9500 Gilman Dr. La Jolla, CA 92093, USA}
 
  \author{Kate H. R. Rubin }
- \affiliation{Department of Astronomy, San Diego State University, San Diego, CA 92182}
+ \affiliation{Department of Astronomy, San Diego State University, San Diego, CA 92182, USA}
 
@@
 One way to better constrain these parameters is to measure the spatial extent of the outflow in emission.
-We perform a VLT/FORS2 narrowband imaging of 5 star-forming galaxies at redshift $z=0.67-0.69$ in the GOODS-S field as part of an effort to spatially resolve and constrain the radial extent of large-scale outflows traced by \ion{Mg}{2} emission.
-These observations probe extended \ion{Mg}{2} emission down to unmatched surface brightness limits of 5.74 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ (5$\sigma$).
-We do not detect any extended \ion{Mg}{2} emission in any of our galaxies, thus placing strong upper limits on the strength of \ion{Mg}{2} emission at projected distances $R_{\perp} = 13-24$ kpc from the sample galaxies.
-We do detect significant spatially-resolved \ion{Mg}{2} absorption, revealing approximately constant absorption strengths across the galaxy disks.
+We perform a VLT/FORS2 narrowband imaging search around 5 star-forming galaxies at redshift $z=0.67-0.69$ in the Great Observatories Origins Deep Survey South (GOODS-S) field to constrain the radial extent of large-scale outflows traced by resonantly scattered \ion{Mg}{2} emission.
+These observations probe unmatched surface brightness limits of 5.74 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ (5$\sigma$).
+We do not detect any extended emission around any of the sample galaxies, thus placing strong upper limits on the brightness of \ion{Mg}{2} emission at projected distances $R_{\perp} = 13-24$ kpc.
+The imaging also resolves the \ion{Mg}{2} observed galaxy spatially, revealing approximately constant absorption strengths across the galaxy disks.
 Our detection limits in concert with a previous studies Keck/LRIS spectra allow us to compare our observations to previous radiative transfer models of \ion{Mg}{2} emission for isotropic and anisotropic dust/dust-free winds.
@@
 \section{Introduction}\label{sec:intro}
-Galactic winds play a critical role in regulating the star formation rates and stellar masses of galaxies \citeth{Werk_2014}; however, the physical mechanism that powers these galactic winds remains uncertain.
-Some possible mechanics have been proposed by theoretical studies that include thermal pressure from core collapse supernova, radiation pressure from starbursts and finally cosmic ray pressure (\citethnop{Larson_1974}; \citethnop{Chevalier_1985}; \citethnop{Springel_2003}; \citethnop{Sugahara_2017}).
-Additionally, the impact galactic winds have on their host galaxies (i.e, their mass and energy content) has remained difficult to constrain with observations.
+Galactic winds play a critical role in regulating the star formation rates and stellar masses of galaxies \citeth{Werk_2014}; however, the physics that powers these winds remains uncertain.
+Some possible mechanisms have been proposed by theoretical studies that include thermal pressure from core collapse supernovae, radiation pressure from starbursts, and finally cosmic ray pressure (\citethnop{Larson_1974}; \citethnop{Chevalier_1985}; \citethnop{Springel_2003}; \citethnop{Sugahara_2017}).
+Additionally, the impact galactic winds have on their host galaxies (i.e., their mass and energy content) has remained difficult to constrain with observations.
 
-An accurate picture of what types of galaxies host outflows comes from numerous absorption line studies of galaxies (\citethnop{Veilleux2005}; \citethnop{Weiner2009}; \citethnop{Martin2012}; \citethnop{Rubin_2014}).
-Outflows are detected by measuring the blueshift (outflow) or redshift (inflow) of absorption transitions with respect to the host galaxy systematic velocity.
- %Spectroscopy of galaxies from low to high redshifts probing cold gas ($T \lesssim 10^2$ K) which absorbs in \ion{Na}{1} and cool gas ($T \sim 10^4$ K) in \ion{Mg}{2} has revealed outflows in most galaxies that host active star-formation (e.g.
+An accurate picture of the types of galaxies that host outflows comes from numerous absorption line studies of galaxies (\citethnop{Veilleux2005}; \citethnop{Weiner2009}; \citethnop{Martin2012}; \citethnop{Rubin_2014}).
+Gas flows are detected by measuring the blueshift (outflow) or redshift (inflow) of absorption transitions with respect to the host galaxy systemic velocity.
+Spectroscopy of galaxies from low to high redshifts probing cold gas ($T \lesssim 10^2$ K) which absorbs in \ion{Na}{1} and cool gas ($T \sim 10^4$ K) in \ion{Mg}{2} has revealed outflows in most galaxies that host active star-formation (e.g.
 \citethnop{chen2010}; \citethnop{Martin2012}; \citethnop{Rubin_2014}).
-Even though these probes can constrain: the radial velocity, column density and covering fraction of the flow, 
-this method is weak in constraining the overall radial extent and provides no information on the morphology of the outflow.
+Even though this technique constrains the radial velocity, column density and covering fraction of the flow, it weakly constrains the overall radial extent and provides no information on the morphology of the gas.
 
-One way of constraining the radial extent and morphology of the outflow is to trace winds in emission.
-This has been demonstrated using rest-frame optical transitions (i.e H$\alpha$, [\ion{O}{3}], etc) as tracers for winds around nearby starbursts \citep[][]{{Matsubayashi2009,Veilleux2009,Tripp2011}} as these transitions can trace the warm shock heated phase of the gas.
-A novel, alternative transition potentially useful for tracing winds in emission is the \ion{Mg}{2} $\lambda\lambda 2976,2803$ doublet in the rest-frame ultraviolet
-\citep[UV,][]{{Weiner2009, Kornei2013}}.
+An alternative method that can in principal asses the radial extent and morphology of outflows is to trace the gas in emission.
+This has been demonstrated using rest-frame optical transitions (i.e H$\alpha$, [\ion{O}{3}], etc) as tracers for winds around nearby starbursts \citep[][]{{Matsubayashi2009,Veilleux2009}} as these transitions can trace the warm shock heated phase of the gas.
+Another transition potentially useful for tracing winds in emission is the \ion{Mg}{2} $\lambda\lambda 2976,2803$ doublet in the rest-frame ultraviolet
+\citep[UV;][]{{Weiner2009, Kornei2013}}.
 While most studies of winds using \ion{Mg}{2} have focused on its absorption kinematics, \cite{Rubin_2011} observed  strong \ion{Mg}{2} emission with a P-Cygni line profile in the spectrum of a strongly star-forming galaxy at redshift $z = 0.694$.
-This emission was the first detection of an outflow beyond the spatial extent of the galaxy continuum in the distant universe, with a minimum spatial extent  $>$ 7 kpc.
+In addition, the emission was spatially extended, permitting the first direct measurement of the extent of an outflow ($>$ 7 kpc) in the distant universe.
 
-One proposed production mechanism for the galaxy's observed \ion{Mg}{2} line profile is photon scattering.
-In this mechanism, \ion{Mg}{2} ions in the region of the wind closest to the observer will absorb continuum photons in the resonant transitions, $\lambda_{2796}$ and $\lambda_{2803}$.
-Once these transitions are excited, they may only decay back to the ground state and if the optical depth of the gas is high, then the gas will resonantly trap the absorbed photons.
-Because the photons are absorbed in the rest frame of the gas, the absorption will be blueshifted relative to the galaxy's systematic velocity.
+One proposed production mechanism for such P-Cygni profiles is photon scattering.
+In this mechanism, \ion{Mg}{2} ions in the region of the wind closest to the observer will absorb continuum photons in the resonant transitions at wavelengths 2796\AA, $\lambda_{2796}$, and 2803, \AA $\lambda_{2803}$.
+Once these transitions are excited, they may only decay back to the ground state.
+If the optical depth of the gas is high, then the gas will resonantly trap the absorbed photons.
+Because the photons are absorbed in the rest frame of the gas, the absorption will be blueshifted relative to the galaxy's systemic velocity.
 The \ion{Mg}{2} ions in the section of the wind farthest from the observer will absorb and scatter photons that are redshifted relative to the front portion of the wind.
-Because the photons are redshifted, the photons will be able to travel freely towards the observer through the wind to produce emission at and redward of the systematic velocity of the galaxy (\citethnop{Rubin_2011}, \citethnop{Prochaska_2011}).
-Since the first detection of \ion{Mg}{2} emission by \citet{Rubin_2011}, another detection was reported by \cite{Martin2013}, who observed \ion{Mg}{2} emission that extends $12-18$ kpc from a strongly star-forming galaxy
+Because the photons are redshifted, the photons travel freely towards the observer through the wind to produce emission at and redward of the systemic velocity of the galaxy (\citethnop{Rubin_2011}, \citethnop{Prochaska_2011}).
+Since the first detection of \ion{Mg}{2} emission in an individual galaxy by \citet{Rubin_2011}, another detection was reported by \cite{Martin2013}, who observed \ion{Mg}{2} emission that extends $12-18$ kpc from a strongly star-forming galaxy
 at $z=0.9392$.
-\ion{Mg}{2} has also been studied in wide-field galaxy surveys conducted with Keck/DEIMOS and VLT/MUSE  (\citethnop{Erb2012}, \citethnop{Feltre2018}).
-These surveys, which include galaxies with redshifts $ 0.70 < z < 2.30$, find that \ion{Mg}{2} may be detected in pure emission, pure absorption or with P-Cygni profiles.
-Detections of \ion{Mg}{2} in emission were found to be associated with galaxies of lower stellar mass and bluer spectral slopes.
+\ion{Mg}{2} has also been studied in wide-field galaxy surveys conducted with Keck/DEIMOS and VLT/MUSE  (\citethnop{Weiner2009}, \citethnop{Kornei2013},\citethnop{Erb2012}, \citethnop{Feltre2018}).
+These surveys, which include galaxies with redshifts $ 0.70 < z < 2.30$, find that \ion{Mg}{2} may be detected in pure emission, pure absorption or with P-Cygni profiles and that detections of \ion{Mg}{2} in emission were found to be associated with galaxies of lower stellar mass and bluer spectral slopes.
 
 The diversity of these spectral profiles may be understood using radiative transfer modeling of galactic winds.
-%Various models of galactic winds are explored in 
 \citet{Prochaska_2011} have used this technique to predict 
-%This analysis involved generating 
-spectra for the  \ion{Mg}{2} and  \ion{Fe}{2}$^*$ transitions for a variety of wind morphologies.
-%, using a set of radiative transfer algorithms, for an isotropic and anisotropic set of dust and dust-free winds. 
-The authors demonstrated that isotropic dust-free winds will conserve photon flux, thus predicting that blueshifted absorption lines should be accompanied by emission profiles of winds with similar equivalent widths (EW).
-Anisotropic winds, however, were demonstrated to exhibit significantly weaker emission at strengths proportional to the angular extent (i.e., solid angle) of the wind.
-The scattered emission was additionally weakened by the inclusion of dust and the presence of a strongly-absorbing interstellar medium (ISM).
+spectra for the  \ion{Mg}{2} and  \ion{Fe}{2}$^*$ fine-structure transitions for a variety of wind morphologies.
+The authors demonstrated that isotropic dust-free winds will conserve photon flux, thus predicting that blueshifted absorption lines should be accompanied by emission lines with similar equivalent widths (EW).
+Anisotropic winds, however, were demonstrated to exhibit significantly weaker emission by a factor proportional to the angular extent (i.e., solid angle) of the wind.
+Scattered emission was found to be additionally weakened by the inclusion of dust and the presence of a strongly-absorbing interstellar medium (ISM).
 Thus, spatially-resolved measurement of the surface brightness of this emission constrains not only the radial extent of the emitting material, but also its morphology and dust content.
 
-In this paper, we present the first narrowband imaging of the \ion{Mg}{2} transition around 5 star-forming  galaxies located in the Great Observatories Origins Deep Survey south (GOODS-S) field at redshift $z \sim 0.7$.
-We use two filters: a line filter and a continuum filter. The line filter covers the \ion{Mg}{2} doublet, while the continuum filter is offset from the line filter by ${\sim}47$ \AA.    
+In this paper, we present the first narrowband imaging of the \ion{Mg}{2} transition around 5 star-forming  galaxies located in the  GOODS-S field at redshift $z \sim 0.7$. 
+We use two filters: a  ``line filter" covering the \ion{Mg}{2} doublet, and a ``continuum filter" that is offset from the line filter by ${\sim}47$ \AA.    
 The resulting imaging in each filter has a total integration time of 10 hrs.
-
 As opposed to 1D spectra, the narrowband imaging constrains the surface brightness, optical depth and radial extent of the wind.
-This narrowband imaging allows us to create the first ever high-S/N spatially resolved map of \ion{Mg}{2} emission and absorption.
+These observations allow us to create the first ever high-S/N spatially resolved map of both \ion{Mg}{2} emission and absorption.
 
 In Section \ref{sec:obs_red} we describe our sample of GOOD-S galaxies, supplemental Keck/LRIS spectra, as well as our VLT/FORS2 observations, image reduction, and absolute flux calibration.
-We go into detail in our method of continuum subtraction in Section \ref{sec.cont_sub}.
-The analysis of these data is presented in Section \ref{sec:analysis},
+We describe our method of continuum subtraction in Section \ref{sec.cont_sub}.
+Analysis of these data is presented in Section \ref{sec:analysis},
 including our methods for calculating surface brightness profiles and detection limits for each galaxy, as well as maps of \ion{Mg}{2} equivalent widths.
-%in detail we discuss the production surface bright profiles and limits for each galaxy, as well as the production of narrowband %measured equivalent widths. 
-Section \ref{sec:results} presents results from our narrowband imaging analysis.
+Section \ref{sec:results} presents results from this analysis.
 We compare our SB detection limits to previous detections of extended \ion{Mg}{2} emission,  and compare our observations to predictions made by radiative transfer models in Section \ref{sec:discussion}.
@@
 \subsection{Sample Selection}
-Our target galaxies were selected from a Keck/LRIS survey of UV absorption lines in $\approx 100$ objects having redshifts $0.3< z < 1.4$ and $B_{AB}< 23$ in fields with deep \emph{HST}/ACS imaging \citep{Rubin_2014}.
+Our target galaxies were selected from a Keck/LRIS survey of UV absorption lines in $\approx 100$ objects having redshifts $0.3< z < 1.4$ and $B_{AB}< 23$ in fields with deep Hubble Space Telescope/Advance Camera for Surveys (\emph{HST}/ACS) imaging \citep{Rubin_2014}.
 In particular, this parent survey targeted galaxies in a total of nine Keck/LRIS pointings located in both of the GOODS fields (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004}) and the AEGIS survey field \citep[the Extended Groth Strip;][]{Davis2007}.
@@
 Modeling of the galaxy broad-band spectral energy distributions obtained from multi-wavelength ancillary imaging data yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$.
-The properties and nomenclature of the sample, as well as precise target coordinates taken from \cite{Rubin_2014} ) are listed in Table \ref{tab:prop}.
+The properties of the sample, as well as precise target coordinates taken from \cite{Rubin_2014} are listed in Table \ref{tab:prop}.
 
@@
 Our observations were carried out under photometric and thin cloud conditions (program ID: 090.A-0427A). 
-The seeing values, given in the header of each image, are derived from zenith observations at 0.5 microns with the Paranal differential image motion monitor \citep[DIMM,][]{Sarazin1990}.
-The initial DIMM values are then corrected to the airmass and wavelengths of the science observation.
-Finally, a first order correction is then applied for appropriate for a 8m telescope is applied (see Figure \ref{fig.seeing}).
-The median seeing for the images is $\sim 0.8\arcsec$
-
-Summing the individual exposure times for each filter results in a combined exposure time of $10.0$ hours each for the HeII+47 and HeII/3000+48 filters.
+The seeing values, given in the header of each image, were derived from zenith observations at 0.5 microns with the Paranal differential image motion monitor \citep[DIMM,][]{Sarazin1990} and include a correction for the airmass and wavelengths of the science observation, as well as a first order correction for the larger site of the Antu mirror.
+The distribution of these seeing values are shown in Figure \ref{fig.seeing}.
+The median seeing for the images is $\sim 0.8\arcsec$.
+Summing the individual exposure times for each filter results in a combined exposure time of $10.0$ hours each for the HeII+47 and HeII/3000+48 images.
 
@@
 \centering
-\includegraphics[scale=.73]{../Figures/fors2_color_imstamps.pdf}
+\includegraphics[scale=.75]{../Figures/fors2_color_imstamps.pdf}
 \caption{Color imaging of our sample galaxies in the \emph{HST}/ACS F435W, F606W, and F775W filters obtained as part of the GOODS survey (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004}).
-Each image is 5'' $\times$ 5'' ( or about $ 40 \rm \ kpc \times 40 \rm \ kpc $) .\label{fig:hstims}}
+Each image is 5\arcsec $\times$ 5\arcsec ( or about $ 35 \rm \ kpc \times 35 \rm \ kpc $) .\label{fig:hstims}}
 \end{figure*}
@@
            \fig{../Figures/filt_57_spectra.pdf}{0.5\textwidth}{(e)}
-\caption{Keck/LRIS spectra of the sample galaxies and the transmission curves of the filters HeII+47 (blue dashed line) and HeII/3000+48 (red dashed line) .
+\caption{Keck/LRIS spectra of the sample galaxies and the transmission curves of the filters HeII+47 (blue dashed line) and HeII/3000+48 (red dashed line).
 The left-hand axis is in units of flux density and the right-hand axis is the percentage of light transmitted by the filter at each wavelength.
@@
 \includegraphics[scale=.55]{../Figures/avg_seeing_HEII3000.pdf}
-\caption{\textbf{Top}: Distribution of seeings for the 38 HeII+47 images.
-\textbf{Bottom}: Same HeII/3000+48 images. The median seeing conditions for the images in both filters is $\sim 0.8\arcsec$. 
+\caption{\textbf{Top}: Distribution of seeing measurements for the 38 HeII+47 images.
+\textbf{Bottom}: Same for the HeII/3000+48 images. The median seeing value for the images in both filters is $\sim 0.8\arcsec$. 
 The seeing conditions were calculated from DIMM measurements which are provided by ESO in the header of each science image.
@@
 \subsection{Image Reduction}
-The data were reduced using custom routines written in \emph{Python}. 
+The imaging data were reduced using custom routines written in \emph{Python}. 
 The images were first corrected by subtracting and removing the overscan region of the CCD. 
 Then the images were bias-subtracted and flat-fielded using twilight flats.
-To improve the flat-fielding essential for detecting faint extended emission across the fields,we further correct for the illumination patterns using night-sky flats.
+To improve the flat-fielding essential for detecting faint extended emission across the fields, we further correct for the illumination patterns using night-sky flats.
 The night-sky flats were produced by combining the unregistered science frames with an average sigma-clipping algorithm after masking out all the objects, and any bad pixels.
@@
 The astrometry solutions were calculated via Astrometry.net \citep{Lang}, and yield a standard deviation in the galaxy coordinates of $\sigma \approx 0.10''$.
-Before image stacking, we ran each frame through \emph{SExtractor} \citeth{Bertin} in order to create a root mean square (RMS) map of each science image.
+Before image stacking, we ran each frame through \emph{SExtractor} \citeth{Bertin} to create a root mean square (RMS) map of each science image.
 
@@
 The frames, after background-subtraction, are resampled onto a common astrometric solution using a \textit{Lancosz3} interpolation kernel. 
-The images are weighted by the night-flat image and then  average-combined  in order to increase the signal-to-noise of any \ion{Mg}{2} emission.
+The images are weighted by the night-flat image and then  average-combined to increase the signal-to-noise of any \ion{Mg}{2} emission.
 Additionally, \emph{SWarp} generates stacked RMS images by propagating the error images for each science frame.
@@
 \centering
-\caption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) include both components of the \ion{Mg}{2} doublet and were 
+\caption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) includes both components of the \ion{Mg}{2} doublet and is 
 determined from analysis of the supplemental Keck/LRIS spectra.}
@@
 } & R.A.
-& Dec  & $z$ & SFR($M_{\odot}$ yr$^{-1}$) & $\log{M_{*}/M_{\odot}}$ & EW$_{\rm{obs}}$(\AA) & $\tau_V$\footnote{ Total V-band optical depth of dust.}\smallskip      \\ \hline
+& Dec  & $z$ & SFR($M_{\odot}$ yr$^{-1}$) & $\log{M_{*}/M_{\odot}}$ & EW$_{\rm{obs}}$(\AA) & $\tau_V$\footnote{ Total V-band optical depth of dust as estimated by SED fitting with MAGPHYS.
+}\smallskip      \\ \hline
 J033225.26-274524.0 (J.26)      & 03:32:25.26 & -27:45:23.9 & 0.6660 & $9.1_{-3.7}^{+1.3}$& $9.86_{-0.04}^{+0.05}$ & $7.539\pm 0.354$ &  $1.227_{-0.20}^{+1.54}$\\
@@
 The exposure time of each image is $\approx 10$ hours.
-Each image shows half of the total FOV of $7' \times 7'$ which contains the full sample of galaxies (indicated by the white arrows).
+Each image shows half of the total FOV, $5' \times 7'$ which contains the full sample of galaxies (indicated by the white arrows).
 East is up and North is right.
@@
 We have two goals for our study: (1) assess the surface brightness of line emission in the \ion{Mg}{2} transition in and around each target galaxy; and (2) spatially resolve the morphology of the strong \ion{Mg}{2} absorption observed against the galaxy continua.
-To reach both of these goals, we must perform accurate subtraction of the continuum flux of each object from the filter covering the targeted line emission.
+To reach both of these goals, we must perform accurate subtraction of the continuum flux of each object from the images taken with the filter covering the targeted line emission.
 For four of the five galaxies in our sample, the HeII+47 image includes both line and continuum emission, and the HeII3000+48 image provides a high S/N measurement of the continuum only $\approx30$ \AA\ redward of the line emission in the rest-frame.
-The galaxy excluded from our analysis is instead used as a check on the quality of our continuum subtraction for reasons detailed in Section \ref{subsubsec:SBprofiles}.
+The galaxy excluded from our analysis is J.57.
+As shown in Figure \ref{fig:spec_images}, the \ion{Mg}{2} transition in this galaxy are equally sampled by both of our filters.
+When we subtract the continuum image from the \ion{Mg}{2} image we are effectively subtracting the \ion{Mg}{2} continuum.
+We use this galaxy as check on the quality of our continuum subtraction for reasons.
 
@@
 Next, we take the ratio of both integrated totals, as the ratio will indicate the scaling factor needed to correct our flux measurements prior to continuum subtraction.
-Comparing these ratios between each galaxy, we find that they are effectively the same, within 0.1\%, with a value of 1.118.
-This value is equal to the ratio between the FWHM of the filter transmission curves, allowing us to conclude that the slope of the spectrum of each galaxy is flat, and hence that the continuum level measured in the off-line filter provides an accurate measure of the continuum contribution to the on-line filter flux.
+Comparing these ratios between each galaxy, we find that they are equivalent to within 0.1\%, with a value of 1.118.
+This value is equal to the ratio between the FWHMs of the filter transmission curves, indicating that spectral slope of each galaxy is approximately flat, and that the continuum level measured in the off-line filter provides an accurate measure of the continuum contribution to the on-line filter flux.
 
@@
 \subsection{Surface Brightness Profiles and Limits}\label{sec.sb}
-
-In order to test for the presence of \ion{Mg}{2} emission, we perform aperture photometry on the continuum subtracted images using the python library \emph{Photutils}.
-We choose annuli with a radial thickness of 1 pixel or $0.25 ''$, such that, $r_{inner}=r_{outer}-1$ (in pixels).
+To test for the presence of \ion{Mg}{2} emission, we perform aperture photometry on the continuum subtracted images using the python library \emph{Photutils}.
+We choose annuli with a radial thickness of 1 pixel or $0.25 ''$, such that $r_{inner}=r_{outer}-1$ (in pixels).
 Each annulus is centered on the flux-weighted centroid of the galaxy.
@@
 We convert these RMS values to SB limits per $1~\rm arcsec^2$  aperture.
-We find that the 1$\sigma$ detection limits %per 1 arcsec$^2$ aperture
+We find that the 1$\sigma$ detection limits
 (SB$_1$) are $6.332\times10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ and $5.808\times10^{-19} $ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ in the HeII/3000+48 and HeII+47 filters, respectively.
@@
 The outer radius is chosen to be the inner radius plus 5 pixels.
-Measurements of \ion{Mg}{2} SB will probe projected distances of 13, 18, 21 and 24 kpc from the centers of each target.
+The mean radii of these extended apertures are 18, 18, 24 and 21 kpc from the centers of the target J.26, J.36, J.03 and J.64 respectively.
 The resulting SB measurements are shown in Figure~\ref{fig:sb_profiles}.
@@
 We mask all the artifacts and sources in the continuum-subtracted images.
-Next, we generate apertures with sizes similar to our extended annulus $\sim 20 \rm\ sq.arcsec$, place them at random, and extract the fluxes, $F_{\text{src}}$, within these apertures.
+Next, we generate apertures with sizes similar to our extended annulus ($\sim 20 \rm\ sq.arcsec$), place them at random, and extract the fluxes, $F_{\text{src}}$, within these apertures.
 
@@
 The distribution of $F_{\text{src}}/\sigma_{\text{src}}$ for these apertures is shown in Figure \ref{fig:limits}.
-We calculate the variance and mean of the distribution and find that the variance of the distribution is $\sigma'_{\text{src}}=1.1$ and implies that the SB detection limit for our continuum-subtracted image is broader than $\sigma_{\text{src}}$ by 10\%.
+We calculate the variance and mean of the distribution and find that the variance of the distribution is $\sigma'_{\text{src}}=1.1$, implying that the SB detection limit for our continuum-subtracted image is higher than $\sigma_{\text{src}}$ by a factor of 10\%.
 We thus adopt $F_{\text{limit}} \equiv \sigma'_{\text{src}}$  as the $1 \sigma$ upper limit on the total line flux of extended \ion{Mg}{2} emission.
 The SB$_{\text{limit}}$ is then $F_{\text{limit}}/A_{\rm{src}}$.
-The values of $F_{\text{src}}$ and the 5SB$_{\text{limit}}$ for each galaxy are listed in Table \ref{tab:det_lims}.
+The values of $F_{\text{src}}$ and 5SB$_{\text{limit}}$ for each galaxy are listed in Table \ref{tab:det_lims}.
 
@@
 \subsection{Test of Surface Brightness Limits}\label{subsec:test}
-In order to show that our detection limits are reasonable, we simulate emission with varying intensities.
+To show that our detection limits are reasonable, we simulate emission with varying intensities.
 The results of this exercise are shown in Figure \ref{fig:sigmas}.
@@
 \includegraphics[scale=1.2]{../Figures/sigmas.pdf}
-\caption{Postage stamp $\chi_{\text{smooth}}$ images for the Mg II emission of the 5 galaxies in our sample.
+\caption{Continuum-subtracted $\chi_{\text{smooth}}$ images of the 5 galaxies in our sample.
 Every galaxy is placed in the same row in each column.
-The columns show simulated emission, with levels of 0, 1, 3, 5, 10, and 20 times SB$_{\rm lim}$.
-Each postage stamp has a size of $5'' \times 5''$ (corresponding to $35$ kpc $\times$ $35$ kpc at $z\sim 0.70$).
-Each stamp shows the galaxy along with the same isophotal contour used in previous figures.}
+The columns show simulated emission, with brightness of 0, 1, 3, 5, 10, and 20 times SB$_{\rm lim}$.
+Each image has a size of $5'' \times 5''$ (corresponding to $35$ kpc $\times$ $35$ kpc at $z\sim 0.70$).
+Each image shows the galaxy along with the same isophotal contour used in previous figures (in black).}
 \label{fig:sigmas}
@@
 
-To compare our map of EW$_{\rm{MgII}}$ to the values measured from the Keck/LRIS spectra, we place 0.9 arcsec wide apertures on top of each galaxy.
-The width and angle of the apertures replicate the orientation of the slits used to obtain the spectra.
+\begin{figure*}
+\centering
+\gridline{\fig{../Figures/J26EW.pdf}{0.8\textwidth}{(a: J.26)}}
+ \gridline{\fig{../Figures/J36EW.pdf}{0.8\textwidth}{(b: J.36)}}
+\gridline{\fig{../Figures/J03EW.pdf}{0.8\textwidth}{(c: J.03)}}
+ \gridline{\fig{../Figures/J64EW.pdf}{0.8\textwidth}{(d: J.64)}}
+\caption{Left: Image of the equivalent widths EW$_{\text{\ion{Mg}{2}}}$ inside the red 1SB$_1$ contour.
+The white contour represents the 0.9\arcsec aperture slit used to measure the equivalent width of absorption in the Keck/LRIS spectrum of each galaxy.
+Middle: Distribution of  EW$_{\text{\ion{Mg}{2}}}$ values in pixels with continuum flux S/N greater than 1.5 inside the slit aperture.
+Right: The EW$_{\text{\ion{Mg}{2}}}$ values vs.
+projected in distance from center are in black and binned EW$_{\text{\ion{Mg}{2}}}$ measurements are shown in red.
+The horizontal error bars in the radial axis represent the width of the radial bin used.}
+\label{fig:ews}
+\end{figure*}
+
+To compare our map of EW$_{\text{\ion{Mg}{2}}}$ to the values measured from the Keck/LRIS spectra, we place 0.9 arcsec wide apertures over of each galaxy.
+The width and position angle of the apertures are consistent with the orientation of the slits used to obtain the spectra.
 Next, we determine which pixels lie outside the 1$\sigma$ SB$_1$ contours and set their values to zero.
-Outside this contour, the EW$_{\rm{MgII}}$ values become poorly constrained due to the lack of S/N in the continuum.
-We then apply a S/N $= 1.5$ cut to the continuum image and create a histogram to show the distribution of EW$_{\rm{MgII}}$ inside the contour.
+Outside this contour, the EW$_{\text{\ion{Mg}{2}}}$ values become poorly constrained due to the lack of S/N in the continuum.
+We then select all pixels with a S/N $= 1.5$ in the continuum image contour and create a histogram to show the distribution of their EW$_{\text{\ion{Mg}{2}}}$ values.
 The histograms are shown in Figure \ref{fig:ews}.
-Having removed pixels with low-S/N continuum values from our images, we compute the mean equivalent width inside the Keck/LRIS apertures.
-These values are summarized in Table \ref{tab:abs_props}.
+We also compute the mean equivalent width of these pixels and report their values in Table \ref{tab:abs_props}.
 
-To assess the morphology of the \ion{Mg}{2} absorption, we determine the distance of each pixel from the center of each galaxy in kiloparsecs.
-We plot the EW$_{\rm{MgII}}$ over this projected distance for each galaxy in Figure \ref{fig:ews}.
-Although some of the plots suggest a slight upward trend in the values of the EW$_{\rm{MgII}}$ with increasing radii, we cannot be confident in this trend because of the large scatter.
+To assess the morphology of the \ion{Mg}{2} absorption, we determine the projected distance of each pixel from the center of each galaxy in kiloparsecs.
+We plot the EW$_{\rm{MgII}}$ vs.
+this projected distance for each galaxy in the middle panel of Figure \ref{fig:ews}.
+Although some of the plots suggest a slight upward trend in the values of EW$_{\rm{MgII}}$ with increasing radii, we cannot be confident in this trend because of the large scatter.
 To better visualize the data and test the significance of the trend, we bin the data radially in 3-5 kpc-wide bins.
-For example, in Figure \ref{fig:ews}(c), the EW$_{\rm{MgII}}$ from absorption of J.03 extends out to $\sim$ 25 kpc.
+For example, in Figure \ref{fig:ews}(c), the absorption EW$_{\text{\ion{Mg}{2}}}$ in J.03 extends out to $\sim$ 25 kpc (shown in black in the right-most panel).
 The EW$_{\rm{MgII}}$ values are binned in 5 kpc increments.
-We calculate the mean and scatter of the EW$_{\rm{MgII}}$ in each bin and show these values in Figure \ref{fig:ew_comb}.
+We calculate the mean and scatter of the EW$_{\text{\ion{Mg}{2}}}$ in each bin and show these values, in red in the right panels of Figure \ref{fig:ews} and in \ref{fig:ew_comb}.
 
 \section{Results}\label{sec:results}
+
+\subsection{Limits on \ion{Mg}{2} Emission}
+For our sample of galaxies, we are sensitive to extended emission at minimum projected distances of 
+18, 18, 24 and 21 kpc from the centers of J.26, J.36, J.03 and J.64 respectively.
+We do not detect any significant \ion{Mg}{2} emission at these distances around any of our target galaxies.
+The $\chi_{\text{smooth}}$ images shown in Figure \ref{fig:sigmas} confirm this.
+A comparison of the simulated emission with the $\chi_{\text{smooth}}$ version of the original continuum-subtracted image, shown in the first column, similarly suggests that we do not detect any extended \ion{Mg}{2} emission.
+We thus place $5\sigma$ upper limits on the SB of \ion{Mg}{2} emission for each galaxy in the sample, summarized in Table \ref{tab:det_lims}.
+The most sensitive detection limit using the largest area is SB(\ion{Mg}{2}) = 5.74 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$, computed for the galaxy J.03.
 
@@
 
-\subsubsection{\ion{Mg}{2}\ absorption in surface brightness profiles} \label{subsubsec:SBprofiles}
+\subsubsection{\ion{Mg}{2}\ Absorption in Surface Brightness Profiles} \label{subsubsec:SBprofiles}
 Although we do not detect any extended \ion{Mg}{2} emission, we do observe a decrement of flux, SB$_{\rm abs}$, in the SB profiles of 4 out of 5 galaxies in our sample.
-Figure \ref{fig:sb_profiles} shows the SB profiles for the 5 galaxies in our sample.
-Absorption from \ion{Mg}{2} ions is prevalent in the profiles between 10 - 25 kpc, decreasing radially outward from the maximum absorption at the center of the galaxies.
-In Table \ref{tab:abs_props} we report for the galaxies J.26, J.36 and J.03 a maximum decrement in the SB profile due to absorption $\sim$ -5.00$\times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
-Additionally, we report for galaxy J.64 a SB$_{\rm abs}$ one order of magnitude greater than the previous galaxies with a value of -18.2 $\pm$ 0.127 $\times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
-Finally, for galaxy J.57, SB$_{\rm abs}$ is strongest at the center of the galaxy with a SB value of -1.25 $\pm$ 1.15 $10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
-However, the measured SB of this decrement including error is consistent with measuring zero absorption.
-The measurement of zero absorption for J.57 was expected.
-Figure \ref{fig:spec_images} shows the Keck/LRIS spectrum of J.57 and the transmission curves of the filters HeII+47 and HeII/3000+48.
-The \ion{Mg}{2} transitions of the galaxy are equally sampled by both of our filters.
-When we subtract the continuum image from the \ion{Mg}{2} image we are effectively subtracting the \ion{Mg}{2} as well.
+As shown in Figure \ref{fig:sb_profiles} absorption from \ion{Mg}{2} ions is prevalent in the profiles between 10 - 25 kpc, decreasing radially outward from the maximum absorption at the center of the galaxies.
+In Table \ref{tab:abs_props} we report for the galaxies J.26, J.36 and J.03 a maximum decrement in the SB profile due to absorption (SB$_{\rm abs}$) $\sim$ -5 $\times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
+Additionally, we report for galaxy J.64 a SB$_{\rm abs}$ one order of magnitude greater with a value of -18.2 $\pm$ 0.127 $\times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
+Finally, for J.57, SB$_{\rm abs}$ is strongest at the center of the galaxy with a value of -1.25 $\pm$ 1.115 $\times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
+This value is consistent with measuring zero absorption, as expected given the redshift of this system.
 This measurement suggests that the quality of our subtraction is satisfactory.
-
-The surface brightness profiles presented in Figures \ref{fig:sb_profiles} do not exhibit any signs of extended \ion{Mg}{2} emission.
 
@@
 We have zeroed out any values that lie outside the SB$_1$ contours for each galaxy.
-We also impose a signal-to-noise cut, only including EWs where the continuum S/N is greater than $1.5$.
-The mean EW is computed for all pixels inside each Keck/LRIS aperture, defined in Sec.
+We also impose a signal-to-noise cut, only including EW$_{\text{\ion{Mg}{2}}}$ where the continuum S/N is greater than $1.5$.
+The mean EW$_{\text{\ion{Mg}{2}}}$ is computed for all pixels inside each Keck/LRIS aperture, defined in Sec.
 \ref{subsec.ew}, and the resulting values are summarized in Table \ref{tab:abs_props}.
@@
 The continuum observed near the \ion{Mg}{2} transition is noisy, compared to the spectra of the rest of the sample.
-Since the value of the EW is dependent on the level of the continuum present near the \ion{Mg}{2} transition, it may well be that our choice of continuum level in calculating the EW from the spectrum might be higher relative to the continuum level implied by our narrow-band image.
+Since the value of the EW$_{\text{\ion{Mg}{2}}}$ is dependent on the level of the continuum present near the \ion{Mg}{2} transition, it may well be that our choice of continuum level in calculating the EW$_{\text{\ion{Mg}{2}}}$ from the spectrum might be higher relative to the continuum level implied by our narrow-band image.
 
@@
 
-As demonstrated in our radially-binned EW profiles, a majority of the galaxies exhibit large scatter in the binned EWs out to larger radii.
-To better understand the significance of these trends, we construct a plot that compiles the mean EWs for all the galaxies, shown in Figure \ref{fig:ew_comb}.
+As demonstrated in our radially-binned EW profiles, a majority of the galaxies exhibit large scatter in the binned EW$_{\text{\ion{Mg}{2}}}$ out to larger radii.
+To better understand the significance of these trends, we construct a plot that compiles the mean EW$_{\text{\ion{Mg}{2}}}$ for all the galaxies, shown in Figure \ref{fig:ew_comb}.
 To take into account the varying size of the galaxies, we normalize the distances by the approximate radius of the SB$_1$ contour for each galaxy.
@@
 
-\subsection{Limits on \ion{Mg}{2} Emission}
-For our sample of galaxies, we are sensitive to extended emission at minimum projected distances of 
-13, 18, 21 and 24 kpc, respectively, from the centers of each target.
-
-We do not detect any significant \ion{Mg}{2} emission at these distances around any of our target galaxies.
-The $\chi_{\text{smooth}}$ images shown in Figure \ref{fig:sigmas} confirm this.
-A comparison of the simulated emission with the $\chi_{\text{smooth}}$ image of the original continuum-subtracted image, shown in the first column, similarly suggests that we do not detect any extended \ion{Mg}{2} emission.
-We thus place $5\sigma$ upper limits on \ion{Mg}{2} emission for each galaxy in the sample, summarized in Table \ref{tab:det_lims}.
-The most sensitive detection limit using the largest area is SB(\ion{Mg}{2}) = 5.74 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$, computed for the galaxy J.03.
 \begin{table}[]
@@
 \begin{tabular}{llllll} \hline \hline
-Object & SB$_{abs}$\footnote{ Maximum SB decrement, values are in units of $10^{-18}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$.} & $R$\footnote{ Radius of SB$_1$ contour in kpc.} &\ \ \ EW$_{\rm{obs}}$($\AA$)\footnote{ Measured from EW images.} & EW$_{\rm{obs}}$($\AA$)\footnote{ Measured from Keck/LRIS spectra.}  \\  \hline
+Object & SB$_{abs}$\footnote{ Maximum SB decrement, values are in units of $10^{-18}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$.} & $R$\footnote{ Radius of SB$_1$ contour in kpc.} &\ \ \ EW$_{\text{\ion{Mg}{2}}}^{\rm obs}$($\AA$)\footnote{ Measured from narrowband images, and reported in the observed frame.} & EW$_{\text{\ion{Mg}{2}}}^{\rm obs}$($\AA$)\footnote{ Measured from Keck/LRIS spectra in the observed frame, and includes both lines in the \ion{Mg}{2} doublet.}  \\  \hline
 J.26 &  $-5.39 \pm 1.28 $ & 8 &     $\ \ \ 3.51 \pm 0.80$ & $7.53 \pm 0.35 $\\
@@
 This emission was detected in a 2-dimensional Keck/LRIS spectrum, with flux from the emission reaching $(8.0 \pm 0.4)$ and $(4.4 \pm 0.4)$ $\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at  $\lambda _{2796}$ and $(4.0 \pm 0.3)$ and $(2.5 \pm 0.4)$ $\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at $\lambda_{2803}$ in two independent locations spatially offset from the galaxy continuum.
-The flux from the emission can be converted into two surface brightness values by taking the average of the flux measured at each location and each transition, and dividing by a 1 sq.arcsec aperture.
+The flux from both emission lines can be converted into two surface brightness values by taking the average of the flux measured at each location and each transition, and dividing by a 1 sq.arcsec aperture.
 
-Figure \ref{fig:SFR_lim} shows a plot of the 5$\sigma$ detection limits determined for each galaxy in our sample as well as the SB calculated for the galaxy TKRS 4389 vs SFR.
-The figure suggests that we should be able to detect scattered \ion{Mg}{2} emission with strengths similar to that detected in TKRS 4389.
-Taken at face value the figure could be consistent with a positive correlation between \ion{Mg}{2} SB and SFR.
-Future observations are needed to verify this trend, and thus the possibility of detect \ion{Mg}{2} in emission for high SFR, $>\sim$50 $\msunperyr$.
+Figure \ref{fig:SFR_lim} shows a plot of the 5$\sigma$ detection limits determined for each galaxy in our sample as well as the SB calculated for the galaxy TKRS 4389 vs.
+SFR.
+The figure suggests that we should be able to detect scattered \ion{Mg}{2} emission with strengths similar to that detected in TKRS 4389 in our narrowband imaging.
+Taken at face value, the figure could be consistent with a positive correlation between \ion{Mg}{2} SB and SFR.
+Future observations are needed to verify this trend, and thus the possibility to detect higher SB of values, as compared to TKRS 4389, \ion{Mg}{2} in emission for high SFR, $>\sim$50 $\msunperyr$.
 Figure \ref{fig:detection_lim} shows the same SB values as Figure \ref{fig:SFR_lim} vs $\log(M_*/M_{\odot})$.
-The figure is suggestive that \ion{Mg}{2} is stronger in emission in lower mass galaxies, and is consistent with the results in \cite{Erb2012} and \cite{Feltre2018}.
+The figure is suggestive that extended \ion{Mg}{2} emission may be brighter in lower mass galaxies.
+Both \cite{Erb2012} and \cite{Feltre2018} observed a similar trend in their examination of the total \ion{Mg}{2} emission strength vs.
+galaxy $M_*$.
 
@@
 \caption{Comparison of our detection limits to the measured extended emission of TKRS 4389 vs SFR.
-The arrow color-galaxy scheme is: (Blue) J.26, (Green) J.36, (Red) J.03, (Cyan) J.64, (Magenta) J.57.
+The arrow color-galaxy scheme is: The blue arrow indicates J.26, green indicates J.36, red indicates J.03, and cyan marks J.64.
 Our imaging is sufficiently sensitive to detect extended emission at similar strengths to the extended emission measured for TKRS 4389 with SFR $\sim 50 \msunperyr$.}
@@
 \includegraphics[scale=0.6]{../Figures/mass_limits.pdf}
-\caption{Comparison of our detection limits to the measured extended emission of TKRS 4389 vs Mass.
-Our imaging is sufficiently sensitive to detect extended emission at similar strengths to the extended emission measured for TKRS 4389 with mass $\sim 10 \log(M_*/ M_{\odot})$.
-The color scheme is the same as Figure \ref{fig:SFR_lim}.}
+\caption{Comparison of our detection limits to the measured extended emission of TKRS 4389 vs Stellar Mass. The color scheme is the same as Figure \ref{fig:SFR_lim}.}
 \label{fig:detection_lim}
@@
 \subsection{Geometry of Scattering Material}
-In idealized wind models of cool gas outflows, discussed in \cite{Prochaska_2011}, radiative transfer calculations suggest that strong \ion{Mg}{2} emission is predicted to be generated along with ubiquitous blueshifted absorption of \ion{Mg}{2}.
-For isotropic and dust-free scenarios, photons are conserved, as any absorbed continuum photon is eventually re-emitted, most likely at a different rest wavelength.
+In the context of the idealized models of cool gas outflows, discussed in \cite{Prochaska_2011}, radiative transfer calculations predict that strong \ion{Mg}{2} emission is generated along with ubiquitous blueshifted absorption of \ion{Mg}{2}.
+For isotropic and dust-free scenarios, photons are conserved, as any absorbed continuum photon is eventually re-emitted.
 Therefore, the total equivalent width of both the absorption and emission features is equal to zero in such models.
@@
 Additionally, since our SB limits are dependent on the size of the aperture used, we calculate the SB detection limits of our images inside each of the aforementioned annuli.
-Figure \ref{fig.emission} shows how the SB of emission varies with the spatial extent of the annulus (black squares), as well as how the SB compares with our detection limits (thin black curve).
-Excepting the galaxy J.03, the SB of this ``missing'' emission lies above our detection limits.
-Under the assumption that the wind in these galaxies does in fact extend beyond the $\rm SB_1$ isophotal contour (at $R_{\perp} = 8-21$ kpc), this result suggests that these galaxies do not host isotropic, dust-free winds.
+Figure \ref{fig.emission} shows how the SB of emission varies with the spatial extent of the annulus (red hexagons), as well as how the SB compares with our detection limits (thin black curve).
+Except for the case of galaxy J.03, the SB of this ``missing'' emission lies above our detection limits.
+Under the assumption that the wind in these galaxies does in fact extend beyond the $\rm SB_1$ isophotal contour (at $R = 8-21$ kpc), this result suggests that these galaxies do not host isotropic, dust-free winds.
 
-\subsubsection{Anisotropic and Dust Free Winds}
+\subsubsection{Anisotropic, Dust Free Winds}
 
 There are many phenomena that may reduce the SB of the scattered \ion{Mg}{2} emission so that it is consistent with our observations.
-One factor that can affect the observed emission strength is morphology of the wind.
-Anisotropic winds were shown in \cite{Prochaska_2011} to exhibit reduced emission strength compared to an isotrpic wind.
-Direct evidence of anisotropic winds, specifically bipolar morphology, has been observed in emission from cold and shock heated gas in local starburst galaxies \citep[e.g.][]{{Walter2002,Westmoquette2008M,Strickland2009}}.
-For distant galaxies, enhanced absorption \ion{Mg}{2} along a galaxy's minor axis \citep[][]{{Bordoloi2011,Kacprzak2012,Bouche2012}},  higher outflow velocities toward $z \sim 1$ galaxies having $i < 45 ^{\circ}$ are suggestive of bipolar outflows.
-Furthermore, \cite{Rubin_2014} analysis provide strong evidence for the ubiquity of bipolar outflows in distant galaxies.
+One factor that can affect the observed emission strength is the morphology of the wind.
+Anisotropic winds were shown in \cite{Prochaska_2011} to exhibit reduced emission strengths compared to isotropic winds.
+Direct evidence of anisotropic winds, and specifically of a bipolar morphology, has been observed in emission from cold and shock-heated gas around local starburst galaxies \citep[e.g.][]{{Walter2002,Westmoquette2008M,Strickland2009}}.
+For distant galaxies, enhanced \ion{Mg}{2} absorption along a galaxy's minor axis \citep[][]{{Bordoloi2011,Kacprzak2012,Bouche2012}} observed along background QSO sightlines, are suggestive of bipolar outflows.
+Furthermore, \cite{Rubin_2014} analysis demonstrating a strong dependence of incidence of winds observed via blueshifted absorption on galaxy orientation is suggestive of the ubiquity of bipolar outflows in distant galaxies.
 
-We now assume that the emission in our galaxies is reduced by the effect of anisotropy.
+We now assume that the brightness of emission in our galaxies is reduced by the effect of anisotropy.
 For the anisotropic winds modeled in \cite{Prochaska_2011}, the emission is reduced by the factor $\Omega/4\pi$, where $\Omega$ is the angular extent of the wind.
 As \citet{Prochaska_2011} points out, given that the outflow must cover most of the continuum in order to be detected, the value of $\Omega$ has an approximate lower limit of $\Omega > 2\pi$.
-We show the predicted SB profiles for wind emission from our galaxies assuming  $\Omega = 2\pi$ with blue diamonds in Figure  \ref{fig.emission}.
+We show the predicted SB profiles for wind emission from our galaxies assuming  $\Omega = 2\pi$ with gray diamonds in Figure  \ref{fig.emission}.
 
@@
 However, the SB profile of J.64 remains above our SB detection limits, suggesting additional phenomena are needed to reduce the strength of scattered emission.
-Previously discussed in Section \ref{sec:results}, this object is the intrinsically brightest galaxy of our sample and exhibits the strong \ion{Mg}{2} absorption, which suggests a strong ISM component.
+Previously discussed in Section \ref{sec:results}, this object is the intrinsically brightest galaxy in our sample and exhibits the strongest \ion{Mg}{2} absorption, which suggests the presence of a strong ISM component.
 \cite{Prochaska_2011} note that \ion{Mg}{2} photons can be more effectively trapped in objects with a large amount of dusty interstellar material.
 
-\subsubsection{Anisotropic and Dusty Winds}
+\subsubsection{Anisotropic, Dusty Winds}
 
 Dust in the wind is another factor that can reduce the observed emission strength, and affect the shape of the line profile. 
-In the \cite{Prochaska_2011} radiative models that include dust in the wind material, the dominant effect is that the most redshifted emission is suppressed.
-The strength of the flux is reduced by a factor of $(1+\tau_{\rm{dust}})^{-1}$, where $\tau_{\rm{dust}}$ is the integrated opacity of dust.
-Estimates of the dust content of each galaxy come from SED modeling in \cite{Rubin_2014} and are shown in Table \ref{tab:prop}.
-The green hexagons in Figure \ref{fig.emission} shows the predicted SB profile for an anisotropic wind with dust.
-For the galaxies J.26, J.36 and J.03, the introduction of dust reduces the predicted emission further below our detection limits and profiles reduced by anisotropy only.
-For galaxy J.64, anisotropy alone does not reduce the predicted emission of J.64 below our detection limits.
-The profile in Figure \ref{fig.emission} shows that combination of dust and anisotropy is sufficient in reducing the strength of the scattered emission of J.64 below our detection limits.
+In the \cite{Prochaska_2011} models that include dust in the wind material, the dominant effect is that the most redshifted emission is suppressed.
+The line flux is reduced by a factor of $(1+\tau_{\rm{dust}})^{-1}$, where $\tau_{\rm{dust}}$ is the integrated opacity of dust.
+Estimates of the dust content, assuming that the wind has the same dust content as the ISM, of each galaxy come from the SED modeling performed \cite{Rubin_2014}, and are shown in Table \ref{tab:prop}.
+The blue triangles in Figure \ref{fig.emission} show the predicted SBs for an anisotropic wind with dust.
+For the galaxies J.26, J.36 and J.03, the introduction of dust reduces the predicted emission further below our detection limits.
+For galaxy J.64, in which anisotropy alone did not reduce the predicted emission of J.64 below our detection limits, Figure \ref{fig.emission} shows that a combination of dust and anisotropy is sufficient to reduce the strength of the scattered emission of J.64 below our detection limits.
 
 \section{CONCLUSION}\label{sec:conclusion}
-We presented the results from a narrowband imaging search for \ion{Mg}{2} emission in a sample of star-forming galaxies at a redshift of $z \sim 0.70$ which are known to drive outflows in  \ion{Mg}{2}.
-We did not detect any \ion{Mg}{2} emission in this sample, and place a $5\sigma$ detection upper limit of SB(\ion{Mg}{2}) $\approx$ 5.74 $\times 10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$, measured in an extended annulus, $\sim 20$ sq.arcsec, at minimum projected distances of 13, 18, 21 and 24 kpc from the centers of each target.
-We detected a significant amount of \ion{Mg}{2} absorption in a total of 4 galaxies out of our 5 galaxy sample.
-Furthermore, our imaging allows us to generate spatially-resolved maps of \ion{Mg}{2} absorption in a distant galaxy sample for the first time.
-This absorption covers the center of the galaxies out to an isophotal radius defined by the SB$_1$ (1$\sigma$) depth of a continuum + \ion{Mg}{2} image, at approximately $\sim 22$ kpc, suggesting that the absorbing gas is optically thick and fully covers the stellar disks out to this distance.
-The EWs measured in these maps are in broad agreement with measured EWs using Keck/LRIS integrated slit spectroscopy.
-Additionally, our radial projections of the mean EW for our sample galaxies suggest that the EWs due to \ion{Mg}{2} are approximately constant across the galaxies surfaces.
+We have presented the results of a narrowband imaging search for \ion{Mg}{2} emission around a sample of star-forming galaxies at a redshift of $z \sim 0.70$ which are known to exhibit outflows traced in \ion{Mg}{2} absorption.
+We did not detect any \ion{Mg}{2} emission in this sample, and place a $5\sigma$ detection upper limit on the surface brightness of SB(\ion{Mg}{2}) $\approx$ 5.74 $\times 10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$.
+This limi is determined within annuli with areas of , $\sim 20$ sq.arcsec, and having mean radii of 13, 18, 21 and 24 kpc from the centers of each target.
+Our imaging also spatially resolves the strength of the \ion{Mg}{2} absorption observed against the galaxy continua yielding novel information of the \ion{Mg}{2} absorption morphology.
+This absorption fully covers the galaxies from their centers out to isophotal radii defined by the SB$_1$ (1$\sigma$) depth of a continuum + \ion{Mg}{2} image (at approximately $\sim 22$ kpc), suggesting that the absorbing gas is optically thick and completely covers the stellar disks out to this distance.
+Additionally, radial projections of the mean EW measured for our sample galaxies suggest that the EWs due to \ion{Mg}{2} are approximately constant across the galaxies surfaces.
 
-We compared our detection limits with the prediction of the radiative transfer models of \cite{Prochaska_2011}.
-We are able to rule out that the winds in our sample are isotropic and dust free, as our images are sufficiently sensitive to detect the predicted emission from such models.
-By assuming dust/dust-free anisotropic winds, we were able to reduce the strength of the predicted  \ion{Mg}{2} emission to lie below our detection limit for 4 of our sample galaxies.
-Although our detection limits suggest that the winds in our sample are not isotropic and dust-free, questions linger regarding the relative roles wind anisotropy, dust content, and extent play in reducing scattered emission.
-Thus, Deeper imaging in \ion{Mg}{2} are required to observe any extended emission beyond the depth of our images and up to our predicted SB profiles to characterize the morphology of these winds.
-
-%A new generation of instruments such as the Keck Cosmic Web Imager (KCWI) or the Multi Unit Spectroscopic Explorer (MUSE) should be used to disentangle these issues.
-
-\begin{figure*}
-\centering
-\gridline{\fig{../Figures/J26EW.pdf}{0.8\textwidth}{(a: J.26)}}
- \gridline{\fig{../Figures/J36EW.pdf}{0.8\textwidth}{(b: J.36)}}
-\gridline{\fig{../Figures/J03EW.pdf}{0.8\textwidth}{(c: J.03)}}
- \gridline{\fig{../Figures/J64EW.pdf}{0.8\textwidth}{(d: J.64)}}
-\caption{(Left) Stamp of the equivalent widths (EWs) inside the red 1SB$_1$ contour.
-The white contour represents the 0.9\arcsec aperture slit used to measure the equivalent width of absorption in the Keck/LRIS spectra.
-(Middle) Distribution of absorption pixels with continuum flux S/N greater than 1.5 inside the slit aperture.
-(Right) The EWs of absorption projected in distance from center are in blue and binned EW measurements red.
-The error bars in the radial axis represent the width of the radial bin used.}
-\label{fig:ews}
-\end{figure*}
+We compared our surface brightness detection limits with the prediction of the radiative transfer models of \cite{Prochaska_2011}.
+We are able to rule out that the winds in our sample are isotropic and dust free, as our images are sufficiently sensitive to detect the emission predicted by such models.
+Adopting the assumption of dusty and/or anisotropic winds, reduces the strength of the predicted \ion{Mg}{2} emission to lie below our detection limits.
+Although these limits suggest that the winds in our sample are not isotropic and dust-free, questions linger regarding the relative roles wind anisotropy, dust content, and extent play in reducing scattered emission.
+Thus, deeper imaging or spatially-resoled spectroscopy of \ion{Mg}{2} is will be needed to fully characterize the morphology of these winds.
 
@@
 \includegraphics[scale=0.9]{../Figures/ew_comb.pdf}
-\caption{Normalized radial profile of the mean EW of \ion{Mg}{2} absorption for all galaxies.
-Measurements for the mean EW binned in radial increments compiled to test the significance of any trends found in the individual galaxy profiles.
+\caption{Radial profile of the mean EW of \ion{Mg}{2} absorption for all galaxies.
+The mean EW values are the same as those shown in the right column of Figure \ref{fig:ews}.
+We have normalized the corresponding radii by the approximate size of the SB$_1$ contour of each galacy.
 There is significant scatter relative to the error bars at extended distances.}
@@
 \centering
-\gridline{\fig{../Figures/geo_J26.pdf}{0.5\textwidth}{(a: J.26)}
-          \fig{../Figures/geo_J36.pdf}{0.5\textwidth}{(b: J.36)}}
-\gridline{\fig{../Figures/geo_J03.pdf}{0.5\textwidth}{(c: J.03)}
-          \fig{../Figures/geo_J64.pdf}{0.5\textwidth}{(d: J.64)}}
-\caption{Estimated SB profile of \ion{Mg}{2} emission for isotropic and anisotropic dust-free winds.
-The red hexagons points are SB of predicted \ion{Mg}{2} emission uniformly distributed inside an annulus for an angle $\Omega=4\pi$, or an isotropic wind.
-The black diamond points are SB of missing \ion{Mg}{2} emission uniformly distributed inside an annulus for an angle $\Omega=2\pi$, or an anisotropic wind.
-The blue triangle points are SB of predicted emission for a wind that is anisotropic and affected by dust.
-The solid line shows the value of the SB detection limits.
-The dashed vertical and horizontal lines represent outer radius of the extended annulus used to measure the initial detection limits and the value of the SB detection limit in that annulus.
+\gridline{\fig{../Figures/geo_J26.pdf}{0.5\textwidth}{(a)}
+          \fig{../Figures/geo_J36.pdf}{0.5\textwidth}{(b)}}
+\gridline{\fig{../Figures/geo_J03.pdf}{0.5\textwidth}{(c)}
+          \fig{../Figures/geo_J64.pdf}{0.5\textwidth}{(d)}}
+\caption{Predicted SB of \ion{Mg}{2} emission for isotropic and anisotropic dust-free winds.
+The red hexagons show the expected SB of emission that has been uniformly distributed inside an annulus (with inner radius equal to the radius to that of the galaxy's isophotal radius and an outer radius equal to the x-axis value) for an isotropic wind.
+The gray diamond points show the SB of \ion{Mg}{2} emission for withs with angular extent $\Omega=2\pi$, or an anisotropic wind.
+The blue triangles mark the predicted SB for a wind that is anisotropic and affected by dust.
+The solid line shows the value of our SB detection limits.
+The dashed vertical and horizontal lines represent the outer radius of the extended annulus used to measure the initial detection limits and the value of the SB detection limit in that annulus.
 The legend in panel (a) holds for the remaining panels.}

### 2018-07-27 Manuscript/vaught_2017.tex
7/27/18_ver2

@@
 \begin{tabular}{llllll} \hline \hline
-Object & SB$_{abs}$\footnote{ Maximum SB decrement, values are in units of $10^{-18}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$.} & $R$\footnote{ Radius of SB$_1$ contour in kpc.} &\ \ \ EW$_{\text{\ion{Mg}{2}}}^{\rm obs}$($\AA$)\footnote{ Measured from narrowband images, and reported in the observed frame.} & EW$_{\text{\ion{Mg}{2}}}^{\rm obs}$($\AA$)\footnote{ Measured from Keck/LRIS spectra in the observed frame, and includes both lines in the \ion{Mg}{2} doublet.}  \\  \hline
-J.26 &  $-5.39 \pm 1.28 $ & 8 &     $\ \ \ 3.51 \pm 0.80$ & $7.53 \pm 0.35 $\\
-J.36 &  $-5.64 \pm 0.121 $ & 15 & $\ \ \ 7.69 \pm 1.02$ & $5.83 \pm 0.49$\\
-J.03 &  $-4.41 \pm 0.622 $ & 21 & $\ \ \ 5.39 \pm 0.71$ & $12.7 \pm 1.71$\\
-J.64 &  $-18.2 \pm 0.127 $ & 10 & $\ \ \ 7.55 \pm 0.66$ & $13.2 \pm 0.26$\\
-J.57 &  $-1.25 \pm 1.15   $ & 11& -$0.653 \pm 0.58$ & $6.10 \pm 0.37$\\ \hline
+Object & SB$_{abs}$\footnote{ Maximum SB decrement, values are in units of $10^{-18}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$.} & $R_{\perp}^{\rm{SB}_1}$\footnote{ Radius of SB$_1$ contour in kpc.} &\ \ \ EW$_{\text{\ion{Mg}{2}}}^{\rm obs}$($\AA$)\footnote{ Measured from narrowband images, and reported in the observed frame.} & EW$_{\text{\ion{Mg}{2}}}^{\rm obs}$($\AA$)\footnote{ Measured from Keck/LRIS spectra in the observed frame, and includes both lines in the \ion{Mg}{2} doublet.}  \\  \hline
+J.26 &  $-5.4 \pm 1.28 $ & 8 &     $\ \ \ 3.5 \pm 0.80$ & $7.5 \pm 0.35 $\\
+J.36 &  $-5.6 \pm 0.12 $ & 15 & $\ \ \ 7.7 \pm 1.02$ & $5.8 \pm 0.49$\\
+J.03 &  $-4.4 \pm 0.62 $ & 21 & $\ \ \ 5.4 \pm 0.71$ & $12.7 \pm 1.71$\\
+J.64 &  $-18.2 \pm 0.13 $ & 10 & $\ \ \ 7.6 \pm 0.66$ & $13.2 \pm 0.26$\\
+J.57 &  $-1.3 \pm 1.15   $ & 11& -$0.65 \pm 0.58$ & $6.10 \pm 0.37$\\ \hline
 \end{tabular}
@@
 The mean EW values are the same as those shown in the right column of Figure \ref{fig:ews}.
-We have normalized the corresponding radii by the approximate size of the SB$_1$ contour of each galacy.
+We have normalized the corresponding radii by the approximate size of the SB$_1$ contour of each galaxy.
 There is significant scatter relative to the error bars at extended distances.}

### 2018-07-27 Manuscript/vaught_2017.tex

@@
 \begin{abstract}
-
-The mass and energy of galactic winds remain poorly constrained via QSO and ``down-the-barrel" absorption line studies.
-One way to better constrain these parameters is to measure the spatial extent of the outflow in emission.
+%The mass and energy of galactic winds remain poorly constrained via QSO and ``down-the-barrel" absorption line studies.
+One way to better constrain these %parameters is to measure the spatial extent of the outflow in emission.
 We perform a VLT/FORS2 narrowband imaging search around 5 star-forming galaxies at redshift $z=0.67-0.69$ in the Great Observatories Origins Deep Survey South (GOODS-S) field to constrain the radial extent of large-scale outflows traced by resonantly scattered \ion{Mg}{2} emission.
-These observations probe unmatched surface brightness limits of 5.74 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ (5$\sigma$).
-We do not detect any extended emission around any of the sample galaxies, thus placing strong upper limits on the brightness of \ion{Mg}{2} emission at projected distances $R_{\perp} = 13-24$ kpc.
-The imaging also resolves the \ion{Mg}{2} observed galaxy spatially, revealing approximately constant absorption strengths across the galaxy disks.
-Our detection limits in concert with a previous studies Keck/LRIS spectra allow us to compare our observations to previous radiative transfer models of \ion{Mg}{2} emission for isotropic and anisotropic dust/dust-free winds.
+The sample galaxies span SFRs in the range $4\msunperyr< SFR < 40\msunperyr$ and have stellar masses $9.9 \lesssim \log M_{*}/M_{\odot} lesssim 11.0$, and exhibit outflows traced by \ion{Mg}{2} absorption with velocities $\sim150-420\mkms$.
+These observations probe unmatched surface brightness limits of 5.81 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ per 1 arcsec$^2$ aperture (at 5$\sigma$ significance).
+We do not detect any extended emission around any of the sample galaxies, thus placing sensitive upper limits on the brightness of extended \ion{Mg}{2} emission of $<6.51 \times 10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ at projected distances $R_{\perp} > 8-21$ kpc.
+The imaging also resolves the \ion{Mg}{2} absorption observed toward each galaxy spatially, revealing approximately constant absorption strengths across the galaxy disks.
+In concert with radiative transfer models predicting the surface brightness of \ion{Mg}{2} emission for a variety of simple wind morphologies, our detection limits suggest that either (1) the extent of the \ion{Mg}{2}-emitting material in the ouflows from these galaxies is limited to $\lesssim 20$ kpc; or (2) the outflows are anisotropic and/or dusty.
+%Our detection limits in concert with a previous studies Keck/LRIS spectra allow us to compare our observations to previous radiative transfer models of \ion{Mg}{2} emission for isotropic and anisotropic dust/dust-free winds.
 Based on these comparisons, if our galaxies do host \ion{Mg}{2} emission, then the predicted \ion{Mg}{2} based on this modeling suggests that these winds are anisotropic and dusty for any scattered \ion{Mg}{2} emission to lie below our 5$\sigma$ detection limits.
-
 \end{abstract}
@@
 \end{tabular}
+\begin{tablenotes}
+\small
+\item The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' spectral energy distributions with Magphys \citep{duCunha2008} as described in \citet{Rubin_2014}.
+\end{tablenotes}
 \label{tab:prop}
@@
 Taken at face value, the figure could be consistent with a positive correlation between \ion{Mg}{2} SB and SFR.
-Future observations are needed to verify this trend, and thus the possibility to detect higher SB of values, as compared to TKRS 4389, \ion{Mg}{2} in emission for high SFR, $>\sim$50 $\msunperyr$.
-Figure \ref{fig:detection_lim} shows the same SB values as Figure \ref{fig:SFR_lim} vs $\log(M_*/M_{\odot})$.
-The figure is suggestive that extended \ion{Mg}{2} emission may be brighter in lower mass galaxies.
+Future observations are needed to verify this trend, and the possibility that objects with yet higher SFRs ($>\sim$50 $\msunperyr$) exhibit brighter \ion{Mg}{2} emission.
+%to detect higher SB values, as compared to TKRS 4389, \ion{Mg}{2} in emission for high SFR, $>\sim$50 $\msunperyr$. 
+Figure \ref{fig:detection_lim} shows the same SB values as in Figure \ref{fig:SFR_lim} vs.
+$\log(M_*/M_{\odot})$.
+The figure suggests that extended \ion{Mg}{2} emission may be brighter in lower mass galaxies.
 Both \cite{Erb2012} and \cite{Feltre2018} observed a similar trend in their examination of the total \ion{Mg}{2} emission strength vs.
 galaxy $M_*$.
+If it is ultimately confirmed that low-$M_*$ galaxies with the highest SFRs exhibit the brightest emission, this could point to a physical link between the escape velocity of galaxies and the spatial extent of wind material.
 
@@
 
+\acknowledgements
+
+K.H.R.R.
+acknowledges support from the Alexander von Humboldt foundation in the context of the Humboldt Postdoctoral Fellowship.
+The Humboldt foundation is funded by the German Federal Ministry for Education and Research.
+
+These findings are in part based on observations collected at the
+European Organisation for Astronomical Research in the Southern
+Hemisphere under ESO programs 090.A-0427(A).
+
 \bibliography{references2017}

### 2018-08-17 for_submission/rvaught_2018.tex
added new folder

--- 2018-07-27 Manuscript/vaught_2017.tex
@@
 \begin{abstract}
-%The mass and energy of galactic winds remain poorly constrained via QSO and ``down-the-barrel" absorption line studies.
-One way to better constrain these %parameters is to measure the spatial extent of the outflow in emission.
-We perform a VLT/FORS2 narrowband imaging search around 5 star-forming galaxies at redshift $z=0.67-0.69$ in the Great Observatories Origins Deep Survey South (GOODS-S) field to constrain the radial extent of large-scale outflows traced by resonantly scattered \ion{Mg}{2} emission.
-The sample galaxies span SFRs in the range $4\msunperyr< SFR < 40\msunperyr$ and have stellar masses $9.9 \lesssim \log M_{*}/M_{\odot} lesssim 11.0$, and exhibit outflows traced by \ion{Mg}{2} absorption with velocities $\sim150-420\mkms$.
+We perform a Very Large Telescope FOcal Reducer and low dispersion Spectrograph 2 (VLT/FORS2) narrowband imaging search around 5 star-forming galaxies at redshift $z=0.67-0.69$ in the Great Observatories Origins Deep Survey South (GOODS-S) field to constrain the radial extent of large-scale outflows traced by resonantly scattered \ion{Mg}{2} emission.
+The sample galaxies span SFRs in the range $4\msunperyr< SFR < 40\msunperyr$ and have stellar masses $9.9 \lesssim \log M_{*}/M_{\odot} \lesssim 11.0$, and exhibit outflows traced by \ion{Mg}{2} absorption with velocities $\sim150-420\mkms$.
 These observations probe unmatched surface brightness limits of 5.81 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ per 1 arcsec$^2$ aperture (at 5$\sigma$ significance).
@@
 In concert with radiative transfer models predicting the surface brightness of \ion{Mg}{2} emission for a variety of simple wind morphologies, our detection limits suggest that either (1) the extent of the \ion{Mg}{2}-emitting material in the ouflows from these galaxies is limited to $\lesssim 20$ kpc; or (2) the outflows are anisotropic and/or dusty.
-%Our detection limits in concert with a previous studies Keck/LRIS spectra allow us to compare our observations to previous radiative transfer models of \ion{Mg}{2} emission for isotropic and anisotropic dust/dust-free winds.
-Based on these comparisons, if our galaxies do host \ion{Mg}{2} emission, then the predicted \ion{Mg}{2} based on this modeling suggests that these winds are anisotropic and dusty for any scattered \ion{Mg}{2} emission to lie below our 5$\sigma$ detection limits.
 \end{abstract}
 
-\keywords{galaxies: evolution, galaxies: absorption lines}
+\keywords{galaxies: evolution -- galaxies: halo}
 
@@
 One proposed production mechanism for such P-Cygni profiles is photon scattering.
-In this mechanism, \ion{Mg}{2} ions in the region of the wind closest to the observer will absorb continuum photons in the resonant transitions at wavelengths 2796\AA, $\lambda_{2796}$, and 2803, \AA $\lambda_{2803}$.
+In this mechanism, \ion{Mg}{2} ions in the region of the wind closest to the observer will absorb continuum photons in the resonant transitions at wavelengths 2796.35\AA\ ($\lambda_{2796}$) and 2803.53\AA\ ($\lambda_{2803}$) \citep{Morton2003}.
 Once these transitions are excited, they may only decay back to the ground state.
@@
 at $z=0.9392$.
-\ion{Mg}{2} has also been studied in wide-field galaxy surveys conducted with Keck/DEIMOS and VLT/MUSE  (\citethnop{Weiner2009}, \citethnop{Kornei2013},\citethnop{Erb2012}, \citethnop{Feltre2018}).
+\ion{Mg}{2} has also been studied in wide-field galaxy surveys conducted with Keck DEep Imaging Multi-Object Spectrograph (DEIMOS) and VLT Multi Unit Spectroscopic Explorer (MUSE)  (\citethnop{Weiner2009}, \citethnop{Kornei2013},\citethnop{Erb2012}, \citethnop{Feltre2018}).
 These surveys, which include galaxies with redshifts $ 0.70 < z < 2.30$, find that \ion{Mg}{2} may be detected in pure emission, pure absorption or with P-Cygni profiles and that detections of \ion{Mg}{2} in emission were found to be associated with galaxies of lower stellar mass and bluer spectral slopes.
 
-The diversity of these spectral profiles may be understood using radiative transfer modeling of galactic winds.
-\citet{Prochaska_2011} have used this technique to predict 
+The diversity of these spectral profiles may be understood using radiative transfer modeling of galactic winds. \citet{Prochaska_2011} have used this technique to predict 
 spectra for the  \ion{Mg}{2} and  \ion{Fe}{2}$^*$ fine-structure transitions for a variety of wind morphologies.
@@
 
-In this paper, we present the first narrowband imaging of the \ion{Mg}{2} transition around 5 star-forming  galaxies located in the  GOODS-S field at redshift $z \sim 0.7$. 
+In this paper, we present the first narrowband imaging of the \ion{Mg}{2} transition around 5 star-forming  galaxies located in the Great Observatories Origins Deep Survey South (GOODS-S; \citethnop{Giavalisco2004})  field at redshift $z \sim 0.7$.
 We use two filters: a  ``line filter" covering the \ion{Mg}{2} doublet, and a ``continuum filter" that is offset from the line filter by ${\sim}47$ \AA.    
@@
 
-In Section \ref{sec:obs_red} we describe our sample of GOOD-S galaxies, supplemental Keck/LRIS spectra, as well as our VLT/FORS2 observations, image reduction, and absolute flux calibration.
+In Section \ref{sec:obs_red} we describe our sample of GOODS-S galaxies, supplemental Keck I Low Resolution Imaging Spectrometer (Keck/LRIS) spectra, as well as our VLT/FORS2 observations, image reduction, and absolute flux calibration.
 We describe our method of continuum subtraction in Section \ref{sec.cont_sub}.
@@
 The absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2}  with velocities $\sim150-420\mkms$ and equivalent widths (EW) $\sim 2-3$ \AA.
-Modeling of the galaxy broad-band spectral energy distributions obtained from multi-wavelength ancillary imaging data yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$.
+Modeling of the galaxy broad-band spectral energy distributions (SED) obtained from multi-wavelength ancillary imaging data yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$.
 The properties of the sample, as well as precise target coordinates taken from \cite{Rubin_2014} are listed in Table \ref{tab:prop}.
@@
 \centering
-\includegraphics[scale=.75]{../Figures/fors2_color_imstamps.pdf}
+\includegraphics[scale=.75]{fors2_color_imstamps.pdf}
 \caption{Color imaging of our sample galaxies in the \emph{HST}/ACS F435W, F606W, and F775W filters obtained as part of the GOODS survey (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004}).
@@
 \centering
-\gridline{\fig{../Figures/filt_26_spectra.pdf}{0.5\textwidth}{(a)}
-          \fig{../Figures/filt_36_spectra.pdf}{0.5\textwidth}{(b)}}
-\gridline{\fig{../Figures/filt_03_spectra.pdf}{0.5\textwidth}{(c)}
-          \fig{../Figures/filt_64_spectra.pdf}{0.5\textwidth}{(d)}}
-           \fig{../Figures/filt_57_spectra.pdf}{0.5\textwidth}{(e)}
+\gridline{\fig{filt_26_spectra.pdf}{0.5\textwidth}{}
+          \fig{filt_36_spectra.pdf}{0.5\textwidth}{}}
+\gridline{\fig{filt_03_spectra.pdf}{0.5\textwidth}{}
+          \fig{filt_64_spectra.pdf}{0.5\textwidth}{}}
+           \fig{filt_57_spectra.pdf}{0.5\textwidth}{}
 \caption{Keck/LRIS spectra of the sample galaxies and the transmission curves of the filters HeII+47 (blue dashed line) and HeII/3000+48 (red dashed line).
@@
 \centering
-\includegraphics[scale=.55]{../Figures/avg_seeing_HEII.pdf}
-\includegraphics[scale=.55]{../Figures/avg_seeing_HEII3000.pdf}
+\includegraphics[scale=.55]{avg_seeing_HEII.pdf}
+\includegraphics[scale=.55]{avg_seeing_HEII3000.pdf}
 \caption{\textbf{Top}: Distribution of seeing measurements for the 38 HeII+47 images.
@@
 \subsection{Supplemental Keck/LRIS spectra}
-In addition to VLT imaging, in the present analysis we utilize galaxy spectra taken from the \cite{Rubin_2014} Keck I Low Resolution Imaging Spectrometer (LRIS) program.
+In addition to VLT imaging, in the present analysis we utilize galaxy spectra taken from the \cite{Rubin_2014} Keck/LRIS program.
 A $0.9''$ slit width was used for all slitmasks and the median FWHM resolution for the spectra is 274 km s$^{-1}$ at $\lambda_{\rm rest} \approx$ 2800 \AA\ and $286\mkms$  at $\lambda_{\rm rest}\approx$ 2600 \AA\ (see Figure \ref{fig:spec_images}).
@@
 Each individual frame is first sky-subtracted using a background mesh size of 256 pixels which is approximately $64''$. 
-We chose the mesh size to be large enough such that the extended emission is not mistakenly subtracted \citep{Battaia_2015}. 
+We chose the mesh size to be large enough such that the extended emission is not mistakenly subtracted \citep[e.g.,][]{Battaia_2015}. 
 The frames, after background-subtraction, are resampled onto a common astrometric solution using a \textit{Lancosz3} interpolation kernel. 
@@
 J033230.57-274518.2  (J.57)    & 03:32:30.56 & -27:45:18.2 &   0.6807  & $12.6_{-2.1}^{+1.7}$ & $10.48_{-0.07}^{+0.03}$ &$6.106 \pm 0.370$ & $1.262_{-0.40}^{+1.23}$ \\
-
 \hline 
 \end{tabular}
-\begin{tablenotes}
-\small
-\item The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' spectral energy distributions with Magphys \citep{duCunha2008} as described in \citet{Rubin_2014}.
-\end{tablenotes}
+\tablenotemark{}
+\tablenotetext{}{\textit{Note} - The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SED with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}}
 \label{tab:prop}
@@
 \centering
-\includegraphics[scale=.61]{../Figures/HEII_final.png}
-\includegraphics[scale=.61]{../Figures/HEII3000_final.png}
+\includegraphics[scale=.61]{HEII_final.png}
+\includegraphics[scale=.61]{HEII3000_final.png}
 \caption{Top: Stacked HeII+47 image of the galaxy sample.
@@
 The galaxy excluded from our analysis is J.57.
-As shown in Figure \ref{fig:spec_images}, the \ion{Mg}{2} transition in this galaxy are equally sampled by both of our filters.
-When we subtract the continuum image from the \ion{Mg}{2} image we are effectively subtracting the \ion{Mg}{2} continuum.
-We use this galaxy as check on the quality of our continuum subtraction for reasons.
+As shown in Figure \ref{fig:spec_images}, the \ion{Mg}{2} transitions in this galaxy are equally sampled by both of our filters.
+When we subtract the continuum image from the \ion{Mg}{2} image we are effectively subtracting both \ion{Mg}{2} emission (if present) and the continuum.
+We thus use this galaxy as check on the quality of our continuum subtraction.
 
@@
 Comparing these ratios between each galaxy, we find that they are equivalent to within 0.1\%, with a value of 1.118.
-This value is equal to the ratio between the FWHMs of the filter transmission curves, indicating that spectral slope of each galaxy is approximately flat, and that the continuum level measured in the off-line filter provides an accurate measure of the continuum contribution to the on-line filter flux.
+This value is equal to the ratio between the FWHMs of the filter transmission curves, indicating that the spectral slope of each galaxy is approximately flat, and that the continuum level measured in the off-line filter provides an accurate measure of the continuum contribution to the on-line filter flux.
 
@@
 \centering
-\includegraphics[scale=0.7]{../Figures/stamps.pdf}
+\includegraphics[scale=0.7]{stamps.pdf}
 \caption{ $10'' \times 10''$ (or about $70 \rm \ kpc \times 70 \rm \ kpc $) images of each galaxy in our sample.
@@
 \centering
-\gridline{\fig{../Figures/J_26.pdf}{0.5\textwidth}{(a)}
-          \fig{../Figures/J_36.pdf}{0.5\textwidth}{(b)}}
-\gridline{\fig{../Figures/J_03.pdf}{0.5\textwidth}{(c)}
-          \fig{../Figures/J_64.pdf}{0.5\textwidth}{(d)}}
-           \fig{../Figures/J_57.pdf}{0.5\textwidth}{(e)}
+\gridline{\fig{J_26.pdf}{0.5\textwidth}{}
+          \fig{J_36.pdf}{0.5\textwidth}{}}
+\gridline{\fig{J_03.pdf}{0.5\textwidth}{}
+          \fig{J_64.pdf}{0.5\textwidth}{}}
+           \fig{J_57.pdf}{0.5\textwidth}{}
 \caption{SB profiles for our sample galaxies.
@@
 \centering
-\includegraphics[scale=0.6]{../Figures/hist_sblim.pdf}
+\includegraphics[scale=0.6]{hist_sblim.pdf}
 \caption{Normalized distribution of $F_{\text{src}}/\sigma_{\text{src}}$ values for random circular annuli placed on the continuum-subtracted line image.
@@
 \centering
-\includegraphics[scale=1.2]{../Figures/sigmas.pdf}
+\includegraphics[scale=1.2]{sigmas.pdf}
 \caption{Continuum-subtracted $\chi_{\text{smooth}}$ images of the 5 galaxies in our sample.
@@
 \centering
-\gridline{\fig{../Figures/J26EW.pdf}{0.8\textwidth}{(a: J.26)}}
- \gridline{\fig{../Figures/J36EW.pdf}{0.8\textwidth}{(b: J.36)}}
-\gridline{\fig{../Figures/J03EW.pdf}{0.8\textwidth}{(c: J.03)}}
- \gridline{\fig{../Figures/J64EW.pdf}{0.8\textwidth}{(d: J.64)}}
+\gridline{\fig{J26EW.pdf}{0.8\textwidth}{(a: J.26)}}
+ \gridline{\fig{J36EW.pdf}{0.8\textwidth}{(b: J.36)}}
+\gridline{\fig{J03EW.pdf}{0.8\textwidth}{(c: J.03)}}
+ \gridline{\fig{J64EW.pdf}{0.8\textwidth}{(d: J.64)}}
 \caption{Left: Image of the equivalent widths EW$_{\text{\ion{Mg}{2}}}$ inside the red 1SB$_1$ contour.
@@
 We thus place $5\sigma$ upper limits on the SB of \ion{Mg}{2} emission for each galaxy in the sample, summarized in Table \ref{tab:det_lims}.
-The most sensitive detection limit using the largest area is SB(\ion{Mg}{2}) = 5.74 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$, computed for the galaxy J.03.
+The most sensitive detection limit using the largest area is SB(\ion{Mg}{2}) $<$ 5.74 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$, computed for the galaxy J.03.
 
@@
 \begin{tabular}{llllll} \hline \hline
-Object & SB$_{abs}$\footnote{ Maximum SB decrement, values are in units of $10^{-18}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$.} & $R_{\perp}^{\rm{SB}_1}$\footnote{ Radius of SB$_1$ contour in kpc.} &\ \ \ EW$_{\text{\ion{Mg}{2}}}^{\rm obs}$($\AA$)\footnote{ Measured from narrowband images, and reported in the observed frame.} & EW$_{\text{\ion{Mg}{2}}}^{\rm obs}$($\AA$)\footnote{ Measured from Keck/LRIS spectra in the observed frame, and includes both lines in the \ion{Mg}{2} doublet.}  \\  \hline
+Object & SB$_{abs}$\footnote{ Maximum SB decrement, values are in units of $10^{-18}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$.} & $R_{\perp}^{\rm{SB}_1}$\footnote{ Radius of SB$_1$ contour in kpc.} &\ \ \ EW$_{\text{\ion{Mg}{2}}}^{\rm obs}$\footnote{ Measured from narrowband images, and reported in the observed frame.} & EW$_{\text{\ion{Mg}{2}}}^{\rm obs}$\footnote{ Measured from Keck/LRIS spectra in the observed frame, and includes both lines in the \ion{Mg}{2} doublet.}  \\
+	&   & (Kpc) & (\AA) &(\AA)\\ \hline
 J.26 &  $-5.4 \pm 1.28 $ & 8 &     $\ \ \ 3.5 \pm 0.80$ & $7.5 \pm 0.35 $\\
@@
 
-Figure \ref{fig:SFR_lim} shows a plot of the 5$\sigma$ detection limits determined for each galaxy in our sample as well as the SB calculated for the galaxy TKRS 4389 vs.
+%Figure \ref{fig:SFR_lim} shows a plot of the 5$\sigma$ detection limits determined for each galaxy in our sample as well as the SB calculated for the galaxy TKRS 4389 vs.
 SFR.
@@
 Future observations are needed to verify this trend, and the possibility that objects with yet higher SFRs ($>\sim$50 $\msunperyr$) exhibit brighter \ion{Mg}{2} emission.
-%to detect higher SB values, as compared to TKRS 4389, \ion{Mg}{2} in emission for high SFR, $>\sim$50 $\msunperyr$. 
 Figure \ref{fig:detection_lim} shows the same SB values as in Figure \ref{fig:SFR_lim} vs.
@@
 galaxy $M_*$.
-If it is ultimately confirmed that low-$M_*$ galaxies with the highest SFRs exhibit the brightest emission, this could point to a physical link between the escape velocity of galaxies and the spatial extent of wind material.
+Combining the previous figures, Figure \ref{fig:sSFR_lim} shows that the galaxy with detected \ion{Mg}{2} also has the highest specific SFR (SFR/$M_*$).
+If it is ultimately confirmed that low-$M_*$ galaxies with the highest SFRs exhibit the brightest emission this could point to a physical link between the escape velocity of galaxies and the spatial extent of wind material.
 
-\begin{figure}[!htb]
+Figure \ref{fig:SFR_lim} shows each galaxy's 5$\sigma$ SB detection limit and the SB calculated for the galaxy TKRS 4389 vs SFR and $\log(M_*/M_{\odot})$.
+These figures suggest that we should be able to detect scattered \ion{Mg}{2} emission with strengths similar to that detected in TKRS 4389 in our narrowband imaging.
+Taken at face value, Figure \ref{fig:SFR_lim} could be consistent with a positive correlation between \ion{Mg}{2} SB and SFR.
+Future observations are needed to verify this trend, and the possibility that objects with yet higher SFRs ($>\sim$50 $\msunperyr$) exhibit brighter \ion{Mg}{2} emission.
+The trend in Figure \ref{fig:detection_lim} suggests that extended \ion{Mg}{2} emission may be brighter in lower mass galaxies.
+Both \cite{Erb2012} and \cite{Feltre2018} observed a similar trend in their examination of the total \ion{Mg}{2} emission strength vs.
+galaxy $M_*$.
+The trends in SFR and mass can be combined to show each galaxies SB vs the specific SFR, shown in the right panel of \ref{fig:sSFR_lim}.
+The figure shows that the galaxy with detected \ion{Mg}{2} also has the highest specific SFR.
+If it is ultimately confirmed that low-$M_*$ galaxies with the highest SFRs, or highest specific SFR, exhibit the brightest emission this could point to a physical link between the escape velocity of galaxies and the spatial extent of wind material.
+
+\begin{figure*}[!htb]
 \centering
-\includegraphics[scale=0.6]{../Figures/limits.pdf}
-\caption{Comparison of our detection limits to the measured extended emission of TKRS 4389 vs SFR.
-The arrow color-galaxy scheme is: The blue arrow indicates J.26, green indicates J.36, red indicates J.03, and cyan marks J.64.
-Our imaging is sufficiently sensitive to detect extended emission at similar strengths to the extended emission measured for TKRS 4389 with SFR $\sim 50 \msunperyr$.}
+\includegraphics[scale=0.7]{ew_comb.pdf}
+\caption{Radial profile of the mean EW of \ion{Mg}{2} absorption for all galaxies.
+The blue points indicates J.26, the green squares indicates J.36, the red circles indicates J.03, and the cyan stars marks J.64.
+The mean EW values are the same as those shown in the right column of Figure \ref{fig:ews}.
+We have normalized the corresponding radii by the approximate size of the SB$_1$ contour of each galaxy.
+There is significant scatter relative to the error bars at extended distances.}
+\label{fig:ew_comb}
+\end{figure*}
+
+\begin{figure*}[!htb]
+\centering
+\includegraphics[scale=0.58]{all_limits.pdf}
+\caption{Comparison of our detection limits to the measured extended emission of TKRS 4389.
+The left panel compares the SB with each galaxies SFR.
+The middle panel compares the SB with each galaxies total stellar mass.
+The right panel compares the SB with sSFR.
+Our imaging is sufficiently sensitive to detect extended emission at similar strengths to the extended emission measured for TKRS 4389 with SFR $\sim 50 \msunperyr$.
+The color scheme is the same as Figure \ref{fig:ew_comb}}
 \label{fig:SFR_lim}
-\end{figure}
+\end{figure*}
 
-\begin{figure}[!htb]
-\centering
-\includegraphics[scale=0.6]{../Figures/mass_limits.pdf}
-\caption{Comparison of our detection limits to the measured extended emission of TKRS 4389 vs Stellar Mass. The color scheme is the same as Figure \ref{fig:SFR_lim}.}
-\label{fig:detection_lim}
-\end{figure}
+%\begin{figure}[!htb]
+%\centering
+%\includegraphics[scale=0.6]{mass_limits.pdf}
+%\caption{Comparison of our detection limits to the measured extended emission of TKRS 4389 vs Stellar Mass. The color scheme is the same as Figure \ref{fig:ew_comb}.}
+%\label{fig:detection_lim}
+%\end{figure}
+
+%\begin{figure}[!htb]
+%\centering
+%\includegraphics[scale=0.6]{sSFR_limits.pdf}
+%\caption{Comparison of our detection limits to the measured extended emission of TKRS 4389 vs sSFR. The color scheme is the same as Figure \ref{fig:ew_comb}.}
+%\label{fig:sSFR_lim}
+%\end{figure}
 
@@
 Except for the case of galaxy J.03, the SB of this ``missing'' emission lies above our detection limits.
-Under the assumption that the wind in these galaxies does in fact extend beyond the $\rm SB_1$ isophotal contour (at $R = 8-21$ kpc), this result suggests that these galaxies do not host isotropic, dust-free winds.
+Under the assumption that the wind in these galaxies does in fact extend beyond the $\rm SB_1$ isophotal contour (at $R_{\perp}^{\rm{SB}_1} = 8-21$ kpc), this result suggests that these galaxies do not host isotropic, dust-free winds.
 
 \subsubsection{Anisotropic, Dust Free Winds}
-
 There are many phenomena that may reduce the SB of the scattered \ion{Mg}{2} emission so that it is consistent with our observations.
@@
 
-\section{CONCLUSION}\label{sec:conclusion}
-We have presented the results of a narrowband imaging search for \ion{Mg}{2} emission around a sample of star-forming galaxies at a redshift of $z \sim 0.70$ which are known to exhibit outflows traced in \ion{Mg}{2} absorption.
-We did not detect any \ion{Mg}{2} emission in this sample, and place a $5\sigma$ detection upper limit on the surface brightness of SB(\ion{Mg}{2}) $\approx$ 5.74 $\times 10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$.
-This limi is determined within annuli with areas of , $\sim 20$ sq.arcsec, and having mean radii of 13, 18, 21 and 24 kpc from the centers of each target.
-Our imaging also spatially resolves the strength of the \ion{Mg}{2} absorption observed against the galaxy continua yielding novel information of the \ion{Mg}{2} absorption morphology.
-This absorption fully covers the galaxies from their centers out to isophotal radii defined by the SB$_1$ (1$\sigma$) depth of a continuum + \ion{Mg}{2} image (at approximately $\sim 22$ kpc), suggesting that the absorbing gas is optically thick and completely covers the stellar disks out to this distance.
-Additionally, radial projections of the mean EW measured for our sample galaxies suggest that the EWs due to \ion{Mg}{2} are approximately constant across the galaxies surfaces.
-
-We compared our surface brightness detection limits with the prediction of the radiative transfer models of \cite{Prochaska_2011}.
-We are able to rule out that the winds in our sample are isotropic and dust free, as our images are sufficiently sensitive to detect the emission predicted by such models.
-Adopting the assumption of dusty and/or anisotropic winds, reduces the strength of the predicted \ion{Mg}{2} emission to lie below our detection limits.
-Although these limits suggest that the winds in our sample are not isotropic and dust-free, questions linger regarding the relative roles wind anisotropy, dust content, and extent play in reducing scattered emission.
-Thus, deeper imaging or spatially-resoled spectroscopy of \ion{Mg}{2} is will be needed to fully characterize the morphology of these winds.
-
-\begin{figure*}[!htb]
-\centering
-\includegraphics[scale=0.9]{../Figures/ew_comb.pdf}
-\caption{Radial profile of the mean EW of \ion{Mg}{2} absorption for all galaxies.
-The mean EW values are the same as those shown in the right column of Figure \ref{fig:ews}.
-We have normalized the corresponding radii by the approximate size of the SB$_1$ contour of each galaxy.
-There is significant scatter relative to the error bars at extended distances.}
-\label{fig:ew_comb}
-\end{figure*}
-
 \begin{figure*}[h]
 \centering
-\gridline{\fig{../Figures/geo_J26.pdf}{0.5\textwidth}{(a)}
-          \fig{../Figures/geo_J36.pdf}{0.5\textwidth}{(b)}}
-\gridline{\fig{../Figures/geo_J03.pdf}{0.5\textwidth}{(c)}
-          \fig{../Figures/geo_J64.pdf}{0.5\textwidth}{(d)}}
+\gridline{\fig{geo_J26.pdf}{0.5\textwidth}{(a)}
+          \fig{geo_J36.pdf}{0.5\textwidth}{(b)}}
+\gridline{\fig{geo_J03.pdf}{0.5\textwidth}{(c)}
+          \fig{geo_J64.pdf}{0.5\textwidth}{(d)}}
 \caption{Predicted SB of \ion{Mg}{2} emission for isotropic and anisotropic dust-free winds.
@@
 
+\section{CONCLUSION}\label{sec:conclusion}
+We have presented the results of a narrowband imaging search for \ion{Mg}{2} emission around a sample of star-forming galaxies at a redshift of $z \sim 0.70$ which are known to exhibit outflows traced in \ion{Mg}{2} absorption.
+We did not detect any \ion{Mg}{2} emission in this sample, and place a $5\sigma$ detection upper limit on the surface brightness of SB(\ion{Mg}{2}) $\approx$ 5.74 $\times 10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$.
+This limit is determined within annuli with areas of, $\sim 20$ sq.arcsec, and having mean radii of 13, 18, 21 and 24 kpc from the centers of each target.
+Our imaging also spatially resolves the strength of the \ion{Mg}{2} absorption observed against the galaxy continua yielding novel information of the \ion{Mg}{2} absorption morphology.
+This absorption fully covers the galaxies from their centers out to isophotal radii defined by the SB$_1$ (1$\sigma$) depth of a continuum + \ion{Mg}{2} image (at approximately $\sim 22$ kpc), suggesting that the absorbing gas is optically thick and completely covers the stellar disks out to this distance.
+Additionally, radial projections of the mean EW measured for our sample galaxies suggest that the EWs due to \ion{Mg}{2} are approximately constant across the galaxies surfaces.
+
+We compared our surface brightness detection limits with the prediction of the radiative transfer models of \cite{Prochaska_2011}.
+We are able to rule out that the winds in our sample are isotropic and dust free, as our images are sufficiently sensitive to detect the emission predicted by such models.
+Adopting the assumption of dusty and/or anisotropic winds, reduces the strength of the predicted \ion{Mg}{2} emission to lie below our detection limits.
+Although these limits suggest that the winds in our sample are not isotropic and dust-free, questions linger regarding the relative roles wind anisotropy, dust content, and extent play in reducing scattered emission.
+Thus, deeper imaging or spatially-resoled spectroscopy of \ion{Mg}{2} will be needed to fully characterize the morphology of these winds.
+
 \acknowledgements
-
+R.R.V gratefully thanks Joe Burchett, Karin Sandstrom and Jessica Werk for enlightening discussions which improved this work.
 K.H.R.R.
@@
 
+\newpage
 \bibliography{references2017}

### 2018-08-18 for_submission/rvaught_2018.tex
updated figure 11

@@
 The imaging also resolves the \ion{Mg}{2} absorption observed toward each galaxy spatially, revealing approximately constant absorption strengths across the galaxy disks.
-In concert with radiative transfer models predicting the surface brightness of \ion{Mg}{2} emission for a variety of simple wind morphologies, our detection limits suggest that either (1) the extent of the \ion{Mg}{2}-emitting material in the ouflows from these galaxies is limited to $\lesssim 20$ kpc; or (2) the outflows are anisotropic and/or dusty.
+In concert with radiative transfer models predicting the surface brightness of \ion{Mg}{2} emission for a variety of simple wind morphologies, our detection limits suggest that either (1) the extent of the \ion{Mg}{2}-emitting material in the outflows from these galaxies is limited to $\lesssim 20$ kpc; or (2) the outflows are anisotropic and/or dusty.
 \end{abstract}
@@
 
-Figure \ref{fig:SFR_lim} shows each galaxy's 5$\sigma$ SB detection limit and the SB calculated for the galaxy TKRS 4389 vs SFR and $\log(M_*/M_{\odot})$.
+Figure \ref{fig:all_limits} shows each galaxy's 5$\sigma$ SB detection limit and the SB calculated for the galaxy TKRS 4389 vs SFR in the left panel and $\log(M_*/M_{\odot})$ in the middle panel.
 These figures suggest that we should be able to detect scattered \ion{Mg}{2} emission with strengths similar to that detected in TKRS 4389 in our narrowband imaging.
-Taken at face value, Figure \ref{fig:SFR_lim} could be consistent with a positive correlation between \ion{Mg}{2} SB and SFR.
+Taken at face value, the left panel of Figure \ref{fig:all_limits} could be consistent with a positive correlation between \ion{Mg}{2} SB and SFR.
 Future observations are needed to verify this trend, and the possibility that objects with yet higher SFRs ($>\sim$50 $\msunperyr$) exhibit brighter \ion{Mg}{2} emission.
-The trend in Figure \ref{fig:detection_lim} suggests that extended \ion{Mg}{2} emission may be brighter in lower mass galaxies.
+The trend in The middle panel of Figure \ref{fig:all_limits} suggests that extended \ion{Mg}{2} emission may be brighter in lower mass galaxies.
 Both \cite{Erb2012} and \cite{Feltre2018} observed a similar trend in their examination of the total \ion{Mg}{2} emission strength vs.
 galaxy $M_*$.
-The trends in SFR and mass can be combined to show each galaxies SB vs the specific SFR, shown in the right panel of \ref{fig:sSFR_lim}.
+The trends in SFR and mass can be combined to show each galaxies SB vs the specific SFR, shown in the right panel of \ref{fig:all_limits}.
 The figure shows that the galaxy with detected \ion{Mg}{2} also has the highest specific SFR.
@@
 \centering
-\includegraphics[scale=0.58]{all_limits.pdf}
+\includegraphics[scale=0.57]{all_limitsv2.pdf}
 \caption{Comparison of our detection limits to the measured extended emission of TKRS 4389.
@@
 The color scheme is the same as Figure \ref{fig:ew_comb}}
-\label{fig:SFR_lim}
+\label{fig:all_limits}
 \end{figure*}

### 2018-08-31 for_submission/rvaught_2018.tex

@@
 \affiliation{Department of Astronomy, San Diego State University, San Diego, CA 92182}
-\affiliation{Department of Physics, University of California, San Diego, 9500 Gilman Dr. La Jolla, CA 92093, USA}
+\affiliation{Department of Physics, University of California, San Diego, 9500 Gilman Dr., La Jolla, CA 92093, USA}
 
@@
  \author{J. Xavier Prochaska}
- \affiliation{Astronomy \& Astrophysics, UC Santa Cruz, 1156 High St., Santa Cruz, CA 95064 USA}
+ \affiliation{Department of Astronomy \& Astrophysics, University of California, 1156 High St., Santa Cruz, CA 95064 USA}
 
@@
 We perform a Very Large Telescope FOcal Reducer and low dispersion Spectrograph 2 (VLT/FORS2) narrowband imaging search around 5 star-forming galaxies at redshift $z=0.67-0.69$ in the Great Observatories Origins Deep Survey South (GOODS-S) field to constrain the radial extent of large-scale outflows traced by resonantly scattered \ion{Mg}{2} emission.
-The sample galaxies span SFRs in the range $4\msunperyr< SFR < 40\msunperyr$ and have stellar masses $9.9 \lesssim \log M_{*}/M_{\odot} \lesssim 11.0$, and exhibit outflows traced by \ion{Mg}{2} absorption with velocities $\sim150-420\mkms$.
-These observations probe unmatched surface brightness limits of 5.81 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ per 1 arcsec$^2$ aperture (at 5$\sigma$ significance).
-We do not detect any extended emission around any of the sample galaxies, thus placing sensitive upper limits on the brightness of extended \ion{Mg}{2} emission of $<6.51 \times 10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ at projected distances $R_{\perp} > 8-21$ kpc.
+The sample galaxies span star formation rates in the range $4\msunperyr< \mathrm{SFR} < 40\msunperyr$ and have stellar masses $9.9 \lesssim \log M_{*}/M_{\odot} \lesssim 11.0$, and exhibit outflows traced by \ion{Mg}{2} absorption with velocities $\sim150-420\mkms$.
+These observations are uniquely sensitive, reaching surface brightness limits of 5.81 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ per 1 arcsec$^2$ aperture (at 5$\sigma$ significance).
+We do not detect any extended emission around any of the sample galaxies, thus placing  upper limits on the brightness of extended \ion{Mg}{2} emission of $<6.51 \times 10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ at projected distances $R_{\perp} > 8-21$ kpc.
 The imaging also resolves the \ion{Mg}{2} absorption observed toward each galaxy spatially, revealing approximately constant absorption strengths across the galaxy disks.
@@
 Galactic winds play a critical role in regulating the star formation rates and stellar masses of galaxies \citeth{Werk_2014}; however, the physics that powers these winds remains uncertain.
-Some possible mechanisms have been proposed by theoretical studies that include thermal pressure from core collapse supernovae, radiation pressure from starbursts, and finally cosmic ray pressure (\citethnop{Larson_1974}; \citethnop{Chevalier_1985}; \citethnop{Springel_2003}; \citethnop{Sugahara_2017}).
+Some possible mechanisms have been proposed by theoretical studies that include thermal pressure from core collapse supernovae, radiation pressure from starbursts, and finally cosmic ray pressure (e.g., \citethnop{Larson_1974}; \citethnop{Chevalier_1985}; \citethnop{Springel_2003}; \citethnop{Sugahara_2017}).
 Additionally, the impact galactic winds have on their host galaxies (i.e., their mass and energy content) has remained difficult to constrain with observations.
 
-An accurate picture of the types of galaxies that host outflows comes from numerous absorption line studies of galaxies (\citethnop{Veilleux2005}; \citethnop{Weiner2009}; \citethnop{Martin2012}; \citethnop{Rubin_2014}).
+An accurate picture of the types of galaxies that host outflows comes from numerous absorption line studies of galaxies (e.g., \citethnop{Veilleux2005}; \citethnop{Weiner2009}; \citethnop{Martin2012}; \citethnop{Rubin_2014}).
 Gas flows are detected by measuring the blueshift (outflow) or redshift (inflow) of absorption transitions with respect to the host galaxy systemic velocity.
-Spectroscopy of galaxies from low to high redshifts probing cold gas ($T \lesssim 10^2$ K) which absorbs in \ion{Na}{1} and cool gas ($T \sim 10^4$ K) in \ion{Mg}{2} has revealed outflows in most galaxies that host active star-formation (e.g.
+Spectroscopy of galaxies from low to high redshifts probing cold gas ($T \lesssim 10^2$ K) which absorbs in \ion{Na}{1} and cool gas ($T \sim 10^4$ K) absorbing \ion{Mg}{2} has revealed outflows in most galaxies that host active star formation (e.g.
 \citethnop{chen2010}; \citethnop{Martin2012}; \citethnop{Rubin_2014}).
-Even though this technique constrains the radial velocity, column density and covering fraction of the flow, it weakly constrains the overall radial extent and provides no information on the morphology of the gas.
+While this technique is useful for constraining the radial velocity, column density and covering fraction of the flow, it weakly constrains the overall radial extent and provides little information on the morphology of the gas.
 
-An alternative method that can in principal asses the radial extent and morphology of outflows is to trace the gas in emission.
-This has been demonstrated using rest-frame optical transitions (i.e H$\alpha$, [\ion{O}{3}], etc) as tracers for winds around nearby starbursts \citep[][]{{Matsubayashi2009,Veilleux2009}} as these transitions can trace the warm shock heated phase of the gas.
+An alternative method that can in principle assess the radial extent and morphology of outflows is to trace the gas in emission.
+This has been demonstrated using rest-frame optical transitions (i.e., H$\alpha$, [\ion{O}{3}]) as tracers for winds around nearby starbursts \citep[e.g.,][]{{Matsubayashi2009,Veilleux2009}} as these transitions can trace the warm shock-heated phase of the gas.
 Another transition potentially useful for tracing winds in emission is the \ion{Mg}{2} $\lambda\lambda 2976,2803$ doublet in the rest-frame ultraviolet
@@
 While most studies of winds using \ion{Mg}{2} have focused on its absorption kinematics, \cite{Rubin_2011} observed  strong \ion{Mg}{2} emission with a P-Cygni line profile in the spectrum of a strongly star-forming galaxy at redshift $z = 0.694$.
-In addition, the emission was spatially extended, permitting the first direct measurement of the extent of an outflow ($>$ 7 kpc) in the distant universe.
+In addition, the emission was spatially extended, permitting the first direct measurement of the extent of an outflow ($\gtrsim$ 7 kpc) in the distant universe.
 
@@
 Because the photons are redshifted, the photons travel freely towards the observer through the wind to produce emission at and redward of the systemic velocity of the galaxy (\citethnop{Rubin_2011}, \citethnop{Prochaska_2011}).
+
 Since the first detection of \ion{Mg}{2} emission in an individual galaxy by \citet{Rubin_2011}, another detection was reported by \cite{Martin2013}, who observed \ion{Mg}{2} emission that extends $12-18$ kpc from a strongly star-forming galaxy
 at $z=0.9392$.
-\ion{Mg}{2} has also been studied in wide-field galaxy surveys conducted with Keck DEep Imaging Multi-Object Spectrograph (DEIMOS) and VLT Multi Unit Spectroscopic Explorer (MUSE)  (\citethnop{Weiner2009}, \citethnop{Kornei2013},\citethnop{Erb2012}, \citethnop{Feltre2018}).
-These surveys, which include galaxies with redshifts $ 0.70 < z < 2.30$, find that \ion{Mg}{2} may be detected in pure emission, pure absorption or with P-Cygni profiles and that detections of \ion{Mg}{2} in emission were found to be associated with galaxies of lower stellar mass and bluer spectral slopes.
+\ion{Mg}{2} has also been studied in wide-field galaxy surveys conducted with the Keck DEep Imaging Multi-Object Spectrograph (DEIMOS) and the VLT Multi Unit Spectroscopic Explorer (MUSE)  (\citethnop{Weiner2009}, \citethnop{Kornei2013}, \citethnop{Erb2012}, \citethnop{Feltre2018}).
+These surveys, which include galaxies with redshifts $ 0.70 < z < 2.30$, find that \ion{Mg}{2} may be detected in pure emission, pure absorption or with P-Cygni profiles and that detections of \ion{Mg}{2} in emission were found to be more commonly associated with galaxies of lower stellar mass and with bluer spectral slopes.
 
@@
 The resulting imaging in each filter has a total integration time of 10 hrs.
-As opposed to 1D spectra, the narrowband imaging constrains the surface brightness, optical depth and radial extent of the wind.
+As opposed to 1D spectra, the narrowband imaging constrains the surface brightness and radial extent of the wind.
 These observations allow us to create the first ever high-S/N spatially resolved map of both \ion{Mg}{2} emission and absorption.
@@
 Section \ref{sec:results} presents results from this analysis.
-We compare our SB detection limits to previous detections of extended \ion{Mg}{2} emission,  and compare our observations to predictions made by radiative transfer models in Section \ref{sec:discussion}.
+We compare our SB detection limits to previous detections of extended \ion{Mg}{2} emission,  and compare our observations to predictions made using radiative transfer models in Section \ref{sec:discussion}.
 We conclude this paper in Section \ref{sec:conclusion}.
@@
 \subsection{Sample Selection}
-Our target galaxies were selected from a Keck/LRIS survey of UV absorption lines in $\approx 100$ objects having redshifts $0.3< z < 1.4$ and $B_{AB}< 23$ in fields with deep Hubble Space Telescope/Advance Camera for Surveys (\emph{HST}/ACS) imaging \citep{Rubin_2014}.
+Our target galaxies were selected from a Keck/LRIS survey of UV absorption lines in $\approx 100$ objects having redshifts $0.3< z < 1.4$ and rest-frame $B$-band magnitudes $B_{\rm AB}< 23$ in fields with deep Hubble Space Telescope/Advanced Camera for Surveys (\emph{HST}/ACS) imaging \citep{Rubin_2014}.
 In particular, this parent survey targeted galaxies in a total of nine Keck/LRIS pointings located in both of the GOODS fields (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004}) and the AEGIS survey field \citep[the Extended Groth Strip;][]{Davis2007}.
-In inspecting the redshift distribution of the portion of this sample observable from the Southern Hemisphere, we uncovered a narrow peak of nine galaxies in the interval $0.66 < z < 0.68$.
+In inspecting the redshift distribution of the portion of this sample observable from the Southern Hemisphere, we uncovered a narrow peak of nine galaxies in the interval $0.66 \lesssim z \lesssim 0.68$.
 This peak is in fact the global maximum of the distribution, as all other bins of width $\Delta z = 0.02$ have at most four galaxies.
-Moreover, there are two narrow interference filters available on VLT/FORS2 centered at $\lambda \sim 4675$ and 4722 \AA\ which cover the \ion{Mg}{2} $\lambda \lambda 2796, 2803$ transition in precisely this redshift interval.
-We selected our final sample of five of these galaxies at $0.66 < z < 0.68$ to be close on the sky such that they could be imaged in a single $7' \times 7' $ FORS2 pointing.
+Moreover, there are two narrow interference filters available on VLT/FORS2 centered at $\lambda \sim 4675$ \AA\ and 4722 \AA\ which cover the \ion{Mg}{2} $\lambda \lambda 2796, 2803$ transition in precisely this redshift interval.
+We selected our final sample of five of these galaxies %at %$0.66 < z < 0.68$
+to be close on the sky such that they could be imaged in a single $7' \times 7' $ FORS2 pointing.  
 We show color {\it HST}/ACS images of these objects in Figure~\ref{fig:hstims}.
@@
 The absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2}  with velocities $\sim150-420\mkms$ and equivalent widths (EW) $\sim 2-3$ \AA.
-Modeling of the galaxy broad-band spectral energy distributions (SED) obtained from multi-wavelength ancillary imaging data yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$.
-The properties of the sample, as well as precise target coordinates taken from \cite{Rubin_2014} are listed in Table \ref{tab:prop}.
+Modeling of the galaxy broad-band spectral energy distributions (SEDs) obtained from multi-wavelength ancillary imaging data yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$.
+The properties of the sample, as well as precise target coordinates taken from \cite{Rubin_2014}, are listed in Table \ref{tab:prop}.
 
 \subsection{VLT/FORS2 Observations}
-Our narrow-band imaging data were taken in service-mode using the FORS2 instrument on the VLT 8.2m telescope Antu between October 2012 and February 2013. 
+Our narrow-band imaging data were taken in service mode using the FORS2 instrument on the VLT 8.2m telescope Antu between October 2012 and February 2013. 
 We used two narrowband filters, HeII+47 and HeII/3000+48, that have peak transmission at wavelengths that correspond to the \ion{Mg}{2} doublet lines at our sample redshift of $z\sim0.7$ (see Table \ref{tab:filters}).
@@
 Our observations were carried out under photometric and thin cloud conditions (program ID: 090.A-0427A). 
-The seeing values, given in the header of each image, were derived from zenith observations at 0.5 microns with the Paranal differential image motion monitor \citep[DIMM,][]{Sarazin1990} and include a correction for the airmass and wavelengths of the science observation, as well as a first order correction for the larger site of the Antu mirror.
-The distribution of these seeing values are shown in Figure \ref{fig.seeing}.
+The seeing values, given in the header of each image, were derived from zenith observations at 0.5 micron with the Paranal differential image motion monitor \citep[DIMM;][]{Sarazin1990} and include a correction for the airmass and wavelengths of the science observations, as well as a first order correction for the larger size of the Antu mirror.
+The distribution of these seeing values is shown in Figure \ref{fig.seeing}.
 The median seeing for the images is $\sim 0.8\arcsec$.
@@
 \caption{Color imaging of our sample galaxies in the \emph{HST}/ACS F435W, F606W, and F775W filters obtained as part of the GOODS survey (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004}).
-Each image is 5\arcsec $\times$ 5\arcsec ( or about $ 35 \rm \ kpc \times 35 \rm \ kpc $) .\label{fig:hstims}}
+Each image is 5\arcsec $\times$ 5\arcsec\ (or about $35 \rm \ kpc \times 35 \rm \ kpc$).\label{fig:hstims}}
 \end{figure*}
@@
 Then the images were bias-subtracted and flat-fielded using twilight flats.
-To improve the flat-fielding essential for detecting faint extended emission across the fields, we further correct for the illumination patterns using night-sky flats.
-The night-sky flats were produced by combining the unregistered science frames with an average sigma-clipping algorithm after masking out all the objects, and any bad pixels.
-Each individual image was cleaned of cosmic rays and bad pixels by utilizing the \emph{L.A.
-Cosmic} algorithm \citep{Dokkum2001}.
+%%% KHRR -- adjusting the following to be different from FAB's words
+%To improve the flat-fielding essential for detecting faint extended emission across the %fields, we further correct for the illumination patterns using night-sky flats.
+The %night-sky flats were produced by combining the unregistered science frames with an %average sigma-clipping algorithm after masking out all the objects, and any bad pixels.
+%%%
+An additional flat-fielding correction was performed using night-sky flats to improve our sensitivity to faint extended emission.
+The night-sky flats were produced by first masking out all objects and bad pixels in the science frames, and then combining them using an average sigma-clipping algorithm.
+Each individual image was cleaned of cosmic rays and bad pixels by utilizing the \emph{L. A. Cosmic} algorithm \citep{Dokkum2001}.
 The astrometry solutions were calculated via Astrometry.net \citep{Lang}, and yield a standard deviation in the galaxy coordinates of $\sigma \approx 0.10''$.
@@
 Each individual frame is first sky-subtracted using a background mesh size of 256 pixels which is approximately $64''$. 
-We chose the mesh size to be large enough such that the extended emission is not mistakenly subtracted \citep[e.g.,][]{Battaia_2015}. 
+We chose the mesh size to be large enough such that any extended emission is not mistakenly subtracted \citep[e.g.,][]{Battaia_2015}. 
 The frames, after background-subtraction, are resampled onto a common astrometric solution using a \textit{Lancosz3} interpolation kernel. 
@@
 \begin{table*}[t]
-\centering
+%\centering
 \caption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) includes both components of the \ion{Mg}{2} doublet and is 
@@
 \tablenotemark{}
-\tablenotetext{}{\textit{Note} - The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SED with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}}
+\tablenotetext{}{\textit{Note} - The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SEDs with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}}
 \label{tab:prop}
@@
 \caption{Filter properties  and exposure times of the VLT/FORS2 observations.
-The width of the transmission curves ($\Delta\lambda$) are calculated by convolving the transmission curve with the total wavelength range of the filter.
-These values differ slightly from those reported by the European Space Observatory.
+The widths of the transmission curves ($\Delta\lambda$) are calculated by convolving the transmission curves over the total wavelength range of each filter.
+These values differ slightly from those reported by the European Southern Observatory.
 }
@@
 However, we calculate the integral numerically.
-The system sensitivity, including the defects of the telescope optics and detector response is then given by
+The system sensitivity, including the sensitivity of the telescope optics and the detector response is then given by
 \begin{equation*}
@@
 The exposure time of each image is $\approx 10$ hours.
-Each image shows half of the total FOV, $5' \times 7'$ which contains the full sample of galaxies (indicated by the white arrows).
+Each image shows half of the total FOV ($7' \times 5'$), which contains the full sample of galaxies (indicated by the white arrows).
 East is up and North is right.
@@
 We have two goals for our study: (1) assess the surface brightness of line emission in the \ion{Mg}{2} transition in and around each target galaxy; and (2) spatially resolve the morphology of the strong \ion{Mg}{2} absorption observed against the galaxy continua.
-To reach both of these goals, we must perform accurate subtraction of the continuum flux of each object from the images taken with the filter covering the targeted line emission.
-For four of the five galaxies in our sample, the HeII+47 image includes both line and continuum emission, and the HeII3000+48 image provides a high S/N measurement of the continuum only $\approx30$ \AA\ redward of the line emission in the rest-frame.
-The galaxy excluded from our analysis is J.57.
+To achieve both of these goals, we must perform accurate subtraction of the continuum flux of each object from the images taken with the filter covering the targeted line emission.
+For four of the five galaxies in our sample, the HeII+47 image includes both line and continuum emission, and the HeII3000+48 image provides a high S/N measurement of the continuum only $\approx30$ \AA\ redward of the line emission in the rest frame.
+%The galaxy excluded from our analysis is J.57.
+The spectral coverage of these filters is qualitatively different for the fifth galaxy in our sample (J.57).
 As shown in Figure \ref{fig:spec_images}, the \ion{Mg}{2} transitions in this galaxy are equally sampled by both of our filters.
@@
 Next, we take the ratio of both integrated totals, as the ratio will indicate the scaling factor needed to correct our flux measurements prior to continuum subtraction.
+
 Comparing these ratios between each galaxy, we find that they are equivalent to within 0.1\%, with a value of 1.118.
@@
 where $F_{\rm{MgII}}$ and $\Delta \lambda_{\rm MgII}$ are the observed flux per pixel in the \ion{Mg}{2} filter and the transmission FWHM of the \ion{Mg}{2} filter.
-The continuum subtracted images of each galaxy are shown in Figure \ref{fig:stamp_images}.
-The continuum subtracted image has uniform background and no obvious signatures of emission.
+The continuum-subtracted images of each galaxy are shown in Figure \ref{fig:stamp_images}.
+The continuum-subtracted image has uniform background and no obvious signatures of emission.
 
@@
 \subsection{Surface Brightness Profiles and Limits}\label{sec.sb}
-To test for the presence of \ion{Mg}{2} emission, we perform aperture photometry on the continuum subtracted images using the python library \emph{Photutils}.
+To test for the presence of \ion{Mg}{2} emission, we perform aperture photometry on the continuum-subtracted images using the python library \emph{Photutils}.
 We choose annuli with a radial thickness of 1 pixel or $0.25 ''$, such that $r_{inner}=r_{outer}-1$ (in pixels).
@@
 \caption{SB profiles for our sample galaxies.
-(Top panel) Continuum SB profile (black) measured for each galaxy.
-The green points show the Mg II + continuum SB measured for the galaxy in the pre-continuum subtracted image.
-The blue points show the Mg II line SB measured for the galaxy in the continuum subtracted line emission image.
+Top panels: Continuum SB profile (gray) measured for each galaxy.
+The red points show the Mg II + continuum SB measured for the galaxy in the pre-continuum-subtracted image.
+The blue points show the Mg II line SB measured  in the continuum-subtracted line emission image.
 The profile exhibits SB decrements from \ion{Mg}{2} absorption.
 Photometry was performed in circular annuli.
-(Bottom panel) The vertical hashes in the bottom show the inner and outer radius of each annulus in kpc.
-Distance from the center of the galaxy (x-axis) is computed using the average value of the inner and outer radii of each annulus.}
+Bottom panel: The vertical hashes show the inner and outer radii of each annulus in kpc.
+The distance from the center of the galaxy is marked with filled squares and is computed using the average value of the inner and outer radii of each annulus.}
 \label{fig:sb_profiles}
@@
 The outer radius is chosen to be the inner radius plus 5 pixels.
-The mean radii of these extended apertures are 18, 18, 24 and 21 kpc from the centers of the target J.26, J.36, J.03 and J.64 respectively.
+The mean radii of these extended apertures are 18, 18, 24 and 21 kpc from the centers of the targets J.26, J.36, J.03 and J.64, respectively.
 The resulting SB measurements are shown in Figure~\ref{fig:sb_profiles}.
@@
 %\begin{minipage}{4in}
-\caption{Significance of extracted flux and detection limits\label{tab:det_lims}}  
+\caption{Significance of extracted flux and detection limits.\label{tab:det_lims}}  
 \begin{tabular}{lllll} \hline \hline
-Object & F$_{\rm{src}}$(\ion{Mg}{2})\footnote{ \ion{Mg}{2} flux is in $10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$.
-The value in the parenthesis is the statistical significance with respect to $\sigma_{\text{src}}$.
-} & 5SB$_{\text{limit}}$\footnote{ Limits are in $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^{-2}$.} & Area\footnote{ Area of the extended annulus in sq.arcsec.} \\  \hline
+Object & F$_{\rm{src}}$(\ion{Mg}{2})\footnote{ \ion{Mg}{2} flux is in units of $10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$.
+The value in parentheses is the statistical significance with respect to $\sigma_{\text{src}}$.
+} & 5SB$_{\text{limit}}$\footnote{ Limits are in units of $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^{-2}$.} & Area\footnote{ Area of the extended annulus in arcsec$^2$.} \\  \hline
 J033225.26-274524.0 &  2.44(0.92)& 6.51	& 21 \\
@@
 \end{equation}
-where the CONVOLVE$^2$ operation indicates the convolution of the variance image with the square of the Gaussian kernel. The smoothed $\chi$ image is defined by
+where the CONVOLVE$^2$ operation indicates the convolution of the variance image with the square of the Gaussian kernel. The smoothed $\chi$ image is then
 \begin{equation}
@@
 Figure \ref{fig:sigmas} shows the $\chi_{\text{smooth}}$ images for the 5 levels of simulated \ion{Mg}{2} emission.
-We also include the $\chi_{\text{smooth}}$ image of each galaxy without any simulated emission (in the left most column).
+We also include the $\chi_{\text{smooth}}$ image of each galaxy without any simulated emission (in the left-most column).
 The galaxies are outlined by a black isophotal contour corresponding to 1SB$_1$ and the simulated emission is contained inside the extended annulus surrounding each contour.
 The  $\chi_{\text{smooth}}$ images confirm that we should be able to detect extended \ion{Mg}{2} emission down to a conservative level of 5SB$_{\text{limit}}$.
-Note again that the SB$_{\text{limit}}$ does indeed take into account the systematics from imperfect continuum subtraction.
+
+%Note again that the SB$_{\text{limit}}$ does indeed take into account the systematics from imperfect continuum subtraction.
 
@@
 Every galaxy is placed in the same row in each column.
-The columns show simulated emission, with brightness of 0, 1, 3, 5, 10, and 20 times SB$_{\rm lim}$.
+The columns show simulated emission, with brightnesses of 0, 1, 3, 5, 10, and 20 times SB$_{\rm lim}$.
 Each image has a size of $5'' \times 5''$ (corresponding to $35$ kpc $\times$ $35$ kpc at $z\sim 0.70$).
@@
 \begin{equation}
-EW_{\rm{MgII}}=-\frac{F_{\rm{MgII}}}{f_{\rm{cont}}}.
+{\rm EW}_{\rm{MgII}}=-\frac{F_{\rm{MgII}}}{f_{\rm{cont}}}.
 \end{equation}
@@
  \gridline{\fig{J64EW.pdf}{0.8\textwidth}{(d: J.64)}}
-\caption{Left: Image of the equivalent widths EW$_{\text{\ion{Mg}{2}}}$ inside the red 1SB$_1$ contour.
-The white contour represents the 0.9\arcsec aperture slit used to measure the equivalent width of absorption in the Keck/LRIS spectrum of each galaxy.
-Middle: Distribution of  EW$_{\text{\ion{Mg}{2}}}$ values in pixels with continuum flux S/N greater than 1.5 inside the slit aperture.
-Right: The EW$_{\text{\ion{Mg}{2}}}$ values vs.
-projected in distance from center are in black and binned EW$_{\text{\ion{Mg}{2}}}$ measurements are shown in red.
-The horizontal error bars in the radial axis represent the width of the radial bin used.}
+\caption{Left: Images of the equivalent widths EW$_{\text{\ion{Mg}{2}}}$ inside the 1SB$_1$ contour for each galaxy (red).
+The white contour shows the placement and orientation of the 0.9\arcsec-wide slit used to measure the equivalent width of absorption in the Keck/LRIS spectrum of each galaxy.
+Middle: Distribution of  EW$_{\text{\ion{Mg}{2}}}$ values in pixels with continuum S/N $>1.5$ inside the slit aperture.
+Right: The EW$_{\text{\ion{Mg}{2}}}$ values of these high-S/N pixels vs.
+projected distance from the galaxy center are shown in black, and binned EW$_{\text{\ion{Mg}{2}}}$ measurements are shown in red.
+The horizontal error bars represent the width of the radial bin used.}
 \label{fig:ews}
@@
 
-To compare our map of EW$_{\text{\ion{Mg}{2}}}$ to the values measured from the Keck/LRIS spectra, we place 0.9 arcsec wide apertures over of each galaxy.
+To compare our map of EW$_{\text{\ion{Mg}{2}}}$ to the values measured from the Keck/LRIS spectra, we place 0.9 arcsec-wide apertures over each galaxy.
 The width and position angle of the apertures are consistent with the orientation of the slits used to obtain the spectra.
@@
 Outside this contour, the EW$_{\text{\ion{Mg}{2}}}$ values become poorly constrained due to the lack of S/N in the continuum.
-We then select all pixels with a S/N $= 1.5$ in the continuum image contour and create a histogram to show the distribution of their EW$_{\text{\ion{Mg}{2}}}$ values.
+We then select all pixels with a S/N $\ge 1.5$ within
+%%% KHRR -- changing this info to match the fig. captio 
+% the continuum image contour 
+each slit aperture
+and create a histogram to show the distribution of their EW$_{\text{\ion{Mg}{2}}}$ values.
 The histograms are shown in Figure \ref{fig:ews}.
@@
 We plot the EW$_{\rm{MgII}}$ vs.
-this projected distance for each galaxy in the middle panel of Figure \ref{fig:ews}.
+this projected distance for each galaxy in the right panels of Figure \ref{fig:ews}.
 Although some of the plots suggest a slight upward trend in the values of EW$_{\rm{MgII}}$ with increasing radii, we cannot be confident in this trend because of the large scatter.
@@
 The EW$_{\rm{MgII}}$ values are binned in 5 kpc increments.
-We calculate the mean and scatter of the EW$_{\text{\ion{Mg}{2}}}$ in each bin and show these values, in red in the right panels of Figure \ref{fig:ews} and in \ref{fig:ew_comb}.
+We calculate the mean and scatter of the EW$_{\text{\ion{Mg}{2}}}$ in each bin and show these values in red in the right panels of Figure \ref{fig:ews} and in \ref{fig:ew_comb}.
 
@@
 \subsection{Limits on \ion{Mg}{2} Emission}
-For our sample of galaxies, we are sensitive to extended emission at minimum projected distances of 
-18, 18, 24 and 21 kpc from the centers of J.26, J.36, J.03 and J.64 respectively.
+For our sample of galaxies, we are sensitive to extended emission in annuli at %minimum 
+projected distances of 
+18, 18, 24 and 21 kpc from the centers of J.26, J.36, J.03 and J.64, respectively.
+%%% KHRR -- don't understand these distances
  We do not detect any significant \ion{Mg}{2} emission at these distances around any of our target galaxies.
@@
 We thus place $5\sigma$ upper limits on the SB of \ion{Mg}{2} emission for each galaxy in the sample, summarized in Table \ref{tab:det_lims}.
-The most sensitive detection limit using the largest area is SB(\ion{Mg}{2}) $<$ 5.74 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$, computed for the galaxy J.03.
+The most sensitive detection limit using the largest area is SB(\ion{Mg}{2}) $<$ 5.74 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^{-2}$, computed for the galaxy J.03.
 
@@
 
-\subsubsection{\ion{Mg}{2}\ Absorption in Surface Brightness Profiles} \label{subsubsec:SBprofiles}
+\subsubsection{Effects of \ion{Mg}{2}\ Absorption on Surface Brightness Profiles} \label{subsubsec:SBprofiles}
 Although we do not detect any extended \ion{Mg}{2} emission, we do observe a decrement of flux, SB$_{\rm abs}$, in the SB profiles of 4 out of 5 galaxies in our sample.
-As shown in Figure \ref{fig:sb_profiles} absorption from \ion{Mg}{2} ions is prevalent in the profiles between 10 - 25 kpc, decreasing radially outward from the maximum absorption at the center of the galaxies.
-In Table \ref{tab:abs_props} we report for the galaxies J.26, J.36 and J.03 a maximum decrement in the SB profile due to absorption (SB$_{\rm abs}$) $\sim$ -5 $\times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
-Additionally, we report for galaxy J.64 a SB$_{\rm abs}$ one order of magnitude greater with a value of -18.2 $\pm$ 0.127 $\times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
-Finally, for J.57, SB$_{\rm abs}$ is strongest at the center of the galaxy with a value of -1.25 $\pm$ 1.115 $\times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ per sq.arcsec.
-This value is consistent with measuring zero absorption, as expected given the redshift of this system.
-This measurement suggests that the quality of our subtraction is satisfactory.
+As shown in Figure \ref{fig:sb_profiles}, absorption from \ion{Mg}{2} ions is prevalent in the profiles at projected distances $\lesssim5$ kpc, and decreases radially outward from the maximum absorption at the center of the galaxies.
+In Table \ref{tab:abs_props} we report for the galaxies J.26, J.36 and J.03 a maximum decrement in the SB profile due to absorption (SB$_{\rm abs}$) $\approx$ -5 $\times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ arcsec$^{-2}$.
+Additionally, we report for galaxy J.64 a SB$_{\rm abs}$ with a significantly more negative value of $(-18.2 \pm 0.1) \times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ arcsec$^{-2}$.
+Finally, for J.57, %SB$_{\rm abs}$ is strongest at the center of the galaxy with a
+the value of SB$_{\rm abs} = (-1.25 \pm 1.12) \times10^{-18}$ erg s$^{-1}$ cm$^{-2}$ arcsec$^{-2}$, and is consistent with measuring zero absorption as expected given the redshift of this system.
+This measurement suggests that the quality of our continuum subtraction is satisfactory.
 
 \subsubsection{Morphology of MgII Absorption}
-Figures \ref{fig:ews}  show the images, distributions and radial projections of \ion{Mg}{2} EWs.
+Figure \ref{fig:ews}  shows the images, distributions and radial projections of \ion{Mg}{2} EWs.
 We have zeroed out any values that lie outside the SB$_1$ contours for each galaxy.
-We also impose a signal-to-noise cut, only including EW$_{\text{\ion{Mg}{2}}}$ where the continuum S/N is greater than $1.5$.
+We also impose a signal-to-noise cut, only including EW$_{\text{\ion{Mg}{2}}}$ values in the middle and right panels for pixels in which the continuum S/N is greater than $1.5$.
 The mean EW$_{\text{\ion{Mg}{2}}}$ is computed for all pixels inside each Keck/LRIS aperture, defined in Sec.
 \ref{subsec.ew}, and the resulting values are summarized in Table \ref{tab:abs_props}.
-Comparing our narrowband EWs with those measured from the spectra, we find agreement to within a 1.6-4.6$\sigma$ for galaxies J.26 and J.36, and more statistically significant differences for galaxies J.03 and J.64.
+Comparing our narrowband EWs with those measured from the spectra, we find agreement to within  1.6-4.6$\sigma$ for galaxies J.26 and J.36, and more statistically significant differences for galaxies J.03 and J.64.
 We discuss possible causes for these differences below.
+We also note here that given the size of the median seeing disk for these observations ($\rm FWHM\approx0.8\arcsec$), the EW$_{\text{\ion{Mg}{2}}}$ values measured in adjacent pixels (each of which subtends $0.25\arcsec$) are not independent, and hence their errors are covariant.
+This covariance implies that the uncertainties in our mean EW$_{\text{\ion{Mg}{2}}}$ values are underestimated, such that the discrepancies between these values and those measured in our LRIS spectra are likely less significant than the tension described above.
 
 Figure \ref{fig:spec_images}(c) shows the Keck/LRIS spectrum of galaxy J.03.
-The continuum observed near the \ion{Mg}{2} transition is noisy, compared to the spectra of the rest of the sample.
-Since the value of the EW$_{\text{\ion{Mg}{2}}}$ is dependent on the level of the continuum present near the \ion{Mg}{2} transition, it may well be that our choice of continuum level in calculating the EW$_{\text{\ion{Mg}{2}}}$ from the spectrum might be higher relative to the continuum level implied by our narrow-band image.
+The continuum observed near the \ion{Mg}{2} transition has low S/N compared to the spectra of the rest of the sample.
+Since the value of EW$_{\text{\ion{Mg}{2}}}$ depends on the level of the continuum, %present near the \ion{Mg}{2} transition,
+it may well be that our choice of continuum level in calculating the EW$_{\text{\ion{Mg}{2}}}$ from the spectrum is higher than the continuum level implied by our narrow-band image.
 
 Figure \ref{fig:spec_images}(d) shows the Keck/LRIS spectrum of galaxy J.64.
-This galaxy is the brightest galaxy in the sample, and also exhibits the highest-velocity wind.
+This object is the brightest galaxy in the sample, and also exhibits the highest-velocity wind.
 This shifts the \ion{Mg}{2} absorption profile toward the blue end of the
-HeII+47 transmission curve, which could cause the flux in this filter to be weighted toward the continuum level and the absorption signal to be underestimated.
+HeII+47 transmission curve, which could cause the signal in this filter to be dominated by the continuum level and the absorption signal to be underestimated.
 
-As demonstrated in our radially-binned EW profiles, a majority of the galaxies exhibit large scatter in the binned EW$_{\text{\ion{Mg}{2}}}$ out to larger radii.
-To better understand the significance of these trends, we construct a plot that compiles the mean EW$_{\text{\ion{Mg}{2}}}$ for all the galaxies, shown in Figure \ref{fig:ew_comb}.
-To take into account the varying size of the galaxies, we normalize the distances by the approximate radius of the SB$_1$ contour for each galaxy.
-
-Upon inspection of Figure \ref{fig:ew_comb}, we see that the galaxies exhibit no statistically significant trend in the mean absorption EW as a function of radius inside our 1SB$_1$ isophotal contour, which suggests that the covering fraction is approximately constant across the surface.
+As demonstrated in our radially-binned EW profiles, a majority of the galaxies exhibit large scatter in the binned EW$_{\text{\ion{Mg}{2}}}$ at large radii.
+To better understand the significance of these trends, we compile the mean EW$_{\text{\ion{Mg}{2}}}$ values for all the galaxies and show their profiles in Figure \ref{fig:ew_comb}.
+To account for the varying sizes of the galaxies, we normalize the radii of the bins by the approximate radius of the SB$_1$ contour for each galaxy.
+Upon inspection of this figure, we see that the galaxies exhibit no statistically significant trend in the mean absorption EW$_{\rm MgII}$ as a function of radius inside our 1SB$_1$ isophotal contour, which suggests that the covering fraction is approximately constant across the surface.
 
@@
 \caption{Properties of \ion{Mg}{2}\ Absorption\label{tab:abs_props}}  
-\begin{tabular}{llllll} \hline \hline
-Object & SB$_{abs}$\footnote{ Maximum SB decrement, values are in units of $10^{-18}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$.} & $R_{\perp}^{\rm{SB}_1}$\footnote{ Radius of SB$_1$ contour in kpc.} &\ \ \ EW$_{\text{\ion{Mg}{2}}}^{\rm obs}$\footnote{ Measured from narrowband images, and reported in the observed frame.} & EW$_{\text{\ion{Mg}{2}}}^{\rm obs}$\footnote{ Measured from Keck/LRIS spectra in the observed frame, and includes both lines in the \ion{Mg}{2} doublet.}  \\
-	&   & (Kpc) & (\AA) &(\AA)\\ \hline
+\begin{tabular}{lccccc} \hline \hline
+Object & SB$_{\rm abs}$\footnote{ Maximum SB decrement in units of $10^{-18}$ erg sec $^{-1}$ cm$^{-2}$ arcsec$^{-2}$.} & $R_{\perp}^{\rm{SB}_1}$\footnote{ Radius of SB$_1$ contour in kpc.} &\ \ \ NB EW$_{\text{\ion{Mg}{2}}}^{\rm obs}$\footnote{ Measured from narrowband images, and reported in the observed frame.} & LRIS EW$_{\text{\ion{Mg}{2}}}^{\rm obs}$\footnote{ Measured from Keck/LRIS spectra in the observed frame.
+Includes both lines in the \ion{Mg}{2} doublet.}  \\
+	&   & (kpc) & (\AA) &(\AA)\\ \hline
 J.26 &  $-5.4 \pm 1.28 $ & 8 &     $\ \ \ 3.5 \pm 0.80$ & $7.5 \pm 0.35 $\\
@@
 Previous constraints on the brightness of scattered \ion{Mg}{2} emission were reported by \cite{Rubin_2011}.
-In this work the authors studied emission from the starburst galaxy TKRS 4389 at $z = 0.69$ with a star formation rate of $49.8\msunperyr$.
+In this work the authors studied emission from the starburst galaxy TKRS 4389 at $z = 0.69$ with a SFR of $49.8\msunperyr$.
 This emission was detected in a 2-dimensional Keck/LRIS spectrum, with flux from the emission reaching $(8.0 \pm 0.4)$ and $(4.4 \pm 0.4)$ $\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at  $\lambda _{2796}$ and $(4.0 \pm 0.3)$ and $(2.5 \pm 0.4)$ $\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at $\lambda_{2803}$ in two independent locations spatially offset from the galaxy continuum.
-The flux from both emission lines can be converted into two surface brightness values by taking the average of the flux measured at each location and each transition, and dividing by a 1 sq.arcsec aperture.
+The flux from both emission lines can be converted into two surface brightness values by taking the average of the flux measured at each location and each transition, and dividing by a 1 arcsec$^2$ aperture.
 
@@
 
-Figure \ref{fig:all_limits} shows each galaxy's 5$\sigma$ SB detection limit and the SB calculated for the galaxy TKRS 4389 vs SFR in the left panel and $\log(M_*/M_{\odot})$ in the middle panel.
+Figure \ref{fig:all_limits} shows each galaxy's 5$\sigma$ SB detection limit and the SB calculated for the galaxy TKRS 4389 vs.
+SFR (left panel) and vs.\ $\log M_*/M_{\odot}$ (middle panel).
 These figures suggest that we should be able to detect scattered \ion{Mg}{2} emission with strengths similar to that detected in TKRS 4389 in our narrowband imaging.
 Taken at face value, the left panel of Figure \ref{fig:all_limits} could be consistent with a positive correlation between \ion{Mg}{2} SB and SFR.
-Future observations are needed to verify this trend, and the possibility that objects with yet higher SFRs ($>\sim$50 $\msunperyr$) exhibit brighter \ion{Mg}{2} emission.
-The trend in The middle panel of Figure \ref{fig:all_limits} suggests that extended \ion{Mg}{2} emission may be brighter in lower mass galaxies.
+Future observations are needed to verify this trend, and the possibility that objects with yet higher SFRs ($\gtrsim50 \msunperyr$) exhibit brighter \ion{Mg}{2} emission.
+The middle panel of Figure \ref{fig:all_limits} suggests that extended \ion{Mg}{2} emission may be brighter in lower mass galaxies.
 Both \cite{Erb2012} and \cite{Feltre2018} observed a similar trend in their examination of the total \ion{Mg}{2} emission strength vs.
 galaxy $M_*$.
-The trends in SFR and mass can be combined to show each galaxies SB vs the specific SFR, shown in the right panel of \ref{fig:all_limits}.
-The figure shows that the galaxy with detected \ion{Mg}{2} also has the highest specific SFR.
-If it is ultimately confirmed that low-$M_*$ galaxies with the highest SFRs, or highest specific SFR, exhibit the brightest emission this could point to a physical link between the escape velocity of galaxies and the spatial extent of wind material.
+%The trends in SFR and mass can be combined to show each galaxies SB vs the specific SFR, shown in the right panel of \ref{fig:all_limits}.
+Finally, the right panel of Figure \ref{fig:all_limits}
+shows that the galaxy with detected \ion{Mg}{2} also has the highest specific SFR.
+If it is ultimately confirmed that low-$M_*$ galaxies with the highest SFRs, or highest specific SFRs, exhibit the brightest emission, this could point to a physical link between the escape velocity of galaxies and the spatial extent of wind material.
 
@@
 \includegraphics[scale=0.7]{ew_comb.pdf}
-\caption{Radial profile of the mean EW of \ion{Mg}{2} absorption for all galaxies.
-The blue points indicates J.26, the green squares indicates J.36, the red circles indicates J.03, and the cyan stars marks J.64.
+\caption{Radial profile of the mean EW of \ion{Mg}{2} absorption for four of our sample galaxies.
+Profiles for J.26,  J.36,  J.03, and J.64 are shown with blue points, green squares, red circles, and cyan stars, respectively.
 The mean EW values are the same as those shown in the right column of Figure \ref{fig:ews}.
@@
 \includegraphics[scale=0.57]{all_limitsv2.pdf}
-\caption{Comparison of our detection limits to the measured extended emission of TKRS 4389.
-The left panel compares the SB with each galaxies SFR.
-The middle panel compares the SB with each galaxies total stellar mass.
-The right panel compares the SB with sSFR.
+\caption{Comparison of our detection limits to the measured SB of extended \ion{Mg}{2} emission around the starburst galaxy TKRS 4389.
+%The left panel shows these surface brightnesses vs.\ SFR; the middle panel shows the same measurements vs.\ ste
+%compares the SB with each galaxies total stellar mass. The right panel compares the SB with sSFR.  
+These surface brightness constraints are plotted vs.\ SFR (left), stellar mass (middle), and specific SFR (right).
 Our imaging is sufficiently sensitive to detect extended emission at similar strengths to the extended emission measured for TKRS 4389 with SFR $\sim 50 \msunperyr$.
-The color scheme is the same as Figure \ref{fig:ew_comb}}
+The symbol colors indicate the same galaxies as in Figure \ref{fig:ew_comb}}
 \label{fig:all_limits}
@@
 \subsection{Geometry of Scattering Material}
-In the context of the idealized models of cool gas outflows, discussed in \cite{Prochaska_2011}, radiative transfer calculations predict that strong \ion{Mg}{2} emission is generated along with ubiquitous blueshifted absorption of \ion{Mg}{2}.
+In the context of the idealized models of cool gas outflows discussed in \cite{Prochaska_2011}, radiative transfer calculations predict that strong \ion{Mg}{2} emission will always accompany the blueshifted \ion{Mg}{2} absorption that is ubiquitously observed to trace galactic-scale winds \citep{Weiner2009,Martin2012,Rubin_2014}.
 For isotropic and dust-free scenarios, photons are conserved, as any absorbed continuum photon is eventually re-emitted.
@@
 Additionally, since our SB limits are dependent on the size of the aperture used, we calculate the SB detection limits of our images inside each of the aforementioned annuli.
-Figure \ref{fig.emission} shows how the SB of emission varies with the spatial extent of the annulus (red hexagons), as well as how the SB compares with our detection limits (thin black curve).
-Except for the case of galaxy J.03, the SB of this ``missing'' emission lies above our detection limits.
+Figure \ref{fig.emission} shows how the predicted SB of emission varies with the spatial extent of the annulus (red octagons), as well as how the SB compares with our detection limits (thin black curve).
+Excepting galaxy J.03, the predicted SB of this  emission lies above our detection limits.
 Under the assumption that the wind in these galaxies does in fact extend beyond the $\rm SB_1$ isophotal contour (at $R_{\perp}^{\rm{SB}_1} = 8-21$ kpc), this result suggests that these galaxies do not host isotropic, dust-free winds.
 
-\subsubsection{Anisotropic, Dust Free Winds}
+\subsubsection{Anisotropic, Dust-Free Winds}
 There are many phenomena that may reduce the SB of the scattered \ion{Mg}{2} emission so that it is consistent with our observations.
@@
 Anisotropic winds were shown in \cite{Prochaska_2011} to exhibit reduced emission strengths compared to isotropic winds.
-Direct evidence of anisotropic winds, and specifically of a bipolar morphology, has been observed in emission from cold and shock-heated gas around local starburst galaxies \citep[e.g.][]{{Walter2002,Westmoquette2008M,Strickland2009}}.
-For distant galaxies, enhanced \ion{Mg}{2} absorption along a galaxy's minor axis \citep[][]{{Bordoloi2011,Kacprzak2012,Bouche2012}} observed along background QSO sightlines, are suggestive of bipolar outflows.
-Furthermore, \cite{Rubin_2014} analysis demonstrating a strong dependence of incidence of winds observed via blueshifted absorption on galaxy orientation is suggestive of the ubiquity of bipolar outflows in distant galaxies.
+Direct evidence for anisotropic winds, and specifically for a bipolar morphology, has been observed in emission from cold and shock-heated gas around local starburst galaxies \citep[e.g.,][]{{Walter2002,Westmoquette2008M,Strickland2009}}.
+Around distant galaxies, enhanced \ion{Mg}{2} absorption along a galaxy's minor axis \citep[][]{{Bordoloi2011,Kacprzak2012,Bouche2012}} observed toward background QSO sightlines is likewise suggestive of bipolar outflows.
+Furthermore, the analysis of \cite{Rubin_2014} demonstrating a strong dependence of the incidence of winds observed ``down the barrel'' on galaxy orientation %is suggestive of the ubiquity of bipolar outflows in distant galaxies.
+was interpreted as additional, strong evidence for such a morphology.
 
@@
 For the anisotropic winds modeled in \cite{Prochaska_2011}, the emission is reduced by the factor $\Omega/4\pi$, where $\Omega$ is the angular extent of the wind.
-As \citet{Prochaska_2011} points out, given that the outflow must cover most of the continuum in order to be detected, the value of $\Omega$ has an approximate lower limit of $\Omega > 2\pi$.
+As \citet{Prochaska_2011} noted, given that the outflow must cover most of the continuum in order to be detected in typical down-the-barrel spectroscopy, the value of $\Omega$ has an approximate lower limit of $\Omega > 2\pi$.
 We show the predicted SB profiles for wind emission from our galaxies assuming  $\Omega = 2\pi$ with gray diamonds in Figure  \ref{fig.emission}.
@@
 After reducing the SB of the expected \ion{Mg}{2} emission by the corresponding factor of 2, we predict profiles that fall below our SB detection limits for galaxies J.26 and J.36.
-However, the SB profile of J.64 remains above our SB detection limits, suggesting additional phenomena are needed to reduce the strength of scattered emission.
-Previously discussed in Section \ref{sec:results}, this object is the intrinsically brightest galaxy in our sample and exhibits the strongest \ion{Mg}{2} absorption, which suggests the presence of a strong ISM component.
-\cite{Prochaska_2011} note that \ion{Mg}{2} photons can be more effectively trapped in objects with a large amount of dusty interstellar material.
+However, the SB profile of J.64 remains above our detection limits, suggesting additional phenomena are needed to reduce the strength of scattered emission.
+As discussed in Section \ref{sec:results}, this object is the brightest in our sample and exhibits the strongest \ion{Mg}{2} absorption, which suggests the presence of a strong ISM component.
+\cite{Prochaska_2011} noted that \ion{Mg}{2} photons can be more effectively trapped in such objects with large amounts of dusty interstellar material.
 
@@
 
-Dust in the wind is another factor that can reduce the observed emission strength, and affect the shape of the line profile. 
+Dust in the wind is another factor that can reduce the observed emission strength and affect the shape of the \ion{Mg}{2} line profile. 
 In the \cite{Prochaska_2011} models that include dust in the wind material, the dominant effect is that the most redshifted emission is suppressed.
 The line flux is reduced by a factor of $(1+\tau_{\rm{dust}})^{-1}$, where $\tau_{\rm{dust}}$ is the integrated opacity of dust.
-Estimates of the dust content, assuming that the wind has the same dust content as the ISM, of each galaxy come from the SED modeling performed \cite{Rubin_2014}, and are shown in Table \ref{tab:prop}.
-The blue triangles in Figure \ref{fig.emission} show the predicted SBs for an anisotropic wind with dust.
-For the galaxies J.26, J.36 and J.03, the introduction of dust reduces the predicted emission further below our detection limits.
-For galaxy J.64, in which anisotropy alone did not reduce the predicted emission of J.64 below our detection limits, Figure \ref{fig.emission} shows that a combination of dust and anisotropy is sufficient to reduce the strength of the scattered emission of J.64 below our detection limits.
+
+The MAGPHYS SED modeling of the sample galaxies performed by \cite{Rubin_2014} provides an
+estimate of the dust opacity in the ISM of each system (shown in Table \ref{tab:prop}). %are available from the SED modeling performed \cite{Rubin_2014}, and are shown in Table \ref{tab:prop}. 
+We make the simplifying assumption
+that the wind has the same dust opacity as the ISM, and predict the SBs for an anisotropic wind with this level of dust opacity using the SB reduction factor given above.
+These values are shown with blue triangles in Figure \ref{fig.emission}.
+%The blue triangles in Figure \ref{fig.emission} show the predicted SBs for an anisotropic wind with dust. 
+For the galaxies J.26, J.36 and J.03, the introduction of dust reduces the predicted emission yet further below our detection limits.
+For galaxy J.64, in which anisotropy alone did not reduce the predicted emission below our detection limits, Figure \ref{fig.emission} shows that a combination of dust and anisotropy is sufficient to reduce the predicted strength of scattered emission %of J.64 below our detection limits.
+so that it is consistent with our observational constraints.
 
@@
           \fig{geo_J64.pdf}{0.5\textwidth}{(d)}}
-\caption{Predicted SB of \ion{Mg}{2} emission for isotropic and anisotropic dust-free winds.
-The red hexagons show the expected SB of emission that has been uniformly distributed inside an annulus (with inner radius equal to the radius to that of the galaxy's isophotal radius and an outer radius equal to the x-axis value) for an isotropic wind.
-The gray diamond points show the SB of \ion{Mg}{2} emission for withs with angular extent $\Omega=2\pi$, or an anisotropic wind.
-The blue triangles mark the predicted SB for a wind that is anisotropic and affected by dust.
+\caption{Predicted SB of \ion{Mg}{2} emission for isotropic, anisotropic, and both anisotropic and dusty winds.
+The red octagons show the expected SB of emission that has been uniformly distributed inside an annulus (with inner radius equal to that of the galaxy's SB$_1$ contour and an outer radius equal to the x-axis value) for an isotropic wind.
+The gray diamond points show the SB of \ion{Mg}{2} emission predicted for an anisotropic wind with angular extent $\Omega=2\pi$.
+The blue triangles mark the predicted SB for a wind that is both anisotropic and affected by dust as described in the text.
 The solid line shows the value of our SB detection limits.
-The dashed vertical and horizontal lines represent the outer radius of the extended annulus used to measure the initial detection limits and the value of the SB detection limit in that annulus.
-The legend in panel (a) holds for the remaining panels.}
+The dashed vertical and horizontal lines represent the outer radius of the extended annulus used to measure the primary detection limits reported for each galaxy and the value of that limit.
+The legend in panel (b) holds for the remaining panels.}
 \label{fig.emission}
@@
 \section{CONCLUSION}\label{sec:conclusion}
-We have presented the results of a narrowband imaging search for \ion{Mg}{2} emission around a sample of star-forming galaxies at a redshift of $z \sim 0.70$ which are known to exhibit outflows traced in \ion{Mg}{2} absorption.
-We did not detect any \ion{Mg}{2} emission in this sample, and place a $5\sigma$ detection upper limit on the surface brightness of SB(\ion{Mg}{2}) $\approx$ 5.74 $\times 10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$.
-This limit is determined within annuli with areas of, $\sim 20$ sq.arcsec, and having mean radii of 13, 18, 21 and 24 kpc from the centers of each target.
-Our imaging also spatially resolves the strength of the \ion{Mg}{2} absorption observed against the galaxy continua yielding novel information of the \ion{Mg}{2} absorption morphology.
-This absorption fully covers the galaxies from their centers out to isophotal radii defined by the SB$_1$ (1$\sigma$) depth of a continuum + \ion{Mg}{2} image (at approximately $\sim 22$ kpc), suggesting that the absorbing gas is optically thick and completely covers the stellar disks out to this distance.
-Additionally, radial projections of the mean EW measured for our sample galaxies suggest that the EWs due to \ion{Mg}{2} are approximately constant across the galaxies surfaces.
+We have presented the results of a narrowband imaging search for \ion{Mg}{2} emission around a sample of five star-forming galaxies at a redshift of $z \sim 0.70$ which are known to exhibit outflows traced in \ion{Mg}{2} absorption.
+We did not detect any \ion{Mg}{2} emission in this sample, and place  upper limits on the surface brightness in the range SB(\ion{Mg}{2}) $< (5.74-6.81) \times 10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ at 5$\sigma$ significance.
+These limits are determined within annuli with areas of $\sim 20~\rm arcsec^2$, and having mean radii ranging from 13 to 24 kpc relative to the centers of each target.
+Our imaging also spatially resolves the strength of the \ion{Mg}{2} absorption observed against the galaxy continua, yielding novel constraints on the \ion{Mg}{2} absorption morphology.
+This absorption fully covers the galaxies from their centers out to isophotal contours defined by the %SB$_1$ 
+1$\sigma$ depth of a continuum + \ion{Mg}{2} image (at %approximately $\sim 22$ kpc), 
+$R_{\perp}^{\rm SB_1} = 8-21$ kpc),
+suggesting that the absorbing gas is optically thick and completely covers the stellar disks out to this distance.
+Additionally, radial profiles of the mean $\rm EW_{MgII}$ measured for our sample galaxies suggest that the EWs %due to \ion{Mg}{2}
+are approximately constant across the galaxies' stellar surfaces.
 
-We compared our surface brightness detection limits with the prediction of the radiative transfer models of \cite{Prochaska_2011}.
+We compared our surface brightness detection limits with the predictions of the radiative transfer models of \cite{Prochaska_2011}.
 We are able to rule out that the winds in our sample are isotropic and dust free, as our images are sufficiently sensitive to detect the emission predicted by such models.
-Adopting the assumption of dusty and/or anisotropic winds, reduces the strength of the predicted \ion{Mg}{2} emission to lie below our detection limits.
+Adopting the assumption of dusty and/or anisotropic winds reduces the strength of the predicted \ion{Mg}{2} emission to lie below our detection limits.
 Although these limits suggest that the winds in our sample are not isotropic and dust-free, questions linger regarding the relative roles wind anisotropy, dust content, and extent play in reducing scattered emission.
-Thus, deeper imaging or spatially-resoled spectroscopy of \ion{Mg}{2} will be needed to fully characterize the morphology of these winds.
+Thus, deeper imaging or spatially-resolved spectroscopy of \ion{Mg}{2} will be needed to fully characterize the morphology of these winds.
 

### 2018-09-02 for_submission/rvaught_2018.tex
update 9/2/18

@@
-\documentclass[twocolumn]{aastex61}
+\documentclass[twocolumn]{aastex62}
 \usepackage{natbib}
@@
 \subsection{Image Reduction}
-The imaging data were reduced using custom routines written in \emph{Python}. 
+The imaging data were fully reduced using custom routines written in \emph{Python}. 
 The images were first corrected by subtracting and removing the overscan region of the CCD. 
@@
 The night-sky flats were produced by first masking out all objects and bad pixels in the science frames, and then combining them using an average sigma-clipping algorithm.
-Each individual image was cleaned of cosmic rays and bad pixels by utilizing the \emph{L. A. Cosmic} algorithm \citep{Dokkum2001}.
+Cosmic rays and bad pixels in the science images are removed by utilizing the \emph{L. A. Cosmic} algorithm \citep{Dokkum2001}.
 The astrometry solutions were calculated via Astrometry.net \citep{Lang}, and yield a standard deviation in the galaxy coordinates of $\sigma \approx 0.10''$.
@@
 
-\begin{table*}[t]
+%\begin{table*}[t]
 %\centering
-\caption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) includes both components of the \ion{Mg}{2} doublet and is 
-determined from analysis of the supplemental Keck/LRIS spectra.}
-\begin{tabular}{llllllll} \hline \hline
-Object\footnote{ Name in parenthesis to be used as shorthand for the objects throughout the remainder of the paper.
+%\caption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) includes both components of the \ion{Mg}{2} doublet and is 
+%determined from analysis of the supplemental Keck/LRIS spectra.}
+%\begin{tabular}{llllllll} \hline \hline
+%Object\footnote{ Name in parenthesis to be used as shorthand for the objects throughout the remainder of the paper.
 } & R.A.
@@
 }\smallskip      \\ \hline
-J033225.26-274524.0 (J.26)      & 03:32:25.26 & -27:45:23.9 & 0.6660 & $9.1_{-3.7}^{+1.3}$& $9.86_{-0.04}^{+0.05}$ & $7.539\pm 0.354$ &  $1.227_{-0.20}^{+1.54}$\\
+%J033225.26-274524.0 (J.26)      & 03:32:25.26 & -27:45:23.9 & 0.6660 & $9.1_{-3.7}^{+1.3}$& $9.86_{-0.04}^{+0.05}$ & $7.539\pm 0.354$ &  $1.227_{-0.20}^{+1.54}$\\
 
-J033231.36-274725.0 (J.36)      & 03:32:31.35 & -27:47:24.9 &   0.6669 & $10.5_{-1.6}^{+1.7}$ & $10.02_{-0.03}^{+0.03}$&$5.835 \pm 0.493$ & $1.377_{-0.23}^{+0.60}$\\
+%J033231.36-274725.0 (J.36)      & 03:32:31.35 & -27:47:24.9 &   0.6669 & $10.5_{-1.6}^{+1.7}$ & $10.02_{-0.03}^{+0.03}$&$5.835 \pm 0.493$ & $1.377_{-0.23}^{+0.60}$\\
 
-J033230.03-274347.3  (J.03)     & 03:32:30.03 & -27:43:47.2  &   0.6679 & $3.8_{-0}^{+0}$ & $10.98_{-0.0}^{+0.01}$ &$12.794 \pm 1.710$ & $0.297_{-0.0}^{+0.0}$ \\
+%J033230.03-274347.3  (J.03)     & 03:32:30.03 & -27:43:47.2  &   0.6679 & $3.8_{-0}^{+0}$ & $10.98_{-0.0}^{+0.01}$ &$12.794 \pm 1.710$ & $0.297_{-0.0}^{+0.0}$ \\
 
-J033229.64-274242.6  (J.64)    & 03:32:29.64 & -27:42:42.5 & 0.6671 & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &$13.239 \pm 0.263$ & $3.897_{-0.93}^{+1.15}$\\
+%J033229.64-274242.6  (J.64)    & 03:32:29.64 & -27:42:42.5 & 0.6671 & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &$13.239 \pm 0.263$ & $3.897_{-0.93}^{+1.15}$\\
 
-J033230.57-274518.2  (J.57)    & 03:32:30.56 & -27:45:18.2 &   0.6807  & $12.6_{-2.1}^{+1.7}$ & $10.48_{-0.07}^{+0.03}$ &$6.106 \pm 0.370$ & $1.262_{-0.40}^{+1.23}$ \\
-\hline 
-\end{tabular}
-\tablenotemark{}
-\tablenotetext{}{\textit{Note} - The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SEDs with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}}
-\label{tab:prop}
-\end{table*}
+%J033230.57-274518.2  (J.57)    & 03:32:30.56 & -27:45:18.2 &   0.6807  & $12.6_{-2.1}^{+1.7}$ & $10.48_{-0.07}^{+0.03}$ &$6.106 \pm 0.370$ & $1.262_{-0.40}^{+1.23}$ \\
+%\hline 
+%\end{tabular}
+%\tablenotemark{}
+%\tablenotetext{}{\textit{Note} - The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SEDs with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}}
+%\label{tab:prop}
+%\end{table*}
 
-\begin{table}[h!]
-\caption{Filter properties  and exposure times of the VLT/FORS2 observations.
+\begin{deluxetable*}{c c c c D D c D}
+\tablecaption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) includes both components of the \ion{Mg}{2} doublet and is 
+determined from analysis of the supplemental Keck/LRIS spectra. \label{tab:prop}}
+\tablehead{\colhead{Object} & \colhead{R.A.} & \colhead{Dec} & \colhead{$z$} & \multicolumn2c{SFR} & \multicolumn2c{$\log{M}$} & \colhead{EW$_{\rm{obs}}$} & \multicolumn2c{ $\tau_V$} \\ 
+\colhead {} & \colhead {} & \colhead {} & \colhead{} & \multicolumn2c{($M_{\odot}$ yr$^{-1}$)} & \multicolumn2c{$\log{M_{*}/M_{\odot}}$} & \colhead{(\AA)} & \multicolumn2c{}}
+\decimals
+\startdata
+J033225.26-274524.0 (J.26)     & 03:32:25.26 & -27:45:23.9  &   0.6660  & $9.1_{-3.7}^{+1.3}$     & $9.86_{-0.04}^{+0.05}$   & \ $7.539\pm 0.354$   &  $1.227_{-0.20}^{+1.54}$ \\ 
+J033231.36-274725.0 (J.36)     & 03:32:31.35 & -27:47:24.9  &   0.6669  & $10.5_{-1.6}^{+1.7}$   & $10.02_{-0.03}^{+0.03}$ & \ $5.835 \pm 0.493$   & $1.377_{-0.23}^{+0.60}$ \\
+J033230.03-274347.3 (J.03)     & 03:32:30.03 & -27:43:47.2  &   0.6679  & $3.8_{-0}^{+0}$           & $10.98_{-0.0}^{+0.01}$   & $12.794 \pm 1.710$ & $0.297_{-0.0}^{+0.0}$ \\
+J033229.64-274242.6 (J.64)     & 03:32:29.64 & -27:42:42.5  &   0.6671  & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ & $13.239 \pm 0.263$ & $3.897_{-0.93}^{+1.15}$ \\
+J033230.57-274518.2 (J.57)     & 03:32:30.56 & -27:45:18.2  &   0.6807  & $12.6_{-2.1}^{+1.7}$   & $10.48_{-0.07}^{+0.03}$ & \ $6.106 \pm 0.370$   & $1.262_{-0.40}^{+1.23}$ \\
+\enddata
+\tablecomments{The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SEDs with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}}
+\end{deluxetable*}
+
+\begin{deluxetable}{c c c c c c}
+\tablecaption{Filter properties  and exposure times of the VLT/FORS2 observations.
 The widths of the transmission curves ($\Delta\lambda$) are calculated by convolving the transmission curves over the total wavelength range of each filter.
 These values differ slightly from those reported by the European Southern Observatory.
-}
-\begin{tabular}{llllll} \hline \hline 
-Filter & $\lambda_{\rm{eff}}$(\AA)\footnote{$ \lambda_{\rm{eff}}$ is the effective wavelength of the filter transmission curve.} & $\Delta\lambda$(\text{\AA})    & $N$\footnote{ Total number of images.}   & $T(s)$\footnote{ Total exposure time.} & $S$\footnote{ S, the sensitivity of the filter, is in units of $10^{-17}$ ergs counts$^{-1}$ cm$^{-2}$ .}\smallskip  \\ \hline
-HeII+47  & 4675.21 & 50.11 & 38  & 35,959 & 2.45 \\
-HeII/3000+48 & 4722.46  & 44.82 & 38 &   36,937 & 2.40  \\ \hline
-\end{tabular}
-\label{tab:filters}
-\end{table}
+\label{tab:filters}}
+\tablehead{\colhead {Filter (Line)} & \colhead {$\lambda_{\rm{eff}}$\tablenotemark{a}} & \colhead {$\Delta\lambda$\tablenotemark{b}} & \colhead {N\tablenotemark{c}} & \colhead{$T$\tablenotemark{d}} & \colhead{$S$\tablenotemark{e}} \\
+\colhead {} & \colhead{(\AA)} & \colhead{(\AA)} & \colhead{} & \colhead{(S)} & \colhead{}}
+\startdata
+HeII+47 (\ion{Mg}{2})         & 4675.21  & 50.11 & 38  & 35,959 & 2.45 \\
+HeII/3000+48 (Cont.) & 4722.46  & 44.82 & 38  & 36,937 & 2.40  \\
+\enddata
+\tablenotetext{a}{$ \lambda_{\rm{eff}}$ is the effective wavelength of the filter transmission curve.}
+\tablenotetext{b}{FWHM of the filter.}
+\tablenotetext{c}{Total number of images.}
+\tablenotetext{d}{Total exposure time.}
+\tablenotetext{e}{S, the sensitivity of the filter, is in units of $10^{-17}$ ergs counts$^{-1}$ cm$^{-2}$.}
+\end{deluxetable}
 
@@
 It is not uncommon to assume that $F(\lambda)$ is constant over the small width of the filter. 
-%However, our filter transmission curves are sampled at $5$\ \AA\ intervals which is the same sampling as the spectral energy distribution of the standard star obtained from the ESO archives (WILL CHECK CALSPEC).
-However, we calculate the integral numerically.
-The system sensitivity, including the sensitivity of the telescope optics and the detector response is then given by
+However, since our filter transmission curves are sampled at wavelengths similar to sampling of the spectrum of GD50 from the the CALSPEC library \citep{Bohlin2017}, we interpolate both spectra and compute the integral numerically.
+The conversion from count rate to flux units for each filter is then given by
 \begin{equation*}
@@
 \caption{ $10'' \times 10''$ (or about $70 \rm \ kpc \times 70 \rm \ kpc $) images of each galaxy in our sample.
-Top row: Continuum surface brightness in ergs s$^{-1}$ cm$^{-2}$ arcsec$^{-2}$ measured in the HeII/3000+48 filter.
+Top row: Continuum surface brightness in ergs s$^{-1}$ cm$^{-2}$ pixel, measured in the HeII/3000+48 filter.
 Bottom row: Continuum-subtracted \ion{Mg}{2} surface brightness.
@@
 \ref{sec.sb}.
-The colorbar shows the scaling used for the \ion{Mg}{2} images.}
+The colorbar shows the scaling used for the bottom row \ion{Mg}{2} images.}
 \label{fig:stamp_images}
@@
 With the 1$\sigma$ detection limit, SB$_1$, determined for the continuum+\ion{Mg}{2} (HeII+47) image, we define a thicker (or ``extended") annulus to be used to search for any extended \ion{Mg}{2} emission.
-This extended annulus has an inner radius approximately the size of the SB$_1$ isophotal contour for each galaxy.
+This annulus will have an inner radius approximately the size of the SB$_1$ isophotal contour for each galaxy.
 The outer radius is chosen to be the inner radius plus 5 pixels.
+With this larger annulus, we can average any flux over large areas to reach lower SB.
 The mean radii of these extended apertures are 18, 18, 24 and 21 kpc from the centers of the targets J.26, J.36, J.03 and J.64, respectively.
@@
 
-The sensitivity required to detect an extended source depends on its size, as one can reach lower SB levels by spatially averaging over large apertures.
-In the ideal case of perfect sky subtraction and continuum subtraction, the 1$\sigma$ SB limit for an extended source is $SB_{1}/\sqrt{A_\text{src}}$, where $A_\text{src}$ is the area in arcsec$^2$ and $SB_{1}$ is the surface brightness limit per 1 arcsec$^2$ aperture.
-In practice, the actual detection limits are affected by systematics from imperfect subtraction.
-Therefore, we empirically determine the limits as follows.
-We mask all the artifacts and sources in the continuum-subtracted images.
-Next, we generate apertures with sizes similar to our extended annulus ($\sim 20 \rm\ sq.arcsec$), place them at random, and extract the fluxes, $F_{\text{src}}$, within these apertures.
+In the case of perfect sky subtraction and continuum subtraction, the 1$\sigma$ SB limit for an extended source is $SB_{1}/\sqrt{A_\text{src}}$, where $A_\text{src}$ is the area in arcsec$^2$ and $SB_{1}$ is the surface brightness limit per 1 arcsec$^2$ aperture.
+However, our actual detection limits are altered by systematic error from imperfect subtraction.
+Therefore, we determine the limits as follows.
+We first mask all the artifacts and sources in the continuum-subtracted images.
+Next, we generate many apertures with sizes similar to our extended annulus ($\sim 20 \rm\ sq.arcsec$), place them at random, and extract the fluxes, $F_{\text{src}}$, within these apertures.
+We then normalize the vales of $F_{\text{src}}$ by dividing by $\sigma_{\text{src}}$, where $\sigma_{\text{src}} \equiv SB_{1}\sqrt{A_\text{src}}$.
+For perfect sky subtraction and continuum subtraction, the distribution of extracted fluxes should follow a Gaussian distribution with a variance equal to $\sigma_{\text{src}}$.
+The distribution of $F_{\text{src}}/\sigma_{\text{src}}$ for these apertures is shown in Figure \ref{fig:limits}
 
- In the ideal case that the sky and continuum are perfectly subtracted the value of $F_{\text{src}}/ \sigma_{\text{src}}$, where $\sigma_{\text{src}} \equiv SB_{1}\sqrt{A_\text{src}}$, from many random apertures should follow a Gaussian distribution with unit variance.
-The distribution of $F_{\text{src}}/\sigma_{\text{src}}$ for these apertures is shown in Figure \ref{fig:limits}.
 We calculate the variance and mean of the distribution and find that the variance of the distribution is $\sigma'_{\text{src}}=1.1$, implying that the SB detection limit for our continuum-subtracted image is higher than $\sigma_{\text{src}}$ by a factor of 10\%.
-We thus adopt $F_{\text{limit}} \equiv \sigma'_{\text{src}}$  as the $1 \sigma$ upper limit on the total line flux of extended \ion{Mg}{2} emission.
+We adopt $F_{\text{limit}} \equiv \sigma'_{\text{src}}$  as the $1 \sigma$ upper limit on the total line flux of extended \ion{Mg}{2} emission.
 The SB$_{\text{limit}}$ is then $F_{\text{limit}}/A_{\rm{src}}$.
@@
 
-\begin{table}[h]
-\centering
-%\begin{minipage}{4in}
-\caption{Significance of extracted flux and detection limits.\label{tab:det_lims}}  
-\begin{tabular}{lllll} \hline \hline
-Object & F$_{\rm{src}}$(\ion{Mg}{2})\footnote{ \ion{Mg}{2} flux is in units of $10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$.
-The value in parentheses is the statistical significance with respect to $\sigma_{\text{src}}$.
-} & 5SB$_{\text{limit}}$\footnote{ Limits are in units of $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^{-2}$.} & Area\footnote{ Area of the extended annulus in arcsec$^2$.} \\  \hline
-J033225.26-274524.0 &  2.44(0.92)& 6.51	& 21 \\
-J033232.36-274725.0 &  -1.40(-0.53)& 6.51 & 21 \\
-J033230.03-274347.3 &  -5.23(-1.75)& 5.74 & 27 \\
-J033229.64-274242.5 &  1.23 (0.44) & 6.22  &26 \\
-J033230.57-274518.2 &  -2.53 (-1.00) & 6.81 &18 \\ \hline
-\end{tabular}
-%\end{minipage}
-\end{table}
+\begin{deluxetable}{c D c c}
+\tablecaption{Significance of extracted flux and detection limits.\label{tab:det_lims}}
+\tablehead{\colhead {Object } & \multicolumn2c{F$_{\rm{src}}$(\ion{Mg}{2})\tablenotemark{a}} & \colhead {5SB$_{\text{limit}}$\tablenotemark{b}} & \colhead {Area\tablenotemark{c}}}
+\decimals
+\startdata
+J033225.26-274524.0 &   2.44(0.92)   & 6.51 & 21 \\
+J033232.36-274725.0 &  -1.40(-0.53)  & 6.51 & 21 \\
+J033230.03-274347.3 &  -5.23(-1.75)  & 5.74 & 27 \\
+J033229.64-274242.5 &   1.23 (0.44)  & 6.22 & 26 \\
+J033230.57-274518.2 &  -2.53 (-1.00) & 6.81 &18 \\
+\enddata
+\tablenotetext{a}{\ion{Mg}{2} flux is in units of $10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$. The value in parentheses is the statistical significance with respect to $\sigma_{\text{src}}$.}
+\tablenotetext{b}{Limits are in units of $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^{-2}$.}
+\tablenotetext{c}{Area of the extended annulus in arcsec$^2$.}
+\end{deluxetable}
 
 \subsection{Test of Surface Brightness Limits}\label{subsec:test}
-To show that our detection limits are reasonable, we simulate emission with varying intensities.
-The results of this exercise are shown in Figure \ref{fig:sigmas}.
+To show that \ion{Mg}{2} emission with SB strengths comparable to our limits can be detected in our narrowband imaging, we simulate emission with varying intensities of SB$_{\text{limit}}$.
 For each galaxy, we assign our simulated emission a constant surface brightness corresponding to 1, 3, 5, 10 and 20 times the $1\sigma$ SB$_{\text{limit}}$ inside the largest annulus used (i.e., the extended annulus).
-Additionally, we assume Gaussian noise with 1$\sigma$ equal to 1SB$_{\text{limit}}$.
-After placing the simulated emission around the galaxy, we subtract the continuum in the same manner as explained in Section \ref{subsec.cont_sub}.
+We assume Gaussian noise with 1$\sigma$ equal to 1SB$_{\text{limit}}$.
+Next, we subtract the continuum in the same manner as explained in Section \ref{subsec.cont_sub}.
 
-We then construct a smoothed $\chi$ image following the techniques in \cite{Hennawi2013} and \cite{Battaia_2015}. First, we smooth the continuum-subtracted image:
+We construct smoothed $\chi$ images, $\chi_{\text{smooth}}$, for each level of simulated emission, following the techniques in \cite{Hennawi2013} and \cite{Battaia_2015}.
+These $\chi_{\text{smooth}}$ images can aid in identifying the presence and detectability of extended \ion{Mg}{2} emission.
 
+First, the model continuum-subtracted image is smoothed by the operation:
 \begin{equation}
-I_{\text{smooth}}= \text{CONVOLVE[NB-CONTINUUM]},
+I_{\text{smooth}}= \text{CONVOLVE[line-continuum]},
 \end{equation}
-where the CONVOLVE operation indicates convolution of the images with a Gaussian kernel with FWHM=1.5 pixels.
-Next, we computed the sigma image ($\sigma_{\text{smooth}}$) for the smoothed image ($I_{\text{smooth}}$) by propagating the noise image of the unsmoothed data:
+where the CONVOLVE operation indicates convolution of the \ion{Mg}{2} images with a Gaussian kernel with FWHM=1.5 pixels.
+Next, we computed the sigma image, $\sigma_{\text{smooth}}$, by convolving the propagated error image:
 \begin{equation}
-\sigma_{\text{smooth}}=\sqrt{\text{CONVOLVE}^2[\sigma^2_{\text{unsmooth}}]},
+\sigma_{\text{smooth}}=\sqrt{\text{CONVOLVE}^2[\sigma^2]},
 \end{equation}
-where the CONVOLVE$^2$ operation indicates the convolution of the variance image with the square of the Gaussian kernel. The smoothed $\chi$ image is then
+where the CONVOLVE$^2$ operation indicates convolution of the image with the square of the Gaussian kernel. The smoothed $\chi$ image is then the product of the data image divided by the sigma image.
 \begin{equation}
@@
 \end{equation}
-This $\chi_{\text{smooth}}$ image aids in recognizing the presence of extended \ion{Mg}{2} emission.
 
@@
 \subsection{Limits on \ion{Mg}{2} Emission}
-For our sample of galaxies, we are sensitive to extended emission in annuli at %minimum 
-projected distances of 
-18, 18, 24 and 21 kpc from the centers of J.26, J.36, J.03 and J.64, respectively.
+For our sample of galaxies, we are sensitive to extended emission in annuli at projected distances of 18, 18, 24 and 14 kpc from the centers of J.26, J.36, J.03 and J.64, respectively.
 %%% KHRR -- don't understand these distances
@@
 The mean EW$_{\text{\ion{Mg}{2}}}$ is computed for all pixels inside each Keck/LRIS aperture, defined in Sec.
-\ref{subsec.ew}, and the resulting values are summarized in Table \ref{tab:abs_props}.
+\ref{subsec.ew}, and the error is propagated in quadrature.
+The resulting values of the mean EW and the error of the measurements are summarized in Table \ref{tab:abs_props}.
 Comparing our narrowband EWs with those measured from the spectra, we find agreement to within  1.6-4.6$\sigma$ for galaxies J.26 and J.36, and more statistically significant differences for galaxies J.03 and J.64.
@@
 
-\begin{table}[]
-\centering
-\caption{Properties of \ion{Mg}{2}\ Absorption\label{tab:abs_props}}  
-\begin{tabular}{lccccc} \hline \hline
-Object & SB$_{\rm abs}$\footnote{ Maximum SB decrement in units of $10^{-18}$ erg sec $^{-1}$ cm$^{-2}$ arcsec$^{-2}$.} & $R_{\perp}^{\rm{SB}_1}$\footnote{ Radius of SB$_1$ contour in kpc.} &\ \ \ NB EW$_{\text{\ion{Mg}{2}}}^{\rm obs}$\footnote{ Measured from narrowband images, and reported in the observed frame.} & LRIS EW$_{\text{\ion{Mg}{2}}}^{\rm obs}$\footnote{ Measured from Keck/LRIS spectra in the observed frame.
-Includes both lines in the \ion{Mg}{2} doublet.}  \\
-	&   & (kpc) & (\AA) &(\AA)\\ \hline
-J.26 &  $-5.4 \pm 1.28 $ & 8 &     $\ \ \ 3.5 \pm 0.80$ & $7.5 \pm 0.35 $\\
-J.36 &  $-5.6 \pm 0.12 $ & 15 & $\ \ \ 7.7 \pm 1.02$ & $5.8 \pm 0.49$\\
-J.03 &  $-4.4 \pm 0.62 $ & 21 & $\ \ \ 5.4 \pm 0.71$ & $12.7 \pm 1.71$\\
-J.64 &  $-18.2 \pm 0.13 $ & 10 & $\ \ \ 7.6 \pm 0.66$ & $13.2 \pm 0.26$\\
-J.57 &  $-1.3 \pm 1.15   $ & 11& -$0.65 \pm 0.58$ & $6.10 \pm 0.37$\\ \hline
-\end{tabular}
-\end{table}
+\begin{deluxetable}{c c c c c}
+\tablecaption{Properties of \ion{Mg}{2}\ Absorption\label{tab:abs_props}}
+\tablehead{\colhead {Object } & \colhead {SB$_{\rm abs}$\tablenotemark{a}} & \colhead {$R_{\perp}^{\rm{SB}_1}$\tablenotemark{b}} & \colhead {LRIS EW$_{\text{\ion{Mg}{2}}}^{\rm obs}$\tablenotemark{c}} & \colhead {NB EW$_{\text{\ion{Mg}{2}}}^{\rm obs}$\tablenotemark{d}} \\
+\colhead{} & \colhead{} & \colhead{(kpc)} & \colhead{(\AA)} & \colhead{(\AA)}}
+\startdata
+J.26 & \ $-5.4 \pm 1.2 $  & 8   &\  $7.5 \pm 0.4$ & \ \ $3.5 \pm 0.8$ \\
+J.36 & \ $-5.6 \pm 0.1 $  & 15 &\  $5.8 \pm 0.5$ & \ \ $7.7 \pm 1.0$ \\
+J.03 &\  $-4.4 \pm 0.6 $  & 21 & $12.7 \pm 1.7$ & \ \ $5.4 \pm 0.7$  \\
+J.64 & $-18.2 \pm 0.1$ & 10 & $13.2 \pm 0.3$   &\ \ $7.6 \pm 0.7$ \\
+J.57 &\  $-1.3 \pm 1.2 $  & 11 & $6.10 \pm 0.4$ & $-0.7 \pm 0.6$ \\
+\enddata
+\tablenotetext{a}{Maximum SB decrement in units of $10^{-18}$ erg sec $^{-1}$ cm$^{-2}$ arcsec$^{-2}$.}
+\tablenotetext{b}{Radius of SB$_1$ contour.}
+\tablenotetext{c}{Measured from Keck/LRIS spectra in the observed frame. Includes both lines in the \ion{Mg}{2} doublet.}
+\tablenotetext{d}{Measured from narrowband images, and reported in the observed frame.}
+\end{deluxetable}
 
@@
 The flux from both emission lines can be converted into two surface brightness values by taking the average of the flux measured at each location and each transition, and dividing by a 1 arcsec$^2$ aperture.
-
-%Figure \ref{fig:SFR_lim} shows a plot of the 5$\sigma$ detection limits determined for each galaxy in our sample as well as the SB calculated for the galaxy TKRS 4389 vs.
-SFR.
-The figure suggests that we should be able to detect scattered \ion{Mg}{2} emission with strengths similar to that detected in TKRS 4389 in our narrowband imaging.
-Taken at face value, the figure could be consistent with a positive correlation between \ion{Mg}{2} SB and SFR.
-Future observations are needed to verify this trend, and the possibility that objects with yet higher SFRs ($>\sim$50 $\msunperyr$) exhibit brighter \ion{Mg}{2} emission.
-Figure \ref{fig:detection_lim} shows the same SB values as in Figure \ref{fig:SFR_lim} vs.
-$\log(M_*/M_{\odot})$.
-The figure suggests that extended \ion{Mg}{2} emission may be brighter in lower mass galaxies.
-Both \cite{Erb2012} and \cite{Feltre2018} observed a similar trend in their examination of the total \ion{Mg}{2} emission strength vs.
-galaxy $M_*$.
-Combining the previous figures, Figure \ref{fig:sSFR_lim} shows that the galaxy with detected \ion{Mg}{2} also has the highest specific SFR (SFR/$M_*$).
-If it is ultimately confirmed that low-$M_*$ galaxies with the highest SFRs exhibit the brightest emission this could point to a physical link between the escape velocity of galaxies and the spatial extent of wind material.
 
@@
 The mean EW values are the same as those shown in the right column of Figure \ref{fig:ews}.
-We have normalized the corresponding radii by the approximate size of the SB$_1$ contour of each galaxy.
-There is significant scatter relative to the error bars at extended distances.}
+We have normalized the corresponding radii by the approximate size of the SB$_1$ contour of each galaxy.}
 \label{fig:ew_comb}
@@
 
-%\begin{figure}[!htb]
-%\centering
-%\includegraphics[scale=0.6]{mass_limits.pdf}
-%\caption{Comparison of our detection limits to the measured extended emission of TKRS 4389 vs Stellar Mass. The color scheme is the same as Figure \ref{fig:ew_comb}.}
-%\label{fig:detection_lim}
-%\end{figure}
-
-%\begin{figure}[!htb]
-%\centering
-%\includegraphics[scale=0.6]{sSFR_limits.pdf}
-%\caption{Comparison of our detection limits to the measured extended emission of TKRS 4389 vs sSFR. The color scheme is the same as Figure \ref{fig:ew_comb}.}
-%\label{fig:sSFR_lim}
-%\end{figure}
-
 \subsection{Geometry of Scattering Material}
@@
 Excepting galaxy J.03, the predicted SB of this emission lies above our detection limits.
-Under the assumption that the wind in these galaxies does in fact extend beyond the $\rm SB_1$ isophotal contour (at $R_{\perp}^{\rm{SB}_1} = 8-21$ kpc), this result suggests that these galaxies do not host isotropic, dust-free winds.
+Under the assumption that the wind in these galaxies does in fact extend beyond the $\rm SB_1$ isophotal contour (at $R_{\perp}^{\rm{SB}_1} = 8-21$ kpc), the absence of the predicted emission, calculated from an isotropic wind model, in our narrowband imaging suggests that these galaxies do not host isotropic, dust-free winds.
 
@@
 We compared our surface brightness detection limits with the predictions of the radiative transfer models of \cite{Prochaska_2011}.
-We are able to rule out that the winds in our sample are isotropic and dust free, as our images are sufficiently sensitive to detect the emission predicted by such models.
+If the winds in these galaxies do extend beyond the stellar disk, $\lesssim 20$ kpc, then we are able to rule out that the winds in our sample are isotropic and dust free, as our images are sufficiently sensitive to detect the emission predicted by such models.
 Adopting the assumption of dusty and/or anisotropic winds reduces the strength of the predicted \ion{Mg}{2} emission to lie below our detection limits.

### 2018-09-09 for_submission/rvaught_2018.tex
update 9/2/18
Sept 8th

@@
 \author{Ryan Rickards Vaught}
-\affiliation{Department of Astronomy, San Diego State University, San Diego, CA 92182}
+\affiliation{Department of Astronomy, San Diego State University, San Diego, CA 92182, USA}
 \affiliation{Department of Physics, University of California, San Diego, 9500 Gilman Dr., La Jolla, CA 92093, USA}
 
- \author{Kate H. R. Rubin }
+ \author{Kate H. R. Rubin}
  \affiliation{Department of Astronomy, San Diego State University, San Diego, CA 92182, USA}
@@
  \author{J. Xavier Prochaska}
- \affiliation{Department of Astronomy \& Astrophysics, University of California, 1156 High St., Santa Cruz, CA 95064 USA}
+ \affiliation{Department of Astronomy \& Astrophysics, University of California, 1156 High Street, Santa Cruz, CA 95064, USA}
 
 \author{Joseph F. Hennawi}
-\affiliation{Department of Physics, Broida Hall, University of California, Santa Barbara, CA 93106-9530}
+\affiliation{Department of Physics, Broida Hall, University of California, Santa Barbara, CA 93106, USA}
 
@@
 
-%\begin{table*}[t]
-%\centering
-%\caption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) includes both components of the \ion{Mg}{2} doublet and is 
-%determined from analysis of the supplemental Keck/LRIS spectra.}
-%\begin{tabular}{llllllll} \hline \hline
-%Object\footnote{ Name in parenthesis to be used as shorthand for the objects throughout the remainder of the paper.
-} & R.A.
-& Dec  & $z$ & SFR($M_{\odot}$ yr$^{-1}$) & $\log{M_{*}/M_{\odot}}$ & EW$_{\rm{obs}}$(\AA) & $\tau_V$\footnote{ Total V-band optical depth of dust as estimated by SED fitting with MAGPHYS.
-}\smallskip      \\ \hline
-%J033225.26-274524.0 (J.26)      & 03:32:25.26 & -27:45:23.9 & 0.6660 & $9.1_{-3.7}^{+1.3}$& $9.86_{-0.04}^{+0.05}$ & $7.539\pm 0.354$ &  $1.227_{-0.20}^{+1.54}$\\
-
-%J033231.36-274725.0 (J.36)      & 03:32:31.35 & -27:47:24.9 &   0.6669 & $10.5_{-1.6}^{+1.7}$ & $10.02_{-0.03}^{+0.03}$&$5.835 \pm 0.493$ & $1.377_{-0.23}^{+0.60}$\\
-
-%J033230.03-274347.3  (J.03)     & 03:32:30.03 & -27:43:47.2  &   0.6679 & $3.8_{-0}^{+0}$ & $10.98_{-0.0}^{+0.01}$ &$12.794 \pm 1.710$ & $0.297_{-0.0}^{+0.0}$ \\
-
-%J033229.64-274242.6  (J.64)    & 03:32:29.64 & -27:42:42.5 & 0.6671 & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &$13.239 \pm 0.263$ & $3.897_{-0.93}^{+1.15}$\\
-
-%J033230.57-274518.2  (J.57)    & 03:32:30.56 & -27:45:18.2 &   0.6807  & $12.6_{-2.1}^{+1.7}$ & $10.48_{-0.07}^{+0.03}$ &$6.106 \pm 0.370$ & $1.262_{-0.40}^{+1.23}$ \\
-%\hline 
-%\end{tabular}
-%\tablenotemark{}
-%\tablenotetext{}{\textit{Note} - The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SEDs with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}}
-%\label{tab:prop}
-%\end{table*}
-
 \begin{deluxetable*}{c c c c D D c D}
@@
 determined from analysis of the supplemental Keck/LRIS spectra. \label{tab:prop}}
-\tablehead{\colhead{Object} & \colhead{R.A.} & \colhead{Dec} & \colhead{$z$} & \multicolumn2c{SFR} & \multicolumn2c{$\log{M}$} & \colhead{EW$_{\rm{obs}}$} & \multicolumn2c{ $\tau_V$} \\ 
-\colhead {} & \colhead {} & \colhead {} & \colhead{} & \multicolumn2c{($M_{\odot}$ yr$^{-1}$)} & \multicolumn2c{$\log{M_{*}/M_{\odot}}$} & \colhead{(\AA)} & \multicolumn2c{}}
+\tablehead{\colhead{Object} & \colhead{R.A.} & \colhead{Dec} & \colhead{$z$} & \multicolumn2c{$\log$(SFR)} & \multicolumn2c{$\log{(M)}$} & \colhead{EW$_{\rm{obs}}$} & \multicolumn2c{ $\tau_V$} \\ 
+\colhead {} & \colhead {} & \colhead {} & \colhead{} & \multicolumn2c{($\log M_{\odot}$ yr$^{-1}$)} & \multicolumn2c{($\log{M_{*}/M_{\odot}}$)} & \colhead{(\AA)} & \multicolumn2c{}}
 \decimals
@@
 It is not uncommon to assume that $F(\lambda)$ is constant over the small width of the filter. 
-However, since our filter transmission curves are sampled at wavelengths similar to sampling of the spectrum of GD50 from the the CALSPEC library \citep{Bohlin2017}, we interpolate both spectra and compute the integral numerically.
+However, since our filter transmission curves are sampled at wavelengths similar to sampling of the spectrum of GD50 from the the CALSPEC library \citep{Bohlin2017}, we interpolate both spectra and compute the integral without the constant $F(\lambda)$ assumption .
 The conversion from count rate to flux units for each filter is then given by
@@
 We convert these RMS values to SB limits per $1~\rm arcsec^2$  aperture.
-We find that the 1$\sigma$ detection limits
-(SB$_1$) are $6.332\times10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ and $5.808\times10^{-19} $ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ in the HeII/3000+48 and HeII+47 filters, respectively.
+We find that the 1$\sigma$ detection limits (SB$_1$) are $6.332\times10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ and $5.808\times10^{-19} $ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ in the HeII/3000+48 and HeII+47 filters, respectively.
 With the 1$\sigma$ detection limit, SB$_1$, determined for the continuum+\ion{Mg}{2} (HeII+47) image, we define a thicker (or ``extended") annulus to be used to search for any extended \ion{Mg}{2} emission.
@@
 Next, we generate many apertures with sizes similar to our extended annulus ($\sim 20 \rm\ sq.arcsec$), place them at random, and extract the fluxes, $F_{\text{src}}$, within these apertures.
-We then normalize the vales of $F_{\text{src}}$ by dividing by $\sigma_{\text{src}}$, where $\sigma_{\text{src}} \equiv SB_{1}\sqrt{A_\text{src}}$.
+We then normalize the values of $F_{\text{src}}$ by dividing by $\sigma_{\text{src}}$, where $\sigma_{\text{src}} \equiv SB_{1}\sqrt{A_\text{src}}$.
 For perfect sky subtraction and continuum subtraction, the distribution of extracted fluxes should follow a Gaussian distribution with a variance equal to $\sigma_{\text{src}}$.
@@
 
-We construct smoothed $\chi$ images, $\chi_{\text{smooth}}$, for each level of simulated emission, following the techniques in \cite{Hennawi2013} and \cite{Battaia_2015}.
-These $\chi_{\text{smooth}}$ images can aid in identifying the presence and detectability of extended \ion{Mg}{2} emission.
+To aid in identifying the presence and detectability of extended \ion{Mg}{2} emission, we construct a $\chi_{\text{smooth}}$, for each level of simulated emission, following the techniques in \cite{Hennawi2013} and \cite{Battaia_2015}.
 
-First, the model continuum-subtracted image is smoothed by the operation:
+To construct this smoothed image, we first performed the following operation on a continuum-subtracted image:
 \begin{equation}

### 2018-09-09 for_submission/rvaught_2018.tex
Sept 9th

@@
 \tablenotetext{e}{S, the sensitivity of the filter, is in units of $10^{-17}$ ergs counts$^{-1}$ cm$^{-2}$.}
-\end{deluxetable}
+\end{deluxetable}\ 
+\\
 
 \subsection{Absolute Flux Calibration}
-We acquired observations of the standard star GD50 from archival ESO calibration imaging at 4 independent epochs.
+We acquired observations of the standard star GD50 from archival European Southern Observatory (ESO) calibration imaging at 4 independent epochs.
 Performing aperture photometry at each epoch and airmass, we calculated the atmospheric extinction coefficients, $k$, to be 0.181 magnitudes for the HeII/3000+48 filter and 0.190 magnitudes for the HeII+47 filter.
@@
 It is not uncommon to assume that $F(\lambda)$ is constant over the small width of the filter. 
-However, since our filter transmission curves are sampled at wavelengths similar to sampling of the spectrum of GD50 from the the CALSPEC library \citep{Bohlin2017}, we interpolate both spectra and compute the integral without the constant $F(\lambda)$ assumption .
+However, since our filter transmission curves are sampled at wavelengths similar to sampling of the spectrum of GD50 from the latest CALSPEC spectral library \citep{Bohlin2017}, we interpolate both spectra and compute the integral without the above assumption .
 The conversion from count rate to flux units for each filter is then given by
@@
 To test for the presence of \ion{Mg}{2} emission, we perform aperture photometry on the continuum-subtracted images using the python library \emph{Photutils}.
-We choose annuli with a radial thickness of 1 pixel or $0.25 ''$, such that $r_{inner}=r_{outer}-1$ (in pixels).
+We choose annuli with a radial thickness of 1 pixel or $0.25 ''$, such that the inner radius is, $r_{inner}=r_{outer}-1$ (in pixels).
 Each annulus is centered on the flux-weighted centroid of the galaxy.
@@
 The outer radius is chosen to be the inner radius plus 5 pixels.
-With this larger annulus, we can average any flux over large areas to reach lower SB.
-The mean radii of these extended apertures are 18, 18, 24 and 21 kpc from the centers of the targets J.26, J.36, J.03 and J.64, respectively.
+With this larger annulus, we can average any flux over large areas to reach lower values of SB.
+The mean radii of these extended apertures are 18, 18, 24 and 14 kpc from the centers of the targets J.26, J.36, J.03 and J.64, respectively.
 The resulting SB measurements are shown in Figure~\ref{fig:sb_profiles}.
@@
 
-To aid in identifying the presence and detectability of extended \ion{Mg}{2} emission, we construct a $\chi_{\text{smooth}}$, for each level of simulated emission, following the techniques in \cite{Hennawi2013} and \cite{Battaia_2015}.
+To aid in identifying the presence and detectability of extended \ion{Mg}{2} emission we construct a $\chi_{\text{smooth}}$ image for each level of simulated emission following the technique described in \cite{Hennawi2013} and \cite{Battaia_2015}.
 
-To construct this smoothed image, we first performed the following operation on a continuum-subtracted image:
+To construct the set of smoothed images, we first performed the following operation on the continuum-subtracted images:
 \begin{equation}
@@
 \end{equation}
-where the CONVOLVE$^2$ operation indicates convolution of the image with the square of the Gaussian kernel. The smoothed $\chi$ image is then the product of the data image divided by the sigma image.
-\begin{equation}
-\chi_{\text{smooth}}=\frac{I_{\text{smooth}}}{\sigma_{\text{smooth}}}.
-\end{equation}
+where the CONVOLVE$^2$ operation indicates convolution of the image with the square of the Gaussian kernel.
+The smoothed $\chi$ image, $\chi_{\text{smooth}}$, is then the product of the smoothed line image, $I_{\text{smooth}}$, divided by the sigma image, $\sigma_{\text{smooth}}$.
+%\begin{equation}
+%\chi_{\text{smooth}}=\frac{I_{\text{smooth}}}{\sigma_{\text{smooth}}}.
+%\end{equation}
 
@@
 \subsection{Limits on \ion{Mg}{2} Emission}
-For our sample of galaxies, we are sensitive to extended emission in annuli at projected distances of 18, 18, 24 and 14 kpc from the centers of J.26, J.36, J.03 and J.64, respectively.
+For our sample of galaxies, we are sensitive to extended emission in annuli with mean distances of 18, 18, 24 and 14 kpc from the centers of J.26, J.36, J.03 and J.64, respectively.
 %%% KHRR -- don't understand these distances
@@
 We discuss possible causes for these differences below.
-We also note here that given the size of the median seeing disk for these observations ($\rm FWHM\approx0.8\arcsec$), the EW$_{\text{\ion{Mg}{2}}}$ values measured in adjacent pixels (each of which subtends $0.25\arcsec$) are not independent, and hence their errors are covariant.
+
+Given the size of the median seeing disk for these observations ($\rm FWHM\approx0.8\arcsec$), the EW$_{\text{\ion{Mg}{2}}}$ values measured in adjacent pixels (each of which subtends $0.25\arcsec$) are not independent, and hence their errors are covariant.
 This covariance implies that the uncertainties in our mean EW$_{\text{\ion{Mg}{2}}}$ values are underestimated, such that the discrepancies between these values and those measured in our LRIS spectra are likely less significant than the tension described above.

### 2019-01-09 for_submission/rvaught_2018.tex
9/15

@@
 \section{Introduction}\label{sec:intro}
-Galactic winds play a critical role in regulating the star formation rates and stellar masses of galaxies \citeth{Werk_2014}; however, the physics that powers these winds remains uncertain.
-Some possible mechanisms have been proposed by theoretical studies that include thermal pressure from core collapse supernovae, radiation pressure from starbursts, and finally cosmic ray pressure (e.g., \citethnop{Larson_1974}; \citethnop{Chevalier_1985}; \citethnop{Springel_2003}; \citethnop{Sugahara_2017}).
+Galactic winds likely play a critical role in regulating the star formation rates and stellar masses of galaxies (e.g., \citethnop{SP1999}; \citethnop{Keres2009}; \citethnop{Oppenheimer2010}; \citethnop{Hopkins2014}; \citethnop{Werk_2014}); however, the physics that powers these winds remains uncertain.
+Some possible mechanisms have been proposed by theoretical studies that include thermal pressure from core collapse supernovae, radiation pressure from starbursts, and finally cosmic ray pressure (e.g., \citethnop{Larson_1974}; \citethnop{MO1977}; \citethnop{Chevalier_1985}; \citethnop{Breitschwerdt1991}; \citethnop{Springel_2003}; \citethnop{Murray2011}; \citethnop{Uhlig2012}).
+%\citethnop{Sugahara_2017}
 Additionally, the impact galactic winds have on their host galaxies (i.e., their mass and energy content) has remained difficult to constrain with observations.
 
-An accurate picture of the types of galaxies that host outflows comes from numerous absorption line studies of galaxies (e.g., \citethnop{Veilleux2005}; \citethnop{Weiner2009}; \citethnop{Martin2012}; \citethnop{Rubin_2014}).
+An accurate picture of the types of galaxies that host outflows comes from numerous absorption line studies of galaxy spectroscopy 
+(e.g., \citethnop{Heckman2000}; \citethnop{Shapley2003}; \citethnop{Rupke2005b}; \citethnop{Veilleux2005}; \citethnop{Weiner2009}; \citethnop{Martin2012}; \citethnop{Rubin_2014}).
 Gas flows are detected by measuring the blueshift (outflow) or redshift (inflow) of absorption transitions with respect to the host galaxy systemic velocity.
-Spectroscopy of galaxies from low to high redshifts probing cold gas ($T \lesssim 10^2$ K) which absorbs in \ion{Na}{1} and cool gas ($T \sim 10^4$ K) absorbing \ion{Mg}{2} has revealed outflows in most galaxies that host active star formation (e.g.
-\citethnop{chen2010}; \citethnop{Martin2012}; \citethnop{Rubin_2014}).
-While this technique is useful for constraining the radial velocity, column density and covering fraction of the flow, it weakly constrains the overall radial extent and provides little information on the morphology of the gas.
+Spectroscopy of galaxies from low to high redshifts probing cold gas ($T \lesssim 10^2$ K) which absorbs in \ion{Na}{1} and cool gas ($T \sim 10^4$ K) absorbing \ion{Mg}{2} has revealed outflows in most galaxies that host active star formation (e.g., \citethnop{chen2010}; \citethnop{Martin2012}; \citethnop{Rubin_2014}).
+However, while this technique is useful for constraining the radial velocity, column density and covering fraction of the flow, it weakly constrains the overall radial extent and provides little information on the morphology of the gas.
 
 An alternative method that can in principle assess the radial extent and morphology of outflows is to trace the gas in emission.
-This has been demonstrated using rest-frame optical transitions (i.e., H$\alpha$, [\ion{O}{3}]) as tracers for winds around nearby starbursts \citep[e.g.,][]{{Matsubayashi2009,Veilleux2009}} as these transitions can trace the warm shock-heated phase of the gas.
+This has been demonstrated using rest-frame optical transitions (i.e., H$\alpha$, [\ion{O}{3}]) as tracers for winds around nearby starbursts \citep[e.g.,][]{{Heckman1990,Lehnert1999,Veilleux2003,Matsubayashi2009}} %Veilleux2009}
+% I removed Veilleux2009 as it is about imaging in the near-IR tracing molecular gas 
+as these transitions are sensitive to the warm shock-heated phase of the gas. 
 Another transition potentially useful for tracing winds in emission is the \ion{Mg}{2} $\lambda\lambda 2976,2803$ doublet in the rest-frame ultraviolet
-\citep[UV;][]{{Weiner2009, Kornei2013}}.
-While most studies of winds using \ion{Mg}{2} have focused on its absorption kinematics, \cite{Rubin_2011} observed  strong \ion{Mg}{2} emission with a P-Cygni line profile in the spectrum of a strongly star-forming galaxy at redshift $z = 0.694$.
-In addition, the emission was spatially extended, permitting the first direct measurement of the extent of an outflow ($\gtrsim$ 7 kpc) in the distant universe.
+\citep[UV; e.g.,][]{{Weiner2009, Kornei2013}}.
+While most studies of winds using \ion{Mg}{2} have focused on its absorption kinematics, \cite{Rubin_2011} observed  strong \ion{Mg}{2} emission with a P-Cygni line profile in the Keck/Low Resolution Imaging Spectrometer (LRIS) spectrum of a strongly star-forming galaxy at redshift $z = 0.694$.
+In addition, the emission was spatially extended beyond the galaxy continuum, permitting the first direct measurement of the extent of an outflow ($\gtrsim$ 7 kpc) in the distant universe.
 
@@
 If the optical depth of the gas is high, then the gas will resonantly trap the absorbed photons.
-Because the photons are absorbed in the rest frame of the gas, the absorption will be blueshifted relative to the galaxy's systemic velocity.
+Because the photons are absorbed in the rest frame of the gas, the absorption is observed to be blueshifted relative to the galaxy's systemic velocity.
 The \ion{Mg}{2} ions in the section of the wind farthest from the observer will absorb and scatter photons that are redshifted relative to the front portion of the wind.
-Because the photons are redshifted, the photons travel freely towards the observer through the wind to produce emission at and redward of the systemic velocity of the galaxy (\citethnop{Rubin_2011}, \citethnop{Prochaska_2011}).
+Because the photons are redshifted, the photons travel freely toward the observer through the wind to produce emission at and redward of the systemic velocity of the galaxy (e.g., \citethnop{Rubin_2011}, \citethnop{Prochaska_2011}).
 
-Since the first detection of \ion{Mg}{2} emission in an individual galaxy by \citet{Rubin_2011}, another detection was reported by \cite{Martin2013}, who observed \ion{Mg}{2} emission that extends $12-18$ kpc from a strongly star-forming galaxy
+Since the first detection of \ion{Mg}{2} emission in 
+an individual galaxy by \citet{Rubin_2011}, another detection was reported by \cite{Martin2013}, who observed \ion{Mg}{2} emission that extends $12-18$ kpc from a strongly star-forming galaxy
 at $z=0.9392$.
-\ion{Mg}{2} has also been studied in wide-field galaxy surveys conducted with the Keck DEep Imaging Multi-Object Spectrograph (DEIMOS) and the VLT Multi Unit Spectroscopic Explorer (MUSE)  (\citethnop{Weiner2009}, \citethnop{Kornei2013}, \citethnop{Erb2012}, \citethnop{Feltre2018}).
-These surveys, which include galaxies with redshifts $ 0.70 < z < 2.30$, find that \ion{Mg}{2} may be detected in pure emission, pure absorption or with P-Cygni profiles and that detections of \ion{Mg}{2} in emission were found to be more commonly associated with galaxies of lower stellar mass and with bluer spectral slopes.
+\ion{Mg}{2} has also been studied in galaxy surveys conducted with Keck/LRIS, the Keck DEep Imaging Multi-Object Spectrograph (DEIMOS), the VLT Multi Unit Spectroscopic Explorer (MUSE), and the MMT Blue Channel Spectrograph  (\citethnop{Weiner2009}; \citethnop{Erb2012}; \citethnop{Kornei2013}; \citethnop{Feltre2018}; \citethnop{Henry2018}).
+These surveys, which include galaxies with redshifts $ 0.20 < z < 2.30$, find that \ion{Mg}{2} may be detected in pure emission, pure absorption or with P-Cygni profiles, and that detections of \ion{Mg}{2} in emission were found to be more commonly associated with galaxies of lower stellar mass and with bluer spectral slopes.
 
@@
 spectra for the  \ion{Mg}{2} and  \ion{Fe}{2}$^*$ fine-structure transitions for a variety of wind morphologies.
-The authors demonstrated that isotropic dust-free winds will conserve photon flux, thus predicting that blueshifted absorption lines should be accompanied by emission lines with similar equivalent widths (EW).
+The authors demonstrated that isotropic, dust-free winds will conserve photon flux, thus predicting that blueshifted absorption lines should be accompanied by emission lines with similar equivalent widths (EW).
 Anisotropic winds, however, were demonstrated to exhibit significantly weaker emission by a factor proportional to the angular extent (i.e., solid angle) of the wind.
@@
 In this paper, we present the first narrowband imaging of the \ion{Mg}{2} transition around 5 star-forming  galaxies located in the Great Observatories Origins Deep Survey South (GOODS-S; \citethnop{Giavalisco2004})  field at redshift $z \sim 0.7$.
-We use two filters: a  ``line filter" covering the \ion{Mg}{2} doublet, and a ``continuum filter" that is offset from the line filter by ${\sim}47$ \AA.    
+We use two filters: a  ``line filter'' covering the \ion{Mg}{2} doublet in the observed frame, and a ``continuum filter'' that is offset from the line filter by ${\sim}47$ \AA.    
 The resulting imaging in each filter has a total integration time of 10 hrs.
-As opposed to 1D spectra, the narrowband imaging constrains the surface brightness and radial extent of the wind.
-These observations allow us to create the first ever high-S/N spatially resolved map of both \ion{Mg}{2} emission and absorption.
+As opposed to slit or fiber spectra, the narrowband imaging fully constrains the surface brightness and projected radial extent of the wind.
+These observations allow us to create the first ever high-S/N spatially-resolved map of both detection limits on \ion{Mg}{2} emission and on \ion{Mg}{2} absorption.
 
-In Section \ref{sec:obs_red} we describe our sample of GOODS-S galaxies, supplemental Keck I Low Resolution Imaging Spectrometer (Keck/LRIS) spectra, as well as our VLT/FORS2 observations, image reduction, and absolute flux calibration.
+In Section \ref{sec:obs_red} we describe our sample of GOODS-S galaxies, supplemental Keck/LRIS spectra, as well as our VLT/FORS2 observations, image reduction, and absolute flux calibration.
 We describe our method of continuum subtraction in Section \ref{sec.cont_sub}.
@@
 \subsection{VLT/FORS2 Observations}
-Our narrow-band imaging data were taken in service mode using the FORS2 instrument on the VLT 8.2m telescope Antu between October 2012 and February 2013. 
+Our narrowband imaging data were taken in service mode using the FORS2 instrument on the VLT 8.2m telescope Antu between October 2012 and February 2013. 
 We used two narrowband filters, HeII+47 and HeII/3000+48, that have peak transmission at wavelengths that correspond to the \ion{Mg}{2} doublet lines at our sample redshift of $z\sim0.7$ (see Table \ref{tab:filters}).
@@
 \includegraphics[scale=.55]{avg_seeing_HEII3000.pdf}
-\caption{\textbf{Top}: Distribution of seeing measurements for the 38 HeII+47 images.
-\textbf{Bottom}: Same for the HeII/3000+48 images. The median seeing value for the images in both filters is $\sim 0.8\arcsec$. 
+\caption{\emph{Top}: Distribution of seeing measurements for the 38 HeII+47 images.
+\emph{Bottom}: Same for the HeII/3000+48 images. The median seeing value for the images in both filters is $\sim 0.8\arcsec$. 
 The seeing conditions were calculated from DIMM measurements which are provided by ESO in the header of each science image.
@@
 
-\subsection{Supplemental Keck/LRIS spectra}
+\subsection{Supplemental Keck/LRIS Spectra}
 In addition to VLT imaging, in the present analysis we utilize galaxy spectra taken from the \cite{Rubin_2014} Keck/LRIS program.
@@
 \enddata
-\tablecomments{The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SEDs with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}}
+\tablecomments{The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SEDs with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}.}
 \end{deluxetable*}
@@
 The widths of the transmission curves ($\Delta\lambda$) are calculated by convolving the transmission curves over the total wavelength range of each filter.
-These values differ slightly from those reported by the European Southern Observatory.
+%These values differ slightly from those reported by the European Southern Observatory.
  \label{tab:filters}}
 \tablehead{\colhead {Filter (Line)} & \colhead {$\lambda_{\rm{eff}}$\tablenotemark{a}} & \colhead {$\Delta\lambda$\tablenotemark{b}} & \colhead {N\tablenotemark{c}} & \colhead{$T$\tablenotemark{d}} & \colhead{$S$\tablenotemark{e}} \\
-\colhead {} & \colhead{(\AA)} & \colhead{(\AA)} & \colhead{} & \colhead{(S)} & \colhead{}}
+\colhead {} & \colhead{(\AA)} & \colhead{(\AA)} & \colhead{} & \colhead{(sec)} & \colhead{}}
 \startdata
@@
 \end{deluxetable}\ 
-\\
+%\\
 
@@
 It is not uncommon to assume that $F(\lambda)$ is constant over the small width of the filter. 
-However, since our filter transmission curves are sampled at wavelengths similar to sampling of the spectrum of GD50 from the latest CALSPEC spectral library \citep{Bohlin2017}, we interpolate both spectra and compute the integral without the above assumption .
+However, since our filter transmission curves are sampled at wavelength intervals similar to the sampling of the spectrum of GD50 from the latest CALSPEC spectral library \citep{Bohlin2017}, we interpolate both spectra and compute the integral without the above assumption.
 The conversion from count rate to flux units for each filter is then given by
@@
 \includegraphics[scale=.61]{HEII3000_final.png}
-\caption{Top: Stacked HeII+47 image of the galaxy sample.
-Bottom: Stacked HeII3000+48 image of the same pointing.
+\caption{\emph{Top:} Stacked HeII+47 image of the galaxy sample.
+\emph{Bottom:} Stacked HeII3000+48 image of the same pointing.
 The exposure time of each image is $\approx 10$ hours.
-Each image shows half of the total FOV ($7' \times 5'$), which contains the full sample of galaxies (indicated by the white arrows).
+Each image shows approximately half of the total FORS2 FOV ($7' \times 5'$), which contains the full sample of galaxies (indicated by the white arrows).
 East is up and North is right.
@@
 The spectral coverage of these filters is qualitatively different for the fifth galaxy in our sample (J.57).
-As shown in Figure \ref{fig:spec_images}, the \ion{Mg}{2} transitions in this galaxy are equally sampled by both of our filters.
+As shown in Figure \ref{fig:spec_images}, the \ion{Mg}{2} transitions in this galaxy are approximately equally sampled by both of our filters.
 When we subtract the continuum image from the \ion{Mg}{2} image we are effectively subtracting both \ion{Mg}{2} emission (if present) and the continuum.
@@
 This value is equal to the ratio between the FWHMs of the filter transmission curves, indicating that the spectral slope of each galaxy is approximately flat, and that the continuum level measured in the off-line filter provides an accurate measure of the continuum contribution to the on-line filter flux.
+We thus do not apply any spectral correction in the following analysis.
 
@@
 The continuum-subtracted images of each galaxy are shown in Figure \ref{fig:stamp_images}.
-The continuum-subtracted image has uniform background and no obvious signatures of emission.
+%The continuum-subtracted
+These
+images have a uniform background and no obvious signatures of emission.
 
@@
 \ref{sec.sb}.
-The colorbar shows the scaling used for the bottom row \ion{Mg}{2} images.}
+The colorbar shows the scaling used for the \ion{Mg}{2} images in the bottom row.}
 \label{fig:stamp_images}
@@
 To test for the presence of \ion{Mg}{2} emission, we perform aperture photometry on the continuum-subtracted images using the python library \emph{Photutils}.
-We choose annuli with a radial thickness of 1 pixel or $0.25 ''$, such that the inner radius is, $r_{inner}=r_{outer}-1$ (in pixels).
+We choose annuli with a radial thickness of 1 pixel or $0.25 ''$, such that the inner radius is $r_{inner}=r_{outer}-1$ (in pixels).
 Each annulus is centered on the flux-weighted centroid of the galaxy.
@@
 Top panels: Continuum SB profile (gray) measured for each galaxy.
-The red points show the Mg II + continuum SB measured for the galaxy in the pre-continuum-subtracted image.
+The red points show the Mg II + continuum SB measured for the galaxy in the pre-continuum-subtracted line image.
 The blue points show the Mg II line SB measured  in the continuum-subtracted line emission image.
@@
 In the case of perfect sky subtraction and continuum subtraction, the 1$\sigma$ SB limit for an extended source is $SB_{1}/\sqrt{A_\text{src}}$, where $A_\text{src}$ is the area in arcsec$^2$ and $SB_{1}$ is the surface brightness limit per 1 arcsec$^2$ aperture.
-However, our actual detection limits are altered by systematic error from imperfect subtraction.
+However, our actual detection limits are altered by systematic errors from imperfect subtraction.
 Therefore, we determine the limits as follows.
 We first mask all the artifacts and sources in the continuum-subtracted images.
-Next, we generate many apertures with sizes similar to our extended annulus ($\sim 20 \rm\ sq.arcsec$), place them at random, and extract the fluxes, $F_{\text{src}}$, within these apertures.
+Next, we generate many apertures with sizes similar to our extended annuli ($\sim 20 \rm\ sq.arcsec$), place them at random, and extract the fluxes, $F_{\text{src}}$, within these apertures.
 We then normalize the values of $F_{\text{src}}$ by dividing by $\sigma_{\text{src}}$, where $\sigma_{\text{src}} \equiv SB_{1}\sqrt{A_\text{src}}$.
@@
 \subsection{Test of Surface Brightness Limits}\label{subsec:test}
-To show that \ion{Mg}{2} emission with SB strengths comparable to our limits can be detected in our narrowband imaging, we simulate emission with varying intensities of SB$_{\text{limit}}$.
+To show that \ion{Mg}{2} emission with SB strengths comparable to our limits can be detected in our narrowband imaging, we simulate emission with varying intensities relative to SB$_{\text{limit}}$.
 For each galaxy, we assign our simulated emission a constant surface brightness corresponding to 1, 3, 5, 10 and 20 times the $1\sigma$ SB$_{\text{limit}}$ inside the largest annulus used (i.e., the extended annulus).
@@
 
-To aid in identifying the presence and detectability of extended \ion{Mg}{2} emission we construct a $\chi_{\text{smooth}}$ image for each level of simulated emission following the technique described in \cite{Hennawi2013} and \cite{Battaia_2015}.
+To aid in identifying the presence and detectability of extended \ion{Mg}{2} emission we construct a so-called $\chi_{\text{smooth}}$ image for each level of simulated emission following the technique described in \cite{Hennawi2013} and \cite{Battaia_2015}.
 
@@
 \end{equation}
-where the CONVOLVE$^2$ operation indicates convolution of the image with the square of the Gaussian kernel.
-The smoothed $\chi$ image, $\chi_{\text{smooth}}$, is then the product of the smoothed line image, $I_{\text{smooth}}$, divided by the sigma image, $\sigma_{\text{smooth}}$.
+where the CONVOLVE$^2$ operation indicates convolution of the image with the square of the Gaussian kernel. The smoothed $\chi$ image, $\chi_{\text{smooth}}$, is then 
+%the product of 
+the smoothed line image, $I_{\text{smooth}}$, divided by the sigma image, $\sigma_{\text{smooth}}$.
 %\begin{equation}
@@
 
-Using the above equation along with the continuum and continuum-subtracted images, we produce images of the observed-frame EW$_{\rm{MgII}}$.
-The observed-frame EW$_{\rm{MgII}}$ images are displayed for each galaxy in Figure \ref{fig:ews} and show only the EWs within the 1$\sigma$ SB$_1$ contours of the corresponding \ion{Mg}{2} images (prior to continuum subtraction).
+Using the above equation along with the continuum and continuum-subtracted images, we produce images of the observed-frame EW$_{\rm{MgII}}$. %The observed-frame EW$_{\rm{MgII}}$ images 
+They are displayed for each galaxy in Figure \ref{fig:ews} and show only the EWs within the 1$\sigma$ SB$_1$ contours of the corresponding \ion{Mg}{2} images (prior to continuum subtraction).
 
@@
 
-To compare our map of EW$_{\text{\ion{Mg}{2}}}$ to the values measured from the Keck/LRIS spectra, we place 0.9 arcsec-wide apertures over each galaxy.
+To compare our map of EW$_{\text{\ion{Mg}{2}}}$ to the values measured from the Keck/LRIS spectra, we place 0.9 arcsec-wide slit-like apertures over each galaxy.
 The width and position angle of the apertures are consistent with the orientation of the slits used to obtain the spectra.
@@
 Although some of the plots suggest a slight upward trend in the values of EW$_{\rm{MgII}}$ with increasing radii, we cannot be confident in this trend because of the large scatter.
-To better visualize the data and test the significance of the trend, we bin the data radially in 3-5 kpc-wide bins.
-For example, in Figure \ref{fig:ews}(c), the absorption EW$_{\text{\ion{Mg}{2}}}$ in J.03 extends out to $\sim$ 25 kpc (shown in black in the right-most panel).
-The EW$_{\rm{MgII}}$ values are binned in 5 kpc increments.
-We calculate the mean and scatter of the EW$_{\text{\ion{Mg}{2}}}$ in each bin and show these values in red in the right panels of Figure \ref{fig:ews} and in \ref{fig:ew_comb}.
+To better visualize the data and test the significance of the trend, we bin the data radially in bins with widths between 3 and 5 kpc.
+For example, in Figure \ref{fig:ews}(c), %the absorption
+EW$_{\text{\ion{Mg}{2}}}$ values shown for J.03 extend 
+out to $\sim$ 25 kpc (shown in black in the right-most panel).
+We bin these EW$_{\rm{MgII}}$ values in 5 kpc increments.
+We calculate the mean and scatter of the EW$_{\text{\ion{Mg}{2}}}$ in each bin and show these values in red in the right panels of Figure \ref{fig:ews} and in Figure \ref{fig:ew_comb}.
 
@@
 \subsection{Limits on \ion{Mg}{2} Emission}
-For our sample of galaxies, we are sensitive to extended emission in annuli with mean distances of 18, 18, 24 and 14 kpc from the centers of J.26, J.36, J.03 and J.64, respectively.
+For our sample of galaxies, we are sensitive to emission in our ``extended'' annuli with mean distances of 18, 18, 24 and 14 kpc from the centers of J.26, J.36, J.03 and J.64, respectively.
 %%% KHRR -- don't understand these distances
@@
 We have zeroed out any values that lie outside the SB$_1$ contours for each galaxy.
-We also impose a signal-to-noise cut, only including EW$_{\text{\ion{Mg}{2}}}$ values in the middle and right panels for pixels in which the continuum S/N is greater than $1.5$.
-The mean EW$_{\text{\ion{Mg}{2}}}$ is computed for all pixels inside each Keck/LRIS aperture, defined in Sec.
-\ref{subsec.ew}, and the error is propagated in quadrature.
-The resulting values of the mean EW and the error of the measurements are summarized in Table \ref{tab:abs_props}.
+We also impose a signal-to-noise cut, only including EW$_{\text{\ion{Mg}{2}}}$ values in the middle and right panels for pixels in which the continuum S/N is greater than $1.5$ and which are inside each Keck/LRIS aperture, defined in Sec.
+\ref{subsec.ew}.
+The mean EW$_{\text{\ion{Mg}{2}}}$ is computed for all pixels inside these apertures %each Keck/LRIS aperture, defined in Sec. \ref{subsec.ew}, 
+and the error is propagated in quadrature.
+The resulting values of the mean EW and the error in these measurements are summarized in Table \ref{tab:abs_props}.
 Comparing our narrowband EWs with those measured from the spectra, we find agreement to within  1.6-4.6$\sigma$ for galaxies J.26 and J.36, and more statistically significant differences for galaxies J.03 and J.64.
@@
 it may well be that our choice of continuum level in calculating the EW$_{\text{\ion{Mg}{2}}}$ from the spectrum is higher than the continuum level implied by our narrow-band image.
+Such a systematic error could give rise to a higher spectroscopic EW.
 
@@
 
-As demonstrated in our radially-binned EW profiles, a majority of the galaxies exhibit large scatter in the binned EW$_{\text{\ion{Mg}{2}}}$ at large radii.
-To better understand the significance of these trends, we compile the mean EW$_{\text{\ion{Mg}{2}}}$ values for all the galaxies and show their profiles in Figure \ref{fig:ew_comb}.
+As demonstrated in %our radially-binned EW profiles, 
+the right panels of Figure \ref{fig:ews}, 
+a majority of the galaxies exhibit large scatter in %the binned 
+EW$_{\text{\ion{Mg}{2}}}$ at large radii. To better understand the significance of any possible trends in these values, %these trends, 
+we compile the mean EW$_{\text{\ion{Mg}{2}}}$ values for all the galaxies and show their profiles in Figure \ref{fig:ew_comb}.
 To account for the varying sizes of the galaxies, we normalize the radii of the bins by the approximate radius of the SB$_1$ contour for each galaxy.
-Upon inspection of this figure, we see that the galaxies exhibit no statistically significant trend in the mean absorption EW$_{\rm MgII}$ as a function of radius inside our 1SB$_1$ isophotal contour, which suggests that the covering fraction is approximately constant across the surface.
+Upon inspection of this figure, we see that the galaxies exhibit no statistically significant trend in the mean absorption EW$_{\rm MgII}$ as a function of radius inside our 1SB$_1$ isophotal contour, which suggests that the covering fraction
+of saturated \ion{Mg}{2} absorption
+is approximately constant across the surface.
 
@@
 \caption{Radial profile of the mean EW of \ion{Mg}{2} absorption for four of our sample galaxies.
-Profiles for J.26,  J.36,  J.03, and J.64 are shown with blue points, green squares, red circles, and cyan stars, respectively.
+Profiles for J.26,  J.36,  J.03, and J.64 are shown with small blue circles, green squares, large red circles, and cyan stars, respectively.
 The mean EW values are the same as those shown in the right column of Figure \ref{fig:ews}.
@@
 Excepting galaxy J.03, the predicted SB of this emission lies above our detection limits.
-Under the assumption that the wind in these galaxies does in fact extend beyond the $\rm SB_1$ isophotal contour (at $R_{\perp}^{\rm{SB}_1} = 8-21$ kpc), the absence of the predicted emission, calculated from an isotropic wind model, in our narrowband imaging suggests that these galaxies do not host isotropic, dust-free winds.
+Under the assumption that the wind in these galaxies does in fact extend beyond the $\rm SB_1$ isophotal contour (at $R_{\perp}^{\rm{SB}_1} = 8-21$ kpc), the absence of the predicted emission %, calculated for an isotropic wind,
+in our narrowband imaging suggests that these galaxies do not host isotropic, dust-free winds.
 
@@
 We compared our surface brightness detection limits with the predictions of the radiative transfer models of \cite{Prochaska_2011}.
-If the winds in these galaxies do extend beyond the stellar disk, $\lesssim 20$ kpc, then we are able to rule out that the winds in our sample are isotropic and dust free, as our images are sufficiently sensitive to detect the emission predicted by such models.
+If the winds in these galaxies do extend beyond the stellar disk, to $\gtrsim 20$ kpc, then we are able to rule out that the winds in our sample are isotropic and dust free, as our images are sufficiently sensitive to detect the emission predicted by such models.
 Adopting the assumption of dusty and/or anisotropic winds reduces the strength of the predicted \ion{Mg}{2} emission to lie below our detection limits.
-Although these limits suggest that the winds in our sample are not isotropic and dust-free, questions linger regarding the relative roles wind anisotropy, dust content, and extent play in reducing scattered emission.
+Although these limits may suggest that the winds in our sample are not isotropic and dust-free, questions linger regarding the relative roles wind anisotropy, dust content, and extent play in reducing scattered emission.
 Thus, deeper imaging or spatially-resolved spectroscopy of \ion{Mg}{2} will be needed to fully characterize the morphology of these winds.
@@
 \acknowledgements
-R.R.V gratefully thanks Joe Burchett, Karin Sandstrom and Jessica Werk for enlightening discussions which improved this work.
+R.R.V. gratefully thanks Joe Burchett, Karin Sandstrom and Jessica Werk for enlightening discussions which improved this work.
 K.H.R.R.

### 2019-02-20 for_submission/rvaught_2018.tex
02/19/2018

@@
 \author{Ryan Rickards Vaught}
+\affiliation{Department of Physics, University of California, San Diego, 9500 Gilman Dr., La Jolla, CA 92093, USA}
 \affiliation{Department of Astronomy, San Diego State University, San Diego, CA 92182, USA}
-\affiliation{Department of Physics, University of California, San Diego, 9500 Gilman Dr., La Jolla, CA 92093, USA}
 
@@
 These observations are uniquely sensitive, reaching surface brightness limits of 5.81 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ per 1 arcsec$^2$ aperture (at 5$\sigma$ significance).
-We do not detect any extended emission around any of the sample galaxies, thus placing  upper limits on the brightness of extended \ion{Mg}{2} emission of $<6.51 \times 10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ at projected distances $R_{\perp} > 8-21$ kpc.
+We do not detect any extended emission around any of the sample galaxies, thus placing 5$\sigma$ upper limits on the brightness of extended \ion{Mg}{2} emission of $<6.51 \times 10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ at projected distances $R_{\perp} > 8-21$ kpc.
 The imaging also resolves the \ion{Mg}{2} absorption observed toward each galaxy spatially, revealing approximately constant absorption strengths across the galaxy disks.
@@
 
-The absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2}  with velocities $\sim150-420\mkms$ and equivalent widths (EW) $\sim 2-3$ \AA.
+The absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2}  with velocities $\sim150-420\mkms$ and \textbf{rest-frame} equivalent widths (EW) $\sim 2-3$ \AA.
 Modeling of the galaxy broad-band spectral energy distributions (SEDs) obtained from multi-wavelength ancillary imaging data yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$.
@@
 \centering
-\includegraphics[scale=.75]{fors2_color_imstamps.pdf}
+\includegraphics[scale=.75]{figure1.pdf}%fors2_color_imstamps.pdf%%
 \caption{Color imaging of our sample galaxies in the \emph{HST}/ACS F435W, F606W, and F775W filters obtained as part of the GOODS survey (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004}).
@@
 \centering
-\gridline{\fig{filt_26_spectra.pdf}{0.5\textwidth}{}
-          \fig{filt_36_spectra.pdf}{0.5\textwidth}{}}
-\gridline{\fig{filt_03_spectra.pdf}{0.5\textwidth}{}
-          \fig{filt_64_spectra.pdf}{0.5\textwidth}{}}
-           \fig{filt_57_spectra.pdf}{0.5\textwidth}{}
+\gridline{\fig{figure2a.pdf}{0.5\textwidth}{}
+          \fig{figure2b.pdf}{0.5\textwidth}{}}
+\gridline{\fig{figure2c.pdf}{0.5\textwidth}{}
+          \fig{figure2d.pdf}{0.5\textwidth}{}}
+         \fig{figure2e.pdf}{0.5\textwidth}{}
 \caption{Keck/LRIS spectra of the sample galaxies and the transmission curves of the filters HeII+47 (blue dashed line) and HeII/3000+48 (red dashed line).
@@
 \centering
-\includegraphics[scale=.55]{avg_seeing_HEII.pdf}
-\includegraphics[scale=.55]{avg_seeing_HEII3000.pdf}
+\includegraphics[scale=.55]{figure3a.pdf}
+\includegraphics[scale=.55]{figure3b.pdf}
 \caption{\emph{Top}: Distribution of seeing measurements for the 38 HeII+47 images.
@@
 Then the images were bias-subtracted and flat-fielded using twilight flats.
-%%% KHRR -- adjusting the following to be different from FAB's words
-%To improve the flat-fielding essential for detecting faint extended emission across the %fields, we further correct for the illumination patterns using night-sky flats.
-The %night-sky flats were produced by combining the unregistered science frames with an %average sigma-clipping algorithm after masking out all the objects, and any bad pixels.
-%%%
 An additional flat-fielding correction was performed using night-sky flats to improve our sensitivity to faint extended emission.
@@
 determined from analysis of the supplemental Keck/LRIS spectra. \label{tab:prop}}
-\tablehead{\colhead{Object} & \colhead{R.A.} & \colhead{Dec} & \colhead{$z$} & \multicolumn2c{$\log$(SFR)} & \multicolumn2c{$\log{(M)}$} & \colhead{EW$_{\rm{obs}}$} & \multicolumn2c{ $\tau_V$} \\ 
-\colhead {} & \colhead {} & \colhead {} & \colhead{} & \multicolumn2c{($\log M_{\odot}$ yr$^{-1}$)} & \multicolumn2c{($\log{M_{*}/M_{\odot}}$)} & \colhead{(\AA)} & \multicolumn2c{}}
+\tablehead{\colhead{Object} & \colhead{R.A.} & \colhead{Dec} & \colhead{$z$} & \multicolumn2c{SFR} & \multicolumn2c{$\log{(M)}$} & \colhead{EW$_{\rm{obs}}$} & \multicolumn2c{ $\tau_V$} \\ 
+\colhead {} & \colhead {} & \colhead {} & \colhead{} & \multicolumn2c{($M_{\odot}$ yr$^{-1}$)} & \multicolumn2c{($\log{M_{*}/M_{\odot}}$)} & \colhead{(\AA)} & \multicolumn2c{}}
 \decimals
 \startdata
-J033225.26-274524.0 (J.26)     & 03:32:25.26 & -27:45:23.9  &   0.6660  & $9.1_{-3.7}^{+1.3}$     & $9.86_{-0.04}^{+0.05}$   & \ $7.539\pm 0.354$   &  $1.227_{-0.20}^{+1.54}$ \\ 
-J033231.36-274725.0 (J.36)     & 03:32:31.35 & -27:47:24.9  &   0.6669  & $10.5_{-1.6}^{+1.7}$   & $10.02_{-0.03}^{+0.03}$ & \ $5.835 \pm 0.493$   & $1.377_{-0.23}^{+0.60}$ \\
-J033230.03-274347.3 (J.03)     & 03:32:30.03 & -27:43:47.2  &   0.6679  & $3.8_{-0}^{+0}$           & $10.98_{-0.0}^{+0.01}$   & $12.794 \pm 1.710$ & $0.297_{-0.0}^{+0.0}$ \\
-J033229.64-274242.6 (J.64)     & 03:32:29.64 & -27:42:42.5  &   0.6671  & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ & $13.239 \pm 0.263$ & $3.897_{-0.93}^{+1.15}$ \\
-J033230.57-274518.2 (J.57)     & 03:32:30.56 & -27:45:18.2  &   0.6807  & $12.6_{-2.1}^{+1.7}$   & $10.48_{-0.07}^{+0.03}$ & \ $6.106 \pm 0.370$   & $1.262_{-0.40}^{+1.23}$ \\
+J033225.26-274524.0 (J.26)     & 03:32:25.26 & -27:45:23.9  &   0.6660  & $9.1_{-3.7}^{+1.3}$     & $9.86_{-0.04}^{+0.05}$   & \ $7.5\pm 0.4$   &  $1.227_{-0.20}^{+1.54}$ \\ 
+J033231.36-274725.0 (J.36)     & 03:32:31.35 & -27:47:24.9  &   0.6669  & $10.5_{-1.6}^{+1.7}$   & $10.02_{-0.03}^{+0.03}$ & \ $5.8 \pm 0.5$   & $1.377_{-0.23}^{+0.60}$ \\
+J033230.03-274347.3 (J.03)     & 03:32:30.03 & -27:43:47.2  &   0.6679  & $3.8_{-0}^{+0}$           & $10.98_{-0.0}^{+0.01}$   & $12.8 \pm 1.7$ & $0.297_{-0.0}^{+0.0}$ \\
+J033229.64-274242.6 (J.64)     & 03:32:29.64 & -27:42:42.5  &   0.6671  & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ & $13.2 \pm 0.3$ & $3.897_{-0.93}^{+1.15}$ \\
+J033230.57-274518.2 (J.57)     & 03:32:30.56 & -27:45:18.2  &   0.6807  & $12.6_{-2.1}^{+1.7}$   & $10.48_{-0.07}^{+0.03}$ & \ $6.1 \pm 0.4$   & $1.262_{-0.40}^{+1.23}$ \\
 \enddata
-\tablecomments{The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SEDs with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}.}
+\tablecomments{The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ i.e.
+\textbf{dust opacity of the galaxy}, values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SEDs with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}.}
 \end{deluxetable*}
@@
 \tablenotetext{a}{$ \lambda_{\rm{eff}}$ is the effective wavelength of the filter transmission curve.}
-\tablenotetext{b}{FWHM of the filter.}
+\tablenotetext{b}{The effective width of the filter.}
 \tablenotetext{c}{Total number of images.}
@@
 \centering
-\includegraphics[scale=.61]{HEII_final.png}
-\includegraphics[scale=.61]{HEII3000_final.png}
+\includegraphics[scale=.61]{figure4a.pdf}
+\includegraphics[scale=.61]{figure4b.pdf}
 \caption{\emph{Top:} Stacked HeII+47 image of the galaxy sample.
@@
 Comparing these ratios between each galaxy, we find that they are equivalent to within 0.1\%, with a value of 1.118.
-This value is equal to the ratio between the FWHMs of the filter transmission curves, indicating that the spectral slope of each galaxy is approximately flat, and that the continuum level measured in the off-line filter provides an accurate measure of the continuum contribution to the on-line filter flux.
+This value is equal to the ratio between the effective widths of the filter transmission curves, indicating that the spectral slope of each galaxy is approximately flat, and that the continuum level measured in the off-line filter provides an accurate measure of the continuum contribution to the on-line filter flux.
 We thus do not apply any spectral correction in the following analysis.
@@
 \end{equation}\\
-where $F_{\rm{cont}}$ and $\Delta \lambda_{\rm{cont}}$ are the observed flux per pixel of the continuum image and the transmission FWHM of the continuum filter, respectively.
+where $F_{\rm{cont}}$ and $\Delta \lambda_{\rm{cont}}$ are the observed flux per pixel of the continuum image and the effective width of the continuum filter, respectively.
 With $f_{\rm cont}$ it is then possible to calculate the flux of any excess emission, $F_{\rm{line}}$:
@@
 \end{equation}
-where $F_{\rm{MgII}}$ and $\Delta \lambda_{\rm MgII}$ are the observed flux per pixel in the \ion{Mg}{2} filter and the transmission FWHM of the \ion{Mg}{2} filter.
+where $F_{\rm{MgII}}$ and $\Delta \lambda_{\rm MgII}$ are the observed flux per pixel in the \ion{Mg}{2} filter and the effective width of the \ion{Mg}{2} filter.
 The continuum-subtracted images of each galaxy are shown in Figure \ref{fig:stamp_images}.
@@
 \centering
-\includegraphics[scale=0.7]{stamps.pdf}
+\includegraphics[scale=0.7]{figure5.pdf}%stamps.pdf
 \caption{ $10'' \times 10''$ (or about $70 \rm \ kpc \times 70 \rm \ kpc $) images of each galaxy in our sample.
@@
 \centering
-\gridline{\fig{J_26.pdf}{0.5\textwidth}{}
-          \fig{J_36.pdf}{0.5\textwidth}{}}
-\gridline{\fig{J_03.pdf}{0.5\textwidth}{}
-          \fig{J_64.pdf}{0.5\textwidth}{}}
-           \fig{J_57.pdf}{0.5\textwidth}{}
+\gridline{\fig{figure6a.pdf}{0.5\textwidth}{}
+          \fig{figure6b.pdf}{0.5\textwidth}{}}
+\gridline{\fig{figure6c.pdf}{0.5\textwidth}{}
+          \fig{figure6d.pdf}{0.5\textwidth}{}}
+           \fig{figure6e.pdf}{0.5\textwidth}{}
 \caption{SB profiles for our sample galaxies.
@@
 Bottom panel: The vertical hashes show the inner and outer radii of each annulus in kpc.
-The distance from the center of the galaxy is marked with filled squares and is computed using the average value of the inner and outer radii of each annulus.}
+The distance from the center of the galaxy is marked with filled squares and is computed using the average value of the inner and outer radii of each annulus.
+The annuli with the largest radial distance from the galaxy are used to measure extended SBs.}
 \label{fig:sb_profiles}
@@
 We then normalize the values of $F_{\text{src}}$ by dividing by $\sigma_{\text{src}}$, where $\sigma_{\text{src}} \equiv SB_{1}\sqrt{A_\text{src}}$.
-For perfect sky subtraction and continuum subtraction, the distribution of extracted fluxes should follow a Gaussian distribution with a variance equal to $\sigma_{\text{src}}$.
+For perfect sky subtraction and continuum subtraction, the distribution of extracted fluxes should follow a Gaussian distribution with a standard deviation equal to $\sigma_{\text{src}}$.
 The distribution of $F_{\text{src}}/\sigma_{\text{src}}$ for these apertures is shown in Figure \ref{fig:limits}
 
-We calculate the variance and mean of the distribution and find that the variance of the distribution is $\sigma'_{\text{src}}=1.1$, implying that the SB detection limit for our continuum-subtracted image is higher than $\sigma_{\text{src}}$ by a factor of 10\%.
+We calculate the standard deviation and mean of the distribution and find that the variance of the distribution is $\sigma'_{\text{src}}=1.1$, implying that the SB detection limit for our continuum-subtracted image is higher than $\sigma_{\text{src}}$ by a factor of 10\%.
 We adopt $F_{\text{limit}} \equiv \sigma'_{\text{src}}$  as the $1 \sigma$ upper limit on the total line flux of extended \ion{Mg}{2} emission.
@@
 \centering
-\includegraphics[scale=0.6]{hist_sblim.pdf}
+\includegraphics[scale=0.6]{figure7.pdf}%hist_sblim
 \caption{Normalized distribution of $F_{\text{src}}/\sigma_{\text{src}}$ values for random circular annuli placed on the continuum-subtracted line image.
 $F_{\text{src}}$ is the total flux within an aperture and $\sigma_{\text{src}}$ is the expected $1\sigma$ flux limit in the ideal case of perfect sky and continuum subtraction, i.e $SB_{1}\sqrt{A_\text{src}}$.
+The red line is a Gaussian fit to this normalized distribution with standard deviation, $\sigma=1.112$, and mean, $\mu=-0.441$.
 The black arrows point to the statistical significance of the flux inside the ``extended annulus'' of each galaxy.}
@@
 \centering
-\includegraphics[scale=1.2]{sigmas.pdf}
+\includegraphics[scale=1.2]{figure8.pdf}%sigmas.pdf
 \caption{Continuum-subtracted $\chi_{\text{smooth}}$ images of the 5 galaxies in our sample.
@@
 \end{equation}
-we begin by dividing Eq \ref{eq:subtraction} by the flux density of the continuum and the FWHM of the on-line filter,
+we begin by dividing Eq \ref{eq:subtraction} by the flux density of the continuum and the effective width of the on-line filter,
 \begin{equation}
-\frac{F_{\lambda}}{f_{\rm{cont}}\Delta \lambda_{\rm{MgII}}}=\frac{F_{\rm{MgII}}}{f_{\rm{cont}}\Delta \lambda_{\rm{MgII}}}- 1.
+\frac{F_{\rm{line}}}{f_{\rm{cont}}\Delta \lambda_{\rm{MgII}}}=\frac{F_{\rm{MgII}}}{f_{\rm{cont}}\Delta \lambda_{\rm{MgII}}}- 1.
 \end{equation}
@@
 \begin{equation}
--\frac{F_{\lambda}}{f_{\rm{cont}}\Delta \lambda_{\rm{MgII}}}=1-\frac{f_{\rm{MgII}}}{f_{\rm{cont}}}.
+-\frac{F_{\rm{line}}}{f_{\rm{cont}}\Delta \lambda_{\rm{MgII}}}=1-\frac{f_{\rm{MgII}}}{f_{\rm{cont}}}.
 \end{equation}
-We then approximate the integration in Eq. \ref{eq:specEW} by multiplying the integrand above by the FWHM of the on-line filter $d\lambda=\Delta \lambda_{\rm{MgII}},$
+We then approximate the integration in Eq. \ref{eq:specEW} by multiplying the integrand above by the effective width of the on-line filter $d\lambda=\Delta \lambda_{\rm{MgII}},$
 \begin{equation}
--\frac{F_{\lambda}}{f_{\rm{cont}}}=(1-\frac{f_{\rm{MgII}}}{f_{\rm{cont}}})\Delta \lambda_{\rm{MgII}};
+-\frac{F_{\rm{line}}}{f_{\rm{cont}}}=(1-\frac{f_{\rm{MgII}}}{f_{\rm{cont}}})\Delta \lambda_{\rm{MgII}};
 \end{equation}
@@
 \begin{equation}
-{\rm EW}_{\rm{MgII}}=-\frac{F_{\rm{MgII}}}{f_{\rm{cont}}}.
+{\rm EW}_{\rm{MgII}}=-\frac{F_{\rm{line}}}{f_{\rm{cont}}}.
 \end{equation}
@@
 \centering
-\gridline{\fig{J26EW.pdf}{0.8\textwidth}{(a: J.26)}}
- \gridline{\fig{J36EW.pdf}{0.8\textwidth}{(b: J.36)}}
-\gridline{\fig{J03EW.pdf}{0.8\textwidth}{(c: J.03)}}
- \gridline{\fig{J64EW.pdf}{0.8\textwidth}{(d: J.64)}}
+\gridline{\fig{figure9a.pdf}{0.8\textwidth}{(a: J.26)}}
+ \gridline{\fig{figure9b.pdf}{0.8\textwidth}{(b: J.36)}}
+\gridline{\fig{figure9c.pdf}{0.8\textwidth}{(c: J.03)}}
+ \gridline{\fig{figure9d.pdf}{0.8\textwidth}{(d: J.64)}}
 \caption{Left: Images of the equivalent widths EW$_{\text{\ion{Mg}{2}}}$ inside the 1SB$_1$ contour for each galaxy (red).
@@
 \centering
-\includegraphics[scale=0.7]{ew_comb.pdf}
+\includegraphics[scale=0.7]{figure10.pdf}%ew_comb.pdf
 \caption{Radial profile of the mean EW of \ion{Mg}{2} absorption for four of our sample galaxies.
@@
 \centering
-\includegraphics[scale=0.57]{all_limitsv2.pdf}
-\caption{Comparison of our detection limits to the measured SB of extended \ion{Mg}{2} emission around the starburst galaxy TKRS 4389.
-%The left panel shows these surface brightnesses vs.\ SFR; the middle panel shows the same measurements vs.\ ste
-%compares the SB with each galaxies total stellar mass. The right panel compares the SB with sSFR.  
+\includegraphics[scale=0.57]{figure11.pdf}%all_limitsv2.pdf
+\caption{Comparison of our detection limits to the SB, measured in two independent locations spatially offset from the galaxy continuum, of extended \ion{Mg}{2} emission around the starburst galaxy TKRS 4389.
 These surface brightness constraints are plotted vs.\ SFR (left), stellar mass (middle), and specific SFR (right).
@@
 \centering
-\gridline{\fig{geo_J26.pdf}{0.5\textwidth}{(a)}
-          \fig{geo_J36.pdf}{0.5\textwidth}{(b)}}
-\gridline{\fig{geo_J03.pdf}{0.5\textwidth}{(c)}
-          \fig{geo_J64.pdf}{0.5\textwidth}{(d)}}
+\gridline{\fig{figure12a.pdf}{0.5\textwidth}{(a)}
+          \fig{figure12b.pdf}{0.5\textwidth}{(b)}}
+\gridline{\fig{figure12c.pdf}{0.5\textwidth}{(c)}
+          \fig{figure12d.pdf}{0.5\textwidth}{(d)}}
 \caption{Predicted SB of \ion{Mg}{2} emission for isotropic, anisotropic, and both anisotropic and dusty winds.

### 2019-03-01 for_submission/rvaught_2018.tex
02/28/2018

@@
 
-The absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2}  with velocities $\sim150-420\mkms$ and \textbf{rest-frame} equivalent widths (EW) $\sim 2-3$ \AA.
+The \textbf{Bayesian} absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2}  with velocities $\sim150-420\mkms$ and \textbf{rest-frame} equivalent widths (EW) $\sim 2-3$ \AA.
+\textbf{Due to the photon scattering process described in Section \ref{sec:intro}, it is possible that scattered emission can fill in the deepest parts of the absorption line near systemic velocity and shift the trough of the line blueward.
+To mitigate the effects of any scattered emission, \cite{Rubin_2014} implement a two velocity component ``flow" model in tandem with a single ``fixed-velocity", with respect to the central wavelength of \ion{Mg}{2}, model to quantify the absorption line kinematics.
+The qualitative conetext of this scattering process, as it pertains to galactic winds, can be improved via higher resolution spectrum and radiative transfer analysis \cite{Prochaska_2011}}.
 Modeling of the galaxy broad-band spectral energy distributions (SEDs) obtained from multi-wavelength ancillary imaging data yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$.
@@
 \section{Discussion}\label{sec:discussion}
-\subsection{Previous Detections of Extended \ion{Mg}{2} Emission}
+\subsection{Previous Detection of extended \ion{Mg}{2} Emission}
 Previous constraints on the brightness of scattered \ion{Mg}{2} emission were reported by \cite{Rubin_2011}.
@@
 The flux from both emission lines can be converted into two surface brightness values by taking the average of the flux measured at each location and each transition, and dividing by a 1 arcsec$^2$ aperture.
-
 Figure \ref{fig:all_limits} shows each galaxy's 5$\sigma$ SB detection limit and the SB calculated for the galaxy TKRS 4389 vs.
@@
 Future observations are needed to verify this trend, and the possibility that objects with yet higher SFRs ($\gtrsim50 \msunperyr$) exhibit brighter \ion{Mg}{2} emission.
-The middle panel of Figure \ref{fig:all_limits} suggests that extended \ion{Mg}{2} emission may be brighter in lower mass galaxies.
-Both \cite{Erb2012} and \cite{Feltre2018} observed a similar trend in their examination of the total \ion{Mg}{2} emission strength vs.
+
+\subsection{Strength of \ion{Mg}{2} emission and Correlation with Galaxy Properties }
+\textbf{The middle panel of Figure \ref{fig:all_limits} suggests that extended \ion{Mg}{2} emission may be brighter in lower mass galaxies.
+A similar trend was observed by both \cite{Erb2012} and \cite{Feltre2018} in their examination of the total \ion{Mg}{2} emission strength vs.
 galaxy $M_*$.
-%The trends in SFR and mass can be combined to show each galaxies SB vs the specific SFR, shown in the right panel of \ref{fig:all_limits}.
+IN addition to the observed trend that emission strength may be correlated with galaxy mass, a recent study by \cite{Henry2018} detected significant \ion{Mg}{2} emission, characterized with escape fractions between $0-0.9$, in a sample of $z \sim 0.2-0.3$ Green Pea galaxies.
+Finally, the right panel of Figure \ref{fig:all_limits} shows that the galaxy with detected \ion{Mg}{2} also has the highest specific SFR.
+If it is ultimately confirmed that low-$M_*$ galaxies with the highest SFRs, or highest specific SFRs, exhibit the brightest emission, this could point to a physical link between the escape velocity of galaxies and the spatial extent of wind material}
+
+%Both \cite{Erb2012} and \cite{Feltre2018} observed a similar trend in their examination of the total \ion{Mg}{2} emission strength vs.
+galaxy $M_*$.
 Finally, the right panel of Figure \ref{fig:all_limits}
-shows that the galaxy with detected \ion{Mg}{2} also has the highest specific SFR.
+%shows that the galaxy with detected \ion{Mg}{2} also has the highest specific SFR.
 If it is ultimately confirmed that low-$M_*$ galaxies with the highest SFRs, or highest specific SFRs, exhibit the brightest emission, this could point to a physical link between the escape velocity of galaxies and the spatial extent of wind material.

### 2019-03-01 for_submission/rvaught_2018.tex
02/28/2018

@@
 The \textbf{Bayesian} absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2}  with velocities $\sim150-420\mkms$ and \textbf{rest-frame} equivalent widths (EW) $\sim 2-3$ \AA.
-\textbf{Due to the photon scattering process described in Section \ref{sec:intro}, it is possible that scattered emission can fill in the deepest parts of the absorption line near systemic velocity and shift the trough of the line blueward.
+\textbf{Due to the photon scattering process described in Section \ref{sec:intro}, it is possible that scattered emission can fill in the deepest parts of the absorption line near systemic velocity and shift the valley of the line blueward.
 To mitigate the effects of any scattered emission, \cite{Rubin_2014} implement a two velocity component ``flow" model in tandem with a single ``fixed-velocity", with respect to the central wavelength of \ion{Mg}{2}, model to quantify the absorption line kinematics.
@@
 galaxy $M_*$.
-IN addition to the observed trend that emission strength may be correlated with galaxy mass, a recent study by \cite{Henry2018} detected significant \ion{Mg}{2} emission, characterized with escape fractions between $0-0.9$, in a sample of $z \sim 0.2-0.3$ Green Pea galaxies.
+In addition to the observed trend that emission strength may be correlated with galaxy mass, a recent study by \cite{Henry2018} showed significant \ion{Mg}{2} emission, characterized with escape fractions between $0-0.9$, in a sample of $z \sim 0.2-0.3$ Green Pea galaxies.
+Photoionization modeling of the observed strength of emission suggests that a secondary source of \ion{Mg}{2} emission is nebular emission from HII regions.
 Finally, the right panel of Figure \ref{fig:all_limits} shows that the galaxy with detected \ion{Mg}{2} also has the highest specific SFR.

### 2019-03-01 for_submission/rvaught_2018.tex
03/01/2018

@@
 \textbf{Due to the photon scattering process described in Section \ref{sec:intro}, it is possible that scattered emission can fill in the deepest parts of the absorption line near systemic velocity and shift the valley of the line blueward.
-To mitigate the effects of any scattered emission, \cite{Rubin_2014} implement a two velocity component ``flow" model in tandem with a single ``fixed-velocity", with respect to the central wavelength of \ion{Mg}{2}, model to quantify the absorption line kinematics.
+To mitigate the effects of any scattered emission, \cite{Rubin_2014} implement two models in their absorption line modeling.
+First, the absorption line is fit with a single velocity component, centered on the central wavelength of the transition, secondly a two velocity component or ``flow model" is implemented that assumes the absorption line is comprised of two velocities instead of one.
 The qualitative conetext of this scattering process, as it pertains to galactic winds, can be improved via higher resolution spectrum and radiative transfer analysis \cite{Prochaska_2011}}.
@@
 In addition to the observed trend that emission strength may be correlated with galaxy mass, a recent study by \cite{Henry2018} showed significant \ion{Mg}{2} emission, characterized with escape fractions between $0-0.9$, in a sample of $z \sim 0.2-0.3$ Green Pea galaxies.
-Photoionization modeling of the observed strength of emission suggests that a secondary source of \ion{Mg}{2} emission is nebular emission from HII regions.
+Photoionization modeling of the observed strength of emission suggests that in addition to scattering of continuum photons, HII regions may also produce a non-negligible contribution to observed \ion{Mg}{2} emission.
 Finally, the right panel of Figure \ref{fig:all_limits} shows that the galaxy with detected \ion{Mg}{2} also has the highest specific SFR.

### 2019-03-07 referee_response.txt
03/06/2018

Dear Anonymous Referee,

Thank you so much for your kind words and comments on the manuscript "A VLT/FORS2 Narrowband
Imaging Search for MgII Emission in z~0.70 Galaxies". Below is a list of your comments and
our edits according to these comments.

Comment:"In the last paragraph of Section 2.1 a little more information about the absorption lines would be helpful. 
The velocities are quoted as ~150-420 km/s -- is this measured from the centroids of the lines? 
As the authors know, the velocity of MgII can be significantly affected by infilling from emission, so a bit 
more detail on where these numbers come from and how to interpret them would be useful. 
It would also be helpful to note that the equivalent widths given here are in the rest frame, since 
they are discussed in the observed frame in most of the rest of the paper."

Reply: We expanded the last paragraph to include a refined description of the velocities being reported. We 
added the velocity reported for each galaxy in Table 1. Additionally, we discussed what type of model is being used
to measure the lines and how these mitigate the effect of infilling emission. We also note that the EW's mentioned
here are the rest-frame equivalent widths.

Comment: Please add a note to Table 1 explaining what tau_V is, since it isn't discussed until later in the paper
and it is a bit less obvious than the other quantities in the table.

Reply: We added a note to Table 1 which gives more insight to tau_V.

Comment:In the discussion of previous results in Section 6.1, I think providing some context from Henry et al 2018 would
be useful. Although this paper didn't present spatially extended emission, their results on which galaxies are 
likely to have strong MgII emission is relevant, in particular the finding that nebular emission is important as 
well as resonantly scattered continuum photons, and the finding that the strength of the emission may be set by the 
escape fraction of MgII photons rather than the intrinsic production.

Reply: Added a discussion of Henry et al 2016 and Guseva et al.(2019).

### 2019-03-07 for_submission/rvaught_2018.tex
03/06/2018

--- 2019-03-01 for_submission/rvaught_2018.tex
@@
-\documentclass[twocolumn]{aastex62}
+%\documentclass[twocolumn]{aastex62}
+\documentclass[trackchanges,twocolumn]{aastex62}
 \usepackage{natbib}
@@
 
-The \textbf{Bayesian} absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2}  with velocities $\sim150-420\mkms$ and \textbf{rest-frame} equivalent widths (EW) $\sim 2-3$ \AA.
-\textbf{Due to the photon scattering process described in Section \ref{sec:intro}, it is possible that scattered emission can fill in the deepest parts of the absorption line near systemic velocity and shift the trough of the line blueward.
-To mitigate the effects of any scattered emission, \cite{Rubin_2014} implement a two velocity component ``flow" model in tandem with a single ``fixed-velocity", with respect to the central wavelength of \ion{Mg}{2}, model to quantify the absorption line kinematics.
-The qualitative conetext of this scattering process, as it pertains to galactic winds, can be improved via higher resolution spectrum and radiative transfer analysis \cite{Prochaska_2011}}.
+The \added{Bayesian} absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2} with \added{maximum outflow} velocities, $\Delta v_{\rm max}$ $\sim150-420\mkms$ and \textbf{rest-frame} equivalent widths (EW) $\sim 2-3$ \AA.
+\added{The reported maximum outflow velocities, see Table \ref{tab:prop}, are the result of fitting a two-velocity component model to the absorption line profile.
+The two component model assumes that there is a systemic velocity and ``flow" velocity that both contribute to the overall line profile.
+The maximum outflow velocity is the velocity of the flow, $v_{\rm flow}$ minus a fitted doppler parameter, $b_{D,\rm flow}/\sqrt{2}$.
+The use of the two component model is helpful to mitigate the effects of scattered emission filling up the absorption line which in turn pushes the trough of the line blueward.
+It is assumed that the resonant emission will reduce the systemic velocity, leaving the flow velocity to characterize the outflow.
+The qualitative context of this scattering process, as it pertains to galactic winds, can be improved via higher resolution spectrum and radiative transfer analysis \cite{Prochaska_2011}}.
 Modeling of the galaxy broad-band spectral energy distributions (SEDs) obtained from multi-wavelength ancillary imaging data yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$.
@@
 
-\begin{deluxetable*}{c c c c D D c D}
+%\begin{deluxetable*}{c c c c D D c D}
+%\tablecaption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) includes both components of the \ion{Mg}{2} doublet and is 
+%determined from analysis of the supplemental Keck/LRIS spectra. \label{tab:prop}}
+%\tablehead{\colhead{Object} & \colhead{R.A.} & \colhead{Dec} & \colhead{$z$} & \multicolumn2c{SFR} & \multicolumn2c{$\log{(M)}$} & \colhead{EW$_{\rm{obs}}$} & \multicolumn2c{ $\tau_V$} \\ 
+%\colhead {} & \colhead {} & \colhead {} & \colhead{} & \multicolumn2c{($M_{\odot}$ yr$^{-1}$)} & \multicolumn2c{($\log{M_{*}/M_{\odot}}$)} & \colhead{(\AA)} & \multicolumn2c{}}
+%\decimals
+%\startdata
+%J033225.26-274524.0 (J.26)     & 03:32:25.26 & -27:45:23.9  &   0.6660  & $9.1_{-3.7}^{+1.3}$     & $9.86_{-0.04}^{+0.05}$   & \ $7.5\pm 0.4$   &  $1.227_{-0.20}^{+1.54}$ \\ 
+%J033231.36-274725.0 (J.36)     & 03:32:31.35 & -27:47:24.9  &   0.6669  & $10.5_{-1.6}^{+1.7}$   & $10.02_{-0.03}^{+0.03}$ & \ $5.8 \pm 0.5$   & $1.377_{-0.23}^{+0.60}$ \\
+%J033230.03-274347.3 (J.03)     & 03:32:30.03 & -27:43:47.2  &   0.6679  & $3.8_{-0}^{+0}$           & $10.98_{-0.0}^{+0.01}$   & $12.8 \pm 1.7$ & $0.297_{-0.0}^{+0.0}$ \\
+%J033229.64-274242.6 (J.64)     & 03:32:29.64 & -27:42:42.5  &   0.6671  & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ & $13.2 \pm 0.3$ & $3.897_{-0.93}^{+1.15}$ \\
+%J033230.57-274518.2 (J.57)     & 03:32:30.56 & -27:45:18.2  &   0.6807  & $12.6_{-2.1}^{+1.7}$   & $10.48_{-0.07}^{+0.03}$ & \ $6.1 \pm 0.4$   & $1.262_{-0.40}^{+1.23}$ \\
+%\enddata
+%\tablecomments{The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ i.e.
+\textbf{dust opacity of the galaxy}, values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SEDs with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}.}
+%\end{deluxetable*}
+
+\begin{deluxetable*}{c c D D D c D}
 \tablecaption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) includes both components of the \ion{Mg}{2} doublet and is 
 determined from analysis of the supplemental Keck/LRIS spectra. \label{tab:prop}}
-\tablehead{\colhead{Object} & \colhead{R.A.} & \colhead{Dec} & \colhead{$z$} & \multicolumn2c{SFR} & \multicolumn2c{$\log{(M)}$} & \colhead{EW$_{\rm{obs}}$} & \multicolumn2c{ $\tau_V$} \\ 
-\colhead {} & \colhead {} & \colhead {} & \colhead{} & \multicolumn2c{($M_{\odot}$ yr$^{-1}$)} & \multicolumn2c{($\log{M_{*}/M_{\odot}}$)} & \colhead{(\AA)} & \multicolumn2c{}}
+\tablehead{\colhead{Object\tablenotemark{a}} &  \colhead{$z$} & \multicolumn2c{SFR} & \multicolumn2c{$\log{(M)}$} &\colhead{$\Delta v_{\rm max}$\tablenotemark{b}} &\multicolumn2c{EW$_{\rm{obs}}$} & \multicolumn2c{ $\tau_V$\tablenotemark{c}} \\
+\colhead {} & \colhead{} & \multicolumn2c{($M_{\odot}$ yr$^{-1}$)} & \multicolumn2c{($\log{M_{*}/M_{\odot}}$)} & \colhead{(km s$^{-1}$)} & \multicolumn2c{(\AA)} & \multicolumn2c{}}
 \decimals
 \startdata
-J033225.26-274524.0 (J.26)     & 03:32:25.26 & -27:45:23.9  &   0.6660  & $9.1_{-3.7}^{+1.3}$     & $9.86_{-0.04}^{+0.05}$   & \ $7.5\pm 0.4$   &  $1.227_{-0.20}^{+1.54}$ \\ 
-J033231.36-274725.0 (J.36)     & 03:32:31.35 & -27:47:24.9  &   0.6669  & $10.5_{-1.6}^{+1.7}$   & $10.02_{-0.03}^{+0.03}$ & \ $5.8 \pm 0.5$   & $1.377_{-0.23}^{+0.60}$ \\
-J033230.03-274347.3 (J.03)     & 03:32:30.03 & -27:43:47.2  &   0.6679  & $3.8_{-0}^{+0}$           & $10.98_{-0.0}^{+0.01}$   & $12.8 \pm 1.7$ & $0.297_{-0.0}^{+0.0}$ \\
-J033229.64-274242.6 (J.64)     & 03:32:29.64 & -27:42:42.5  &   0.6671  & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ & $13.2 \pm 0.3$ & $3.897_{-0.93}^{+1.15}$ \\
-J033230.57-274518.2 (J.57)     & 03:32:30.56 & -27:45:18.2  &   0.6807  & $12.6_{-2.1}^{+1.7}$   & $10.48_{-0.07}^{+0.03}$ & \ $6.1 \pm 0.4$   & $1.262_{-0.40}^{+1.23}$ \\
+J033225.26-274524.0 (J.26)     &   0.6660  & $9.1_{-3.7}^{+1.3}$     & $9.86_{-0.04}^{+0.05}$   &   $-187_{-16}^{+12}$ & \ $7.5\pm 0.4$   &  $1.227_{-0.20}^{+1.54}$ \\ 
+J033231.36-274725.0 (J.36)     &   0.6669  & $10.5_{-1.6}^{+1.7}$   & $10.02_{-0.03}^{+0.03}$ &   $-168_{-126}^{+33}$ & \ $5.8 \pm 0.5$   & $1.377_{-0.23}^{+0.60}$ \\
+J033230.03-274347.3 (J.03)     &   0.6679  & $3.8_{-0}^{+0}$           & $10.98_{-0.0}^{+0.01}$   &   $-400_{-64}^{+132}$ & $12.8 \pm 1.7$ & $0.297_{-0.0}^{+0.0}$ \\
+J033229.64-274242.6 (J.64)     &   0.6671  & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &   $-378_{-12}^{+12}$ & $13.2 \pm 0.3$ & $3.897_{-0.93}^{+1.15}$ \\
+J033230.57-274518.2 (J.57)     &   0.6807  & $12.6_{-2.1}^{+1.7}$   & $10.48_{-0.07}^{+0.03}$ &   $-266_{-38}^{+44}$ & \ $6.1 \pm 0.4$   & $1.262_{-0.40}^{+1.23}$ \\
 \enddata
-\tablecomments{The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ i.e.
-\textbf{dust opacity of the galaxy}, values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SEDs with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}.}
+\tablenotetext{a}{\added{Galaxy ID's are named according to the object R.A and DEC. position.}}
+\tablenotetext{b}{\added{Maximum outflow velocity, $\Delta v_{\rm max} \approx v_{\rm flow}- b_{D,\rm flow}/\sqrt{2}$ where $b_{D,\rm flow}$ is the Doppler parameter or velocity width of the absorption.}}
+\tablenotetext{c}{\added{Total V-band optical depth.}} 
+\tablecomments{The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SEDs with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}.}
 \end{deluxetable*}
@@
 \end{deluxetable}\
-%\\
 
@@
 \subsection{Strength of \ion{Mg}{2} emission and Correlation with Galaxy Properties }
-\textbf{The middle panel of Figure \ref{fig:all_limits} suggests that extended \ion{Mg}{2} emission may be brighter in lower mass galaxies.
+\added{The middle panel of Figure \ref{fig:all_limits} suggests that extended \ion{Mg}{2} emission may be brighter in lower mass galaxies.
 A similar trend was observed by both \cite{Erb2012} and \cite{Feltre2018} in their examination of the total \ion{Mg}{2} emission strength vs.
 galaxy $M_*$.
-IN addition to the observed trend that emission strength may be correlated with galaxy mass, a recent study by \cite{Henry2018} detected significant \ion{Mg}{2} emission, characterized with escape fractions between $0-0.9$, in a sample of $z \sim 0.2-0.3$ Green Pea galaxies.
-Finally, the right panel of Figure \ref{fig:all_limits} shows that the galaxy with detected \ion{Mg}{2} also has the highest specific SFR.
-If it is ultimately confirmed that low-$M_*$ galaxies with the highest SFRs, or highest specific SFRs, exhibit the brightest emission, this could point to a physical link between the escape velocity of galaxies and the spatial extent of wind material}
+In addition to the observed trend that emission strength may be correlated with galaxy mass, recent studies by \cite{Henry2018} and \cite{Guseva2019} show significant contribution from nebular emission to the total \ion{Mg}{2} emission strength.
+In \cite{Henry2018} report strong \ion{Mg}{2} emission, characterized with escape fractions between $0-0.9$, in a sample of $z \sim 0.2-0.3$ Green Pea galaxies.
+Photoionization modeling of the observed strength of emission suggests that in addition to scattering of continuum photons, HII regions may also produce a non-negligible contribution to observed \ion{Mg}{2} emission, with the strength set b the escape fraction.
+In \cite{Guseva2019}, the authors find that low metallicity \ion{Mg}{2} emitters from \cite{Feltre2018} and \cite{Finley2017} have high H$\beta$ EW's, confirming that \ion{Mg}{2} emission has nebular origin.
+However, our sample of galaxies are comparitavely more massive and thus richer in metal than the galaxies that are known to contain significant nebular emission.
+The total contribution from nebular \ion{Mg}{2} to the total \ion{Mg}{2} emission remains to be determined for more massive and metal rich galaxies.}
+
+Finally, the right panel of Figure \ref{fig:all_limits} shows that the galaxy with detected extended \ion{Mg}{2} also has the highest specific SFR.
+If it is ultimately confirmed that low-$M_*$ galaxies with the highest SFRs, or highest specific SFRs, exhibit the brightest emission, this could point to a physical link between the escape velocity of galaxies and the spatial extent of wind material.
 
@@
 \bibliography{references2017}
-
+\listofchanges
 \end{document}

### 2019-03-27 referee_response.txt
03/07/2018
Kate's final edits

@@
-Dear Anonymous Referee,
-
-Thank you so much for your kind words and comments on the manuscript "A VLT/FORS2 Narrowband
-Imaging Search for MgII Emission in z~0.70 Galaxies". Below is a list of your comments and
-our edits according to these comments.
+We wish to thank the referee for their supportive and helpful comments on our
+manuscript "A VLT/FORS2 Narrowband Imaging Search for MgII Emission in
+z~0.70 Galaxies".  We have implemented each of the suggestions they
+sent in their report (in boldface type).  Please see our direct
+responses to each comment below.
 
@@
 
-Reply: We expanded the last paragraph to include a refined description of the velocities being reported. We 
-added the velocity reported for each galaxy in Table 1. Additionally, we discussed what type of model is being used
-to measure the lines and how these mitigate the effect of infilling emission. We also note that the EW's mentioned
-here are the rest-frame equivalent widths.
+Reply: We expanded the last paragraph of Section 2.1 to include a more
+detailed description of the velocities being reported.  We also
+added the velocity reported for each galaxy to Table 1. Additionally,
+we now discuss the type of model that was used
+to fit the lines and how this mitigates the effects of infilling from scattered
+emission.  We have added a note stating that the EWs mentioned
+here are rest-frame equivalent widths.
 
-Comment: Please add a note to Table 1 explaining what tau_V is, since it isn't discussed until later in the paper
-and it is a bit less obvious than the other quantities in the table.
+Comment: "Please add a note to Table 1 explaining what tau_V is, since it isn't discussed until later in the paper
+and it is a bit less obvious than the other quantities in the table."
 
-Reply: We added a note to Table 1 which gives more insight to tau_V.
+Reply: We have added a note to Table 1 which gives some description of tau_V.
 
-Comment:In the discussion of previous results in Section 6.1, I think providing some context from Henry et al 2018 would
+Comment: "In the discussion of previous results in Section 6.1, I think providing some context from Henry et al 2018 would
 be useful. Although this paper didn't present spatially extended emission, their results on which galaxies are 
@@
 well as resonantly scattered continuum photons, and the finding that the strength of the emission may be set by the 
-escape fraction of MgII photons rather than the intrinsic production.
+escape fraction of MgII photons rather than the intrinsic production."
 
-Reply: Added a discussion of Henry et al 2016 and Guseva et al.(2019).
+Reply: We have added discussion of results from Henry et al (2018) to
+a new section following Section 6.1 as requested (see Section 6.2).

### 2019-03-27 for_submission/rvaught_2018.tex
Kate's final edits

@@
 
-The \added{Bayesian} absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2} with \added{maximum outflow} velocities, $\Delta v_{\rm max}$ $\sim150-420\mkms$ and \textbf{rest-frame} equivalent widths (EW) $\sim 2-3$ \AA.
-\added{The reported maximum outflow velocities, see Table \ref{tab:prop}, are the result of fitting a two-velocity component model to the absorption line profile.
-The two component model assumes that there is a systemic velocity and ``flow" velocity that both contribute to the overall line profile.
-The maximum outflow velocity is the velocity of the flow, $v_{\rm flow}$ minus a fitted doppler parameter, $b_{D,\rm flow}/\sqrt{2}$.
-The use of the two component model is helpful to mitigate the effects of scattered emission filling up the absorption line which in turn pushes the trough of the line blueward.
-It is assumed that the resonant emission will reduce the systemic velocity, leaving the flow velocity to characterize the outflow.
-The qualitative context of this scattering process, as it pertains to galactic winds, can be improved via higher resolution spectrum and radiative transfer analysis \cite{Prochaska_2011}}.
-Modeling of the galaxy broad-band spectral energy distributions (SEDs) obtained from multi-wavelength ancillary imaging data yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$.
-The properties of the sample, as well as precise target coordinates taken from \cite{Rubin_2014}, are listed in Table \ref{tab:prop}.
+The \added{Bayesian} absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2} with \added{maximum outflow} velocities $\Delta v_{\rm max}$ $\sim150-420\mkms$ and \textbf{rest-frame} equivalent widths (EW) $\sim 2-3$ \AA.
+\added{These maximum outflow velocities (listed in Table \ref{tab:prop}) are determined from fitting a two-velocity component model to the absorption line profiles.
+The two-component model assumes that there is an absorption component due to stellar atmospheres and the interstellar medium with a velocity fixed at systemic, as well as a ``flow'' absorption component with a velocity that is allowed to float.
+%that both contribute to the overall line profile.
+The maximum outflow velocity $\Delta v_{\rm max}$ is the fitted central velocity of the flow component, $v_{\rm flow}$, minus the fitted Doppler parameter, $b_{D,\rm flow}/\sqrt{2}$.
+It thus is indicative of the most extreme flow velocities traced by each absorption line profile.
+The two-component model does not explicitly include a contribution to the line profile from scattered emission, which
+can be significant at velocities close to systemic \citep{Prochaska_2011}.
+However, as discussed in \cite{Rubin_2014}, it is expected that scattered emission will primarily tend to reduce the strength of the fitted systemic component, and will have a minor effect on fitted flow component velocities and line widths (see their Appendix C).
+%The use of the two-component model mitigates the effect of scattered emission
+%on the fitted velocity.
+%filling up the absorption line which in turn pushes the trough of the line blueward.
+It is assumed that the resonant emission will reduce the systemic %velocity, leaving the flow velocity to characterize the outflow.
+%The qualitative context of this scattering process, as it pertains to galactic winds, can be improved via higher resolution spectrum and radiative transfer analysis \cite{Prochaska_2011}
+}
+
+Modeling of the galaxy broad-band spectral energy distributions (SEDs) obtained from multi-wavelength ancillary imaging data, also performed by \cite{Rubin_2014}, yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$.
+All of these sample properties as well as target coordinates %taken from \cite{Rubin_2014},
+are listed in Table \ref{tab:prop}.
 
@@
 J033225.26-274524.0 (J.26)     &   0.6660  & $9.1_{-3.7}^{+1.3}$     & $9.86_{-0.04}^{+0.05}$   &   $-187_{-16}^{+12}$ & \ $7.5\pm 0.4$   &  $1.227_{-0.20}^{+1.54}$ \\ 
+J033229.64-274242.6 (J.64)     &   0.6671  & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &   $-378_{-12}^{+12}$ & $13.2 \pm 0.3$ & $3.897_{-0.93}^{+1.15}$ \\
+J033230.03-274347.3 (J.03)     &   0.6679  & $3.8_{-0}^{+0}$           & $10.98_{-0.0}^{+0.01}$   &   $-400_{-64}^{+132}$ & $12.8 \pm 1.7$ & $0.297_{-0.0}^{+0.0}$ \\
+J033230.57-274518.2 (J.57)     &   0.6807  & $12.6_{-2.1}^{+1.7}$   & $10.48_{-0.07}^{+0.03}$ &   $-266_{-38}^{+44}$ & \ $6.1 \pm 0.4$   & $1.262_{-0.40}^{+1.23}$ \\
 J033231.36-274725.0 (J.36)     &   0.6669  & $10.5_{-1.6}^{+1.7}$   & $10.02_{-0.03}^{+0.03}$ &   $-168_{-126}^{+33}$ & \ $5.8 \pm 0.5$   & $1.377_{-0.23}^{+0.60}$ \\
-J033230.03-274347.3 (J.03)     &   0.6679  & $3.8_{-0}^{+0}$           & $10.98_{-0.0}^{+0.01}$   &   $-400_{-64}^{+132}$ & $12.8 \pm 1.7$ & $0.297_{-0.0}^{+0.0}$ \\
-J033229.64-274242.6 (J.64)     &   0.6671  & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &   $-378_{-12}^{+12}$ & $13.2 \pm 0.3$ & $3.897_{-0.93}^{+1.15}$ \\
-J033230.57-274518.2 (J.57)     &   0.6807  & $12.6_{-2.1}^{+1.7}$   & $10.48_{-0.07}^{+0.03}$ &   $-266_{-38}^{+44}$ & \ $6.1 \pm 0.4$   & $1.262_{-0.40}^{+1.23}$ \\
 \enddata
-\tablenotetext{a}{\added{Galaxy ID's are named according to the object R.A and DEC. position.}}
-\tablenotetext{b}{\added{Maximum outflow velocity, $\Delta v_{\rm max} \approx v_{\rm flow}- b_{D,\rm flow}/\sqrt{2}$ where $b_{D,\rm flow}$ is the Doppler parameter or velocity width of the absorption.}}
-\tablenotetext{c}{\added{Total V-band optical depth.}} 
+%\tablenotetext{a}{\added{Galaxy names include their  are named according to the object R.A and DEC. position.}}
+\tablenotetext{a}{\added{Galaxy names include their R.A. and Declination in the J2000.0 epoch.  The names in parentheses are used to identify each object throughout the paper.}}
+\tablenotetext{b}{\added{Maximum outflow velocity traced by \ion{Mg}{2}, $\Delta v_{\rm max} \approx v_{\rm flow}- b_{D,\rm flow}/\sqrt{2}$, where $b_{D,\rm flow}$ is the fitted Doppler parameter and $v_{\rm flow}$ is the fitted central velocity of the ``flow'' component in a two-component model of the absorption line profile.}}
+\tablenotetext{c}{\added{Total $V$-band optical depth of dust attenuating light from the young stellar population in each galaxy as modeled by MAGPHYS.
+This includes contributions from dust in both \ion{H}{2}  regions and the ambient ISM.} }
 \tablecomments{The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SEDs with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}.}
@@
 \section{Discussion}\label{sec:discussion}
-\subsection{Previous Detection of extended \ion{Mg}{2} Emission}
+\subsection{Previous Detections of Extended \ion{Mg}{2} Emission}
 Previous constraints on the brightness of scattered \ion{Mg}{2} emission were reported by \cite{Rubin_2011}.
@@
 These figures suggest that we should be able to detect scattered \ion{Mg}{2} emission with strengths similar to that detected in TKRS 4389 in our narrowband imaging.
-Taken at face value, the left panel of Figure \ref{fig:all_limits} could be consistent with a positive correlation between \ion{Mg}{2} SB and SFR.
-Future observations are needed to verify this trend, and the possibility that objects with yet higher SFRs ($\gtrsim50 \msunperyr$) exhibit brighter \ion{Mg}{2} emission.
 
-\subsection{Strength of \ion{Mg}{2} emission and Correlation with Galaxy Properties }
-\added{The middle panel of Figure \ref{fig:all_limits} suggests that extended \ion{Mg}{2} emission may be brighter in lower mass galaxies.
-A similar trend was observed by both \cite{Erb2012} and \cite{Feltre2018} in their examination of the total \ion{Mg}{2} emission strength vs.
-galaxy $M_*$.
-In addition to the observed trend that emission strength may be correlated with galaxy mass, recent studies by \cite{Henry2018} and \cite{Guseva2019} show significant contribution from nebular emission to the total \ion{Mg}{2} emission strength.
-In \cite{Henry2018} report strong \ion{Mg}{2} emission, characterized with escape fractions between $0-0.9$, in a sample of $z \sim 0.2-0.3$ Green Pea galaxies.
-Photoionization modeling of the observed strength of emission suggests that in addition to scattering of continuum photons, HII regions may also produce a non-negligible contribution to observed \ion{Mg}{2} emission, with the strength set b the escape fraction.
-In \cite{Guseva2019}, the authors find that low metallicity \ion{Mg}{2} emitters from \cite{Feltre2018} and \cite{Finley2017} have high H$\beta$ EW's, confirming that \ion{Mg}{2} emission has nebular origin.
-However, our sample of galaxies are comparitavely more massive and thus richer in metal than the galaxies that are known to contain significant nebular emission.
-The total contribution from nebular \ion{Mg}{2} to the total \ion{Mg}{2} emission remains to be determined for more massive and metal rich galaxies.}
+\subsection{Possible Correlation of \ion{Mg}{2} Emission Strength with Galaxy Properties }
+{\bf Taken at face value, the left panel of Figure \ref{fig:all_limits} could be consistent with a positive correlation between \ion{Mg}{2} SB and SFR. 
+The constraints shown in the middle panel of Figure \ref{fig:all_limits} are similarly suggestive of (and consistent with) a negative correlation between the SB of extended \ion{Mg}{2} emission and galaxy stellar mass.
+Future observations are needed to verify these trends, and the possibility that objects with yet higher SFRs ($\gtrsim50 \msunperyr$) exhibit brighter extended \ion{Mg}{2} emission.  
+Finally, the right panel of Figure \ref{fig:all_limits} shows that the galaxy with detected extended \ion{Mg}{2} also has the highest specific SFR.
+If it is ultimately confirmed that low-$M_*$ galaxies with the highest SFRs, or highest specific SFRs, exhibit the brightest emission, this could point to a physical link between the escape velocity of galaxies and the spatial extent and/or optical depth of wind material.
+%Such a finding could be indicative of higher optical depth material extending to larger distances from more highly star-forming galaxies.
+Here we note that a similar trend was observed by both \cite{Erb2012} and \cite{Feltre2018} in their examination of the total \ion{Mg}{2} emission strength vs. $M_*$. }
 
-Finally, the right panel of Figure \ref{fig:all_limits} shows that the galaxy with detected extended \ion{Mg}{2} also has the highest specific SFR.
-If it is ultimately confirmed that low-$M_*$ galaxies with the highest SFRs, or highest specific SFRs, exhibit the brightest emission, this could point to a physical link between the escape velocity of galaxies and the spatial extent of wind material.
+{\bf A potential complicating factor in the interpretation of trends in \ion{Mg}{2} SB with galaxy properties is the possible contribution of nebular emission to the \ion{Mg}{2} line profiles.
+%In addition to this observed 
+%anticorrelation,
+%trend that emission strength may be correlated with galaxy mass,
+Recent studies by \cite{Henry2018} and \cite{Guseva2019} suggest that there may be a significant contribution from nebular emission (i.e., from \ion{H}{2} regions) to the total \ion{Mg}{2} emission strength in some galaxies.
+In detail, \cite{Henry2018} report strong \ion{Mg}{2} emission having %escape fractions between $0-0.9$ 
+$\rm EW_{2796}\sim 0.4-9.1$ \AA\ along with negligible absorption
+arising in a sample of extreme compact starburst galaxies (``Green Peas'') at $z \sim 0.2-0.3$. 
+Their photoionization modeling of the emission line strengths suggests that the observed 
+\ion{Mg}{2} emission fluxes can in fact be 
+dominated by \ion{H}{2} region emission in such low-metallicity systems (with $Z = 0.16-0.32 Z_{\odot}$).
+They also note that higher metallicity and/or more dusty conditions will produce weaker nebular emission.
+Moreover, these authors find that the strength of observed \ion{Mg}{2} emission is correlated with the escape fraction of \ion{Mg}{2} photons, suggesting that within their sample, galaxies with the weakest observed emission may have the strongest intrinsic nebular emission.
+}
+
+%in addition to scattering of continuum photons, HII regions may also produce a non-negligible contribution to observed \ion{Mg}{2} emission, with the strength set b the escape fraction. 
+%In \cite{Guseva2019}, the authors find that low metallicity \ion{Mg}{2} emitters from \cite{Feltre2018} and \cite{Finley2017} have high H$\beta$ EW's, confirming that \ion{Mg}{2} emission has nebular origin.
+{\bf Given that our sample of galaxies exhibits quite weak emission in comparison to those studied by \citet{Henry2018}, at face value this latter finding suggests that they likely have \ion{H}{2} regions producing significant intrinsic \ion{Mg}{2} emission.
+However, our sample (along with TKRS4389) is also $\gtrsim1$ dex higher in stellar mass and thus richer in both metals (by $\sim +0.9$ dex in $\log$ O/H; \citethnop{Zahid2011}) and dust than the \citet{Henry2018} Green Peas.
+%the galaxies that are known to produce significant nebular emission. 
+While there may indeed be a nebular contribution to \ion{Mg}{2} emission when it is observed in galaxies in this mass range,  
+%The nebular contribution %from nebular \ion{Mg}{2} to the total 
+more detailed photoionization modeling is required to estimate line luminosities for the relevant physical conditions.
+As nebular emission is reprocessed by scattering just as continuum photons are, its presence would tend to brighten any spatially-extended line component, and any trends in nebular emission line strengths with $M_*$ or SFR would be reflected in the surface brightnesses of extended emission.
+  The nebular contribution should therefore be considered by future studies interpreting the meaning of putative trends in extended line SB with galaxy properties.}
+%\ion{Mg}{2} emission remains to be determined for more massive and metal rich galaxies.}
+%SAY SOMETHING ABOUT HOW THIS IS SEPARATE / IRRELEVANT TO EXTENDED EMISSION STUDIES
 
@@
 Therefore, the total equivalent width of both the absorption and emission features is equal to zero in such models.
-Assuming that our galaxies host an isotropic and dust-free wind, we wish to determine how much emission is predicted to be generated by this wind, and how the SB of this emission compares to our detection limits.
+Assuming that our galaxies host an isotropic and dust-free wind {\bf (and that they do not produce significant nebular \ion{Mg}{2} emission)}, we wish to determine how much emission is predicted to be generated by this wind, and how the SB of this emission compares to our detection limits.
 

### 2019-04-08 for_submission/rvaught_2018.tex
added Martin_2013_galaxy

@@
 
-The \added{Bayesian} absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2} with \added{maximum outflow} velocities $\Delta v_{\rm max}$ $\sim150-420\mkms$ and \textbf{rest-frame} equivalent widths (EW) $\sim 2-3$ \AA.
-\added{These maximum outflow velocities (listed in Table \ref{tab:prop}) are determined from fitting a two-velocity component model to the absorption line profiles.
+The \textbf{Bayesian} absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2} with \textbf{maximum outflow} velocities $\Delta v_{\rm max}$ $\sim150-420\mkms$ and \textbf{rest-frame} equivalent widths (EW) $\sim 2-3$ \AA.
+\textbf{These maximum outflow velocities (listed in Table \ref{tab:prop}) are determined from fitting a two-velocity component model to the absorption line profiles.
 The two-component model assumes that there is an absorption component due to stellar atmospheres and the interstellar medium with a velocity fixed at systemic, as well as a ``flow'' absorption component with a velocity that is allowed to float.
@@
 %\tablenotetext{a}{\added{Galaxy names include their  are named according to the object R.A and DEC. position.}}
-\tablenotetext{a}{\added{Galaxy names include their R.A. and Declination in the J2000.0 epoch.  The names in parentheses are used to identify each object throughout the paper.}}
-\tablenotetext{b}{\added{Maximum outflow velocity traced by \ion{Mg}{2}, $\Delta v_{\rm max} \approx v_{\rm flow}- b_{D,\rm flow}/\sqrt{2}$, where $b_{D,\rm flow}$ is the fitted Doppler parameter and $v_{\rm flow}$ is the fitted central velocity of the ``flow'' component in a two-component model of the absorption line profile.}}
-\tablenotetext{c}{\added{Total $V$-band optical depth of dust attenuating light from the young stellar population in each galaxy as modeled by MAGPHYS.
+\tablenotetext{a}{\textbf{Galaxy names include their R.A. and Declination in the J2000.0 epoch.  The names in parentheses are used to identify each object throughout the paper.}}
+\tablenotetext{b}{\textbf{Maximum outflow velocity traced by \ion{Mg}{2}, $\Delta v_{\rm max} \approx v_{\rm flow}- b_{D,\rm flow}/\sqrt{2}$, where $b_{D,\rm flow}$ is the fitted Doppler parameter and $v_{\rm flow}$ is the fitted central velocity of the ``flow'' component in a two-component model of the absorption line profile.}}
+\tablenotetext{c}{\textbf{Total $V$-band optical depth of dust attenuating light from the young stellar population in each galaxy as modeled by MAGPHYS.
 This includes contributions from dust in both \ion{H}{2}  regions and the ambient ISM.} }
@@
 \subsection{Previous Detections of Extended \ion{Mg}{2} Emission}
-Previous constraints on the brightness of scattered \ion{Mg}{2} emission were reported by \cite{Rubin_2011}.
-In this work the authors studied emission from the starburst galaxy TKRS 4389 at $z = 0.69$ with a SFR of $49.8\msunperyr$.
+Previous constraints on the brightness of scattered \ion{Mg}{2} emission were reported by \cite{Rubin_2011} and \cite{Martin2013}.
+In \cite{Rubin_2011} the authors studied emission from the starburst galaxy TKRS 4389 at $z = 0.69$ with a SFR of $49.8\msunperyr$.
 This emission was detected in a 2-dimensional Keck/LRIS spectrum, with flux from the emission reaching $(8.0 \pm 0.4)$ and $(4.4 \pm 0.4)$ $\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at  $\lambda _{2796}$ and $(4.0 \pm 0.3)$ and $(2.5 \pm 0.4)$ $\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at $\lambda_{2803}$ in two independent locations spatially offset from the galaxy continuum.
 The flux from both emission lines can be converted into two surface brightness values by taking the average of the flux measured at each location and each transition, and dividing by a 1 arcsec$^2$ aperture.
-Figure \ref{fig:all_limits} shows each galaxy's 5$\sigma$ SB detection limit and the SB calculated for the galaxy TKRS 4389 vs.
+
+\textbf{In addition to TKRS 4389, a second detection of extended \ion{Mg}{2} emission is reported in \cite{Martin2013}.
+In this study, the authors spatially resolve extended \ion{Mg}{2} emission in the galaxy, 32016857, at a redshift of $z=0.9392$ with SFR of $\sim 80\msunperyr$.
+Detected using a 2-dimensional Keck/LRIS spectrum, the \ion{Mg}{2} emission extends out to $\sim11$ kpc eastward away from the galaxy continuum.
+In the integrated spectrum, the observed flux in \ion{Mg}{2} emission is approximately $1.5$$\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at  $\lambda _{2796}$ and $ 1.0$ $\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at $\lambda_{2803}$ to 20\% accuracy.
+The extended \ion{Mg}{2} component contributes up to 46\% of the total integrated \ion{Mg}{2} flux.
+We convert the extended flux to SB using a 1 arcsec$^2$ aperture.
+Figure \ref{fig:all_limits} shows each galaxy's 5$\sigma$ SB detection limit and the SB calculated for the galaxies TKRS 4389 and 32016857 vs.
 SFR (left panel) and vs.\ $\log M_*/M_{\odot}$ (middle panel).
-These figures suggest that we should be able to detect scattered \ion{Mg}{2} emission with strengths similar to that detected in TKRS 4389 in our narrowband imaging.
+These figures suggest that we should be able to detect scattered \ion{Mg}{2} emission with strengths similar to that detected in TKRS 4389 in our narrowband imaging.}
 
@@
 \includegraphics[scale=0.57]{figure11.pdf}%all_limitsv2.pdf
-\caption{Comparison of our detection limits to the SB, measured in two independent locations spatially offset from the galaxy continuum, of extended \ion{Mg}{2} emission around the starburst galaxy TKRS 4389.
+\caption{Comparison of our detection limits to the SB, measured in two independent locations spatially offset from the galaxy continuum, of extended \ion{Mg}{2} emission around the starburst galaxy TKRS 4389 \textbf{and one independent location spatially offset from the galaxy continuum eastward of 32016857}.
 These surface brightness constraints are plotted vs.\ SFR (left), stellar mass (middle), and specific SFR (right).
-Our imaging is sufficiently sensitive to detect extended emission at similar strengths to the extended emission measured for TKRS 4389 with SFR $\sim 50 \msunperyr$.
+Our imaging is sufficiently sensitive to detect extended emission at similar strengths to the extended emission measured for TKRS 4389 with SFR $\sim 50 \msunperyr$ and 32016857 with SFR $\sim 80 \msunperyr$.
 The symbol colors indicate the same galaxies as in Figure \ref{fig:ew_comb}}

### 2019-04-19 for_submission/rvaught_2018.tex
updated Martin_2013_galaxy_SB

@@
 In this study, the authors spatially resolve extended \ion{Mg}{2} emission in the galaxy, 32016857, at a redshift of $z=0.9392$ with SFR of $\sim 80\msunperyr$.
-Detected using a 2-dimensional Keck/LRIS spectrum, the \ion{Mg}{2} emission extends out to $\sim11$ kpc eastward away from the galaxy continuum.
+Detected using a 2-dimensional Keck/LRIS spectrum, the \ion{Mg}{2} emission extends out to $\sim11$ kpc, or 1.4\arcsec\ at redshift $z\sim 0.94$, eastward away from the galaxy continuum.
 In the integrated spectrum, the observed flux in \ion{Mg}{2} emission is approximately $1.5$$\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at  $\lambda _{2796}$ and $ 1.0$ $\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at $\lambda_{2803}$ to 20\% accuracy.
 The extended \ion{Mg}{2} component contributes up to 46\% of the total integrated \ion{Mg}{2} flux.
-We convert the extended flux to SB using a 1 arcsec$^2$ aperture.
+Likewise to TKRS 4389: We calculate a SB for the extended \ion{Mg}{2} emission, assuming that the total extended \ion{Mg}{2} emission is $0.46\times2.5$$\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ is collected in an aperture of 1.4\arcsec\ times the the 1.2\arcsec\ Keck/LRIS slit-width.
 Figure \ref{fig:all_limits} shows each galaxy's 5$\sigma$ SB detection limit and the SB calculated for the galaxies TKRS 4389 and 32016857 vs.

### 2019-04-23 for_submission/rvaught_2018.tex

--- 2019-04-08 for_submission/rvaught_2018.tex
@@
 
-\textbf{In addition to TKRS 4389, a second detection of extended \ion{Mg}{2} emission is reported in \cite{Martin2013}.
-In this study, the authors spatially resolve extended \ion{Mg}{2} emission in the galaxy, 32016857, at a redshift of $z=0.9392$ with SFR of $\sim 80\msunperyr$.
-Detected using a 2-dimensional Keck/LRIS spectrum, the \ion{Mg}{2} emission extends out to $\sim11$ kpc eastward away from the galaxy continuum.
+\textbf{A second detection of extended \ion{Mg}{2} emission is reported in \cite{Martin2013}.
+In this study, the authors spatially resolve extended \ion{Mg}{2} emission in the galaxy 32016857 at a redshift of $z=0.9392$ with a SFR of $\sim 80\msunperyr$.
+Detected using a 2-dimensional Keck/LRIS spectrum, the \ion{Mg}{2} emission extends out to $\sim11$ kpc, or 1.4\arcsec\ at $z\sim 0.94$, away from the galaxy continuum to the East.
 In the integrated spectrum, the observed flux in \ion{Mg}{2} emission is approximately $1.5$$\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at  $\lambda _{2796}$ and $ 1.0$ $\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at $\lambda_{2803}$ to 20\% accuracy.
 The extended \ion{Mg}{2} component contributes up to 46\% of the total integrated \ion{Mg}{2} flux.
-We convert the extended flux to SB using a 1 arcsec$^2$ aperture.
-Figure \ref{fig:all_limits} shows each galaxy's 5$\sigma$ SB detection limit and the SB calculated for the galaxies TKRS 4389 and 32016857 vs.
+As for TKRS4389, we calculate a SB  assuming that the total extended \ion{Mg}{2} emission flux is $0.46\times2.5$$\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ and that it covers an area of 1.4\arcsec\ times the 1.2\arcsec\ Keck/LRIS slit width.
+Figure \ref{fig:all_limits} shows 5$\sigma$ SB detection limits for each galaxy in our sample and the SB calculated for the galaxies TKRS 4389 and 32016857 vs.
 SFR (left panel) and vs.\ $\log M_*/M_{\odot}$ (middle panel).
-These figures suggest that we should be able to detect scattered \ion{Mg}{2} emission with strengths similar to that detected in TKRS 4389 in our narrowband imaging.}
+These figures suggest that we should be able to detect scattered \ion{Mg}{2} emission with strengths similar to that detected in both TKRS 4389 and 32016857 in our narrowband imaging.}
 

### 2019-04-23 for_submission/rvaught_2018.tex
update2 Martin_2013_galaxy_SB

@@
 Detected using a 2-dimensional Keck/LRIS spectrum, the \ion{Mg}{2} emission extends out to $\sim11$ kpc, or 1.4\arcsec\ at $z\sim 0.94$, away from the galaxy continuum to the East.
-In the integrated spectrum, the observed flux in \ion{Mg}{2} emission is approximately $1.5$$\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at  $\lambda _{2796}$ and $ 1.0$ $\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ at $\lambda_{2803}$ to 20\% accuracy.
+In the integrated spectrum, the observed flux in \ion{Mg}{2} emission is approximately $1.5$$\times10^{-17}$ ergs sec$^{-1}$ cm$^{-2}$ at  $\lambda _{2796}$ and $ 1.0$ $\times10^{-17}$ ergs sec$^{-1}$ cm$^{-2}$ at $\lambda_{2803}$ to 20\% accuracy.
 The extended \ion{Mg}{2} component contributes up to 46\% of the total integrated \ion{Mg}{2} flux.

### 2019-04-24 for_submission/rvaught_2018.tex
update3 Martin_2013_galaxy_SB

@@
 The extended \ion{Mg}{2} component contributes up to 46\% of the total integrated \ion{Mg}{2} flux.
-As for TKRS4389, we calculate a SB  assuming that the total extended \ion{Mg}{2} emission flux is $0.46\times2.5$$\times10^{-18}$ ergs sec$^{-1}$ cm$^{-2}$ and that it covers an area of 1.4\arcsec\ times the 1.2\arcsec\ Keck/LRIS slit width.
+As for TKRS4389, we calculate a SB  assuming that the total extended \ion{Mg}{2} emission flux is $0.46\times2.5$$\times10^{-17}$ ergs sec$^{-1}$ cm$^{-2}$ and that it covers an area of 1.4\arcsec\ times the 1.2\arcsec\ Keck/LRIS slit width.
 Figure \ref{fig:all_limits} shows 5$\sigma$ SB detection limits for each galaxy in our sample and the SB calculated for the galaxies TKRS 4389 and 32016857 vs.

### 2019-04-25 for_submission/rvaught_2018.tex

@@
 \includegraphics[scale=0.57]{figure11.pdf}%all_limitsv2.pdf
-\caption{Comparison of our detection limits to the SB, measured in two independent locations spatially offset from the galaxy continuum, of extended \ion{Mg}{2} emission around the starburst galaxy TKRS 4389 \textbf{and one independent location spatially offset from the galaxy continuum eastward of 32016857}.
+\caption{Comparison of our detection limits to the SB of extended \ion{Mg}{2} emission measured in two independent locations spatially offset from the continuum around the starburst galaxy TKRS 4389 (reported by \citealt{Rubin_2011}), \textbf{and in one location spatially offset from the continuum eastward of the star-forming galaxy 32016857 (reported by \citealt{Martin2013})}.
 These surface brightness constraints are plotted vs.\ SFR (left), stellar mass (middle), and specific SFR (right).
 Our imaging is sufficiently sensitive to detect extended emission at similar strengths to the extended emission measured for TKRS 4389 with SFR $\sim 50 \msunperyr$ and 32016857 with SFR $\sim 80 \msunperyr$.
-The symbol colors indicate the same galaxies as in Figure \ref{fig:ew_comb}}
+The symbol colors indicate the same galaxies as in Figure \ref{fig:ew_comb}.}
 \label{fig:all_limits}
